### 2015-04-14 paper.tex
Initialize

\documentclass[preprint]{aastex}

%\usepackage{phoenician}

%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
\usepackage{lscape}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

\begin{document}

\title{Dusty galaxies and the degeneracy between their dust distributions and
the attenuation formula}

\author{Kyle Penner\altaffilmark{1}, Mark Dickinson\altaffilmark{2},
Benjamin Weiner\altaffilmark{3}, Hanae Inami\altaffilmark{2},
Jeyhan Kartaltepe\altaffilmark{2}, Janine Pforr\altaffilmark{4},
Hooshang Nayyeri\altaffilmark{5},
Susan Kassin\altaffilmark{6},
Casey Papovich\altaffilmark{7},
Alexandra Pope\altaffilmark{8}
}

\email{kdpenner@gmail.com}

\altaffiltext{1}{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
91191 Gif-sur-Yvette, France}
\altaffiltext{2}{National Optical Astronomy Observatory,
Tucson, AZ 85719, USA}
\altaffiltext{3}{Department of Astronomy, University of Arizona,
Tucson, AZ 85721, USA}
\altaffiltext{4}{Laboratoire d'Astrophysique de Marseille, Aix
Marseille Universit\'e, 13388 Marseille cedex 13, France}
\altaffiltext{5}{Department of Astronomy, University of California Riverside,
Riverside, CA 92521, USA}
\altaffiltext{6}{Space Telescope Science Institute, Baltimore, MD 21218, USA}
\altaffiltext{7}{Department of Physics \& Astronomy, Texas A\&M University,
College Station, TX 77843, USA}
\altaffiltext{8}{Department of Astronomy, University of Massachusetts Amherst,
Amherst, MA 01003, USA}

\begin{abstract}
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.
\end{abstract}

\section{Introduction}

A galaxy's morphology is often defined as its spatial distribution of stars.
Rest-frame optical images of galaxies show diverse arrangements of
their stellar components: smooth ellipticals, tightly-wound spirals, clumpy
disks, barred disks, train-wrecks, fuzzballs, and whatever Willman 1 is.
Little more than spatial extent is known about distributions of dust in dusty
galaxies
\citep{younger10,diaz10,simpson15}.  (The arrangement of
dust is often described, oddly, as its geometry.)  Yet spatial distributions of
all galactic components have intrinsic value.  If we want to learn about
galaxies, morphology should be a wavelength-independent word.  Surprises
surely abound: for example, galaxies at $z \sim 0.3$ have dust out to several
Mpc.  Their average dust mass profile is a constant fraction of their average
halo mass profile \citep[][see also \citealt{zaritsky94}]{menard10}.

Dust attenuates a galaxy's intrinsic luminosity at ultraviolet (UV) and optical
wavelengths.  We often assume that dust grains
are distributed as a uniformly thick screen between us and the galaxy's stars
and gas \citep{calzetti94}.  From the uniform screen assumption follows an
attenuation
formula that depends solely on wavelength; intrinsic luminosity is recovered
from emergent luminosity and attenuation calculated from the formula.

An attenuation formula is denoted $k(\lambda)$ or $k'(\lambda)$.  It differs
from an extinction formula, which is independent of the spatial distribution
of dust.  When we derive an extinction formula, it is valid for the small area
surrounding a star in the Milky Way, not the large area containing a mix of
stars and gas in distant galaxies.  In an illustrative sense an attenuation
formula is an extinction formula convolved with a spatial distribution of dust.

The uniform screen assumption is unrealistic.  A low-redshift galaxy with a
high emergent UV luminosity and a low IR luminosity---a dust-poor
galaxy---suffers a low amount of UV attenuation.  The \citet{calzetti00} formula
predicts how much H$\alpha$ attenuation it should suffer; the prediction
underestimates the measured H$\alpha$ attenuation.  The galaxy's regions with
$>10$ M$_{\odot}$ stars, which ionize gas, have more dust than its regions
with less massive stars that emit in the UV and leave the gas unionized
\citep{calzetti94,calzetti97b}.  While the discrepancy in amounts of dust does
not invalidate the screen part of our assumption, it does invalidate the
uniform part.

The screen part of our assumption is suspect, but it may be a
good approximation to the truth.  The
screen assumption is qualitatively similar to a scenario in which dust is
distributed in a large number of clumps \citep{calzetti94}.  \citet{liu13} find
that the dust
distribution around ionizing stars throughout M83 is clumpy at a spatial scale
of 6 pc;
if the spatial resolution is degraded to 100 pc, we conclude that the
distribution around ionizing stars is a screen.  If we choose to think of dust
distributions as clumpy, the number of clumps surrounding nonionizing
UV-emitting stars in low-redshift dust-poor galaxies is 60\% of the number of
clumps surrounding ionizing stars \citep{calzetti97a}.

The discrepancy between the uniform assumption and real dust
distributions in low-redshift dust-poor galaxies grows even larger if we
consider that galaxies have centers and outskirts.  A number of studies find
that H$\alpha$ and UV attenuation decrease with increasing radius
\citep{boissier04,prescott07,munoz09}.  Ionizing stars are surrounded by more
dust than nonionizing UV-emitting stars; ionizing stars
at large radii have less dust than ionizing stars at small radii, and similarly
for nonionizing UV-emitting stars.

We know little about dust distributions in low-redshift dusty galaxies, which
have high IR luminosities and low-to-high emergent UV luminosities.  Their
IR emitting regions span a range of sizes, from sub- to several kpc
\citep{diaz10}.  Measuring a size is hard enough; imaging a distribution is
even harder.  If a dusty galaxy's measured H$\alpha$ attenuation agreed with
the prediction from the \citet{calzetti00} attenuation formula, we might
conclude that the galaxy has a uniform dust distribution only if we believe
that the prediction is valid.  If a dusty galaxy's measured H$\alpha$
attenuation disagreed with the prediction from the \citet{calzetti00}
formula, the galaxy might have a nonuniform dust distribution, like that of a
dust-poor galaxy.  This explanation for the disagreement is not unique.  The
galaxy might have a uniform distribution and obey a different $k(\lambda)$.

We have nothing more than vague and conflicting ideas of dust distributions in
all high-redshift galaxies.  \citet{onodera10}, \citet{kashino13}, and 
\citet{price13} argue for nonuniform distributions in their samples, which
comprise dusty and dust-poor galaxies; \citet{erb06} present evidence for
uniform distributions in a similarly mixed sample.

In this paper, we ask the question, For dusty galaxies at $z \sim 0$ and
$z \sim 1$, how does H$\alpha$ attenuation relate to the prediction made by
the \citet{calzetti00} attenuation formula?  We: (1) show that H$\alpha$
attenuation differs from
the prediction; (2) show that the relations between H$\alpha$ and UV
attenuation differ from the relation for low-redshift dust-poor galaxies; and
(3) argue that an interpretation in the context of dust distributions relies on
the shaky assumption that the \citet{calzetti00} attenuation formula is
universally valid.

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.

\section{Data}\label{sec:data}

Measured and derived quantities are in Tables \ref{tbl:highz} and
\ref{tbl:lowz}.

\subsection{Measured quantities}

We use IR, emergent UV, and H$\alpha$ luminosities to determine attenuation by
dust.  In this section we detail our catalogs and samples.

\subsubsection{Sample of dusty galaxies at $z > 0.7$}

Our study uses observations of the GOODS-S, COSMOS, and UDS regions.  A
catalog of \emph{Herschel}/PACS 100$\,\micron$ sources for GOODS-S comes from
\citet{magnelli13}; for COSMOS and UDS, we use catalogs produced for the
\emph{Herschel} survey of CANDELS regions (Inami et al., in prep).  A
100$\,\micron$ source is defined as a $\ge 3\sigma$ flux density measurement
from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\micron$ source, which is based
on an IRAC 3.6$\,\micron$ source prior.  In GOODS-S, the catalog has
flux densities at 24, 70, 100, and 160$\,\micron$; in COSMOS and
UDS, the catalogs have flux densities at 24, 100, 160, 250, 350,
and 500$\,\micron$.  All flux densities are $\ge 3\sigma$.  We do not use the
250, 350, and 500$\,\micron$ flux
densities in the COSMOS and UDS catalogs, to avoid the effects of source
confusion on PSF fitting.  (Including them changes our results negligibly.)

We associate each 100$\,\micron$ source with a 1.6$\,\micron$ ($H$-band) source
in the
catalogs produced by CANDELS
\citep[Nayyeri et al., in prep;][]{galametz13,guo13}.  Each catalog has
broadband flux densities at many wavelengths, not all of which are common to the
other two.  We require the 1.6$\,\micron$ source to be a unique match
within 0.7$\arcsec$ of the position of the 100$\,\micron$ source's
3.6$\,\micron$ prior.  The match radius is an estimate for maximizing the
number of unique matches while minimizing the number of multiple matches.

The final quantity of interest for each matched source is an H$\alpha$ line
flux or flux limit.  These come from our reduction of observations from the
\emph{HST}/WFC3-IR grism survey 3D-\emph{HST} \citep{brammer12}.
We match each 100$\,\micron$ source to a counterpart in the direct image
accompanying the grism observations.  Two people in our group visually inspect
the counterpart's spectrum and then review and reconcile any discrepant redshift
assignments.  The
H$\alpha$ line falls in the grism's wavelength range for galaxies at
$0.7 < z < 1.5$.  The spectra have low enough wavelength resolution that the
H$\alpha$ and [N II] lines are blended; we assume that the line flux of [NII]
at $\lambda = 0.6583\,\micron$ is 0.3 times the H$\alpha$ line flux and that
the line flux of [N II] at $\lambda = 0.6548\,\micron$ is 0.1 times the
H$\alpha$ line flux.  The ratio of [N II] to H$\alpha$ line fluxes depends on
gas-phase metallicity so these values may be incorrect for some star-forming
galaxies.
The values will be correct for a significant fraction of galaxies in our
sample if the sample has a distribution of
gas-phase metallicity similar to that of low-redshift galaxies
\citep{kauffmann03}.  The values will be correct for a larger fraction of
galaxies in our sample if the sample has a distribution of gas-phase
metallicity similar to that of low-redshift galaxies which are luminous in
the near-IR \citep{weiner07}.  For each 1D spectrum with a visible and
uncontaminated
line complex, we fit a linear model to the continuum and Gaussian profiles to
the emission lines and extract the H$\alpha$ line flux.  The uncertainty on the
line flux comes from the covariance matrix times the fit's reduced $\chi^{2}$.
We replace $< 5\sigma$ H$\alpha$ line fluxes with limits.  We multiply the line
fluxes and limits by 1.1 as an aperture correction.

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\micron$ source to a source with a spectroscopic redshift in
the catalogs of: \citet{lefevre04,szokoly04,mignoli05,yamada05,ravikumar07,
vanzella08,lilly09,balestra10,fadda10,simpson12,kurk13,santini14}; Simpson et
al. (in prep.); Almaini et al. (in prep.); and
M. Dickinson (private communication).  (Operationally both the
100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.)
If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
(The direct
image is the image taken as part of the grism observations.)  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

To summarize, our high-redshift sample contains galaxies with: (1) detected
emission at 100$\,\micron$; (2) detected emission at 1.6$\,\micron$; and (3)
spectroscopically-determined redshifts at $0.7 < z < 1.5$.

\subsubsection{Samples of dust-poor and dusty galaxies at $z < 0.2$}

We use a nonstandard method to determine H$\alpha$ attenuation, so we test this
method first for low-redshift dust-poor galaxies which have known dust
properties.  We choose a sample of star-forming galaxies at $z \sim 0$ that are
analogs of common star-forming galaxies at high redshift
\citep[LBAs;][]{overzier09,overzier11}.

We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
densities (per the recommendations in the enhanced imaging products quick start
guide); these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\micron$ (NUV and FUV bands), from \emph{GALEX} observations.
H$\alpha$ line
fluxes, from SDSS observations, are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

\subsection{Derived quantities}

In this section we detail how we estimate total IR and emergent UV
luminosities, UV continuum power-law indices, and star formation rates for the
galaxies in our samples.

\subsubsection{IR luminosities}

We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  If the galaxy has one
measured IR flux density, we find the SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.
%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
%the signal-to-noise ratio of the flux density, in the single flux density
%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
%$\chi^{2}$-fitting case.

\citet{overzier11}, in their footnote 14, find that the \citet{chary01} SEDs do
not fit low-redshift dust-poor galaxies as well as other SEDs.  They measured
IR flux density limits at 70 and 160$\,\micron$ as well as flux densities at
24$\,\micron$.  The footnote explains that the \citet{chary01} SEDs, when
fit to 24$\,\micron$ flux densities, predict flux densities at 70 and
160$\,\micron$ that fall above their upper limits.  Our IR luminosities are
high compared to theirs---on average, a factor of 1.4 times higher; at most, a
factor of 2.5 times higher.  We present results for both sets of IR
luminosities for the low-redshift dust-poor galaxies.

IR luminosities are between $5\times10^{10}$ and $1\times10^{12} L_{\odot}$
for the central 95\% of the sample of high-redshift dusty galaxies; between
$7\times10^{10}$ and $4\times10^{11} L_{\odot}$ for the low-redshift dusty
galaxies; and between $4\times10^{10}$ and $5\times10^{11} L_{\odot}$ for
the low-redshift dust-poor galaxies.

\subsubsection{UV continuum power-law indices and luminosities}

For galaxies with UV emission from newly formed massive stars the continuum
between 0.125 and 0.263$\,\micron$ is approximately a power law with index
$\beta$:
\begin{equation}
S_{\lambda} = C\lambda^{\beta}
\end{equation}
where $S_{\lambda}$ is flux density and $\lambda$ is wavelength.
We use all measured flux densities and uncertainties in this rest-frame
wavelength range to fit for $\beta$ and the constant factor $C$ or
for their limits.  Measured flux densities may be negative---the sky aperture
may be brighter than the galaxy aperture---which
complicates our fitting procedure.  When a galaxy has only two measured flux
densities in the wavelength range, the solution for $\beta$ and $C$ is
analytic, so for a solution to exist the flux densities must be positive.  If
they both are, we make no cuts on their signal-to-noise ratio (S/N).
If the only positive flux density, among multiple measurements, is $> 3\sigma$,
we calculate a $\beta$ limit using that flux density and a $3\sigma$ limit for
another in the rest-frame wavelength range.  Whether the limit is an upper or
lower one depends on whether the detected flux density's wavelength is lower
or higher than the limit's wavelength.  We do not estimate a $\beta$ limit when
the only positive flux density, among multiple measurements, is $< 3\sigma$.
If more than two measured flux densities are positive, regardless of their S/N
and whether the surplus measurements are negative or positive, we minimize
$\chi^{2}$.
%The uncertainty on $\beta$ comes from the propagation of
%flux density uncertainties, in the analytic case, or from the covariance
%matrix times the reduced $\chi^{2}$, in the $\chi^{2}$-fitting case.

We estimate an emergent UV luminosity or a
limit at rest-frame 0.16$\,\micron$ for each galaxy using its redshift and
the power-law fit to the rest-frame UV flux densities.  We refer to the
luminosity as $0.16 \times L_{0.16}$.

\subsubsection{Star formation rates}\label{sfrs}

The equations in \citet{kennicutt98} relate IR, emergent UV, and emergent
H$\alpha$ luminosities to star formation rates (SFRs).  We assume
that a galaxy's total SFR: (1) is the sum of its IR- and emergent UV-derived
SFR; and (2) equals the intrinsic (not emergent)
H$\alpha$-derived SFR.  The SFR equations are valid under different assumptions
for the duration of a galaxy's star formation episode.  Our assumptions will not
conflict with those of \citet{kennicutt98} if: (1) the SFR has been
constant for $\sim 10^{8}$ yr, so that the instantaneous H$\alpha$-derived SFR
equals the prolonged UV- and IR-derived SFRs; and (2) the dominant
source for the IR luminosity is not old stars or an active nucleus.

We must exclude galaxies with active nuclei because fractions of their IR,
emergent UV, and emergent H$\alpha$ luminosities will be unrelated to newly
formed massive stars.  We identify 5 AGN hosts among the high-redshift dusty
galaxies; we use the \citet{donley12} criteria, which are based on mid-IR flux
densities (which all 3 CANDELS catalogs have).  These criteria will miss some
AGN hosts \citep{juneau13}.  We accept the contaminants because in some fields
we lack data---for example, X-ray data---that we could use to identify the
missed AGN hosts.

Among the low-redshift dusty
galaxies, we keep only those identified as star-forming by \citet{hwang13}.
They use rest-frame optical line flux ratios to discriminate between an AGN host
and a star-forming galaxy without an AGN.  None of the low-redshift dust-poor
galaxies host an AGN \citep{overzier11}.

\begin{landscape}
\begin{deluxetable}{llllllllllllll}
\tablecolumns{14}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the sample at $z > 0.7$
\label{tbl:highz}}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA, IR} &
\colhead{Dec, IR} &
\colhead{RA, opt.} &
\colhead{Dec, opt.} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
}
\startdata
\cutinhead{GOODS-S}
53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09
\enddata
\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
\tablecomments{Columns: RA and Dec, IR, are positions in the
\emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
priors.  RA and Dec, opt., are positions in the CANDELS catalogs.
$L_{\mathrm{H}\alpha}$ lim. is a 5$\sigma$ upper limit to the H$\alpha$
line luminosity.  The entire table is published in the electronic edition of
\apj.  A portion is shown here for guidance regarding its form and content.}
\end{deluxetable}
\clearpage
\end{landscape}

\begin{landscape}
\begin{deluxetable}{llllllllllllll}
\tablecolumns{14}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the sample at $z > 0.7$}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA, IR} &
\colhead{Dec, IR} &
\colhead{RA, opt.} &
\colhead{Dec, opt.} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
}
\startdata
\cutinhead{GOODS-S}
53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09  \\
53.177864 & -27.909479 & 53.177902 & -27.909540 & 1.104 & -2.24 & 0.07 & 5.7e+10 & 5.9e+08 & 4.5e+08 & 1.7e+07 & \ldots & 1.1e+11 & 4.7e+09  \\
53.141853 & -27.901850 & 53.141862 & -27.901907 & 0.823 & -1.04 & 0.26 & 4.7e+09 & 3.3e+08 & 6.0e+07 & 6.7e+06 & \ldots & 9.4e+10 & 1.2e+09  \\
53.086948 & -27.901337 & 53.086917 & -27.901404 & 0.967 & -1.69 & 0.18 & 1.3e+10 & 4.4e+08 & 2.5e+08 & 1.0e+07 & \ldots & 6.1e+10 & 1.1e+08  \\
53.072140 & -27.898058 & 53.072299 & -27.898007 & 1.359 & -1.25 & 0.01 & 1.4e+10 & 1.2e+08 & 4.0e+08 & 2.0e+07 & \ldots & 2.2e+11 & 1.4e+10  \\
53.169991 & -27.895391 & 53.170031 & -27.895423 & 0.977 & -2.06 & 0.17 & 1.3e+10 & 4.5e+08 & 4.0e+08 & 1.0e+07 & \ldots & 1.7e+11 & 1.4e+10  \\
53.087067 & -27.895485 & 53.087099 & -27.895559 & 1.044 & 0.17 & 0.84 & 1.4e+09 & 1.9e+08 & \ldots & \ldots & 4.4e+07 & 1.3e+11 & 2.4e+10  \\
53.232769 & -27.891096 & 53.232826 & -27.891097 & 0.983 & -1.67 & 0.20 & 1.6e+10 & 5.7e+08 & 4.0e+08 & 3.7e+07 & \ldots & 1.9e+11 & 6.1e+09  \\
53.144283 & -27.890127 & 53.144189 & -27.890129 & 1.107 & -2.20 & 0.14 & 2.8e+10 & 5.0e+08 & 6.8e+08 & 2.9e+07 & \ldots & 4.6e+11 & 1.3e+10  \\
53.197105 & -27.890034 & 53.197131 & -27.890055 & 1.296 & 0.00 & 0.15 & 1.8e+09 & 2.1e+08 & 2.1e+08 & 2.3e+07 & \ldots & 2.0e+11 & 4.0e+08  \\
53.127056 & -27.886671 & 53.127085 & -27.886729 & 1.017 & -1.42 & 0.57 & 2.4e+09 & 2.7e+08 & 1.0e+08 & 1.3e+07 & \ldots & 8.4e+10 & 4.5e+09  \\
53.213146 & -27.885704 & 53.213217 & -27.885701 & 0.979 & -1.51 & 0.22 & 1.3e+10 & 5.3e+08 & 3.2e+08 & 5.9e+07 & \ldots & 1.4e+11 & 8.0e+09  \\
53.127460 & -27.881624 & 53.127474 & -27.881659 & 1.019 & -2.73 & 0.40 & 6.2e+09 & 4.2e+08 & 2.2e+08 & 3.1e+07 & \ldots & 1.2e+11 & 7.5e+09  \\
53.198139 & -27.878679 & 53.198186 & -27.878674 & 1.249 & -1.82 & 0.08 & 6.9e+10 & 4.7e+08 & 8.4e+08 & 4.3e+07 & \ldots & 3.6e+11 & 5.1e+10  \\
53.071480 & -27.880896 & 53.071486 & -27.880972 & 0.990 & -2.19 & 0.22 & 1.5e+10 & 5.9e+08 & \ldots & \ldots & 4.5e+08 & 1.3e+11 & 7.6e+09  \\
53.076183 & -27.873486 & 53.076058 & -27.873614 & 0.740 & -0.40 & 0.25 & 3.2e+09 & 2.5e+08 & 2.1e+08 & 9.2e+06 & \ldots & 2.0e+11 & 1.1e+10  \\
53.073376 & -27.874519 & 53.073386 & -27.874583 & 1.098 & -0.26 & 0.32 & 1.1e+10 & 4.3e+08 & 4.4e+08 & 4.6e+07 & \ldots & 3.7e+11 & 1.3e+10  \\
53.071579 & -27.872364 & 53.071535 & -27.872459 & 1.097 & 0.28 & 0.57 & 3.9e+09 & 2.8e+08 & 3.1e+08 & 2.1e+07 & \ldots & 9.6e+11 & 9.4e+10  \\
53.089268 & -27.864340 & 53.089349 & -27.864418 & 0.833 & -2.16 & 0.15 & 2.0e+10 & 7.6e+08 & 2.6e+08 & 1.1e+07 & \ldots & 6.5e+10 & 1.3e+07  \\
53.178032 & -27.866461 & 53.178037 & -27.866461 & 1.123 & -1.53 & 0.47 & 5.2e+09 & 2.9e+08 & 2.4e+08 & 1.4e+07 & \ldots & 1.8e+11 & 9.6e+08  \\
53.221905 & -27.859411 & 53.221923 & -27.859399 & 0.736 & -0.65 & 0.12 & 8.7e+09 & 3.5e+08 & \ldots & \ldots & 8.3e+07 & 8.3e+10 & 2.6e+09  \\
53.135319 & -27.861332 & 53.135431 & -27.861352 & 0.997 & -1.67 & 0.41 & 4.9e+09 & 3.5e+08 & 1.5e+08 & 7.3e+06 & \ldots & 4.6e+10 & 1.9e+08  \\
53.137783 & -27.856565 & 53.137827 & -27.856632 & 0.735 & 0.83 & 0.64 & 1.0e+09 & 2.0e+08 & \ldots & \ldots & 1.0e+08 & 5.6e+10 & 4.3e+09  \\
53.130970 & -27.860342 & 53.130982 & -27.860409 & 1.382 & -1.25 & 0.01 & 1.9e+10 & 1.3e+08 & 3.4e+08 & 2.5e+07 & \ldots & 1.4e+11 & 5.5e+07  \\
53.058479 & -27.856730 & 53.058534 & -27.856808 & 1.220 & -1.37 & 0.36 & 9.1e+09 & 2.7e+08 & \ldots & \ldots & 1.1e+08 & 1.7e+11 & 2.7e+08  \\
53.056168 & -27.855335 & 53.056169 & -27.855367 & 1.226 & -1.75 & 0.20 & 1.8e+10 & 3.1e+08 & 4.8e+08 & 3.2e+07 & \ldots & 1.5e+11 & 7.3e+09  \\
53.220245 & -27.854082 & 53.220274 & -27.854091 & 1.002 & -0.86 & 0.29 & 9.2e+09 & 4.4e+08 & 3.6e+08 & 3.7e+07 & \ldots & 4.3e+11 & 9.8e+09  \\
53.220829 & -27.851294 & 53.220908 & -27.851331 & 0.734 & 4.05 & 1.17 & 8.7e+07 & 3.4e+07 & \ldots & \ldots & 7.0e+07 & 1.4e+11 & 1.3e+10  \\
53.196545 & -27.851704 & 53.196571 & -27.851696 & 1.224 & 0.20 & 0.70 & 3.7e+09 & 2.0e+08 & 3.5e+08 & 2.3e+07 & \ldots & 6.3e+11 & 1.8e+10  \\
53.122547 & -27.852680 & 53.122554 & -27.852730 & 0.735 & 1.74 & 1.32 & 2.2e+08 & 9.1e+07 & \ldots & \ldots & 4.9e+07 & 9.6e+10 & 3.2e+09  \\
53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablenotemark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\
53.070782 & -27.850611 & 53.070771 & -27.850671 & 0.991 & -3.56 & 0.72 & 2.8e+09 & 3.7e+08 & 1.8e+08 & 2.1e+07 & \ldots & 3.0e+11 & 8.7e+09  \\
53.104969 & -27.849974 & 53.104994 & -27.850023 & 0.841 & -2.07 & 0.14 & 1.8e+10 & 6.4e+08 & 2.0e+08 & 1.4e+07 & \ldots & 4.8e+10 & 1.5e+09  \\
53.115479 & -27.844624 & 53.115494 & -27.844666 & 1.097 & -0.94 & 0.30 & 1.1e+10 & 4.2e+08 & 6.5e+08 & 1.8e+07 & \ldots & 9.9e+11 & 8.1e+10  \\
53.214821 & -27.845755 & 53.214866 & -27.845737 & 0.980 & -2.12 & 0.68 & 3.5e+09 & 4.1e+08 & 2.1e+08 & 1.7e+07 & \ldots & 1.1e+11 & 4.7e+09  \\
53.186874 & -27.841162 & 53.186881 & -27.841169 & 0.783 & -1.43 & 0.14 & 1.2e+10 & 5.1e+08 & 1.0e+08 & 1.0e+07 & \ldots & 4.8e+10 & 2.1e+09  \\
53.055374 & -27.843821 & 53.055380 & -27.843884 & 1.296 & -0.91 & 0.10 & 4.4e+09 & 2.8e+08 & \ldots & \ldots & 1.8e+08 & 2.1e+11 & 3.2e+09  \\
53.107754 & -27.838791 & 53.107758 & -27.838812 & 1.095 & -1.93 & 0.11 & 2.7e+10 & 4.6e+08 & 1.1e+09 & 1.6e+08 & \ldots & 2.8e+11 & 6.6e+09  \\
53.109276 & -27.835032 & 53.109331 & -27.834890 & 1.096 & -1.53 & 1.40 & 1.9e+09 & 3.3e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 1.3e+09  \\
53.124714 & -27.842196 & 53.124767 & -27.842230 & 1.389 & -1.04 & 0.03 & 4.1e+09 & 8.6e+07 & 1.3e+08 & 1.3e+07 & \ldots & 1.4e+11 & 6.5e+09  \\
53.214905 & -27.838238 & 53.214939 & -27.838237 & 0.853 & -1.59 & 0.09 & 3.1e+10 & 7.2e+08 & 5.1e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.8e+09  \\
53.155365 & -27.835815 & 53.155401 & -27.835815 & 1.140 & -3.21 & 0.94 & 3.9e+09 & 3.7e+08 & \ldots & \ldots & 8.0e+07 & 1.1e+11 & 1.7e+09  \\
53.215519 & -27.830894 & 53.215526 & -27.830835 & 0.736 & -0.17 & 0.15 & 7.1e+09 & 3.3e+08 & 4.6e+08 & 4.1e+07 & \ldots & 2.3e+11 & 3.3e+09  \\
53.146038 & -27.833027 & 53.146185 & -27.832905 & 1.049 & -2.17 & 0.49 & 4.9e+09 & 3.7e+08 & 1.1e+08 & 1.0e+07 & \ldots & 6.8e+10 & 1.0e+09  \\
53.218082 & -27.833673 & 53.218135 & -27.833687 & 0.853 & -1.05 & 0.21 & 8.2e+09 & 4.3e+08 & 2.6e+08 & 1.9e+07 & \ldots & 1.8e+11 & 6.5e+09  \\
53.089886 & -27.828199 & 53.089889 & -27.828241 & 1.110 & -2.10 & 0.50 & 5.7e+09 & 3.3e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 1.4e+10  \\
53.216496 & -27.821653 & 53.216570 & -27.821606 & 1.247 & -1.90 & 0.34 & 1.2e+10 & 2.5e+08 & \ldots & \ldots & 1.2e+08 & 1.5e+11 & 1.8e+09  \\
53.051586 & -27.820166 & 53.051606 & -27.820193 & 1.048 & -2.14 & 0.09 & 4.2e+10 & 6.2e+08 & 1.9e+08 & 1.2e+07 & \ldots & 5.1e+10 & 4.2e+08  \\
53.074184 & -27.821064 & 53.074268 & -27.821097 & 1.127 & -2.10 & 0.17 & 1.9e+10 & 4.0e+08 & 2.3e+08 & 2.4e+07 & \ldots & 6.9e+10 & 1.7e+09  \\
53.066761 & -27.816540 & 53.066754 & -27.816593 & 1.413 & 11.31 & 11.23 & 9.3e+06 & 1.9e+09 & 3.5e+08 & 4.4e+07 & \ldots & 1.4e+12 & 6.6e+10  \\
53.181011 & -27.817177 & 53.181037 & -27.817160 & 1.370 & -0.00 & 0.31 & 2.2e+09 & 6.3e+08 & \ldots & \ldots & 2.3e+08 & 9.8e+11 & 7.5e+10  \\
53.149857 & -27.813999 & 53.149886 & -27.813998 & 1.307 & -1.44 & 0.06 & 7.6e+10 & 3.2e+09 & 8.8e+08 & 4.6e+07 & \ldots & 3.7e+11 & 3.8e+10  \\
53.044754 & -27.816416 & 53.044892 & -27.816469 & 1.380 & -0.42 & 0.16 & 3.2e+09 & 3.8e+08 & \ldots & \ldots & 1.5e+08 & 3.4e+11 & 9.3e+10  \\
53.145061 & -27.809834 & 53.145087 & -27.809851 & 1.245 & -1.87 & 0.14 & 9.4e+09 & 2.0e+08 & 2.5e+08 & 2.3e+07 & \ldots & 1.5e+11 & 2.0e+10  \\
53.164284 & -27.810833 & 53.164307 & -27.810827 & 0.735 & 0.55 & 0.28 & 5.6e+08 & 6.5e+07 & 5.9e+07 & 1.1e+07 & \ldots & 3.6e+10 & 1.6e+08  \\
53.073448 & -27.803240 & 53.073456 & -27.803292 & 0.735 & 2.17 & 1.10 & 2.3e+08 & 8.2e+07 & \ldots & \ldots & 6.6e+07 & 9.1e+10 & 1.3e+09  \\
53.066555 & -27.797188 & 53.066761 & -27.797223 & 1.296 & 1.44 & 0.14 & 1.8e+09 & 3.2e+08 & \ldots & \ldots & 1.3e+08 & 3.1e+11 & 1.4e+10  \\
53.076847 & -27.799187 & 53.076879 & -27.799206 & 1.079 & -2.19 & 0.24 & 1.3e+10 & 4.1e+08 & 1.7e+08 & 1.7e+07 & \ldots & 4.8e+10 & 7.1e+08  \\
53.034164 & -27.797775 & 53.034171 & -27.797808 & 0.840 & 0.14 & 0.21 & 4.7e+09 & 2.6e+08 & 3.1e+08 & 2.3e+07 & \ldots & 3.2e+11 & 1.1e+10  \\
53.156612 & -27.795471 & 53.156735 & -27.795577 & 1.097 & -1.51 & 0.10 & 1.5e+10 & 3.0e+08 & 2.7e+08 & 2.8e+07 & \ldots & 2.2e+11 & 2.2e+09  \\
53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablenotemark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
53.078960 & -27.799620 & 53.078906 & -27.799642 & 1.085 & -2.09 & 0.42 & 5.5e+09 & 3.1e+08 & 2.1e+08 & 1.1e+07 & \ldots & 6.7e+10 & 3.3e+07  \\
53.026798 & -27.791296 & 53.026811 & -27.791322 & 1.022 & -1.04 & 0.22 & 1.0e+10 & 3.7e+08 & 5.7e+08 & 1.7e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
53.184113 & -27.792627 & 53.184162 & -27.792636 & 0.737 & -0.82 & 0.06 & 9.3e+09 & 2.1e+08 & 2.1e+08 & 2.6e+07 & \ldots & 1.7e+11 & 1.5e+10  \\
53.178066 & -27.792753 & 53.178077 & -27.792740 & 1.427 & -0.75 & 0.07 & 2.5e+09 & 1.1e+08 & \ldots & \ldots & 2.4e+08 & 2.8e+11 & 1.8e+08  \\
53.086002 & -27.787987 & 53.086045 & -27.788089 & 0.734 & -0.29 & 0.11 & 7.2e+09 & 2.6e+08 & \ldots & \ldots & 1.1e+08 & 1.2e+11 & 5.3e+09  \\
53.090660 & -27.790161 & 53.090665 & -27.790186 & 1.000 & -1.54 & 0.38 & 4.1e+09 & 3.0e+08 & 1.9e+08 & 1.1e+07 & \ldots & 1.1e+11 & 4.9e+09  \\
53.166122 & -27.787506 & 53.166177 & -27.787515 & 1.112 & -2.06 & 0.07 & 3.3e+10 & 4.4e+08 & 7.3e+08 & 7.6e+07 & \ldots & 3.1e+11 & 1.8e+10  \\
53.109558 & -27.788197 & 53.109568 & -27.788203 & 0.995 & -1.87 & 0.14 & 2.4e+10 & 5.8e+08 & 1.9e+08 & 1.4e+07 & \ldots & 6.0e+10 & 2.0e+08  \\
53.176544 & -27.785450 & 53.176577 & -27.785446 & 1.314 & 2.94 & 0.31 & 5.3e+08 & 1.5e+08 & 9.9e+07 & 1.7e+07 & \ldots & 3.0e+11 & 2.7e+10  \\
53.071011 & -27.785858 & 53.070981 & -27.785895 & 0.763 & -1.10 & 0.18 & 8.5e+09 & 4.5e+08 & 1.1e+08 & 1.2e+07 & \ldots & 1.2e+11 & 7.7e+08  \\
53.197544 & -27.786417 & 53.197582 & -27.786395 & 1.098 & -2.98 & 0.77 & 1.3e+09 & 2.0e+08 & \ldots & \ldots & 1.3e+08 & 2.0e+11 & 5.9e+09  \\
53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablenotemark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\
53.104275 & -27.788363 & 53.104331 & -27.788388 & 1.357 & -0.62 & 0.20 & 4.7e+09 & 6.3e+08 & \ldots & \ldots & 8.8e+07 & 1.3e+11 & 4.9e+08  \\
53.048252 & -27.783079 & 53.048272 & -27.783100 & 0.814 & -0.53 & 0.27 & 3.8e+09 & 2.8e+08 & 1.1e+08 & 6.4e+06 & \ldots & 8.5e+10 & 1.3e+10  \\
53.135197 & -27.781746 & 53.135245 & -27.781672 & 1.437\tablenotemark{G} & -0.57 & 0.05 & 5.2e+09 & 1.9e+08 & 3.5e+08 & 1.7e+07 & \ldots & 2.5e+11 & 2.4e+10  \\
53.044064 & -27.785015 & 53.044080 & -27.785048 & 1.045 & -1.39 & 0.19 & 1.4e+10 & 4.3e+08 & 1.8e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.5e+10  \\
53.049721 & -27.779055 & 53.049747 & -27.779072 & 1.221 & -1.31 & 1.05 & 3.5e+09 & 2.5e+08 & 2.4e+08 & 2.2e+07 & \ldots & 3.1e+11 & 9.1e+09  \\
53.128693 & -27.780367 & 53.128828 & -27.780418 & 1.173 & -1.03 & 0.43 & 3.5e+09 & 2.1e+08 & 2.0e+08 & 1.4e+07 & \ldots & 2.7e+11 & 9.2e+09  \\
53.077465 & -27.780226 & 53.077453 & -27.780218 & 0.741 & 0.94 & 0.55 & 6.4e+08 & 1.1e+08 & 5.9e+07 & 7.7e+06 & \ldots & 6.2e+10 & 1.3e+09  \\
53.064384 & -27.775332 & 53.064445 & -27.775372 & 0.735 & 3.60 & 0.86 & 1.9e+08 & 5.5e+07 & \ldots & \ldots & 1.0e+08 & 2.4e+11 & 1.9e+10  \\
53.145199 & -27.777922 & 53.145238 & -27.777906 & 1.099 & -1.87 & 0.25 & 4.3e+09 & 2.0e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.0e+11 & 2.1e+10  \\
53.058456 & -27.776129 & 53.058416 & -27.776186 & 0.837 & 1.28 & 0.73 & 6.5e+08 & 1.3e+08 & 7.0e+07 & 9.0e+06 & \ldots & 2.9e+11 & 2.8e+10  \\
53.099220 & -27.777590 & 53.099269 & -27.777610 & 1.221 & -0.71 & 2.74 & 6.8e+08 & 1.4e+08 & \ldots & \ldots & 7.3e+07 & 9.6e+10 & 3.1e+08  \\
53.050873 & -27.772442 & 53.050929 & -27.772409 & 1.033 & 0.48 & 0.55 & 3.6e+09 & 3.0e+08 & 2.1e+08 & 1.1e+07 & \ldots & 4.0e+11 & 2.4e+10  \\
53.193066 & -27.775581 & 53.193097 & -27.775562 & 1.220 & 1.25 & 2.33 & 8.4e+08 & 1.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.2e+11 & 2.6e+07  \\
53.036961 & -27.774698 & 53.037019 & -27.774734 & 1.032 & -3.31 & 0.86 & 3.2e+09 & 4.1e+08 & 1.8e+08 & 9.1e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
53.105900 & -27.771418 & 53.105929 & -27.771412 & 0.896 & -1.20 & 0.30 & 6.4e+09 & 4.3e+08 & 4.3e+08 & 1.1e+07 & \ldots & 3.2e+11 & 2.2e+09  \\
53.098351 & -27.766935 & 53.098373 & -27.766940 & 1.033 & 0.04 & 1.06 & 1.9e+09 & 3.2e+08 & \ldots & \ldots & 1.1e+08 & 2.6e+11 & 3.0e+10  \\
53.162823 & -27.767178 & 53.162858 & -27.767160 & 1.216 & -1.65 & 0.02 & 1.7e+11 & 6.8e+08 & 3.0e+09 & 5.5e+07 & \ldots & 4.2e+11 & 1.2e+11  \\
53.048225 & -27.773033 & 53.048221 & -27.773042 & 1.221 & -1.29 & 0.17 & 3.4e+10 & 4.2e+08 & 4.6e+08 & 3.9e+07 & \ldots & 2.3e+11 & 1.1e+10  \\
53.149010 & -27.774282 & 53.149076 & -27.774305 & 1.094 & -1.03 & 0.43 & 2.7e+09 & 2.3e+08 & 1.0e+08 & 1.3e+07 & \ldots & 1.1e+11 & 1.2e+10  \\
53.127968 & -27.771446 & 53.127979 & -27.771436 & 1.307 & -0.72 & 0.04 & 1.7e+10 & 4.7e+08 & 2.2e+08 & 3.8e+07 & \ldots & 2.1e+11 & 1.7e+10  \\
53.102539 & -27.772264 & 53.102539 & -27.772288 & 1.221 & 0.97 & 1.49 & 1.5e+09 & 1.7e+08 & 1.3e+08 & 2.0e+07 & \ldots & 2.2e+11 & 2.4e+10  \\
53.048153 & -27.770285 & 53.048020 & -27.770415 & 1.039 & -1.14 & 0.39 & 8.2e+09 & 4.7e+08 & \ldots & \ldots & 6.5e+07 & 1.6e+11 & 9.9e+09  \\
53.181160 & -27.765703 & 53.181195 & -27.765678 & 1.220 & -1.57 & 0.23 & 2.0e+10 & 3.4e+08 & 7.7e+08 & 1.3e+08 & \ldots & 2.4e+11 & 1.2e+10  \\
53.151356 & -27.766697 & 53.151369 & -27.766686 & 0.895 & -1.64 & 0.28 & 2.1e+09 & 1.7e+08 & 1.1e+08 & 5.2e+06 & \ldots & 9.8e+10 & 1.3e+10  \\
53.026695 & -27.765194 & 53.026697 & -27.765210 & 1.329 & 3.30 & 0.76 & 2.7e+08 & 3.3e+08 & 3.2e+08 & 2.6e+07 & \ldots & 6.0e+11 & 1.4e+10  \\
53.116947 & -27.768333 & 53.116997 & -27.768349 & 1.109 & -4.67 & 1.71 & 2.8e+09 & 5.1e+08 & 1.4e+08 & 1.1e+07 & \ldots & 2.7e+11 & 3.1e+10  \\
53.096428 & -27.765188 & 53.096474 & -27.765180 & 1.223 & -0.98 & 0.44 & 8.4e+09 & 2.7e+08 & 4.1e+08 & 1.8e+07 & \ldots & 2.3e+11 & 1.6e+10  \\
53.050854 & -27.765091 & 53.050873 & -27.765105 & 1.038 & -1.95 & 0.17 & 2.4e+10 & 6.1e+08 & 2.8e+08 & 1.9e+07 & \ldots & 1.4e+11 & 1.4e+09  \\
53.094173 & -27.762905 & 53.094302 & -27.762978 & 0.840 & 0.26 & 3.08 & 2.0e+08 & 1.5e+08 & \ldots & \ldots & 2.9e+07 & 8.7e+10 & 9.6e+09  \\
53.045513 & -27.762356 & 53.045611 & -27.762371 & 1.039 & -1.87 & 0.18 & 2.8e+10 & 7.2e+08 & 2.1e+08 & 1.5e+07 & \ldots & 5.7e+10 & 3.2e+07  \\
53.163559 & -27.758949 & 53.163589 & -27.758952 & 1.095 & -0.30 & 0.22 & 4.9e+09 & 2.3e+08 & 1.8e+08 & 1.8e+07 & \ldots & 2.7e+11 & 2.3e+09  \\
53.111877 & -27.757845 & 53.111931 & -27.757828 & 0.831 & -0.34 & 0.53 & 2.3e+09 & 3.1e+08 & 1.5e+08 & 1.4e+07 & \ldots & 2.0e+11 & 6.0e+09  \\
53.195179 & -27.753788 & 53.195239 & -27.753782 & 0.840 & -0.74 & 0.26 & 5.2e+09 & 3.5e+08 & \ldots & \ldots & 6.6e+07 & 1.3e+11 & 6.3e+09  \\
53.072784 & -27.757933 & 53.072914 & -27.757849 & 1.039 & -1.92 & 0.32 & 8.1e+09 & 4.0e+08 & 3.2e+08 & 9.0e+06 & \ldots & 2.7e+11 & 1.9e+10  \\
53.022861 & -27.756960 & 53.022876 & -27.757005 & 1.189 & -1.94 & 1.47 & 2.1e+09 & 2.3e+08 & 3.5e+08 & 2.8e+07 & \ldots & 5.3e+11 & 2.1e+10  \\
53.202320 & -27.751293 & 53.202349 & -27.751279 & 1.113 & -0.16 & 0.99 & 1.9e+09 & 2.2e+08 & \ldots & \ldots & 6.5e+07 & 2.6e+11 & 1.3e+10  \\
53.024975 & -27.752018 & 53.024917 & -27.752059 & 1.068 & -1.89 & 0.30 & 7.9e+09 & 3.5e+08 & 3.8e+08 & 2.8e+07 & \ldots & 6.4e+11 & 1.2e+10  \\
53.036190 & -27.752197 & 53.036203 & -27.752228 & 1.296 & 1.39 & 0.21 & 2.0e+09 & 5.6e+08 & 6.8e+08 & 2.8e+07 & \ldots & 8.4e+11 & 1.7e+10  \\
53.096127 & -27.752499 & 53.096209 & -27.752536 & 0.995 & -1.44 & 0.85 & 2.3e+09 & 3.3e+08 & \ldots & \ldots & 4.8e+07 & 9.1e+10 & 5.1e+09  \\
53.125889 & -27.751266 & 53.125899 & -27.751275 & 0.738 & -3.15 & 0.10 & 3.7e+10 & 1.1e+09 & 3.0e+08 & 8.7e+06 & \ldots & 1.2e+11 & 3.9e+10  \\
53.063969 & -27.751907 & 53.063981 & -27.751923 & 0.861 & -1.44 & 0.18 & 1.0e+10 & 4.7e+08 & 1.6e+08 & 1.4e+07 & \ldots & 3.8e+10 & 1.9e+09  \\
53.161648 & -27.746819 & 53.161600 & -27.746925 & 0.735 & 1.47 & 0.75 & 4.5e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 4.2e+11 & 8.9e+10  \\
53.068554 & -27.746864 & 53.068721 & -27.746955 & 0.976 & -2.16 & 0.24 & 1.3e+10 & 5.7e+08 & 2.7e+08 & 2.2e+07 & \ldots & 3.0e+11 & 4.5e+09  \\
53.110130 & -27.745434 & 53.110168 & -27.745444 & 1.014 & 11.47 & 7.24 & 1.0e+07 & 1.9e+07 & \ldots & \ldots & 5.8e+07 & 1.6e+11 & 6.6e+09  \\
53.172813 & -27.744471 & 53.172863 & -27.744457 & 1.295 & -0.64 & 0.32 & 6.9e+09 & 1.5e+09 & \ldots & \ldots & 1.3e+08 & 3.0e+11 & 3.4e+10  \\
53.107323 & -27.741886 & 53.107345 & -27.741911 & 0.891 & 2.54 & 2.80 & 1.6e+08 & 1.0e+08 & 1.4e+08 & 8.8e+06 & \ldots & 4.2e+11 & 5.3e+09  \\
53.063469 & -27.743839 & 53.063481 & -27.743869 & 1.109 & -1.48 & 0.85 & 3.4e+09 & 3.4e+08 & 1.7e+08 & 1.7e+07 & \ldots & 2.2e+11 & 1.9e+10  \\
53.068001 & -27.744961 & 53.067988 & -27.744958 & 1.111 & -2.23 & 0.24 & 1.4e+10 & 4.1e+08 & 2.7e+08 & 1.3e+07 & \ldots & 1.6e+11 & 7.2e+08  \\
53.150074 & -27.739941 & 53.150126 & -27.739926 & 1.038 & -1.95 & 0.15 & 2.4e+10 & 5.6e+08 & 5.4e+08 & 4.0e+07 & \ldots & 2.0e+11 & 3.3e+09  \\
53.083782 & -27.739586 & 53.083793 & -27.739570 & 1.217 & -0.44 & 0.44 & 7.4e+09 & 2.5e+08 & 4.2e+08 & 2.8e+07 & \ldots & 3.6e+11 & 1.8e+10  \\
53.061565 & -27.742525 & 53.061590 & -27.742532 & 0.736 & 4.18 & 3.25 & 2.5e+07 & 2.5e+07 & 3.9e+07 & 4.0e+06 & \ldots & 1.5e+11 & 3.7e+09  \\
53.204159 & -27.738546 & 53.204191 & -27.738536 & 0.984\tablenotemark{G} & -1.92 & 1.20 & 6.9e+09 & 1.3e+09 & 2.3e+08 & 1.5e+07 & \ldots & 1.4e+11 & 4.6e+09  \\
53.144276 & -27.735434 & 53.144345 & -27.735558 & 1.224 & 0.90 & 1.11 & 2.2e+09 & 2.2e+08 & \ldots & \ldots & 9.1e+07 & 1.8e+11 & 1.0e+10  \\
53.155808 & -27.735281 & 53.155851 & -27.735273 & 1.017 & -1.47 & 0.59 & 3.6e+09 & 3.5e+08 & 2.4e+08 & 1.5e+07 & \ldots & 1.7e+11 & 1.2e+10  \\
53.175217 & -27.739241 & 53.175243 & -27.739235 & 1.152 & -2.55 & 0.42 & 8.3e+09 & 3.4e+08 & 2.1e+08 & 2.9e+07 & \ldots & 1.0e+11 & 5.6e+09  \\
53.195465 & -27.735258 & 53.195491 & -27.735229 & 1.146 & -0.92 & 0.51 & 4.7e+09 & 2.7e+08 & 1.8e+08 & 1.2e+07 & \ldots & 2.2e+11 & 6.6e+08  \\
53.099781 & -27.730268 & 53.099810 & -27.730302 & 1.311 & -1.63 & 0.02 & 3.5e+10 & 4.3e+08 & 5.6e+08 & 1.6e+07 & \ldots & 1.3e+11 & 4.2e+08  \\
53.016594 & -27.727051 & 53.016606 & -27.727074 & 0.960 & -0.64 & 1.82 & 1.0e+09 & 3.3e+08 & 2.2e+08 & 1.4e+07 & \ldots & 4.1e+11 & 5.2e+09  \\
53.061180 & -27.726936 & 53.061180 & -27.726970 & 0.981 & -2.02 & 0.37 & 3.8e+09 & 2.8e+08 & 1.0e+08 & 5.7e+06 & \ldots & 5.3e+10 & 9.6e+07  \\
53.173592 & -27.724491 & 53.173807 & -27.724472 & 0.979 & -0.95 & 0.94 & 2.2e+09 & 3.5e+08 & 1.3e+08 & 9.9e+06 & \ldots & 2.9e+11 & 2.2e+10  \\
53.039387 & -27.726641 & 53.039389 & -27.726633 & 1.023 & 2.94 & 1.30 & 6.3e+08 & 1.5e+08 & \ldots & \ldots & 4.8e+07 & 1.0e+11 & 2.4e+09  \\
53.045628 & -27.724943 & 53.045637 & -27.724927 & 1.215 & -1.72 & 0.30 & 1.3e+10 & 3.1e+08 & 4.1e+08 & 2.1e+07 & \ldots & 2.3e+11 & 9.4e+09  \\
53.125111 & -27.721893 & 53.125287 & -27.721940 & 1.098 & -0.23 & 0.25 & 9.2e+09 & 3.2e+08 & 5.0e+08 & 2.9e+07 & \ldots & 7.6e+11 & 2.1e+10  \\
53.124729 & -27.716934 & 53.124780 & -27.717107 & 1.356 & -0.78 & 0.05 & 1.3e+10 & 4.8e+08 & 7.1e+08 & 4.2e+07 & \ldots & 1.2e+12 & 4.6e+10  \\
53.094563 & -27.723654 & 53.094718 & -27.723585 & 0.738\tablenotemark{G} & -0.56 & 0.24 & 3.2e+09 & 2.4e+08 & 7.5e+07 & 6.7e+06 & \ldots & 3.1e+10 & 3.5e+07  \\
53.173607 & -27.722679 & 53.173655 & -27.722641 & 0.978 & -2.56 & 17.70 & 1.2e+08 & 3.6e+08 & \ldots & \ldots & 4.3e+07 & 1.3e+11 & 3.8e+08  \\
53.179310 & -27.722076 & 53.179350 & -27.722054 & 0.743 & -1.17 & 0.14 & 1.0e+10 & 4.4e+08 & 1.3e+08 & 1.3e+07 & \ldots & 5.8e+10 & 1.3e+09  \\
53.171768 & -27.719393 & 53.171840 & -27.719363 & 1.222 & 4.77 & 9.38 & 9.0e+07 & 1.0e+08 & \ldots & \ldots & 6.5e+07 & 2.7e+11 & 6.3e+09  \\
53.023632 & -27.714867 & 53.023645 & -27.714882 & 1.296 & -0.64 & 0.09 & 1.3e+10 & 1.2e+09 & 4.1e+08 & 2.1e+07 & \ldots & 2.5e+11 & 1.1e+10  \\
53.150776 & -27.716162 & 53.150717 & -27.716194 & 0.967 & -1.22 & 0.09 & 3.9e+10 & 6.9e+08 & 8.7e+08 & 4.5e+07 & \ldots & 3.2e+11 & 1.3e+10  \\
53.122067 & -27.712461 & 53.122076 & -27.712461 & 1.040 & -0.26 & 0.81 & 1.4e+09 & 1.9e+08 & 1.9e+08 & 1.0e+07 & \ldots & 1.6e+11 & 1.4e+10  \\
53.142792 & -27.706961 & 53.142848 & -27.706937 & 1.088 & -0.40 & 0.29 & 1.2e+10 & 4.6e+08 & 3.3e+08 & 1.5e+07 & \ldots & 1.8e+11 & 3.2e+09  \\
53.161484 & -27.705112 & 53.161488 & -27.705104 & 1.430 & -0.88 & 0.14 & 5.2e+09 & 4.8e+08 & 1.4e+08 & 1.6e+07 & \ldots & 2.9e+11 & 1.1e+09  \\
53.166592 & -27.703928 & 53.166556 & -27.703810 & 0.815 & 3.03 & 0.09 & 7.6e+09 & 2.1e+08 & 1.1e+08 & 9.4e+06 & \ldots & 7.3e+10 & 1.1e+09  \\
53.158775 & -27.705088 & 53.158811 & -27.705088 & 0.863 & -1.81 & 0.46 & 2.9e+09 & 3.3e+08 & 7.2e+07 & 8.6e+06 & \ldots & 5.8e+10 & 3.1e+10  \\
53.139095 & -27.694304 & 53.139188 & -27.694145 & 1.045 & -1.01 & 0.54 & 5.2e+09 & 4.0e+08 & 1.9e+08 & 1.5e+07 & \ldots & 2.8e+11 & 9.0e+09  \\
53.135094 & -27.697344 & 53.135083 & -27.697251 & 1.297 & -0.89 & 0.05 & 1.7e+10 & 5.0e+08 & 6.2e+08 & 4.2e+07 & \ldots & 4.3e+11 & 9.6e+09  \\
53.111504 & -27.695997 & 53.111521 & -27.695987 & 0.734 & 0.40 & 0.48 & 1.4e+09 & 2.1e+08 & 1.0e+08 & 1.0e+07 & \ldots & 2.3e+11 & 5.7e+10  \\
53.162651 & -27.692356 & 53.162680 & -27.692336 & 0.733\tablenotemark{G} & -1.34 & 0.15 & 8.7e+09 & 4.1e+08 & 9.0e+07 & 1.5e+07 & \ldots & 3.4e+10 & 9.1e+08  \\
53.131149 & -27.688419 & 53.131169 & -27.688368 & 0.837 & -0.83 & 0.16 & 1.3e+10 & 5.4e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 4.2e+09  \\
53.137051 & -27.689989 & 53.137075 & -27.689968 & 1.047 & -0.56 & 0.75 & 3.1e+09 & 3.4e+08 & 2.5e+08 & 4.2e+07 & \ldots & 3.3e+11 & 9.0e+09  \\
53.088108 & -27.685200 & 53.088136 & -27.685181 & 1.110 & -1.41 & 0.43 & 1.0e+10 & 5.1e+08 & 2.9e+08 & 2.3e+07 & \ldots & 3.4e+11 & 1.4e+10  \\
\cutinhead{COSMOS}
150.137010 & 2.243688 & 150.137013 & 2.243673 & 0.752\tablenotemark{G} & 2.42 & 1.13 & 1.3e+08 & 6.4e+07 & \ldots & \ldots & 3.5e+07 & 6.9e+10 & 7.4e+09  \\
150.117280 & 2.327124 & 150.117315 & 2.327120 & 0.903\tablenotemark{G} & -0.08 & 0.28 & 8.4e+09 & 1.1e+09 & 3.2e+08 & 2.0e+07 & \ldots & 2.7e+11 & 1.6e+10  \\
150.130330 & 2.472160 & 150.130346 & 2.472122 & 0.924\tablenotemark{G} & 0.55 & 0.51 & 3.6e+09 & 8.6e+08 & 8.7e+07 & 1.2e+07 & \ldots & 1.1e+11 & 1.9e+08  \\
150.155450 & 2.205458 & 150.155459 & 2.205452 & 0.783\tablenotemark{G} & 1.06 & 0.26 & 2.3e+09 & 2.5e+08 & 1.9e+08 & 1.3e+07 & \ldots & 2.9e+11 & 5.4e+09  \\
150.067080 & 2.372434 & 150.067101 & 2.372425 & 1.257\tablenotemark{G} & 0.57 & 0.57 & 5.7e+09 & 3.1e+09 & 8.5e+08 & 5.5e+07 & \ldots & 6.9e+11 & 4.3e+10  \\
150.105500 & 2.297602 & 150.105557 & 2.297617 & 0.951                  & 0.87 & 1.24 & 3.0e+09 & 1.7e+09 & 2.5e+08 & 1.5e+07 & \ldots & 6.7e+11 & 1.4e+10  \\
150.064130 & 2.409601 & 150.064153 & 2.409603 & 0.895\tablenotemark{G} & 0.48 & 0.91 & 3.9e+09 & 1.7e+09 & 1.7e+08 & 1.3e+07 & \ldots & 1.6e+11 & 1.1e+10  \\
150.112060 & 2.434008 & 150.112096 & 2.433991 & 1.120\tablenotemark{G} & 1.35 & 0.91 & 1.9e+09 & 1.6e+09 & \ldots & \ldots & 1.0e+08 & 2.3e+11 & 1.4e+10  \\
150.096090 & 2.240252 & 150.096111 & 2.240252 & 0.802                  & 1.50 & 0.72 & 3.8e+08 & 1.1e+08 & 6.6e+07 & 1.3e+07 & \ldots & 2.5e+11 & 2.0e+10  \\
150.095390 & 2.255131 & 150.095433 & 2.255139 & 0.727                  & 0.22 & 0.21 & 3.4e+09 & 3.2e+08 & \ldots & \ldots & 1.2e+08 & 2.3e+11 & 6.4e+09  \\
150.164710 & 2.322803 & 150.164713 & 2.322820 & 0.791\tablenotemark{G} & -1.21 & 0.15 & 1.2e+10 & 7.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 1.2e+11 & 4.4e+09  \\
150.103720 & 2.237653 & 150.103747 & 2.237663 & 0.799                  & -0.71 & 0.19 & 6.4e+09 & 4.9e+08 & 2.3e+08 & 3.2e+07 & \ldots & 8.1e+11 & 2.2e+11  \\
150.078210 & 2.287351 & 150.078239 & 2.287367 & 0.931\tablenotemark{G} & 0.23 & 1.84 & 5.5e+08 & 4.9e+08 & \ldots & \ldots & 4.4e+07 & 8.9e+10 & 6.2e+07  \\
150.071750 & 2.361027 & 150.071772 & 2.361027 & 0.908\tablenotemark{G} & 0.75 & 0.77 & 5.7e+09 & 2.2e+09 & 2.8e+08 & 3.4e+07 & \ldots & 3.3e+11 & 1.8e+10  \\
150.134540 & 2.428741 & 150.134551 & 2.428717 & 0.932\tablenotemark{G} & 1.80 & 1.21 & 3.0e+08 & 2.2e+08 & 9.2e+07 & 1.4e+07 & \ldots & 1.5e+11 & 2.3e+09  \\
150.068420 & 2.265476 & 150.068467 & 2.265490 & 0.981                  & 0.62 & 0.47 & 3.5e+09 & 7.6e+08 & 2.2e+08 & 2.7e+07 & \ldots & 1.9e+11 & 7.9e+09  \\
150.179140 & 2.215912 & 150.179144 & 2.215902 & 0.806\tablenotemark{G} & -0.12 & 0.25 & 3.8e+09 & 3.9e+08 & 1.3e+08 & 2.6e+07 & \ldots & 1.5e+11 & 3.9e+07  \\
150.177860 & 2.220603 & 150.177869 & 2.220627 & 1.148\tablenotemark{G} & -0.17 & 0.73 & 1.7e+09 & 6.4e+08 & \ldots & \ldots & 8.5e+07 & 2.1e+11 & 8.3e+09  \\
150.115720 & 2.416342 & 150.115703 & 2.416347 & 1.119\tablenotemark{G} & -0.39 & 0.67 & 1.3e+10 & 4.1e+09 & 4.0e+08 & 3.6e+07 & \ldots & 4.6e+11 & 6.5e+09  \\
150.089820 & 2.234895 & 150.089864 & 2.234888 & 0.838\tablenotemark{G} & 0.10 & 2.46 & 1.3e+09 & 1.4e+09 & \ldots & \ldots & 5.4e+07 & 1.7e+11 & 1.8e+10  \\
150.075070 & 2.450793 & 150.075074 & 2.450787 & 0.942\tablenotemark{G} & 1.57 & 2.56 & 6.9e+08 & 1.0e+09 & \ldots & \ldots & 9.1e+07 & 2.3e+11 & 1.3e+09  \\
150.188810 & 2.321018 & 150.188838 & 2.320997 & 1.000                  & 0.34 & 1.35 & 3.6e+09 & 2.0e+09 & 2.9e+08 & 2.6e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
150.131530 & 2.294352 & 150.131561 & 2.294330 & 1.026\tablenotemark{G} & -1.08 & 0.23 & 1.4e+10 & 1.2e+09 & 3.1e+08 & 1.4e+07 & \ldots & 1.5e+11 & 4.4e+09  \\
150.152270 & 2.219301 & 150.152287 & 2.219311 & 0.927                  & -0.01 & 0.32 & 5.6e+09 & 8.0e+08 & 4.8e+08 & 2.7e+07 & \ldots & 3.8e+11 & 8.2e+09  \\
150.171950 & 2.278365 & 150.171969 & 2.278364 & 0.752\tablenotemark{G} & -0.13 & 0.35 & 1.7e+09 & 2.5e+08 & 7.6e+07 & 8.6e+06 & \ldots & 7.2e+10 & 2.6e+09  \\
150.107370 & 2.329205 & 150.107409 & 2.329204 & 0.924                  & 0.65 & 1.38 & 5.2e+09 & 3.4e+09 & \ldots & \ldots & 1.3e+08 & 2.4e+11 & 6.1e+09  \\
150.064780 & 2.336534 & 150.064830 & 2.336514 & 0.728\tablenotemark{G} & -0.22 & 0.27 & 2.5e+09 & 3.0e+08 & \ldots & \ldots & 6.9e+07 & 4.4e+10 & 1.5e+09  \\
150.062250 & 2.366550 & 150.062272 & 2.366530 & 0.802\tablenotemark{G} & -0.39 & 0.25 & 3.7e+09 & 3.9e+08 & 2.1e+08 & 1.3e+07 & \ldots & 1.5e+11 & 3.7e+09  \\
150.064500 & 2.264089 & 150.064595 & 2.264048 & 1.440\tablenotemark{G} & -0.39 & 0.34 & 9.5e+09 & 4.0e+09 & \ldots & \ldots & 3.0e+08 & 7.4e+11 & 5.5e+10  \\
150.102160 & 2.438384 & 150.102177 & 2.438350 & 1.132\tablenotemark{G} & 1.27 & 0.87 & 2.8e+09 & 2.3e+09 & 7.2e+08 & 1.2e+08 & \ldots & 3.6e+11 & 1.9e+10  \\
150.174710 & 2.360783 & 150.174714 & 2.360774 & 0.900                  & -0.34 & 0.86 & 1.1e+10 & 4.4e+09 & 2.5e+08 & 1.4e+07 & \ldots & 2.4e+11 & 5.8e+08  \\
150.117960 & 2.374386 & 150.117998 & 2.374355 & 1.223\tablenotemark{G} & 0.41 & 0.69 & 3.8e+09 & 1.8e+09 & 4.1e+08 & 2.8e+07 & \ldots & 4.0e+11 & 2.9e+08  \\
150.161460 & 2.320804 & 150.161505 & 2.320777 & 1.336\tablenotemark{G} & 1.32 & 0.63 & 6.9e+08 & 4.9e+08 & 1.8e+08 & 2.2e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
150.099570 & 2.379767 & 150.099593 & 2.379752 & 0.902\tablenotemark{G} & 0.81 & 0.45 & 2.0e+09 & 4.6e+08 & 1.4e+08 & 1.3e+07 & \ldots & 1.2e+11 & 6.9e+09  \\
150.142490 & 2.208299 & 150.142522 & 2.208290 & 0.847                  & -0.85 & 0.53 & 1.1e+10 & 2.4e+09 & 1.3e+08 & 1.6e+07 & \ldots & 8.6e+10 & 5.6e+09  \\
150.070260 & 2.422965 & 150.070271 & 2.422970 & 0.754\tablenotemark{G} & -0.93 & 0.15 & 9.7e+09 & 6.4e+08 & 1.8e+08 & 1.1e+07 & \ldots & 1.1e+11 & 1.0e+10  \\
150.123650 & 2.358258 & 150.123691 & 2.358244 & 0.728                  & -1.00 & 0.08 & 4.1e+10 & 1.5e+09 & 1.2e+09 & 7.0e+07 & \ldots & 3.7e+11 & 2.4e+10  \\
150.152710 & 2.470547 & 150.152748 & 2.470508 & 0.843\tablenotemark{G} & -0.67 & 1.90 & 8.4e+09 & 6.7e+09 & \ldots & \ldots & 1.4e+08 & 1.9e+11 & 7.5e+09  \\
150.152200 & 2.411514 & 150.152224 & 2.411407 & 0.897\tablenotemark{G} & 1.96 & 0.82 & 2.0e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 2.6e+11 & 1.9e+10  \\
150.073580 & 2.346851 & 150.073650 & 2.346819 & 1.353                  & -0.34 & 0.32 & 3.2e+10 & 8.2e+09 & 9.0e+08 & 2.5e+07 & \ldots & 1.4e+12 & 1.4e+11  \\
150.080390 & 2.238965 & 150.080432 & 2.238979 & 0.986\tablenotemark{G} & 1.35 & 1.40 & 2.8e+08 & 2.0e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 1.6e+07  \\
150.081930 & 2.237998 & 150.081964 & 2.237983 & 0.984\tablenotemark{G} & -1.50 & 0.62 & 8.5e+09 & 2.0e+09 & 8.9e+07 & 1.3e+07 & \ldots & 1.3e+11 & 1.1e+10  \\
150.148540 & 2.324634 & 150.148572 & 2.324626 & 0.837                  & 0.85 & 0.41 & 1.6e+09 & 2.9e+08 & 9.0e+07 & 1.2e+07 & \ldots & 1.6e+11 & 5.5e+08  \\
150.167790 & 2.247098 & 150.167779 & 2.247093 & 0.870                  & 0.51 & 0.33 & 3.9e+09 & 6.2e+08 & 3.1e+08 & 1.9e+07 & \ldots & 2.5e+11 & 6.0e+09  \\
150.149530 & 2.233487 & 150.149545 & 2.233485 & 0.731                  & -1.75 & 0.14 & 1.2e+10 & 7.5e+08 & \ldots & \ldots & 9.4e+07 & 1.5e+11 & 1.0e+10  \\
150.154370 & 2.391244 & 150.154402 & 2.391255 & 0.902                  & -0.71 & 1.67 & 2.0e+10 & 1.5e+10 & 2.6e+08 & 2.7e+07 & \ldots & 2.1e+11 & 4.3e+08  \\
150.116920 & 2.386939 & 150.116946 & 2.386924 & 0.940                  & -0.11 & 1.42 & 4.4e+09 & 2.7e+09 & 3.4e+08 & 1.6e+07 & \ldots & 2.6e+11 & 6.7e+09  \\
150.071460 & 2.341721 & 150.071495 & 2.341707 & 0.941\tablenotemark{G} & 1.99 & 1.79 & 3.2e+08 & 3.3e+08 & 9.0e+07 & 1.5e+07 & \ldots & 2.6e+11 & 1.7e+10  \\
150.087520 & 2.404057 & 150.087559 & 2.404051 & 0.748                  & 0.36 & 0.37 & 1.2e+09 & 2.0e+08 & 2.1e+08 & 1.5e+07 & \ldots & 1.6e+11 & 3.6e+09  \\
150.102000 & 2.425978 & 150.102010 & 2.425966 & 0.727                  & 0.48 & 0.14 & 6.4e+09 & 4.1e+08 & 4.8e+08 & 4.3e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
150.097510 & 2.401258 & 150.097538 & 2.401238 & 1.242\tablenotemark{G} & 0.92 & 1.23 & 6.2e+08 & 5.7e+08 & 2.1e+08 & 2.6e+07 & \ldots & 7.3e+11 & 3.2e+10  \\
150.132210 & 2.437227 & 150.132215 & 2.437207 & 0.926\tablenotemark{G} & 0.86 & 1.70 & 2.2e+09 & 1.9e+09 & \ldots & \ldots & 1.4e+08 & 2.6e+11 & 1.3e+10  \\
150.105220 & 2.435001 & 150.105247 & 2.434981 & 0.727                  & 2.22 & 0.30 & 1.0e+09 & 1.4e+08 & \ldots & \ldots & 6.0e+07 & 1.0e+11 & 1.9e+10  \\
150.116700 & 2.265270 & 150.116728 & 2.265269 & 0.756\tablenotemark{G} & 1.00 & 0.40 & 9.7e+08 & 1.7e+08 & \ldots & \ldots & 7.7e+07 & 8.7e+10 & 2.8e+09  \\
150.152130 & 2.444217 & 150.152159 & 2.444192 & 0.981\tablenotemark{G} & -0.63 & 1.05 & 1.3e+10 & 5.4e+09 & 2.6e+08 & 2.9e+07 & \ldots & 2.2e+11 & 1.5e+10  \\
150.107380 & 2.206350 & 150.107397 & 2.206352 & 1.166\tablenotemark{G} & 3.24 & 1.39 & 2.9e+08 & 6.4e+08 & 2.8e+08 & 2.9e+07 & \ldots & 5.7e+11 & 3.4e+10  \\
150.173220 & 2.363148 & 150.173229 & 2.363129 & 0.734\tablenotemark{G} & 1.28 & 0.55 & 5.3e+08 & 1.3e+08 & 7.2e+07 & 7.8e+06 & \ldots & 1.2e+11 & 3.3e+10  \\
150.114380 & 2.221958 & 150.114410 & 2.221948 & 1.230\tablenotemark{G} & -0.35 & 0.74 & 3.2e+09 & 1.2e+09 & \ldots & \ldots & 1.2e+08 & 3.6e+11 & 2.8e+10  \\
150.118560 & 2.223099 & 150.118579 & 2.223095 & 0.845\tablenotemark{G} & 1.33 & 1.79 & 6.4e+08 & 5.3e+08 & 1.1e+08 & 1.3e+07 & \ldots & 4.3e+11 & 5.8e+10  \\
150.136430 & 2.320533 & 150.136464 & 2.320526 & 1.005\tablenotemark{G} & -1.01 & 1.33 & 2.3e+09 & 1.2e+09 & 1.6e+08 & 2.7e+07 & \ldots & 1.7e+11 & 3.7e+09  \\
150.124970 & 2.310285 & 150.125006 & 2.310288 & 0.907\tablenotemark{G} & -0.95 & 0.67 & 1.2e+10 & 3.3e+09 & \ldots & \ldots & 4.9e+08 & 8.1e+10 & 6.1e+07  \\
150.140310 & 2.365965 & 150.140338 & 2.365973 & 0.728                  & -0.32 & 0.22 & 3.8e+09 & 3.7e+08 & \ldots & \ldots & 1.2e+08 & 1.2e+11 & 1.1e+09  \\
150.189650 & 2.316027 & 150.189674 & 2.316022 & 0.759\tablenotemark{G} & -0.22 & 0.31 & 2.2e+09 & 3.0e+08 & 9.6e+07 & 1.8e+07 & \ldots & 9.2e+10 & 5.1e+08  \\
150.101190 & 2.460061 & 150.101191 & 2.460031 & 1.246\tablenotemark{G} & -0.03 & 0.86 & 2.2e+09 & 1.1e+09 & 2.4e+08 & 1.4e+07 & \ldots & 3.3e+11 & 1.5e+09  \\
150.151420 & 2.294050 & 150.151440 & 2.294052 & 0.972\tablenotemark{G} & -0.27 & 0.83 & 3.8e+09 & 1.3e+09 & 1.6e+08 & 1.9e+07 & \ldots & 1.5e+11 & 7.0e+09  \\
150.145470 & 2.293398 & 150.145507 & 2.293397 & 0.881                  & 0.36 & 1.09 & 2.6e+09 & 1.4e+09 & \ldots & \ldots & 6.6e+07 & 1.1e+11 & 4.9e+08  \\
150.074170 & 2.384622 & 150.074210 & 2.384612 & 1.266\tablenotemark{G} & -1.53 & 4.14 & 4.0e+08 & 7.7e+08 & 1.6e+08 & 1.2e+07 & \ldots & 3.9e+11 & 1.6e+10  \\
150.079370 & 2.408439 & 150.079421 & 2.408458 & 0.891                  & -1.25 & 0.30 & 1.0e+10 & 1.3e+09 & 9.9e+07 & 1.8e+07 & \ldots & 1.2e+11 & 6.3e+09  \\
150.173920 & 2.317308 & 150.173946 & 2.317324 & 0.736                  & -0.47 & 0.19 & 5.2e+09 & 4.5e+08 & 1.4e+08 & 1.5e+07 & \ldots & 1.2e+11 & 1.2e+10  \\
150.058980 & 2.301078 & 150.058982 & 2.301089 & 0.734\tablenotemark{G} & 0.59 & 0.40 & 1.1e+09 & 1.9e+08 & 9.4e+07 & 1.6e+07 & \ldots & 9.5e+10 & 1.9e+10  \\
150.160250 & 2.300164 & 150.160269 & 2.300159 & 1.340\tablenotemark{G} & -0.54 & 0.45 & 2.8e+09 & 9.7e+08 & 1.2e+08 & 2.4e+07 & \ldots & 3.2e+11 & 1.0e+10  \\
150.121460 & 2.267281 & 150.121483 & 2.267288 & 0.827                  & -1.50 & 0.58 & 2.8e+10 & 6.8e+09 & 3.5e+08 & 2.7e+07 & \ldots & 7.3e+10 & 3.0e+09  \\
150.137630 & 2.340502 & 150.137613 & 2.340390 & 0.835\tablenotemark{G} & 2.69 & 2.03 & 3.5e+08 & 3.9e+08 & \ldots & \ldots & 4.9e+07 & 8.0e+10 & 3.1e+07  \\
150.167260 & 2.355718 & 150.167275 & 2.355703 & 1.285\tablenotemark{G} & -0.72 & 0.66 & 4.0e+09 & 1.8e+09 & 2.3e+08 & 3.9e+07 & \ldots & 2.5e+11 & 1.6e+10  \\
150.185690 & 2.222366 & 150.185690 & 2.222358 & 1.218\tablenotemark{G} & -0.12 & 0.37 & 8.4e+09 & 1.8e+09 & 4.7e+08 & 1.6e+07 & \ldots & 2.1e+11 & 5.7e+08  \\
150.155170 & 2.405678 & 150.155234 & 2.405743 & 0.899\tablenotemark{G} & 2.31 & 2.33 & 1.0e+08 & 1.7e+08 & \ldots & \ldots & 5.8e+07 & 1.3e+11 & 3.9e+09  \\
150.055920 & 2.233462 & 150.055985 & 2.233450 & 0.938                  & 0.14 & 0.28 & 1.2e+10 & 1.5e+09 & 3.8e+08 & 3.5e+07 & \ldots & 1.2e+12 & 9.1e+10  \\
150.118520 & 2.415591 & 150.118543 & 2.415571 & 0.837                  & -1.77 & 0.18 & 6.5e+10 & 5.0e+09 & 5.6e+08 & 2.7e+07 & \ldots & 1.4e+11 & 2.8e+09  \\
150.144420 & 2.415904 & 150.144400 & 2.415861 & 0.960\tablenotemark{G} & 0.01 & 1.05 & 3.3e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.9e+11 & 8.4e+09  \\
150.126370 & 2.432899 & 150.126391 & 2.432867 & 1.277\tablenotemark{G} & 1.38 & 0.50 & 2.6e+09 & 1.6e+09 & 8.8e+08 & 3.9e+07 & \ldots & 1.0e+12 & 3.4e+10  \\
150.081880 & 2.281767 & 150.081940 & 2.281754 & 0.736\tablenotemark{G} & -0.97 & 0.44 & 1.3e+09 & 2.5e+08 & 9.3e+07 & 1.7e+07 & \ldots & 9.8e+10 & 5.8e+07  \\
150.100450 & 2.308010 & 150.100488 & 2.308021 & 0.950                  & -1.00 & 1.27 & 1.7e+10 & 8.5e+09 & 2.0e+08 & 3.5e+07 & \ldots & 1.6e+11 & 1.7e+09  \\
150.136100 & 2.370533 & 150.136112 & 2.370532 & 0.927                  & 2.39 & 1.46 & 7.4e+08 & 6.9e+08 & 1.9e+08 & 2.0e+07 & \ldots & 7.4e+11 & 7.0e+10  \\
150.169140 & 2.233916 & 150.169152 & 2.233893 & 1.233\tablenotemark{G} & -0.80 & 0.43 & 1.5e+10 & 3.1e+09 & 3.4e+08 & 3.2e+07 & \ldots & 2.3e+11 & 3.7e+08  \\
150.108520 & 2.448166 & 150.108523 & 2.448100 & 1.413\tablenotemark{G} & 1.93 & 0.90 & 2.8e+08 & 7.7e+08 & 2.0e+08 & 3.1e+07 & \ldots & 4.6e+11 & 1.1e+10  \\
150.112240 & 2.387377 & 150.112284 & 2.387391 & 0.757                  & 0.81 & 0.25 & 2.2e+09 & 2.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.3e+11 & 1.3e+10  \\
150.103890 & 2.334655 & 150.103898 & 2.334752 & 0.940\tablenotemark{G} & -0.23 & 1.65 & 1.5e+09 & 1.1e+09 & 6.6e+07 & 8.3e+06 & \ldots & 1.8e+11 & 6.1e+09  \\
150.190930 & 2.235499 & 150.190865 & 2.235393 & 0.864                  & -0.74 & 0.82 & 5.2e+09 & 1.9e+09 & 1.2e+08 & 1.3e+07 & \ldots & 9.5e+10 & 3.3e+08  \\
150.128850 & 2.193221 & 150.128858 & 2.193227 & 0.878                  & 1.31 & 1.27 & 2.4e+09 & 1.6e+09 & \ldots & \ldots & 9.8e+07 & 1.5e+11 & 5.9e+09  \\
150.128430 & 2.419489 & 150.128447 & 2.419440 & 0.741                  & -0.96 & 0.15 & 9.9e+09 & 6.8e+08 & 2.3e+08 & 2.0e+07 & \ldots & 9.8e+10 & 4.8e+08  \\
150.170690 & 2.219165 & 150.170738 & 2.219240 & 0.958                  & 0.13 & 0.85 & 5.8e+09 & 2.1e+09 & \ldots & \ldots & 3.0e+08 & 2.0e+11 & 4.7e+09  \\
150.192700 & 2.333416 & 150.192737 & 2.333482 & 1.081\tablenotemark{G} & 0.21 & 0.66 & 1.8e+09 & 7.8e+08 & \ldots & \ldots & 9.2e+07 & 1.3e+11 & 2.2e+08  \\
150.159290 & 2.235417 & 150.159296 & 2.235413 & 0.932\tablenotemark{G} & -0.31 & 1.31 & 3.6e+09 & 2.0e+09 & \ldots & \ldots & 6.1e+07 & 1.4e+11 & 1.6e+10  \\
150.130870 & 2.215121 & 150.130875 & 2.215134 & 0.859\tablenotemark{G} & 1.60 & 2.49 & 3.9e+08 & 5.8e+08 & \ldots & \ldots & 5.2e+07 & 2.1e+11 & 5.4e+09  \\
150.110190 & 2.208473 & 150.110230 & 2.208474 & 1.249                  & -0.51 & 0.44 & 1.6e+10 & 3.6e+09 & 3.2e+08 & 4.1e+07 & \ldots & 2.5e+11 & 1.8e+08  \\
150.109680 & 2.295734 & 150.109712 & 2.295693 & 1.325\tablenotemark{G} & -0.87 & 0.28 & 7.8e+09 & 1.7e+09 & 2.1e+08 & 3.0e+07 & \ldots & 3.7e+11 & 1.0e+10  \\
150.172490 & 2.233643 & 150.172484 & 2.233629 & 0.925                  & -0.24 & 0.93 & 4.1e+09 & 1.7e+09 & 1.5e+08 & 1.7e+07 & \ldots & 1.5e+11 & 5.8e+09  \\
150.094580 & 2.336367 & 150.094624 & 2.336350 & 0.910                  & 2.72 & 1.52 & 4.2e+08 & 4.3e+08 & 2.2e+08 & 1.5e+07 & \ldots & 5.4e+11 & 5.0e+10  \\
150.083340 & 2.278458 & 150.083386 & 2.278446 & 0.837\tablenotemark{G} & 0.79 & 0.93 & 4.1e+08 & 1.7e+08 & 1.2e+08 & 1.0e+07 & \ldots & 2.6e+11 & 7.5e+09  \\
150.114740 & 2.262723 & 150.114781 & 2.262725 & 0.750\tablenotemark{G} & -0.47 & 0.23 & 3.6e+09 & 3.7e+08 & 1.4e+08 & 1.4e+07 & \ldots & 7.8e+10 & 4.4e+09  \\
150.172610 & 2.353894 & 150.172626 & 2.353883 & 0.757\tablenotemark{G} & 1.75 & 0.43 & 7.3e+08 & 1.4e+08 & 2.2e+08 & 3.4e+07 & \ldots & 4.6e+11 & 2.6e+10  \\
150.067170 & 2.377246 & 150.067215 & 2.377236 & 0.804\tablenotemark{G} & -0.69 & 0.37 & 2.2e+09 & 3.4e+08 & 1.9e+08 & 9.6e+06 & \ldots & 1.6e+11 & 3.8e+09  \\
150.118240 & 2.292143 & 150.118290 & 2.292122 & 1.103                  & 0.07 & 0.47 & 1.1e+10 & 3.0e+09 & 2.8e+08 & 2.6e+07 & \ldots & 3.5e+11 & 1.5e+10  \\
150.103510 & 2.346108 & 150.103512 & 2.346125 & 1.031                  & -0.46 & 1.78 & 1.6e+10 & 1.1e+10 & 9.9e+08 & 8.5e+07 & \ldots & 6.8e+11 & 4.3e+09  \\
150.117520 & 2.285153 & 150.117534 & 2.285159 & 0.921\tablenotemark{G} & -0.88 & 0.95 & 2.7e+09 & 1.1e+09 & 9.7e+07 & 1.5e+07 & \ldots & 9.7e+10 & 1.4e+10  \\
150.165510 & 2.246267 & 150.165496 & 2.246271 & 0.870                  & -1.30 & 0.53 & 1.1e+10 & 2.4e+09 & 1.7e+08 & 2.4e+07 & \ldots & 1.0e+11 & 1.0e+10  \\
150.164850 & 2.354424 & 150.164879 & 2.354407 & 1.263\tablenotemark{G} & -0.06 & 0.39 & 5.5e+09 & 1.8e+09 & 4.9e+08 & 2.6e+07 & \ldots & 3.9e+11 & 5.7e+10  \\
150.082600 & 2.366448 & 150.082676 & 2.366546 & 1.208\tablenotemark{G} & -0.54 & 0.81 & 4.1e+09 & 1.7e+09 & \ldots & \ldots & 7.2e+07 & 1.6e+11 & 1.4e+08  \\
150.085750 & 2.297658 & 150.085794 & 2.297659 & 1.254\tablenotemark{G} & 0.01 & 0.19 & 2.4e+10 & 3.9e+09 & 2.1e+09 & 8.3e+07 & \ldots & 2.0e+12 & 9.4e+10  \\
150.114050 & 2.353890 & 150.114076 & 2.353853 & 1.100\tablenotemark{G} & 5.49 & 1.05 & 7.7e+08 & 2.7e+09 & 1.9e+08 & 1.6e+07 & \ldots & 3.3e+11 & 3.3e+09  \\
150.063620 & 2.254643 & 150.063636 & 2.254647 & 1.087\tablenotemark{G} & -0.48 & 0.41 & 7.0e+09 & 1.6e+09 & 2.1e+08 & 1.3e+07 & \ldots & 1.0e+11 & 8.4e+07  \\
150.135490 & 2.245705 & 150.135500 & 2.245705 & 0.907                  & 0.54 & 1.32 & 3.0e+09 & 1.9e+09 & 2.8e+08 & 4.4e+07 & \ldots & 3.2e+11 & 5.5e+09  \\
150.097230 & 2.302491 & 150.097290 & 2.302497 & 1.462\tablenotemark{G} & -0.26 & 0.30 & 4.1e+09 & 2.0e+09 & 4.3e+08 & 4.0e+07 & \ldots & 5.6e+11 & 1.5e+08  \\
150.144750 & 2.334391 & 150.144778 & 2.334385 & 0.861\tablenotemark{G} & 1.24 & 0.30 & 1.8e+09 & 2.9e+08 & 2.7e+08 & 2.3e+07 & \ldots & 2.1e+11 & 3.2e+10  \\
150.073480 & 2.226387 & 150.073503 & 2.226385 & 1.040                  & -0.57 & 1.37 & 1.3e+10 & 6.6e+09 & \ldots & \ldots & 1.0e+09 & 3.8e+11 & 1.8e+10  \\
150.187670 & 2.344660 & 150.187630 & 2.344672 & 1.302\tablenotemark{G} & -1.43 & 0.29 & 1.0e+10 & 1.5e+09 & 3.3e+08 & 1.8e+07 & \ldots & 3.5e+11 & 2.1e+08  \\
150.101470 & 2.278431 & 150.101499 & 2.278435 & 0.755                  & -1.71 & 0.16 & 8.8e+09 & 6.2e+08 & \ldots & \ldots & 6.8e+07 & 1.0e+11 & 4.1e+09  \\
150.148310 & 2.367414 & 150.148341 & 2.367409 & 1.429\tablenotemark{G} & -0.20 & 0.25 & 4.3e+09 & 1.3e+09 & 3.8e+08 & 4.1e+07 & \ldots & 4.5e+11 & 8.4e+10  \\
150.143560 & 2.268420 & 150.143583 & 2.268431 & 0.886\tablenotemark{G} & 1.53 & 1.26 & 8.9e+08 & 6.2e+08 & 1.9e+08 & 1.7e+07 & \ldots & 2.4e+11 & 6.2e+09  \\
150.141210 & 2.272969 & 150.141229 & 2.272974 & 0.942\tablenotemark{G} & -0.24 & 0.86 & 4.1e+09 & 1.5e+09 & 2.4e+08 & 8.3e+06 & \ldots & 1.4e+11 & 8.3e+08  \\
150.077410 & 2.437059 & 150.077456 & 2.437006 & 0.897\tablenotemark{G} & 1.70 & 3.08 & 3.3e+08 & 5.9e+08 & 7.7e+07 & 1.3e+07 & \ldots & 8.9e+10 & 7.9e+07  \\
150.148070 & 2.331341 & 150.148097 & 2.331332 & 0.856\tablenotemark{G} & 1.99 & 1.17 & 6.8e+08 & 4.9e+08 & 1.7e+08 & 1.8e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
150.153930 & 2.276188 & 150.153960 & 2.276199 & 1.215\tablenotemark{G} & 0.45 & 0.63 & 6.7e+09 & 2.6e+09 & 4.7e+08 & 4.7e+07 & \ldots & 3.3e+11 & 1.1e+10  \\
150.069910 & 2.295822 & 150.069951 & 2.295813 & 0.731                  & -0.57 & 0.41 & 1.5e+09 & 2.6e+08 & \ldots & \ldots & 7.3e+07 & 9.7e+10 & 1.9e+09  \\
150.087940 & 2.326192 & 150.087979 & 2.326153 & 0.939\tablenotemark{G} & -0.12 & 0.62 & 7.9e+09 & 2.1e+09 & 2.7e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.2e+06  \\
150.130570 & 2.361473 & 150.130581 & 2.361458 & 1.410\tablenotemark{G} & 0.19 & 0.10 & 9.4e+09 & 1.5e+09 & 3.2e+08 & 4.0e+07 & \ldots & 5.5e+11 & 4.2e+10  \\
150.177530 & 2.261224 & 150.177536 & 2.261222 & 0.879                  & -1.50 & 0.39 & 1.8e+10 & 2.9e+09 & 1.5e+08 & 1.8e+07 & \ldots & 9.0e+10 & 1.0e+09  \\
150.176210 & 2.264468 & 150.176229 & 2.264448 & 1.008\tablenotemark{G} & -0.78 & 0.59 & 6.7e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.8e+11 & 4.6e+07  \\
150.145010 & 2.336923 & 150.145032 & 2.336921 & 0.937                  & 0.06 & 1.66 & 7.4e+09 & 5.4e+09 & 2.9e+08 & 5.7e+07 & \ldots & 2.9e+11 & 4.2e+07  \\
150.088740 & 2.252818 & 150.088796 & 2.252822 & 0.728                  & 1.71 & 0.58 & 3.3e+08 & 8.7e+07 & \ldots & \ldots & 5.3e+07 & 1.3e+11 & 6.2e+09  \\
150.139590 & 2.407071 & 150.139609 & 2.407059 & 0.901                  & 0.62 & 0.80 & 2.1e+09 & 8.2e+08 & 1.3e+08 & 2.1e+07 & \ldots & 1.2e+11 & 4.5e+09  \\
150.143610 & 2.439931 & 150.143607 & 2.439900 & 1.150\tablenotemark{G} & 0.24 & 1.30 & 9.9e+08 & 9.7e+08 & \ldots & \ldots & 9.6e+07 & 3.0e+11 & 1.6e+10  \\
150.169510 & 2.262296 & 150.169517 & 2.262296 & 1.106\tablenotemark{G} & 0.01 & 1.21 & 1.8e+09 & 1.3e+09 & 2.0e+08 & 1.6e+07 & \ldots & 2.1e+11 & 2.0e+08  \\
150.079250 & 2.448390 & 150.079318 & 2.448336 & 1.401\tablenotemark{G} & -1.05 & 0.14 & 2.2e+10 & 3.2e+09 & 1.5e+08 & 2.7e+07 & \ldots & 2.9e+11 & 2.4e+08  \\
150.108410 & 2.214345 & 150.108425 & 2.214340 & 0.986\tablenotemark{G} & -0.88 & 1.34 & 6.0e+09 & 3.2e+09 & 2.0e+08 & 1.9e+07 & \ldots & 2.0e+11 & 2.5e+08  \\
150.157770 & 2.329275 & 150.157817 & 2.329266 & 0.905\tablenotemark{G} & 0.32 & 1.43 & 2.1e+09 & 1.4e+09 & \ldots & \ldots & 6.8e+07 & 3.6e+11 & 1.4e+10  \\
150.153430 & 2.443099 & 150.153473 & 2.443077 & 0.901\tablenotemark{G} & -0.03 & 0.54 & 1.1e+10 & 2.7e+09 & 1.1e+08 & 1.8e+07 & \ldots & 4.6e+11 & 7.8e+10  \\
150.075630 & 2.387739 & 150.075652 & 2.387737 & 1.264\tablenotemark{G} & -0.90 & 0.84 & 3.8e+09 & 2.0e+09 & 3.1e+08 & 2.5e+07 & \ldots & 3.9e+11 & 7.9e+07  \\
150.090770 & 2.413311 & 150.090791 & 2.413293 & 0.732\tablenotemark{G} & 0.22 & 0.21 & 3.7e+09 & 3.5e+08 & 2.7e+08 & 2.8e+07 & \ldots & 1.3e+11 & 1.7e+10  \\
150.147550 & 2.472620 & 150.147578 & 2.472604 & 0.900\tablenotemark{G} & 0.70 & 0.92 & 3.7e+09 & 1.7e+09 & 2.5e+08 & 2.3e+07 & \ldots & 3.0e+11 & 4.2e+10  \\
150.105770 & 2.380248 & 150.105812 & 2.380245 & 0.916\tablenotemark{G} & -0.43 & 1.07 & 1.9e+10 & 8.9e+09 & 6.0e+08 & 3.8e+07 & \ldots & 5.0e+11 & 2.3e+10  \\
150.115000 & 2.380963 & 150.115038 & 2.380956 & 1.137                  & 0.49 & 0.57 & 6.2e+09 & 2.4e+09 & 3.4e+08 & 4.1e+07 & \ldots & 2.7e+11 & 3.2e+09  \\
150.133530 & 2.261941 & 150.133542 & 2.261944 & 0.751                  & -0.78 & 0.18 & 6.1e+09 & 4.8e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 2.1e+10  \\
150.130290 & 2.259621 & 150.130309 & 2.259626 & 0.749                  & -1.00 & 0.30 & 2.3e+09 & 3.0e+08 & \ldots & \ldots & 5.9e+07 & 9.0e+10 & 5.4e+09  \\
150.127840 & 2.277855 & 150.127861 & 2.277863 & 0.930\tablenotemark{G} & -0.51 & 0.38 & 4.1e+09 & 6.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 9.8e+10 & 9.8e+09  \\
150.110260 & 2.193960 & 150.110268 & 2.193980 & 1.159                  & 1.18 & 0.97 & 2.4e+09 & 1.7e+09 & 2.3e+08 & 3.3e+07 & \ldots & 4.5e+11 & 7.0e+10  \\
150.098190 & 2.414925 & 150.098213 & 2.414914 & 0.841\tablenotemark{G} & -0.19 & 1.87 & 2.5e+09 & 2.0e+09 & 1.0e+08 & 1.1e+07 & \ldots & 1.2e+11 & 1.7e+08  \\
150.079710 & 2.295934 & 150.079746 & 2.295947 & 1.101\tablenotemark{G} & -0.18 & 0.44 & 1.0e+10 & 2.6e+09 & 3.7e+08 & 1.5e+07 & \ldots & 2.1e+11 & 3.5e+08  \\
150.179060 & 2.364153 & 150.179074 & 2.364139 & 1.343                  & 0.31 & 0.18 & 1.4e+10 & 2.2e+09 & 8.6e+08 & 4.7e+07 & \ldots & 7.3e+11 & 2.6e+10  \\
150.075420 & 2.336254 & 150.075468 & 2.336257 & 0.853                  & 1.97 & 1.29 & 4.9e+08 & 4.0e+08 & \ldots & \ldots & 6.6e+07 & 1.0e+11 & 4.3e+08  \\
150.104260 & 2.440705 & 150.104283 & 2.440684 & 0.753\tablenotemark{G} & -0.56 & 0.80 & 5.7e+08 & 2.0e+08 & 7.6e+07 & 1.2e+07 & \ldots & 1.9e+11 & 1.7e+09  \\
150.105960 & 2.213144 & 150.105985 & 2.213151 & 0.925                  & 0.31 & 1.19 & 3.7e+09 & 2.0e+09 & 2.7e+08 & 3.0e+07 & \ldots & 2.9e+11 & 1.5e+10  \\
150.067460 & 2.223537 & 150.067493 & 2.223542 & 0.723                  & 0.47 & 0.17 & 5.7e+09 & 4.2e+08 & 3.8e+08 & 2.7e+07 & \ldots & 2.1e+11 & 1.1e+10  \\
\cutinhead{UDS}
34.289417 & -5.164467 & 34.289461 & -5.164426 & 0.904\tablenotemark{G} & 0.44 & 0.75 & 4.5e+08 & 1.3e+08 & 1.3e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
34.483398 & -5.219781 & 34.483412 & -5.219763 & 0.740\tablenotemark{G} & 0.67 & 0.07 & 2.8e+09 & 9.3e+07 & 1.1e+08 & 2.0e+07 & \ldots & 9.6e+10 & 6.5e+09  \\
34.463700 & -5.230395 & 34.463706 & -5.230378 & 1.279\tablenotemark{G} & -0.46 & 0.26 & 3.1e+09 & 5.7e+08 & 2.7e+08 & 2.0e+07 & \ldots & 4.9e+11 & 2.5e+10  \\
34.241451 & -5.157997 & 34.241492 & -5.157975 & 0.855                  & 0.62 & 0.04 & 7.0e+09 & 1.2e+08 & 5.0e+08 & 2.5e+07 & \ldots & 2.8e+11 & 7.1e+09  \\
34.370277 & -5.246929 & 34.370288 & -5.246901 & 0.922\tablenotemark{G} & 0.52 & 0.12 & 3.1e+09 & 1.4e+08 & 2.8e+08 & 1.4e+07 & \ldots & 4.7e+11 & 2.4e+09  \\
34.286585 & -5.237958 & 34.286618 & -5.237961 & 1.277\tablenotemark{G} & 0.41 & 0.13 & 1.2e+09 & 1.3e+08 & 4.3e+08 & 1.6e+07 & \ldots & 1.1e+12 & 1.6e+10  \\
34.315356 & -5.232962 & 34.315373 & -5.232970 & 1.415\tablenotemark{G} & 1.16 & 1.01 & 6.0e+08 & 5.8e+08 & 4.3e+08 & 3.4e+07 & \ldots & 1.0e+12 & 8.4e+10  \\
34.480474 & -5.247719 & 34.480410 & -5.247806 & 1.469\tablenotemark{G} & 0.48 & 1.42 & 2.0e+09 & 1.9e+09 & 4.4e+08 & 6.6e+07 & \ldots & 7.8e+11 & 1.7e+10  \\
34.325410 & -5.199980 & 34.325420 & -5.199968 & 1.095\tablenotemark{G} & 0.15 & 0.20 & 6.8e+09 & 7.1e+08 & 2.9e+08 & 2.9e+07 & \ldots & 2.9e+11 & 1.9e+10  \\
34.334096 & -5.237701 & 34.334103 & -5.237683 & 0.920                  & 1.88 & 0.51 & 5.0e+08 & 9.5e+07 & 9.1e+07 & 9.4e+06 & \ldots & 1.5e+11 & 9.6e+09  \\
34.435496 & -5.152846 & 34.435522 & -5.152819 & 0.801                  & 2.25 & 0.14 & 1.2e+09 & 7.4e+07 & \ldots & \ldots & 1.5e+08 & 3.5e+11 & 3.9e+10  \\
34.332435 & -5.212034 & 34.332461 & -5.212009 & 1.378\tablenotemark{G} & 0.11 & 0.31 & 6.0e+09 & 1.4e+09 & 4.2e+08 & 2.5e+07 & \ldots & 4.7e+11 & 2.7e+09  \\
34.325370 & -5.223768 & 34.325374 & -5.223737 & 1.415\tablenotemark{G} & 0.28 & 1.42 & 8.3e+08 & 8.0e+08 & 1.3e+08 & 2.1e+07 & \ldots & 8.3e+11 & 3.8e+10  \\
34.368704 & -5.157358 & 34.368684 & -5.157395 & 0.835\tablenotemark{G} & 2.44 & 0.52 & 2.8e+08 & 5.9e+07 & 6.4e+07 & 1.0e+07 & \ldots & 1.4e+11 & 8.3e+09  \\
34.574970 & -5.161715 & 34.574958 & -5.161686 & 1.195\tablenotemark{G} & -0.60 & 0.14 & 2.1e+10 & 1.3e+09 & 6.8e+08 & 2.9e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
34.374753 & -5.227548 & 34.374772 & -5.227530 & 1.429\tablenotemark{G} & -0.15 & 0.32 & 1.1e+10 & 1.9e+09 & 5.8e+08 & 3.7e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
34.435733 & -5.231665 & 34.435744 & -5.231653 & 0.914                  & -0.05 & 0.08 & 6.2e+09 & 1.8e+08 & \ldots & \ldots & 9.4e+07 & 2.3e+11 & 7.4e+09  \\
34.231824 & -5.253116 & 34.231825 & -5.253016 & 0.823\tablenotemark{G} & 0.64 & 0.06 & 3.9e+09 & 9.1e+07 & 3.5e+08 & 1.4e+07 & \ldots & 3.4e+11 & 3.4e+09  \\
34.457636 & -5.164808 & 34.457656 & -5.164792 & 0.916\tablenotemark{G} & -0.32 & 0.04 & 1.3e+10 & 2.1e+08 & \ldots & \ldots & 6.1e+08 & 3.6e+11 & 2.8e+09  \\
34.375611 & -5.204026 & 34.375625 & -5.204000 & 0.915                  & -0.25 & 0.08 & 6.1e+09 & 1.8e+08 & \ldots & \ldots & 6.3e+07 & 1.8e+11 & 3.4e+09  \\
34.359199 & -5.257633 & 34.359225 & -5.257605 & 0.803                  & 0.11 & 0.06 & 5.6e+09 & 1.3e+08 & \ldots & \ldots & 2.3e+08 & 8.9e+10 & 8.1e+09  \\
34.250598 & -5.162615 & 34.250537 & -5.162659 & 0.829\tablenotemark{G} & -0.12 & 0.04 & 8.8e+09 & 1.4e+08 & 2.8e+08 & 2.8e+07 & \ldots & 1.4e+11 & 7.1e+08  \\
34.457290 & -5.229210 & 34.457293 & -5.229258 & 0.929\tablenotemark{G} & -0.11 & 0.12 & 3.7e+09 & 1.6e+08 & 1.9e+08 & 1.3e+07 & \ldots & 1.9e+11 & 9.5e+09  \\
34.268269 & -5.151559 & 34.268324 & -5.151551 & 1.012                  & -0.35 & 0.13 & 4.2e+09 & 1.7e+08 & 3.7e+08 & 1.8e+07 & \ldots & 3.8e+11 & 6.1e+09  \\
34.369105 & -5.172428 & 34.369137 & -5.172404 & 0.825                  & 0.96 & 0.05 & 4.4e+09 & 9.9e+07 & 2.4e+08 & 1.7e+07 & \ldots & 1.6e+11 & 8.4e+09  \\
34.481139 & -5.174353 & 34.481147 & -5.174333 & 1.275\tablenotemark{G} & 0.32 & 0.38 & 3.7e+09 & 1.0e+09 & 6.5e+08 & 1.7e+07 & \ldots & 1.2e+12 & 2.9e+10  \\
34.444958 & -5.168239 & 34.444949 & -5.168229 & 1.417                  & -0.63 & 0.41 & 2.0e+10 & 4.4e+09 & 7.5e+08 & 5.5e+07 & \ldots & 8.3e+11 & 6.9e+10  \\
34.377887 & -5.179532 & 34.377976 & -5.179501 & 1.270\tablenotemark{G} & 1.29 & 0.04 & 6.8e+08 & 1.6e+07 & 2.3e+08 & 1.7e+07 & \ldots & 6.3e+11 & 2.5e+10  \\
34.246973 & -5.265455 & 34.246992 & -5.265421 & 1.420\tablenotemark{G} & 0.96 & 0.80 & 7.6e+08 & 4.4e+08 & 4.6e+08 & 3.9e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
34.347189 & -5.175795 & 34.347225 & -5.175778 & 1.428\tablenotemark{G} & -0.58 & 0.47 & 1.0e+10 & 2.9e+09 & 4.7e+08 & 6.5e+07 & \ldots & 7.3e+11 & 3.6e+10  \\
34.318401 & -5.229057 & 34.318417 & -5.229052 & 1.035\tablenotemark{G} & 0.49 & 0.42 & 1.3e+09 & 1.8e+08 & 1.6e+08 & 1.6e+07 & \ldots & 2.2e+11 & 1.3e+10  \\
34.375082 & -5.164786 & 34.375134 & -5.164736 & 1.089\tablenotemark{G} & 0.93 & 0.52 & 2.3e+09 & 7.8e+08 & \ldots & \ldots & 7.2e+07 & 3.7e+11 & 1.9e+10  \\
34.358432 & -5.175677 & 34.358447 & -5.175662 & 1.431\tablenotemark{G} & -0.98 & 0.35 & 1.5e+10 & 2.7e+09 & 8.2e+08 & 7.5e+07 & \ldots & 9.7e+11 & 7.8e+10  \\
34.255834 & -5.167369 & 34.255891 & -5.167354 & 1.090\tablenotemark{G} & 0.01 & 0.43 & 4.5e+09 & 9.7e+08 & 2.1e+08 & 2.7e+07 & \ldots & 4.2e+11 & 4.5e+10  \\
34.322860 & -5.167645 & 34.322906 & -5.167608 & 1.030                  & 1.30 & 0.11 & 5.0e+09 & 1.8e+08 & 6.5e+08 & 2.2e+07 & \ldots & 9.7e+11 & 1.5e+10  \\
34.399563 & -5.224797 & 34.399633 & -5.224808 & 1.097\tablenotemark{G} & -0.73 & 0.04 & 1.8e+10 & 3.1e+08 & 3.2e+08 & 1.3e+07 & \ldots & 1.7e+11 & 1.9e+10  \\
34.401748 & -5.153146 & 34.401803 & -5.153117 & 1.091\tablenotemark{G} & 1.55 & 0.47 & 6.4e+08 & 2.3e+08 & 1.6e+08 & 1.1e+07 & \ldots & 2.6e+11 & 9.8e+09  \\
34.486134 & -5.254569 & 34.486173 & -5.254550 & 0.947\tablenotemark{G} & 0.53 & 0.22 & 2.2e+09 & 1.7e+08 & 1.4e+08 & 2.1e+07 & \ldots & 3.8e+11 & 1.7e+10  \\
34.444281 & -5.248412 & 34.444279 & -5.248374 & 1.091\tablenotemark{G} & 1.39 & 0.14 & 8.3e+08 & 8.3e+07 & 1.0e+08 & 1.1e+07 & \ldots & 2.1e+11 & 1.5e+10  \\
34.435300 & -5.158785 & 34.435317 & -5.158755 & 1.326\tablenotemark{G} & -0.95 & 0.34 & 1.0e+10 & 2.0e+09 & 4.1e+08 & 3.6e+07 & \ldots & 4.0e+11 & 3.0e+10  \\
34.236833 & -5.197802 & 34.236869 & -5.197786 & 0.790\tablenotemark{G} & 5.96 & 2.43 & 1.3e+07 & 1.5e+07 & 5.0e+07 & 7.0e+06 & \ldots & 9.5e+10 & 5.4e+09  \\
34.486535 & -5.240308 & 34.486568 & -5.240289 & 1.305\tablenotemark{G} & -0.64 & 0.24 & 3.2e+09 & 4.1e+08 & 2.2e+08 & 3.8e+07 & \ldots & 6.3e+11 & 6.5e+10  \\
34.235814 & -5.168167 & 34.235951 & -5.168147 & 1.264\tablenotemark{G} & -1.14 & 0.06 & 1.9e+10 & 4.1e+08 & 5.7e+08 & 3.0e+07 & \ldots & 4.2e+12 & 6.2e+11  \\
34.407596 & -5.239813 & 34.407597 & -5.239785 & 0.752                  & 2.04 & 0.14 & 8.6e+08 & 5.7e+07 & 8.3e+07 & 1.5e+07 & \ldots & 1.2e+11 & 4.8e+08  \\
34.440375 & -5.240249 & 34.440380 & -5.240216 & 1.041\tablenotemark{G} & 1.16 & 0.71 & 6.2e+08 & 1.4e+08 & 9.9e+07 & 1.1e+07 & \ldots & 2.7e+11 & 1.2e+10  \\
34.581318 & -5.178201 & 34.581313 & -5.178152 & 1.046\tablenotemark{G} & -0.65 & 0.07 & 1.0e+10 & 1.9e+08 & 2.9e+08 & 2.2e+07 & \ldots & 1.6e+11 & 1.4e+10  \\
34.338810 & -5.191348 & 34.338853 & -5.191342 & 0.932\tablenotemark{G} & 1.82 & 0.48 & 6.5e+08 & 1.1e+08 & 1.2e+08 & 1.3e+07 & \ldots & 2.9e+11 & 4.1e+09  \\
34.337205 & -5.214391 & 34.337215 & -5.214334 & 0.920\tablenotemark{G} & 1.06 & 0.50 & 5.7e+08 & 1.0e+08 & 7.6e+07 & 1.1e+07 & \ldots & 1.1e+11 & 1.6e+10  \\
34.291195 & -5.191481 & 34.291192 & -5.191474 & 0.825\tablenotemark{G} & 6.82 & 3.02 & 1.3e+07 & 1.7e+07 & \ldots & \ldots & 3.5e+07 & 1.3e+11 & 1.2e+10  \\
34.327458 & -5.197280 & 34.327395 & -5.197192 & 1.141\tablenotemark{G} & -0.63 & 0.10 & 1.2e+10 & 5.6e+08 & 1.8e+08 & 1.8e+07 & \ldots & 2.0e+11 & 2.5e+10  \\
34.246650 & -5.238097 & 34.246662 & -5.238100 & 0.809                  & -0.97 & 0.04 & 8.9e+09 & 1.3e+08 & 1.9e+08 & 1.3e+07 & \ldots & 9.9e+10 & 8.4e+09  \\
34.425930 & -5.174296 & 34.425949 & -5.174306 & 1.158\tablenotemark{G} & 0.38 & 0.34 & 2.0e+09 & 3.8e+08 & 6.3e+07 & 1.2e+07 & \ldots & 2.4e+11 & 2.1e+10  \\
34.441478 & -5.203516 & 34.441496 & -5.203515 & 1.064\tablenotemark{G} & -0.86 & 0.94 & 7.9e+08 & 2.1e+08 & 9.9e+07 & 1.4e+07 & \ldots & 2.7e+11 & 8.5e+09  \\
34.417250 & -5.220560 & 34.417268 & -5.220544 & 0.749\tablenotemark{G} & -0.08 & 0.04 & 5.2e+09 & 1.1e+08 & 1.1e+08 & 1.1e+07 & \ldots & 4.6e+10 & 1.0e+10  \\
34.303624 & -5.187742 & 34.303640 & -5.187698 & 0.995\tablenotemark{G} & -1.24 & 0.13 & 4.8e+09 & 2.0e+08 & 1.5e+08 & 1.3e+07 & \ldots & 2.1e+11 & 3.0e+10  \\
34.338168 & -5.206715 & 34.338190 & -5.206671 & 0.922                  & 2.68 & 0.20 & 1.4e+09 & 1.1e+08 & \ldots & \ldots & 8.2e+07 & 2.8e+11 & 7.2e+09  \\
34.316711 & -5.166855 & 34.316746 & -5.166812 & 1.040\tablenotemark{G} & 2.41 & 2.45 & 1.5e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 2.0e+09  \\
34.479187 & -5.233651 & 34.479221 & -5.233645 & 1.312\tablenotemark{G} & 0.77 & 0.31 & 1.7e+10 & 3.6e+09 & 1.3e+09 & 6.2e+07 & \ldots & 1.1e+12 & 1.0e+11  \\
34.464574 & -5.205369 & 34.464597 & -5.205359 & 1.268\tablenotemark{G} & 0.20 & 0.38 & 2.3e+09 & 4.6e+08 & 5.2e+08 & 1.8e+07 & \ldots & 7.0e+11 & 2.0e+10  \\
34.306728 & -5.161120 & 34.306745 & -5.161058 & 1.454                  & 0.26 & 0.43 & 9.5e+09 & 2.5e+09 & 1.5e+09 & 6.3e+07 & \ldots & 2.8e+12 & 1.6e+11  \\
34.473469 & -5.202807 & 34.473484 & -5.202784 & 1.011\tablenotemark{G} & 0.84 & 0.23 & 1.9e+09 & 1.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.1e+11 & 7.0e+09  \\
34.361009 & -5.189687 & 34.361031 & -5.189685 & 1.344\tablenotemark{G} & -1.00 & 0.37 & 8.1e+09 & 1.6e+09 & 2.2e+08 & 2.2e+07 & \ldots & 4.9e+11 & 5.5e+10  \\
34.262690 & -5.198416 & 34.262708 & -5.198400 & 0.758\tablenotemark{G} & 4.66 & 0.80 & 6.3e+07 & 2.3e+07 & \ldots & \ldots & 5.6e+07 & 4.6e+11 & 6.0e+10  \\
34.430803 & -5.206198 & 34.430856 & -5.206176 & 0.914\tablenotemark{G} & 0.64 & 0.13 & 2.5e+09 & 1.2e+08 & 1.2e+08 & 1.0e+07 & \ldots & 1.4e+11 & 9.8e+09  \\
34.404478 & -5.239535 & 34.404464 & -5.239511 & 0.925\tablenotemark{G} & -1.25 & 0.03 & 1.7e+10 & 2.0e+08 & 1.8e+08 & 1.0e+07 & \ldots & 3.3e+10 & 8.5e+09  \\
34.331573 & -5.180048 & 34.331575 & -5.180048 & 0.828                  & 2.80 & 0.21 & 7.2e+08 & 6.4e+07 & 2.2e+08 & 1.5e+07 & \ldots & 3.5e+11 & 6.3e+09  \\
34.306272 & -5.150911 & 34.306301 & -5.150885 & 1.446\tablenotemark{G} & -0.07 & 0.38 & 4.0e+09 & 9.0e+08 & 5.2e+08 & 3.5e+07 & \ldots & 1.8e+12 & 1.4e+11  \\
34.261751 & -5.204628 & 34.261780 & -5.204633 & 0.896                  & -0.48 & 0.04 & 1.2e+10 & 1.6e+08 & 2.6e+08 & 2.1e+07 & \ldots & 1.4e+11 & 1.6e+10  \\
34.263048 & -5.136277 & 34.263053 & -5.136258 & 0.820\tablenotemark{G} & 2.84 & 0.38 & 2.7e+08 & 4.2e+07 & 1.3e+08 & 5.7e+06 & \ldots & 9.3e+10 & 7.3e+09  \\
34.406678 & -5.198827 & 34.406674 & -5.198821 & 0.920                  & 1.91 & 0.14 & 1.8e+09 & 9.8e+07 & 2.3e+08 & 1.1e+07 & \ldots & 4.8e+11 & 1.2e+10  \\
34.385521 & -5.205044 & 34.385550 & -5.205011 & 1.380\tablenotemark{G} & 2.02 & 0.57 & 1.1e+09 & 5.9e+08 & 5.7e+08 & 3.0e+07 & \ldots & 1.1e+12 & 9.2e+10  \\
34.391148 & -5.240692 & 34.391130 & -5.240724 & 1.449\tablenotemark{G} & -0.82 & 0.54 & 8.7e+09 & 2.4e+09 & 2.4e+08 & 3.3e+07 & \ldots & 5.2e+11 & 3.3e+10  \\
34.438796 & -5.165779 & 34.438816 & -5.165758 & 1.106\tablenotemark{G} & 1.36 & 0.10 & 2.7e+09 & 1.8e+08 & 3.0e+08 & 2.9e+07 & \ldots & 4.4e+11 & 1.7e+10  \\
34.230979 & -5.176122 & 34.231025 & -5.176088 & 1.092                  & 0.34 & 0.37 & 1.2e+10 & 2.4e+09 & 1.0e+09 & 1.1e+08 & \ldots & 5.9e+11 & 3.0e+10  \\
34.433604 & -5.153793 & 34.433623 & -5.153767 & 0.805                  & 0.74 & 0.08 & 3.0e+09 & 1.1e+08 & 1.3e+08 & 1.2e+07 & \ldots & 1.2e+11 & 8.8e+09  \\
34.351795 & -5.210948 & 34.351808 & -5.210919 & 1.093\tablenotemark{G} & 0.92 & 0.00 & 2.1e+09 & 7.4e+06 & 2.5e+08 & 1.8e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
34.367405 & -5.228523 & 34.367420 & -5.228497 & 1.189\tablenotemark{G} & 0.70 & 0.04 & 8.2e+09 & 1.8e+08 & 6.2e+08 & 2.7e+07 & \ldots & 6.7e+11 & 1.5e+10  \\
34.583006 & -5.172723 & 34.582980 & -5.172715 & 1.280\tablenotemark{G} & -1.13 & 0.05 & 5.6e+09 & 1.0e+08 & 2.5e+08 & 1.6e+07 & \ldots & 3.0e+11 & 4.9e+10  \\
34.338183 & -5.254102 & 34.338179 & -5.254077 & 1.039\tablenotemark{G} & 0.28 & 0.72 & 6.9e+08 & 1.5e+08 & 1.1e+08 & 1.3e+07 & \ldots & 3.0e+11 & 1.4e+10  \\
34.335313 & -5.258985 & 34.335319 & -5.258979 & 0.879\tablenotemark{G} & -0.51 & 0.05 & 9.9e+09 & 1.9e+08 & \ldots & \ldots & 1.6e+08 & 1.2e+11 & 8.2e+09  \\
34.265199 & -5.258207 & 34.265234 & -5.258198 & 0.807                  & 0.70 & 0.06 & 3.5e+09 & 9.4e+07 & 1.1e+08 & 1.6e+07 & \ldots & 3.6e+11 & 3.8e+10  \\
34.266225 & -5.258304 & 34.266217 & -5.258304 & 0.806\tablenotemark{G} & 0.45 & 0.04 & 7.6e+09 & 1.3e+08 & 1.8e+08 & 2.2e+07 & \ldots & 2.6e+11 & 1.1e+10  \\
34.282549 & -5.227706 & 34.282574 & -5.227709 & 1.047\tablenotemark{G} & 0.06 & 0.36 & 1.9e+09 & 2.1e+08 & 2.5e+08 & 3.6e+07 & \ldots & 4.1e+11 & 4.5e+10  \\
34.417088 & -5.183261 & 34.417113 & -5.183254 & 0.920                  & 0.86 & 0.10 & 4.2e+09 & 1.5e+08 & 1.8e+08 & 1.8e+07 & \ldots & 1.8e+11 & 6.3e+09  \\
34.287594 & -5.200242 & 34.287609 & -5.200223 & 0.787                  & 1.66 & 0.15 & 1.2e+09 & 7.8e+07 & 1.0e+08 & 1.6e+07 & \ldots & 1.9e+11 & 9.9e+09  \\
34.438839 & -5.263612 & 34.438843 & -5.263605 & 0.784\tablenotemark{G} & 3.07 & 0.17 & 5.9e+08 & 4.5e+07 & 1.3e+08 & 8.7e+06 & \ldots & 2.5e+11 & 1.5e+10  \\
34.412508 & -5.175668 & 34.412537 & -5.175642 & 1.291\tablenotemark{G} & 2.55 & 1.28 & 3.3e+08 & 4.5e+08 & 3.4e+08 & 2.4e+07 & \ldots & 5.9e+11 & 3.2e+10  \\
34.341631 & -5.235338 & 34.341650 & -5.235318 & 1.100\tablenotemark{G} & 0.73 & 0.49 & 2.3e+09 & 6.9e+08 & 2.9e+08 & 1.0e+07 & \ldots & 2.8e+11 & 1.7e+10  \\
34.288088 & -5.245493 & 34.288165 & -5.245476 & 1.474\tablenotemark{G} & -1.50 & 0.05 & 1.9e+10 & 1.1e+09 & 2.3e+08 & 3.2e+07 & \ldots & 4.9e+11 & 2.8e+10  \\
34.315106 & -5.218825 & 34.315157 & -5.218789 & 1.030                  & 3.32 & 1.20 & 3.0e+08 & 1.1e+08 & 1.4e+08 & 1.2e+07 & \ldots & 2.3e+11 & 1.1e+10  \\
34.334173 & -5.190787 & 34.334186 & -5.190781 & 0.916\tablenotemark{G} & 2.98 & 1.07 & 2.0e+08 & 7.9e+07 & 9.7e+07 & 1.5e+07 & \ldots & 4.9e+11 & 4.0e+09  \\
34.258180 & -5.172100 & 34.258232 & -5.172124 & 1.094                  & -0.59 & 0.05 & 9.6e+09 & 2.0e+08 & 2.5e+08 & 1.4e+07 & \ldots & 1.2e+11 & 2.1e+10  \\
34.259985 & -5.172752 & 34.260001 & -5.172724 & 1.410\tablenotemark{G} & 0.64 & 0.99 & 9.7e+08 & 7.4e+08 & \ldots & \ldots & 1.3e+08 & 4.7e+11 & 6.2e+10  \\
34.405981 & -5.249941 & 34.405971 & -5.249905 & 1.067                  & -1.00 & 0.04 & 1.5e+10 & 1.9e+08 & 3.8e+08 & 1.7e+07 & \ldots & 1.8e+11 & 1.3e+10  \\
34.317767 & -5.189676 & 34.317778 & -5.189662 & 0.915\tablenotemark{G} & 0.31 & 0.13 & 2.9e+09 & 1.3e+08 & 2.2e+08 & 1.2e+07 & \ldots & 2.4e+11 & 7.2e+09  \\
34.238729 & -5.168098 & 34.238794 & -5.168072 & 0.821                  & 4.43 & 0.47 & 2.0e+08 & 4.0e+07 & \ldots & \ldots & 1.0e+08 & 1.9e+11 & 7.7e+09  \\
34.370957 & -5.263670 & 34.370973 & -5.263634 & 0.910\tablenotemark{G} & 0.37 & 0.05 & 8.1e+09 & 1.6e+08 & 3.1e+08 & 4.5e+07 & \ldots & 2.2e+11 & 2.5e+09
\enddata
\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
\tablecomments{Columns: RA and Dec, IR, are positions in the
\emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
priors.  RA and Dec, opt., are positions in the CANDELS catalogs.
$L_{\mathrm{H}\alpha}$ lim. is a 5$\sigma$ upper limit to the H$\alpha$
line luminosity.}
\end{deluxetable}
\clearpage
\end{landscape}

\begin{landscape}
\begin{deluxetable}{lllllllllllll}
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the samples at $z < 0.2$
\label{tbl:lowz}}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA} &
\colhead{Dec} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\beta}$} &
\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
}
\startdata
\cutinhead{Dust-poor galaxies}
30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
33.452250 & 12.997628 & 0.219 & -0.45 & 0.05 & 4.3e+10 & 4.3e+08 & 3.6e+07  & \ldots & 1.4e+08 & \ldots & 5.4e+11 & 3.0e+09 \\
52.191625 & 1.197458 & 0.142 & -1.68 & 0.04 & 1.9e+10 & 1.7e+08 & 7.4e+07   & \ldots & 2.4e+08 & \ldots & 5.4e+10 & 1.0e+09 \\
59.391667 & -5.622139 & 0.204 & -1.28 & 0.06 & 2.9e+10 & 3.5e+08 & 9.4e+07  & \ldots & 3.5e+08 & \ldots & 1.1e+11 & 1.9e+09 \\
125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09
\enddata
\tablecomments{The entire table is published in the electronic edition of
\apj.  A portion is shown here for guidance regarding its form and content.}
\end{deluxetable}
\clearpage
\end{landscape}

\begin{landscape}
\begin{deluxetable}{lllllllllllll}
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the samples at $z < 0.2$}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA} &
\colhead{Dec} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\beta}$} &
\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
}
\startdata
\cutinhead{Dust-poor galaxies}
30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
33.452250 & 12.997628 & 0.219 & -0.45 & 0.05 & 4.3e+10 & 4.3e+08 & 3.6e+07  & \ldots & 1.4e+08 & \ldots & 5.4e+11 & 3.0e+09 \\
52.191625 & 1.197458 & 0.142 & -1.68 & 0.04 & 1.9e+10 & 1.7e+08 & 7.4e+07   & \ldots & 2.4e+08 & \ldots & 5.4e+10 & 1.0e+09 \\
59.391667 & -5.622139 & 0.204 & -1.28 & 0.06 & 2.9e+10 & 3.5e+08 & 9.4e+07  & \ldots & 3.5e+08 & \ldots & 1.1e+11 & 1.9e+09 \\
125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09 \\
129.515542 & 44.983411 & 0.143 & -1.93 & 0.03 & 2.3e+10 & 1.7e+08 & 8.5e+07 & \ldots & 2.5e+08 & \ldots & 3.2e+10 & 1.0e+09 \\
140.901917 & 54.810903 & 0.222 & -1.75 & 0.07 & 2.9e+10 & 4.2e+08 & 9.4e+07 & \ldots & 3.4e+08 & \ldots & 7.6e+10 & 2.1e+09 \\
141.501708 & 44.460036 & 0.181 & -2.32 & 0.03 & 4.3e+10 & 2.7e+08 & 2.3e+08 & \ldots & 6.9e+08 & \ldots & 8.8e+10 & 3.0e+09 \\
144.556250 & 54.473636 & 0.102 & -1.75 & 0.01 & 3.3e+10 & 8.9e+07 & 1.7e+08 & \ldots & 5.5e+08 & \ldots & 1.2e+11 & 4.2e+08 \\
156.558208 & 48.749706 & 0.160 & -1.44 & 0.04 & 2.5e+10 & 2.2e+08 & 8.9e+07 & \ldots & 2.8e+08 & \ldots & 9.1e+10 & 1.1e+09 \\
208.482917 & 66.800164 & 0.198 & -0.99 & 0.03 & 5.3e+10 & 3.4e+08 & 1.5e+08 & \ldots & 5.4e+08 & \ldots & 1.3e+11 & 3.1e+09 \\
218.571500 & 2.128494 & 0.180 & -1.03 & 0.05 & 2.7e+10 & 2.8e+08 & 8.3e+07  & \ldots & 3.4e+08 & \ldots & 1.2e+11 & 1.6e+09 \\
326.251083 & 1.199328 & 0.204 & -0.65 & 0.08 & 2.4e+10 & 3.7e+08 & 1.3e+08  & \ldots & 4.8e+08 & \ldots & 1.3e+11 & 2.1e+09 \\
358.448708 & 0.900578 & 0.223 & -1.66 & 0.10 & 2.2e+10 & 4.2e+08 & 1.0e+08  & \ldots & 3.2e+08 & \ldots & 8.5e+10 & 5.9e+09 \\
\cutinhead{Dusty galaxies}
154.474577 & 15.934370 & 0.079 & 0.28 & 0.72 & 1.3e+09 & 2.5e+08 & 4.9e+07 & 8.4e+05 & 3.9e+08 & 3.0e+06 & 3.4e+11 & 2.7e+09 \\
158.388129 & 1.109763 & 0.066 & -1.10 & 0.56 & 9.4e+08 & 1.4e+08 & 1.7e+07 & 5.0e+05 & 1.3e+08 & 1.2e+06 & 2.2e+11 & 1.2e+10 \\
237.971016 & 27.242680 & 0.059 & -1.14 & 0.76 & 1.0e+09 & 2.2e+08 & 1.2e+07 & 3.3e+05 & 9.7e+07 & 8.8e+05 & 2.0e+11 & 7.4e+09 \\
7.449404 & -0.245792 & 0.061 & 0.18 & 0.24 & 4.4e+09 & 3.1e+08 & 5.4e+07 & 1.1e+06 & 2.8e+08 & 2.7e+06 & 1.2e+11 & 3.6e+09 \\
10.901290 & -9.429965 & 0.050 & 0.70 & 0.20 & 8.5e+08 & 5.0e+07 & 2.5e+07 & 3.1e+05 & 1.3e+08 & 8.2e+05 & 8.8e+10 & 5.9e+08 \\
27.858730 & -8.415234 & 0.051 & -0.76 & 0.05 & 1.3e+10 & 1.8e+08 & 4.0e+07 & 8.7e+05 & 1.9e+08 & 2.1e+06 & 1.1e+11 & 7.6e+09 \\
120.588891 & 19.993689 & 0.068 & -0.54 & 0.62 & 1.9e+09 & 3.4e+08 & 5.1e+07 & 8.4e+05 & 3.5e+08 & 2.4e+06 & 3.4e+11 & 6.7e+09 \\
126.945451 & 15.916297 & 0.055 & 0.05 & 0.40 & 3.1e+09 & 3.6e+08 & 4.2e+07 & 6.5e+05 & 2.0e+08 & 1.4e+06 & 8.8e+10 & 9.4e+08 \\
131.509245 & 52.533070 & 0.053 & -0.94 & 0.03 & 1.9e+10 & 1.4e+08 & 3.6e+07 & 9.1e+05 & 1.7e+08 & 2.0e+06 & 8.6e+10 & 3.7e+09 \\
135.288383 & 13.196000 & 0.052 & -0.13 & 0.32 & 1.7e+09 & 1.6e+08 & 1.8e+07 & 3.4e+05 & 1.1e+08 & 8.4e+05 & 7.8e+10 & 5.1e+08 \\
144.201362 & 31.330777 & 0.076 & 0.39 & 0.24 & 6.1e+09 & 4.1e+08 & 7.4e+07 & 1.0e+06 & 4.0e+08 & 3.2e+06 & 3.1e+11 & 4.2e+09 \\
156.207038 & 5.557543 & 0.067 & -0.76 & 0.05 & 5.9e+09 & 8.2e+07 & 3.6e+07 & 7.3e+05 & 1.7e+08 & 1.6e+06 & 1.3e+11 & 6.4e+09 \\
157.561538 & 11.071065 & 0.065 & -0.92 & 0.19 & 1.4e+10 & 7.7e+08 & 6.7e+07 & 9.8e+05 & 2.9e+08 & 2.6e+06 & 2.2e+11 & 4.3e+09 \\
161.115619 & 27.301748 & 0.076 & -1.28 & 0.17 & 2.8e+10 & 1.3e+09 & 1.2e+08 & 1.7e+06 & 4.3e+08 & 3.3e+06 & 1.4e+11 & 7.3e+07 \\
163.210511 & 17.104119 & 0.055 & -0.60 & 0.05 & 3.2e+09 & 4.7e+07 & 2.9e+07 & 4.1e+05 & 1.5e+08 & 1.2e+06 & 1.2e+11 & 5.9e+09 \\
165.068053 & 39.112798 & 0.073 & 0.25 & 0.47 & 3.2e+09 & 4.1e+08 & 5.1e+07 & 1.1e+06 & 3.2e+08 & 2.8e+06 & 2.1e+11 & 1.0e+10 \\
167.405962 & 26.921014 & 0.070 & -0.42 & 0.34 & 5.5e+09 & 5.3e+08 & 6.5e+07 & 9.6e+05 & 3.2e+08 & 2.5e+06 & 3.3e+11 & 4.5e+10 \\
168.081794 & 48.190468 & 0.058 & -0.56 & 0.25 & 6.4e+09 & 4.6e+08 & 5.3e+07 & 6.5e+05 & 2.2e+08 & 1.8e+06 & 1.0e+11 & 1.3e+09 \\
168.202215 & 25.597371 & 0.051 & -0.09 & 0.48 & 1.5e+09 & 2.2e+08 & 3.2e+07 & 7.1e+05 & 1.8e+08 & 2.0e+06 & 8.6e+10 & 6.1e+08 \\
174.714455 & 20.982557 & 0.065 & -0.17 & 0.20 & 1.1e+10 & 6.2e+08 & 1.2e+08 & 1.3e+06 & 7.3e+08 & 4.9e+06 & 4.6e+11 & 2.0e+10 \\
175.317325 & 21.939374 & 0.063 & -1.91 & 0.08 & 8.7e+10 & 1.9e+09 & 2.4e+08 & 1.9e+06 & 9.0e+08 & 5.0e+06 & 2.7e+11 & 1.8e+10 \\
176.292776 & 30.788122 & 0.059 & -1.50 & 0.11 & 2.9e+10 & 8.3e+08 & 9.3e+07 & 7.9e+05 & 2.5e+08 & 1.5e+06 & 1.6e+11 & 2.4e+08 \\
177.740427 & 51.953195 & 0.053 & -0.33 & 0.21 & 5.9e+09 & 3.8e+08 & 2.0e+07 & 6.9e+05 & 9.7e+07 & 1.3e+06 & 8.0e+10 & 2.5e+09 \\
181.448534 & 33.839435 & 0.054 & -1.50 & 0.20 & 3.9e+09 & 2.3e+08 & 1.9e+07 & 2.4e+05 & 1.1e+08 & 6.6e+05 & 1.2e+11 & 6.0e+09 \\
182.654191 & -3.233095 & 0.058 & -0.65 & 0.58 & 1.9e+09 & 3.1e+08 & 2.2e+07 & 7.5e+05 & 1.5e+08 & 1.7e+06 & 1.1e+11 & 5.2e+09 \\
184.248742 & 9.926954 & 0.057 & -0.24 & 0.36 & 3.8e+09 & 4.0e+08 & 2.5e+07 & 4.9e+05 & 1.3e+08 & 1.3e+06 & 8.8e+10 & 2.6e+09 \\
186.816462 & 19.906459 & 0.051 & 0.75 & 0.84 & 8.5e+08 & 2.2e+08 & 1.5e+07 & 2.7e+05 & 8.6e+07 & 7.7e+05 & 7.1e+10 & 8.8e+08 \\
188.015105 & 20.158206 & 0.064 & -1.86 & 0.03 & 8.8e+10 & 6.5e+08 & 1.7e+08 & 1.5e+06 & 6.4e+08 & 3.6e+06 & 3.5e+11 & 1.7e+08 \\
189.883379 & 27.497340 & 0.057 & -0.27 & 0.25 & 3.0e+09 & 2.2e+08 & 3.1e+07 & 5.7e+05 & 1.9e+08 & 1.6e+06 & 1.3e+11 & 7.3e+09 \\
191.550445 & 41.136642 & 0.067 & 0.10 & 0.51 & 2.0e+09 & 3.1e+08 & 1.0e+08 & 1.1e+06 & 4.8e+08 & 3.8e+06 & 3.3e+11 & 2.1e+10 \\
192.017210 & 18.002434 & 0.075 & -0.74 & 0.55 & 2.9e+09 & 4.1e+08 & 6.0e+07 & 1.3e+06 & 4.2e+08 & 3.2e+06 & 2.0e+11 & 2.5e+08 \\
196.262683 & 40.764720 & 0.057 & -0.72 & 0.15 & 6.3e+09 & 2.7e+08 & 5.9e+07 & 6.7e+05 & 2.7e+08 & 2.1e+06 & 1.6e+11 & 1.9e+09 \\
196.443701 & 32.839531 & 0.052 & -0.29 & 0.15 & 5.5e+09 & 2.4e+08 & 9.6e+06 & 5.2e+05 & 4.5e+07 & 8.4e+05 & 6.2e+10 & 3.1e+09 \\
197.424282 & 2.457934 & 0.057 & -1.12 & 0.16 & 1.6e+10 & 7.1e+08 & 4.1e+07 & 7.6e+05 & 1.8e+08 & 1.5e+06 & 1.2e+11 & 4.9e+09 \\
198.249679 & 43.204312 & 0.062 & -0.92 & 0.10 & 2.0e+10 & 5.6e+08 & 7.6e+07 & 1.3e+06 & 4.4e+08 & 3.8e+06 & 2.0e+11 & 3.4e+09 \\
198.576647 & 17.204395 & 0.073 & -0.09 & 0.47 & 3.0e+09 & 3.9e+08 & 3.3e+07 & 7.6e+05 & 2.2e+08 & 2.0e+06 & 2.2e+11 & 8.5e+09 \\
200.864909 & 8.638164 & 0.073 & -1.05 & 0.23 & 5.3e+09 & 3.3e+08 & 6.6e+07 & 8.3e+05 & 3.2e+08 & 2.3e+06 & 1.8e+11 & 1.4e+09 \\
201.432741 & 17.264658 & 0.079 & -0.63 & 0.20 & 2.3e+10 & 1.2e+09 & 1.1e+08 & 1.8e+06 & 5.3e+08 & 4.7e+06 & 2.7e+11 & 1.1e+10 \\
203.549510 & 51.889024 & 0.063 & 0.10 & 0.36 & 6.2e+09 & 6.5e+08 & 7.2e+07 & 1.0e+06 & 3.5e+08 & 2.9e+06 & 1.7e+11 & 3.2e+09 \\
208.483971 & -2.529896 & 0.051 & -1.12 & 0.40 & 3.9e+09 & 4.6e+08 & 5.3e+07 & 5.5e+05 & 2.5e+08 & 1.6e+06 & 1.6e+11 & 6.8e+09 \\
214.777948 & 47.754134 & 0.072 & -0.81 & 0.23 & 1.4e+10 & 8.4e+08 & 5.4e+07 & 1.0e+06 & 2.8e+08 & 2.2e+06 & 2.1e+11 & 6.4e+09 \\
215.283879 & 30.630220 & 0.051 & -1.03 & 0.15 & 1.1e+10 & 5.0e+08 & 2.5e+07 & 5.7e+05 & 1.1e+08 & 1.3e+06 & 1.1e+11 & 1.9e+09 \\
217.679357 & 0.252884 & 0.055 & 0.75 & 0.57 & 1.6e+09 & 2.6e+08 & 1.4e+07 & 3.7e+05 & 1.1e+08 & 9.5e+05 & 8.9e+10 & 7.8e+08 \\
220.337675 & -0.759540 & 0.080 & -0.58 & 0.10 & 6.3e+09 & 1.7e+08 & 5.5e+07 & 9.2e+05 & 3.0e+08 & 2.3e+06 & 2.6e+11 & 8.5e+09 \\
220.968122 & 16.474242 & 0.054 & -0.54 & 0.23 & 8.2e+09 & 5.3e+08 & 7.9e+07 & 9.9e+05 & 3.9e+08 & 3.0e+06 & 1.6e+11 & 1.2e+10 \\
222.786507 & 27.157482 & 0.065 & -0.20 & 0.12 & 3.1e+10 & 1.1e+09 & 2.7e+08 & 2.1e+06 & 8.5e+08 & 4.7e+06 & 3.2e+11 & 1.2e+09 \\
222.976115 & 16.222138 & 0.056 & 2.35 & 0.91 & 1.1e+09 & 2.9e+08 & 2.0e+07 & 5.4e+05 & 1.4e+08 & 1.3e+06 & 1.0e+11 & 6.8e+09 \\
234.661258 & 15.958267 & 0.052 & -0.56 & 0.49 & 2.0e+09 & 3.0e+08 & 2.5e+07 & 3.8e+05 & 1.4e+08 & 1.1e+06 & 7.8e+10 & 4.6e+09 \\
235.272762 & 32.080750 & 0.053 & 0.41 & 0.49 & 1.5e+09 & 2.3e+08 & 1.4e+07 & 1.9e+05 & 8.0e+07 & 6.1e+05 & 1.5e+11 & 8.5e+09 \\
235.907040 & 39.491740 & 0.064 & 0.59 & 0.56 & 1.1e+09 & 1.8e+08 & 1.8e+07 & 5.1e+05 & 1.3e+08 & 1.3e+06 & 1.1e+11 & 3.9e+09 \\
246.251584 & 24.405032 & 0.057 & -1.64 & 0.31 & 4.2e+09 & 3.9e+08 & 3.9e+07 & 5.6e+05 & 2.2e+08 & 1.7e+06 & 1.2e+11 & 3.0e+08 \\
254.332592 & 25.570317 & 0.053 & 1.11 & 0.94 & 3.5e+08 & 9.7e+07 & 8.9e+06 & 2.8e+05 & 5.5e+07 & 5.6e+05 & 7.2e+10 & 6.5e+09 \\
256.212271 & 34.817332 & 0.056 & 0.34 & 0.27 & 3.3e+09 & 2.6e+08 & 6.7e+07 & 7.1e+05 & 3.7e+08 & 2.4e+06 & 2.7e+11 & 6.0e+09 \\
339.895154 & -9.516226 & 0.074 & -0.54 & 0.30 & 4.3e+09 & 3.5e+08 & 4.7e+07 & 8.7e+05 & 2.7e+08 & 2.2e+06 & 2.3e+11 & 4.2e+09 \\
359.226274 & -10.268143 & 0.074 & -0.58 & 0.03 & 1.5e+10 & 1.1e+08 & 1.6e+08 & 1.2e+06 & 6.4e+08 & 3.0e+06 & 4.2e+11 & 7.2e+10
\enddata
\end{deluxetable}
\clearpage
\end{landscape}

\section{Results}\label{sec:results}

Three star formation rates allow us to compare two attenuation values.
We eschew magnitude attenuation in favor of the escape fraction, which
is the ratio of emergent to intrinsic luminosity.  We define the following
quantities.
\begin{itemize}
\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  (In
relation to A$_{\mathrm{UV}}$,
f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.)
\item \alephha~is the escape fraction of the H$\alpha$ line luminosity.
\item \alephuvha~is the escape fraction extrapolated from \alephuv~to the
wavelength of H$\alpha$---the attenuation formula prediction.  For the
attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
\end{itemize}

\citet{calzetti94} argue that, in low-redshift dust-poor galaxies, regions with
ionizing stars are spatially separate from regions with nonionizing
UV-emitting stars.  In this framework \alephuvha~is the escape fraction
of the 0.66$\,\micron$ continuum emission from low-to-high mass stars and
\alephha~is the escape fraction of the 0.66$\,\micron$ line emission from gas
ionized by high mass stars.  These galaxies have \alephha~= \alephuv$^{0.69}$,
equivalent to \alephha~= \alephuvha$^{2.1}$ \citep{calzetti94,calzetti97b}.
Because the ionizing and nonionizing stars are spatially separate, the
escape fractions disagree because the dust distributions are nonuniform.  The
ionizing stars are surrounded by more dust than are the nonionizing stars.

The H$\alpha$ escape fractions in \citet{calzetti94} come from the ratios of
H$\alpha$ to H$\beta$
line luminosities.  In the absence of dust the ratio is 2.86, so
($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86~=~\alephha/\alephhb.  Since
\alephhb~is a power-law function of \alephha, the ratio of line luminosities
uniquely determines \alephha.

The UV and 0.66$\,\micron$ escape fractions in \citet{calzetti94} come from
comparing spectra of
galaxies with H$\alpha$ escape fractions of 1 to spectra of galaxies with
H$\alpha$ escape fractions less than 1.  The H$\alpha$ and H$\beta$ lines in
the spectra must be masked or replaced with continuum values.  The literature
relation is technically
\alephha~= \alephuvha$^{2.3}$.  \citet{calzetti97b} uses the Milky Way
extinction formula of \citet{howarth83} to determine H$\alpha$ escape
fractions for low-redshift dust-poor galaxies; if we instead use the
attenuation formula, we get \alephha~= \alephuvha$^{2.1}$.

Our hypothesis is that the H$\alpha$ and 0.66$\,\micron$ escape fractions
agree---that dusty galaxies have uniform dust distributions.
Our method for determining H$\alpha$ escape fractions is nonstandard; we lack
H$\beta$ luminosities for the $z \sim 1$ dusty galaxies.  We first apply
it to a sample of low-redshift dust-poor galaxies with the aim of reproducing
the \citet{calzetti97b} result.

\subsection{Reproducing the relation for dust-poor galaxies}

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation.  This relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~from IRX: \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  (Equivalent to \alephuv~= [emergent UV
SFR]/[IR SFR + emergent UV SFR].)
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.80}$
for the low-redshift
dust-poor galaxies.  (If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.)  We lack
uncertainties on any SFRs so we also perform a robust linear regression
(which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv).  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

\subsection{A new relation for dusty galaxies at low redshift?}

The top right panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for the low-redshift
dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
SFR (we treat it as the dependent variable) in the weighted fit.  The relation
for dust-poor galaxies is seemingly inapplicable to dusty galaxies at
low redshift.  In \S\ref{subsec:highz} and \ref{sec:discuss} we explain why we
preface `inapplicable' with `seemingly.'

%\begin{figure}[!ht]
%\centering
%\includegraphics[scale=0.5]{aha_auv_lowzdog.eps}
%\caption{The H$\alpha$ escape fraction, \alephha, as a function of the UV
%escape fraction, \alephuv, for the low-redshift dusty galaxies.  The dashed
%purple line shows \alephuvha, the extrapolation of \alephuv~to the wavelength
%of H$\alpha$ using the \citet{calzetti00} attenuation formula, as a function of
%\alephuv.  This is the uniform dust distribution hypothesis for the attenuation
%formula.  If low-redshift dust-poor galaxies were to have this range of UV
%escape fractions, their H$\alpha$ escape fractions would be lower than this
%extrapolation (dotted black line).  Our fit is the solid orange line.  We find
%that, in low-redshift dusty galaxies, regions with ionizing stars have lower
%escape fractions than the extrapolation and higher escape fractions than they
%would in low-redshift dust-poor galaxies.\label{lowzdog}}
%\end{figure}

\subsection{A corresponding relation for dusty galaxies at high
redshift?}\label{subsec:highz}

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.55}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.45}$
and \alephha~= \alephuv$^{0.66}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = 0.47$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  (None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.)  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablewidth{0pc}
\tablecaption{Summary of regressions\label{regress}}
\tablehead{
\colhead{Sample} &
\colhead{$q$} &
\colhead{Std. error of $q$} &
\colhead{Residual std. error} &
\colhead{DOF}
}
\startdata
Low-z dust-poor & 0.799 & 0.094 & 6.0  & 13 \\
Low-z dusty     & 0.548 & 0.029 & 67.0 & 54 \\
High-z dusty    & 0.549 & 0.008 & 6.6  & 320
\enddata
\end{deluxetable}

%\begin{figure}[!ht]
%\centering
%\includegraphics[scale=0.5]{aha_auv_highz_py.eps}
%\caption{The H$\alpha$ escape fraction, \alephha, as a function of the UV
%escape fraction, \alephuv, for the high-redshift dusty galaxies.  The
%dashed purple line shows \alephuvha, the extrapolation of \alephuv~to the
%wavelength of H$\alpha$ using the \citet{calzetti00} attenuation formula, as a
%function of \alephuv.  This is the uniform dust distribution hypothesis for the
%attenuation formula.  If low-redshift dust-poor galaxies were to have this
%range of UV escape fractions, their H$\alpha$ escape fractions would be lower
%than this extrapolation (dotted black line).  Our fit is the solid orange line.
%We find that, in high-redshift dusty galaxies, regions with ionizing stars have
%lower escape fractions than the extrapolation and higher escape fractions than
%they would in low-redshift dust-poor galaxies.\label{highz}}
%\end{figure}

The escape fraction relations of dusty galaxies are subject to selection
effects.  The best-fit relation for the low-redshift dusty galaxies seems to:
(1) underestimate H$\alpha$ escape fractions at low UV escape fractions; and (2)
overestimate H$\alpha$ escape fractions at high UV escape fractions (top
right panel of Fig. \ref{fha_fuv}).  This may reflect our constraint that
\alephha~=1 when
\alephuv~=1, but the lack of galaxies with H$\alpha$ escape fractions at or
below the relation may be due to galaxies with H$\alpha$ SFRs below the limit
of the sample.  We do not measure H$\alpha$ line flux limits for galaxies that
meet the selection criteria of \citet{hwang13} and have undetected H$\alpha$
line fluxes.  If we replace all H$\alpha$-detected SFRs with SFRs corresponding
to the minimum H$\alpha$ line flux of the sample, we fill in the space around
the relation.

High-redshift dusty galaxies with UV escape fractions $< 10^{-2}$ seem to have
less dispersion in their H$\alpha$ escape fractions than do galaxies with UV
escape fractions $> 10^{-2}$.  Despite our best efforts to measure H$\alpha$
line flux limits, we still lack them for galaxies lacking spectroscopic
redshifts.  If we replace all H$\alpha$-detected SFRs with SFRs corresponding
to a reasonable H$\alpha$ line flux limit for the grism observations
($5 \times 10^{-17}$ erg s$^{-1}$ cm$^{-2}$), we fill in the space with low
H$\alpha$ escape fractions at low UV escape fractions.  The decrease in
dispersion is probably an artifact of the grism detection limit and a paucity
of spectroscopic redshifts in UDS and the part of COSMOS in CANDELS.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.365]{fha_fuv.eps}
\caption{{\small \emph{Top left}: The H$\alpha$ escape fraction, \alephha, as a
function of the UV
escape fraction, \alephuv, for the low-redshift
dust-poor galaxies.  The dashed purple line shows \alephuvha, the extrapolation
of \alephuv~to the wavelength of H$\alpha$ using the \citet{calzetti00}
attenuation formula, as a function of \alephuv.  This is the uniform dust
distribution hypothesis for this attenuation formula.  \citet{calzetti97b}, who
study another sample of low-redshift dust-poor galaxies, find
that H$\alpha$ escape fractions are lower than this extrapolation (dotted black
line).  We find a similar result (solid orange line).
We have some confidence that our H$\alpha$ escape fractions are grossly
correct.
\emph{Top right}:  \alephha~as a function of \alephuv~for the low-redshift dusty
galaxies.  In
low-redshift dusty galaxies, regions with ionizing stars have lower
escape fractions than the extrapolation and higher escape fractions than they
would have in low-redshift dust-poor galaxies.
\emph{Bottom left}:  \alephha~as a function of \alephuv~for the high-redshift
dusty galaxies.  In high-redshift dusty galaxies,
regions with ionizing stars have
lower escape fractions than the extrapolation and higher escape fractions than
they would have in low-redshift dust-poor galaxies.  A conclusion about the
uniformity of dust distributions in high-redshift dusty galaxies is subject to
an assumption about the attenuation formula.\label{fha_fuv}}}
\end{figure}

\section{Discussion}\label{sec:discuss}

If we assume that dusty galaxies obey the \citet{calzetti00} attenuation
formula, our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
have \alephha~= \alephuvha$^{1.6}$; like low-redshift dust-poor galaxies,
dusty galaxies have nonuniform dust distributions.  The relations between
\alephha~and \alephuvha~are similar to those found by \citet{onodera10},
\citet{kashino13}, and \citet{price13} and conflict with those of
\citet{erb06}.  These studies assume the applicability of the \citet{calzetti00}
attenuation
formula, and use samples of high-redshift galaxies that are not necessarily
dusty.  Their UV escape fractions come from stellar population modeling, while
ours come from IRX; their H$\alpha$ escape fractions come from ratios of
averaged H$\alpha$ to averaged H$\beta$ luminosities, or ratios of H$\alpha$ to
UV luminosities, while ours come from assumptions about SFRs.

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.2}$.  If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.55}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's instantaneous SFR has,
for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
massive stars formed over 15 Myr instead of 300 Myr, we should multiply
$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  (Another scenario is that massive stars stopped forming within the last
15 Myr.)  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

There are few ways to resolve the uncertainties regarding star formation
histories and the applicability of the \citet{calzetti00} attenuation formula
to dusty galaxies.  One (partial) way is to use the formula and
\alephha~to predict the escape fraction of the H$\beta$ luminosity,
\alephhb.  Both line luminosities are from ionized gas surrounding the same
stars, so this prediction is immune to an uncertain star formation history.
The ratio of intrinsic
H$\alpha$ to H$\beta$ luminosities is 2.86 (under reasonable
assumptions); with H$\beta$ observations, we can use
($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86~=~\alephha/\alephhb~and from this
determine \alephhb.  If the predicted and determined H$\beta$ escape fractions
agree, the assumed attenuation formula is probably valid at optical
wavelengths; the assumed star formation histories are also probably valid.
The histories are valid because the prediction is history-dependent and the
determination is history-independent.  If
the predicted and determined fractions disagree, the attenuation
formula at optical wavelengths can be different for dusty galaxies
or their true \alephha~can be different.  The formula can differ due to dust
not distributed as a uniform foreground screen; see table 1 and fig. 3b of
\citealt{calzetti01}.  Fig. \ref{ahb}
shows this test applied to the low-redshift dusty galaxies.  To apply this
test to high-redshift dusty galaxies, we need near-IR spectra that cover
the H$\beta$ line.  If the dispersion
of H$\alpha$ escape fractions at a given UV escape fraction for high-redshift
dusty galaxies remains, there must be a diversity of dust
distributions.  Either way, this test provides no information on the relation
between UV and 0.66$\,\micron$ escape fractions; more extrapolations are
necessary to definitively interpret Fig. \ref{fha_fuv}.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{ahb_aha_lowzdog.eps}
\caption{H$\beta$ escape fraction, \alephhb, as a function of H$\alpha$ escape
fraction, \alephha, for the low-redshift dusty galaxies.  We determine
\alephhb~using \alephha~and the ratios of H$\alpha$ and H$\beta$ luminosities.
The \citet{calzetti00} attenuation formula has \alephhb~= \alephha$^{1.38}$
(dashed purple line).  If H$\beta$ measurements of high-redshift dusty galaxies
agree with the prediction, we can resolve uncertainties related to star
formation histories and the validity of the \citet{calzetti00} attenuation
formula at optical
wavelengths; otherwise, we might not.\label{ahb}}
\end{figure}

\section{Summary}\label{sec:conclude}

\begin{enumerate}
\item We measure H$\alpha$ line luminosities and limits, from
\emph{HST}/WFC3-IR grism spectra, for $z \sim 1$ galaxies with detected
100$\,\micron$ emission.  We determine rest-frame UV continuum power-law
indices ($\beta$ values) and ratios of IR to UV luminosities (IRX values).
\item For each galaxy we determine \alephuv, the escape fraction at
0.16$\,\micron$, from IRX.  We determine \alephha, the H$\alpha$ escape
fraction, from the H$\alpha$ luminosity and the total star formation rate.
\item For the \citet{overzier11} sample of low-redshift dust-poor galaxies, we
recover the \citet{calzetti97b} relation between H$\alpha$ and UV escape
fractions: \alephha~= \alephuv$^{0.80}$.  Our nonstandard method for determining
H$\alpha$ escape fractions should be grossly correct.
\item For the \citet{hwang13} sample of low-redshift dusty galaxies, we find
that \alephha~= \alephuv$^{0.55}$.
\item For our sample of dusty galaxies at $0.7 < z < 1.5$, we find that
\alephha~= \alephuv$^{0.55}$.  The dispersion about the best-fit relation is
large.
\item The interpretation of the results for dusty galaxies is unclear.  If we
assume that the \citet{calzetti00} attenuation formula applies to these
galaxies, our results agree with those of \citet{onodera10}, \citet{kashino13},
and \citet{price13} and conflict with those of \citet{erb06}: \alephha~=
\alephuvha$^{1.6}$.  They study
samples comprising dust-poor and dusty galaxies.  Dusty galaxies have
nonuniform dust distributions.  However, dusty galaxies may disobey the
\citet{calzetti00} attenuation formula.
\item Measurements of the ratios of H$\alpha$ to H$\beta$ luminosities may
decrease the dispersion in the relation between H$\alpha$ and UV escape
fractions for dusty galaxies at $z \sim 1$.  If the dispersion is real, these
galaxies have diverse dust distributions.
\end{enumerate}

ALMA is beginning to produce images of the dust distributions in galaxies.
These images lead to direct tests, independent of the attenuation formula, of
the uniform screen assumption.  They also have the potential to reveal the
parts of galaxies that may never be detected at UV and optical wavelengths:
surprises surely abound.

\begin{thebibliography}

\bibitem[Balestra et al.(2010)]{balestra10} Balestra, I., Mainieri, V., Popesso,
P., et al.\ 2010, \aap, 512, AA12

\bibitem[Boissier et al.(2004)]{boissier04} Boissier, S., Boselli, A.,
Buat, V., Donas, J., \& Milliard, B.\ 2004, \aap, 424, 465

\bibitem[Brammer et al.(2012)]{brammer12} Brammer, G.~B., van 
Dokkum, P.~G., Franx, M., et al.\ 2012, \apjs, 200, 13

\bibitem[Buat et al.(2012)]{buat12} Buat, V., Noll, S., Burgarella, D.,
et al.\ 2012, \aap, 545, A141

\bibitem[Buat et al.(2011)]{buat11} Buat, V., Giovannoli, E., Heinis, S.,
et al.\ 2011, \aap, 533, A93

\bibitem[Calzetti(2001)]{calzetti01} Calzetti, D.\ 2001, \pasp, 113, 1449

\bibitem[Calzetti et al.(2000)]{calzetti00} Calzetti, D., Armus, L., Bohlin,
R.~C., et al.\ 2000, \apj, 533, 682

\bibitem[Calzetti(1997b)]{calzetti97b} Calzetti, D.\ 1997, American 
Institute of Physics Conference Series, 408, 403

\bibitem[Calzetti(1997a)]{calzetti97a} Calzetti, D.\ 1997, \aj, 113, 162

\bibitem[Calzetti et al.(1994)]{calzetti94} Calzetti, D., Kinney, A.~L., \&
Storchi-Bergmann, T.\ 1994, \apj, 429, 582

\bibitem[Chary \& Elbaz(2001)]{chary01} Chary, R., \& Elbaz, D.\ 2001, \apj,
556, 562

\bibitem[D{\'{\i}}az-Santos et al.(2010)]{diaz10} D{\'{\i}}az-Santos, T.,
Charmandaris, V., Armus, L., et al.\ 2010, \apj, 723, 993

\bibitem[Donley et al.(2012)]{donley12} Donley, J.~L., Koekemoer, A.~M.,
Brusa, M., et al.\ 2012, \apj, 748, 142

\bibitem[Erb et al.(2006)]{erb06} Erb, D.~K., Steidel, C.~C., 
Shapley, A.~E., et al.\ 2006, \apj, 647, 128

\bibitem[Fadda et al.(2010)]{fadda10} Fadda, D., Yan, L., 
Lagache, G., et al.\ 2010, \apj, 719, 425

\bibitem[Galametz et al.(2013)]{galametz13} Galametz, A., Grazian, A.,
Fontana, A., et al.\ 2013, \apjs, 206, 10

\bibitem[Guo et al.(2013)]{guo13} Guo, Y., Ferguson, H.~C., 
Giavalisco, M., et al.\ 2013, \apjs, 207, 24

\bibitem[Howarth(1983)]{howarth83} Howarth, I.~D.\ 1983, \mnras, 203, 301

\bibitem[Hwang \& Geller(2013)]{hwang13} Hwang, H.~S., \& Geller, M.~J.\ 2013,
\apj, 769, 116

\bibitem[Juneau et al.(2013)]{juneau13} Juneau, S., Dickinson, 
M., Bournaud, F., et al.\ 2013, \apj, 764, 176

\bibitem[Kashino et al.(2013)]{kashino13} Kashino, D., Silverman, 
J.~D., Rodighiero, G., et al.\ 2013, \apjl, 777, L8

\bibitem[Kauffmann et al.(2003)]{kauffmann03} Kauffmann, G., 
Heckman, T.~M., Tremonti, C., et al.\ 2003, \mnras, 346, 1055

\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, R., 1999, \araa, 36, 189

\bibitem[Kriek \& Conroy(2013)]{kriek13} Kriek, M., \& Conroy, C.\ 2013,
\apjl, 775, L16

\bibitem[Kurk et al.(2013)]{kurk13} Kurk, J., Cimatti, A., Daddi, E., et al.\
2013, \aap, 549, AA63

\bibitem[Le F{\`e}vre et al.(2004)]{lefevre04} Le F{\`e}vre, O., Vettolani, G.,
Paltani, S., et al.\ 2004, \aap, 428, 1043

\bibitem[Lilly et al.(2009)]{lilly09} Lilly, S.~J., Le Brun, V.,
Maier, C., et al.\ 2009, \apjs, 184, 218

\bibitem[Liu et al.(2013)]{liu13} Liu, G., Calzetti, D., 
Hong, S., et al.\ 2013, \apjl, 778, L41

\bibitem[Madau \& Dickinson(2014)]{madau14} Madau, P., \& Dickinson, M.\ 2014,
arXiv:1403.0007

\bibitem[Magnelli et al.(2013)]{magnelli13} Magnelli, B., Popesso, P.,
Berta, S., et al.\ 2013, \aap, 553, A132

\bibitem[M{\'e}nard et al.(2010)]{menard10} M{\'e}nard, B., Scranton, R.,
Fukugita, M., \& Richards, G.\ 2010, \mnras, 405, 1025

\bibitem[Mignoli et al.(2005)]{mignoli05} Mignoli, M., Cimatti, A., Zamorani,
G., et al.\ 2005, \aap, 437, 883

\bibitem[Mu{\~n}oz-Mateos et al.(2009)]{munoz09} 
Mu{\~n}oz-Mateos, J.~C., Gil de Paz, A., Boissier, S., et al.\ 2009, \apj, 
701, 1965

\bibitem[Onodera et al.(2010)]{onodera10} Onodera, M., Arimoto, 
N., Daddi, E., et al.\ 2010, \apj, 715, 385

\bibitem[Overzier et al.(2011)]{overzier11} Overzier, R.~A., 
Heckman, T.~M., Wang, J., et al.\ 2011, \apjl, 726, L7

\bibitem[Overzier et al.(2009)]{overzier09} Overzier, R.~A., 
Heckman, T.~M., Tremonti, C., et al.\ 2009, \apj, 706, 203

\bibitem[Penner et al.(2012)]{penner12} Penner, K., Dickinson, 
M., Pope, A., et al.\ 2012, \apj, 759, 28

\bibitem[Prescott et al.(2007)]{prescott07} Prescott, M.~K.~M., 
Kennicutt, R.~C., Jr., Bendo, G.~J., et al.\ 2007, \apj, 668, 182

\bibitem[Price et al.(2013)]{price13} Price, S.~H., Kriek, M., 
Brammer, G.~B., et al.\ 2013, arXiv:1310.4177

\bibitem[Ravikumar et al.(2007)]{ravikumar07} Ravikumar, C.~D., Puech, M.,
Flores, H., et al.\ 2007, \aap, 465, 1099

\bibitem[Reddy et al.(2012)]{reddy12} Reddy, N., Dickinson, M.,
Elbaz, D., et al.\ 2012, \apj, 744, 154

\bibitem[Reddy et al.(2010)]{reddy10} Reddy, N.~A., Erb, D.~K.,
Pettini, M., Steidel, C.~C., \& Shapley, A.~E.\ 2010, \apj, 712, 1070

\bibitem[Santini et al.(2014)]{santini14} Santini, P., Ferguson, 
H.~C., Fontana, A., et al.\ 2014, arXiv:1412.5180

\bibitem[Simpson et al.(2012)]{simpson12} Simpson, C., Rawlings, 
S., Ivison, R., et al.\ 2012, \mnras, 421, 3060

\bibitem[Simpson et al.(2015)]{simpson15} Simpson, J.~M., Smail, 
I., Swinbank, A.~M., et al.\ 2015, \apj, 799, 81

\bibitem[Szokoly et al.(2004)]{szokoly04} Szokoly, G.~P., 
Bergeron, J., Hasinger, G., et al.\ 2004, \apjs, 155, 271

\bibitem[Vanzella et al.(2008)]{vanzella08} Vanzella, E., Cristiani, S.,
Dickinson, M., et al.\ 2008, \aap, 478, 83

\bibitem[Weiner et al.(2007)]{weiner07} Weiner, B.~J., Papovich, 
C., Bundy, K., et al.\ 2007, \apjl, 660, L39

\bibitem[Yamada et al.(2005)]{yamada05} Yamada, T., Kodama, T., 
Akiyama, M., et al.\ 2005, \apj, 634, 861

\bibitem[Younger et al.(2010)]{younger10} Younger, J.~D., Fazio, 
G.~G., Ashby, M.~L.~N., et al.\ 2010, \mnras, 407, 1268

\bibitem[Zaritsky(1994)]{zaritsky94} Zaritsky, D.\ 1994, \aj, 108, 
1619

\end{thebibliography}

\end{document}

### 2015-04-14 response.txt
Add response

* In the abstract, it is said "We investigate whether or not the
distributions resemble uniform foreground screens, as commonly
assumed.". I see several issues with this statement. First of all, the
word "uniform" is ambiguous. Later in the paper it appears to probably
mean that it implies there is no differential reddening between the gas
and the stars. At this point it is not clear in my opinion. The terms
used in the paper really need to be properly and strictly defined. As it
is, the paper appears somewhat vague, partly because of that I think.
Also, "foreground screens" are not commonly assumed. I would go as far
as saying they besides a handful of specific cases and academic
exercises, they are nearly never assumed for practical proposes on
entire galaxies. I believe we have known since the IRAS days that a
foreground screen cannot be a good assumption in general for entire
galaxies as this would yield very low dust masses that are not at all in
line with the estimate from IR observations. And for sure it has fallen
even more into disuse since the Calzetti+94 paper and the subsequent
Charlot & Fall+00 model.

We clarify our language in the last paragraph of the Introduction. 
Foreground screens are commonly assumed by the high-redshift community;
we expand our explanation in the Introduction.

* Still on the vocabulary, I do not think it is defined anywhere what
"dust-poor" and "dusty" galaxies are. This sort of thing contributes to
the vagueness of the paper. The reader does not know what she is really
looking it. A more quantitative description of the two samples would be
especially useful. Directly related to this point, another important
issue I have is the very unclear selection of the sample. I do not think
the reader would understand why these sample specifically were selected.

We clarify our language in the last paragraph on the Introduction.  The
sample of low-redshift dust-poor galaxies is included to show that we
can reproduce the Calzetti result; the samples of dusty galaxies are
included because we know little about their dust distributions.

* "We often assume that dust grains are distributed as a uniformly thick
screen between us and the galaxy's stars and gas (Calzetti et al.
1994).". I do not see where Calzetti would have stated that. What they
say in the abstract is "The data from the 39 galaxies are compared with
five models for the geometrical distribution of dust, adopting as
extinction laws both the Milky Way and the Large Magellanic Cloud laws.
The commonly used uniform dust screen is included among the models. We
find that none of the five models is in satisfactory agreement with the
models". What the authors perhaps mean is that 20 years ago some people
still considered an uniform dust screen as an acceptable model. I think
this time is long gone, even though it is sometimes referred to as a
standard comparison point as it has a very simple link with the optical
depth.

The abstract has only a small fraction of the content of the paper. 
Calzetti et al. 1994 has an extended discussion of the uniform screen
model in sections 5.1 and 6.2.  We clarify our discussion of the uniform
screen model in the Introduction.

* "If a dusty galaxy's measured Halpha attenuation agreed with the
prediction from the Calzetti+00 attenuation formula, we might conclude
that the galaxy has a uniform dust distribution only if we believe that
the prediction is valid". I think that this statement is not correct.
First of all, the starburst curve is purely observational. No assumption
whatsoever on the geometry was made. However, it can be explained by
certain geometries, such as for instance the one described in the
Charlot & Fall 2000 model. Perhaps this is what the authors mean?

We clarify our discussion of the uniform screen model in the
Introduction. k(lambda) is an empirical equation; predictions of
attenuation values from k(lambda) do assume a dust distribution.

* First paragraph of Sect. 2.2.3. The K98 IR estimator actually assumes
that the galaxy is totally buried into dust. Therefore, combining the UV
with the TIR directly can be a dangerous game (though quite common in
the literature). As UV is detected, galaxies are not that strongly
attenuated so the assumption does not hold and the dust heating sources
are not the same anymore, which in turn should change the calibration
coefficient. Also, the listed assumptions are not enough in my opinion.
Even if the SFR is constant over 10^8 years, the Halpha and UV+IR SFR
would not be the same, because of contamination by stars older than 100
Myr in the UV but not in Halpha. As possible biases in the derivation of
the SFR would have a direct impact on the results, I suggest that they
are fully taken into account and properly discussed in the paper. In any
case, beyond that, assuming in effect that SFR(Halpha)=SFR(UV+TIR) is a
very strong assumption. If there is a tiny wiggle of the SFR in the last
few Myr, that is sufficient to throw the different SFR completely off
from one another. As said just above, the results of this paper are
sensitive to such effects. I think it is therefore especially important
that the impact of such variations is discussed in more detail than in a
lone paragraph in Section 4.

* In section 3, I find very odd to present the results in terms of
escape fraction, rather than attenuation as is customary. While
technically they are equivalent quantities, I find that using escape
fractions is detrimental to the clarity of the paper. I would strongly
suggest to switch to attenuations.

We disagree.

* Section 3.1. I understand what the authors are trying to do, that is
testing their method. Which is a very good thing of course. That being
said, I cannot help but wonder whether the results are really meaningful
here. If I remember correctly, there is quite a bit of scatter for this
sample around the IRX-beta relation. What if this scatter is driven by a
combination of variations in the attenuation curves and variations in
the age of UV-emitting stellar populations? I think a perhaps more
convincing test would be to create a mock catalog of galaxies and apply
that method on it to see whether it can recover the proper parameters.
As an added bonus, it would be trivial to test whether a variation of
the SFH (for instance including a recent burst of star formation). I
think that would be a very convincing test that the proposed method is
indeed providing good results. Actually at this point I am also a bit
confused regarding beta. Its computation is described earlier in the
paper but I do not see it used in practice.

We are interested in reproducing the literature relation for a sample of
dust-poor galaxies similar to the one studied by Calzetti.  The test
proposed here is for reproducing the relation assumed by a model.  We do
not know what the "true" values are for the Lyman break analogs or the
Calzetti sample.  So while we might be able to say that we reproduce the
relation assumed by the model, we would not be able to say that the mock
galaxies reproduce real galaxies.

We use beta only to obtain rest-frame UV luminosities at a common
wavelength.

* Beginning of Section 4. There is more than just the assumption that
dusty galaxies follow the starburst law. There is also the assumption
that all galaxies in a given sample have the same intrinsic UV color I
think. It is not clear at all to me whether that is actually the case.

* Last paragraph of the conclusion. I doubt ALMA will be used to provide
direct test of the "uniform screen assumption". Not that it cannot, but
rather this assumption is known to be invalid for most practical
purposes. There is an enormous quantity of archival observations
available for numerous instruments showing the beautifully complex
interplay between stars and dust in the Milky and in nearby galaxies.

We clarify that ALMA will be a boon to high-redshift galaxies.

* Finally, some general comments. The differential reddening is not
mentioned in the paper even though that is what the authors aim at
studying. In her last attenuation law papers, Calzetti defines the
difference of the attenuation between the stars and the gas in terms of
differential reddening rather than in terms of escape ratios (that is,
E(B-V)stars=0.44*E(B-V)gas rather than AVstars=0.44*AVgas). This is an
important difference as Rv is different between the starburst law
(Rv=4.05) and the Milky Way law (Rv=3.1). If I remember correctly, that
can make a noticeable difference when computing A(Halpha)/A(FUV).

We hope our language clarifies this point.  We are only interested in
the differential reddening if we believe the Calzetti formula applies to
high-redshift dusty galaxies.  When we discuss whether high-redshift
galaxies obey or disobey the Calzetti attenuation formula, we include Rv
in our definition of the attenuation formula, k(lambda). (In short, we
do not aim to study the differential reddening.)

Some comments on more minor points follow.

* There are sentences between parentheses in the middle of the text. It
disturbs the reading flow in my opinion. I would suggest to either add
them as footnotes and to integrate them fully in the rest of the text.

* Please provide a reference for Willman 1. I assume many readers will
be ignorant of the details of this object, so information should be made
easy to access for those who are curious to know more about it.

* "The arrangement of dust is often described, oddly, as its geometry".
I am not sure what is particularly odd in that. But more precisely, what
is described is the relative arrangement of dust relative to stars as
this is one of the major parameters that govern the actual impact of
dust on the emerging radiation.

* "If we want to learn about galaxies, morphology should be a
wavelength-independent word". Should it? I do not see why. The
differences in morphologies in different bands are extremely informative
on the physics of galaxies.

* "An attenuation formula is denoted k(lambda) or k'(lambda)." I do not
think this statement is useful here. First the term "attenuation
formula" is extremely vague. Then, unless I am mistaken, k is not used
in any meaningful way elsewhere in the paper anyway.

* "A low-redshift galaxy [...] underestimates the measured Halpha
attenuation." Please back this with a reference.

* "Liu+13 find that the dust distribution around ionizing stars
throughout M83 is clumpy at a spatial scale of 6 pc." Unless I am
mistaken, this is not at all what they say. Quoting their abstract
"[...] we conclude that a large diversity of absorber/emitter geometric
configurations can account for the data, implying a more complex
physical structure than the classical foreground screen assumption". The
article barely mentions at all the clumpy distribution.

* "If we choose to think of dust distributions as clumpy [...] 60% of
the number of clumps surrounding ionizing stars (Calzetti+97a)". Once
again, I do not see where the mentioned paper cites that number. If it
is indeed that paper: http://de.arxiv.org/abs/astro-ph/9706121 then the
word clump is not even mentioned even once in the paper. Please clarify
this part.

* "if we consider that galaxies have centers and outskirts." That
statement is odd. Any spatially bounded object has outskirts.

* Price+13 should be Price+14.

* About the correction for the NII contamination, which should be
metallicity dependent, what about using a mass-metallicity relation for
instance? That would be far from perfect but certainly better than
assuming a constant [NII]/Halpha.

* Editorial question, it looks odd that the second author of the paper
is cited for data provided as "private communication".

* Sect. 2.2.1, second paragraph. Maybe I am misunderstanding what is
written, but it appears to say that fitting the CE01 templates on the 24
micron band only will overestimate the 70 and 100 micron fluxes (and
therefore most likely it will also overestimate the TIR), and that the
TIR found in the paper is even higher. If it is the case, I find that
very worrisome. If it is not the case, please clarify this paragraph to
remove ambiguities.

* The TIR luminosities of the so-called dust-poor and dusty galaxies are
not that different. This suggests some possible selection effects. This
aspect should be discussed in detail in the paper.

* The title of Sect. 3.1 is unclear. One would wonder what "relation" is
considered here.

* Sect. 3.1, it would be useful to specify what exactly is the "low
redshift IRX-beta relation".

* Last paragraph of Sect. 4. This assumes that the stars and the gas
follow the same attenuation law. This may or may not be the case.
Calzetti considers that this is not the case. Also later in that
paragraph, I may be missing something, but I do not understand why this
would prove that SFH are correct. Just after the authors rightly mention
that f(Halpha)/f(Hbeta) is SFH-independent. So this test just does not
tell us much of anything regarding the SFH I think. Please clarify.

As a final note, here is the assessment by a statistical expert on the
fitting done in the paper: The choice of regression methodology in Fig 4
is unclear to me. Why do the orange lines seem constrained to pass
through the origin? The resulting fit for the top right diagram, for
example, is clearly poor. Statisticians would recommend that, when
heuristic (e.g. linear) parametric models fit poorly, that nonparametric
local regression methods be used to show the true behavior of the
bivariate relationship. There are various methods -- splines, LOESS,
kriging (= Gaussian process regression) -- some of which give local
confidence bands. Several recent texts are available; e.g. K.Takezawa
`Introduction to Nonparametric Regression'. For implementation in the
public R statistical software environment, see a tutorial on density
estimation at http://www2.astro.psu.edu/users/edf/Caltech_2014.

### 2015-04-14 paper.tex
Updates

@@
 resemble
-uniform foreground screens, as commonly assumed.  We use rest-frame infrared,
+uniform foreground screens, as commonly assumed by the high-redshift galaxy
+community.  We use rest-frame infrared,
 ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
@@
 Dust attenuates a galaxy's intrinsic luminosity at ultraviolet (UV) and optical
-wavelengths.  We often assume that dust grains
+wavelengths.  To recover an intrinsic luminosity from an emergent luminosity we
+often assume that dust grains
 are distributed as a uniformly thick screen between us and the galaxy's stars
-and gas \citep{calzetti94}.  From the uniform screen assumption follows an
-attenuation
-formula that depends solely on wavelength; intrinsic luminosity is recovered
-from emergent luminosity and attenuation calculated from the formula.
+\citep{calzetti94}.  From the uniform screen assumption follows an
+attenuation formula that depends solely on wavelength.
 
@@
 of dust.  When we derive an extinction formula, it is valid for the small area
-surrounding a star in the Milky Way, not the large area containing a mix of
-stars and gas in distant galaxies.  In an illustrative sense an attenuation
-formula is an extinction formula convolved with a spatial distribution of dust.
+surrounding a star in the Milky Way, not the large area containing a mixture of
+stars in distant galaxies.
+
+If we write an equation like this:
+
+\begin{math}
+L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}} = 10^{-\mathrm{A}/2.5} = 10^{-\mathrm{E(B-V)} k(\lambda)/2.5}
+\end{math}
+
+we assume a uniform screen not because $k(\lambda)$ is solely dependent on
+wavelength, but because $L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$ is solely
+dependent on
+wavelength.  In an illustrative sense
+$L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$
+is an attenuation formula convolved with a spatial distribution of dust.
 
@@
 For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
-$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.
+$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
+is: (1) a \emph{uniform} screen is a screen equally thick between a region with
+stars which ionize gas and a region with stars which emit in the UV and do not
+ionize gas; (2) a \emph{dust-poor} galaxy is selected from a UV image and
+generally has low values of UV and H$\alpha$ attenuation; and (3) a \emph{dusty}
+galaxy is selected from an IR image and generally has high values of UV and
+H$\alpha$ attenuation.  The samples of dust-poor and dusty galaxies are not
+dichotomous.  More details are in the following section.
 
@@
 
-ALMA is beginning to produce images of the dust distributions in galaxies.
-These images lead to direct tests, independent of the attenuation formula, of
-the uniform screen assumption.  They also have the potential to reveal the
-parts of galaxies that may never be detected at UV and optical wavelengths:
-surprises surely abound.
+ALMA is beginning to produce images of the dust distributions in high-redshift
+galaxies.  These images lead to direct tests, independent of the attenuation
+formula, of the uniform screen assumption.  They also have the potential to
+reveal the parts of galaxies that may never be detected at UV and optical
+wavelengths: surprises surely abound.
 

### 2015-04-14 response.txt
Better summary of Liu results

@@
 
-The abstract has only a small fraction of the content of the paper. 
-Calzetti et al. 1994 has an extended discussion of the uniform screen
-model in sections 5.1 and 6.2.  We clarify our discussion of the uniform
-screen model in the Introduction.
+The abstract has a small fraction of the content of the paper. Calzetti
+et al. 1994 has an extended discussion of the uniform screen model in
+sections 5.1 and 6.2.  We clarify our discussion of the uniform screen
+model in the Introduction.
 
@@
 
+We clarify our summary of their conclusions.  The abstract has a small
+fraction of the content of the paper.  The clumpy distributions are
+discussed in detail in section 3.2.
+
 * "If we choose to think of dust distributions as clumpy [...] 60% of
@@
 this part.
+
+The referee has an incorrect link.  The paper we cite is: Calzetti, D.
+1997, AJ, 113, 162.
 

### 2015-04-14 paper.tex
Better summary of Liu results

@@
 The screen part of our assumption is suspect, but it may be a
-good approximation to the truth.  The
-screen assumption is qualitatively similar to a scenario in which dust is
-distributed in a large number of clumps \citep{calzetti94}.  \citet{liu13} find
-that the dust
-distribution around ionizing stars throughout M83 is clumpy at a spatial scale
-of 6 pc;
-if the spatial resolution is degraded to 100 pc, we conclude that the
-distribution around ionizing stars is a screen.  If we choose to think of dust
-distributions as clumpy, the number of clumps surrounding nonionizing
-UV-emitting stars in low-redshift dust-poor galaxies is 60\% of the number of
-clumps surrounding ionizing stars \citep{calzetti97a}.
+good approximation to the truth---the alternative assumption being that dust
+mixes with stars.  \citet{liu13} study the dust distribution of M83 at a
+spatial scale of 6 pc.  They divide M83 into a center and outskirts.  For each
+part, they calculate the percentage of regions with ionizing stars mixed with
+dust.  Only in the center does this percentage exceed 50.  If they degrade the
+spatial resolution to 100 pc, they conclude that the dust distribution around
+ionizing stars is a screen.  The screen assumption is qualitatively similar to
+a scenario in which dust is distributed in a large number of clumps
+\citep{calzetti94}.  If we choose to think of dust distributions as clumpy, the
+number of clumps surrounding nonionizing UV-emitting stars in low-redshift
+dust-poor galaxies is 60\% of the number of clumps surrounding ionizing stars
+\citep{calzetti97a}.
 

### 2015-04-28 response.txt
Final edits?

@@
 
+We agree that determinations of star formation rates are fraught with
+uncertainty. Attenuation does not have to decrease with increasing UV
+emission: galaxies may have one set of star forming regions which are
+totally buried and another set which are totally exposed.  Many papers
+discuss in much detail the assumptions made by those who convert
+luminosity to star formation rate.  K98 and the review article by Madau
+& Dickinson, which we cite in section 4, mention many of these same
+issues.
+
+An extended discussion on our part can be arbitrarily complex---for
+example, some in the stellar community might argue that we don't know
+even the evolution of the ionizing luminosity of a simple stellar
+population (Sana et al. 2012); some in the extragalactic community might
+argue that we're extrapolating a total infrared luminosity from two or
+three flux densities.  Our assumptions are strong but we do acknowledge
+them.  In our view these important details have deserved their own
+papers.
+
 * In section 3, I find very odd to present the results in terms of
@@
 
+We add this assumption to the first paragraph of section 4.
+
 * Last paragraph of the conclusion. I doubt ALMA will be used to provide
@@
 
+Integrated.
+
 * Please provide a reference for Willman 1. I assume many readers will
@@
 easy to access for those who are curious to know more about it.
+
+Provided.
 
@@
 
+We removed this statement.
+
 * "If we want to learn about galaxies, morphology should be a
@@
 on the physics of galaxies.
+
+We say that morphology should be a wavelength-independent word.  We do
+not say that morphology itself is independent of wavelength.  In our
+view the community reserves the word morphology for "what we see at
+visible wavelengths."
 
@@
 
+We expanded our discussion of k'(lambda).
+
 * "A low-redshift galaxy [...] underestimates the measured Halpha
 attenuation." Please back this with a reference.
+
+The relevant citations come at the end of the next sentence: Calzetti et
+al. 94 and 97b.
 
@@
 
+Any spatially bound object has outskirts but they are not always
+considered. We added a sentence.
+
 * Price+13 should be Price+14.
+
+Corrected.
 
@@
 
+Weiner et al. 2007 have a sample of galaxies with -23 < M_H < -21 for
+which the average correction is roughly constant.  This is the basis for
+our correction.
+
 * Editorial question, it looks odd that the second author of the paper
 is cited for data provided as "private communication".
+
+We don't know how else to cite the data.
 
@@
 
+We use the CE01 templates for all samples in the paper to be consistent.
+We have presented results based on both our luminosities and the
+luminosities from Overzier et al. 2011.
+
 * The TIR luminosities of the so-called dust-poor and dusty galaxies are
@@
 
+The UV luminosities are different.  We have discussed the origins of the
+low-redshift samples.
+
 * The title of Sect. 3.1 is unclear. One would wonder what "relation" is
@@
 
+Clarified.
+
 * Sect. 3.1, it would be useful to specify what exactly is the "low
 redshift IRX-beta relation".
+
+We are unsure what the referee means by "exactly."  Our subsequent
+sentences explain the IRX-beta relation.
 
@@
 
-As a final note, here is the assessment by a statistical expert on the
+We have mentioned and clarified these assumptions in the text.
+
+* As a final note, here is the assessment by a statistical expert on the
 fitting done in the paper: The choice of regression methodology in Fig 4
@@
 estimation at http://www2.astro.psu.edu/users/edf/Caltech_2014.
+
+The problem with nonparametric regression methods lies in the
+interpretation. We choose to fit through the origin because we want our
+model to lack dust around Ha emitting regions when there is no dust
+around UV emitting regions. A very basic prediction of the attenuation
+formula is that if the escape fraction is 1 at any wavelength it is 1 at
+all wavelengths.  Another basic prediction is that if the escape
+fraction is less than 1 at any wavelength it is less than 1 at all
+wavelengths.
+
+We mention a reason for the poor fit to the low-redshift dusty galaxies
+in section 3.4.  This section existed previously; we divided section 3.3
+into two sections for clarity.

### 2015-04-28 paper.tex
Final edits?

@@
 \usepackage{lscape}
+\usepackage{amsmath}
 \newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
@@
 Marseille Universit\'e, 13388 Marseille cedex 13, France}
-\altaffiltext{5}{Department of Astronomy, University of California Riverside,
-Riverside, CA 92521, USA}
+\altaffiltext{5}{Department of Physics \& Astronomy, University of California
+Irvine, Irvine, CA 92697, USA}
 \altaffiltext{6}{Space Telescope Science Institute, Baltimore, MD 21218, USA}
@@
 their stellar components: smooth ellipticals, tightly-wound spirals, clumpy
-disks, barred disks, train-wrecks, fuzzballs, and whatever Willman 1 is.
+disks, barred disks, train-wrecks, fuzzballs, and whatever Willman 1 is
+\citep{willman05,willman11}.
 Little more than spatial extent is known about distributions of dust in dusty
 galaxies
-\citep{younger10,diaz10,simpson15}.  (The arrangement of
-dust is often described, oddly, as its geometry.)  Yet spatial distributions of
+\citep{younger10,diaz10,simpson15}.  Yet spatial distributions of
 all galactic components have intrinsic value.  If we want to learn about
@@
 
-If we write an equation like this:
-
-\begin{math}
+If we write this equation:
+\begin{equation*}
 L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}} = 10^{-\mathrm{A}/2.5} = 10^{-\mathrm{E(B-V)} k(\lambda)/2.5}
-\end{math}
-
+\end{equation*}
 we assume a uniform screen not because $k(\lambda)$ is solely dependent on
@@
 distributions in low-redshift dust-poor galaxies grows even larger if we
-consider that galaxies have centers and outskirts.  A number of studies find
+consider that galaxies have centers and outskirts---that galaxies are not
+point sources.  A number of studies find
 that H$\alpha$ and UV attenuation decrease with increasing radius
@@
 densities in the COSMOS and UDS catalogs, to avoid the effects of source
-confusion on PSF fitting.  (Including them changes our results negligibly.)
+confusion on PSF fitting.  Including them changes our results negligibly.
 
@@
 al. (in prep.); Almaini et al. (in prep.); and
-M. Dickinson (private communication).  (Operationally both the
-100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.)
+M. Dickinson (private communication).  Operationally both the
+100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
 If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
@@
 surface brightness for the region of the direct image surrounding the galaxy.
-(The direct
-image is the image taken as part of the grism observations.)  We then fit
+The direct
+image is the image taken as part of the grism observations.  We then fit
 the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
@@
 the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
-densities (per the recommendations in the enhanced imaging products quick start
-guide); these sources are excluded.  The remaining 23 galaxies have flux
+densities per the recommendations in the enhanced imaging products quick start
+guide; these sources are excluded.  The remaining 23 galaxies have flux
 densities at
@@
 galaxies; we use the \citet{donley12} criteria, which are based on mid-IR flux
-densities (which all 3 CANDELS catalogs have).  These criteria will miss some
+densities, which all 3 CANDELS catalogs have.  These criteria will miss some
 AGN hosts \citep{juneau13}.  We accept the contaminants because in some fields
@@
 \begin{itemize}
-\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  (In
+\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  In
 relation to A$_{\mathrm{UV}}$,
-f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.)
+f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
 \item \alephha~is the escape fraction of the H$\alpha$ line luminosity.
@@
 
-\subsection{Reproducing the relation for dust-poor galaxies}
+\subsection{Reproducing the relation between escape fractions for dust-poor
+galaxies}
 
@@
 \begin{itemize}
-\item \alephuv~from IRX: \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
-L_{\mathrm{0.16}}$)+1)$^{-1}$.  (Equivalent to \alephuv~= [emergent UV
-SFR]/[IR SFR + emergent UV SFR].)
+\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
+L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
+SFR)/(IR SFR + emergent UV SFR).
 %\item \alephuvha~= \alephuv$^{0.33}$.
@@
 for the low-redshift
-dust-poor galaxies.  (If we use the IR and UV luminosities from
-\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.)  We lack
-uncertainties on any SFRs so we also perform a robust linear regression
-(which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv).  It
+dust-poor galaxies.  If we use the IR and UV luminosities from
+\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.  We lack
+uncertainties on any SFRs so we also perform a robust linear regression,
+which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv.  It
 returns a similar result, as does a bootstrap resampling.  We recover a relation
@@
 dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
-SFR (we treat it as the dependent variable) in the weighted fit.  The relation
+SFR---we treat it as the dependent variable---in the weighted fit.  The relation
 for dust-poor galaxies is seemingly inapplicable to dusty galaxies at
-low redshift.  In \S\ref{subsec:highz} and \ref{sec:discuss} we explain why we
+low redshift.  In \S\ref{subsec:select} and \ref{sec:discuss} we explain why we
 preface `inapplicable' with `seemingly.'
@@
 $q\,\log\,$\alephuv, finds $q = 0.47$, as does a simple linear regression using
-only the H$\alpha$-detected SFRs.  (None of the galaxies have limits for both
-the UV and H$\alpha$ SFRs.)  The main effect of including limits in the
+only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
+the UV and H$\alpha$ SFRs.  The main effect of including limits in the
 regression is to increase the standard error of the sample's best-fit index; a
@@
 %\end{figure}
+
+\subsection{Issues with the regressions}\label{subsec:select}
 
@@
 
-If we assume that dusty galaxies obey the \citet{calzetti00} attenuation
-formula, our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
+If we assume that dusty galaxies:
+\begin{enumerate}
+\item obey the \citet{calzetti00} attenuation formula; and
+\item were to have the same UV spectrum in the absence of dust,
+\end{enumerate}
+our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
 fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
@@
 because the true total SFR is higher, the true H$\alpha$ escape fraction is
-lower.  (Another scenario is that massive stars stopped forming within the last
-15 Myr.)  Perhaps some of the high-redshift dusty galaxies have
+lower.  Another scenario is that massive stars stopped forming within the last
+15 Myr.  Perhaps some of the high-redshift dusty galaxies have
 complicated star formation histories; the combined effect of deriving correct
@@
 \alephha~to predict the escape fraction of the H$\beta$ luminosity,
-\alephhb.  Both line luminosities are from ionized gas surrounding the same
-stars, so this prediction is immune to an uncertain star formation history.
-The ratio of intrinsic
-H$\alpha$ to H$\beta$ luminosities is 2.86 (under reasonable
-assumptions); with H$\beta$ observations, we can use
+\alephhb.  The ratio of intrinsic
+H$\alpha$ to H$\beta$ luminosities is 2.86 under reasonable
+assumptions; with H$\beta$ observations, we can use
 ($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86~=~\alephha/\alephhb~and from this
@@
 The histories are valid because the prediction is history-dependent and the
-determination is history-independent.  If
+determination is history-independent---both line luminosities are from ionized
+gas surrounding the same stars.  If
 the predicted and determined fractions disagree, the attenuation
@@
 \bibitem[Price et al.(2013)]{price13} Price, S.~H., Kriek, M., 
-Brammer, G.~B., et al.\ 2013, arXiv:1310.4177
+Brammer, G.~B., et al.\ 2014, \apj, 788, 86
 
@@
 
+\bibitem[Willman et al.(2011)]{willman11} Willman, B., Geha, M., 
+Strader, J., et al.\ 2011, \aj, 142, 128
+
+\bibitem[Willman et al.(2005)]{willman05} Willman, B., Blanton, 
+M.~R., West, A.~A., et al.\ 2005, \aj, 129, 2692
+
 \bibitem[Yamada et al.(2005)]{yamada05} Yamada, T., Kodama, T., 

### 2015-04-28 paper.tex
Removed enumerate

@@
 
-If we assume that dusty galaxies:
-\begin{enumerate}
-\item obey the \citet{calzetti00} attenuation formula; and
-\item were to have the same UV spectrum in the absence of dust,
-\end{enumerate}
+If we assume that dusty galaxies: (1) obey the \citet{calzetti00} attenuation
+formula; and (2) were to all have the same UV spectrum in the absence of dust;
 our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape

### 2015-04-28 paper.tex
Added Reddy discussion

@@
 comprise dusty and dust-poor galaxies; \citet{erb06} present evidence for
-uniform distributions in a similarly mixed sample.
+uniform distributions in a similarly mixed sample.  \citet{reddy15} argue
+that the uniformity of the dust distribution depends on the galaxy's
+star formation rate: as the star formation rate increases the dust distribution
+becomes less uniform.
 
@@
 \alephha~and \alephuvha~are similar to those found by \citet{onodera10},
-\citet{kashino13}, and \citet{price13} and conflict with those of
+\citet{kashino13}, \citet{price13}, and \citet{reddy15} and conflict with those of
 \citet{erb06}.  These studies assume the applicability of the \citet{calzetti00}
@@
 escape fractions for just the regions with nonionizing UV-emitting stars
-\citep{reddy10,reddy12,buat11,buat12,penner12,kriek13}.  The true attenuation
+\citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
 formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
@@
 this \citet{kriek13} formula and our result implies that
-\alephha~= \alephuvha$^{2.2}$.  If the true formula instead has a
+\alephha~= \alephuvha$^{2.2}$.  The \citep{reddy15} attenuation formula has
+\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
+If the true formula instead has a
 much lower 0.66$\,\micron$ escape fraction for a given UV escape
@@
 galaxies, our results agree with those of \citet{onodera10}, \citet{kashino13},
-and \citet{price13} and conflict with those of \citet{erb06}: \alephha~=
+\citet{price13}, and \citet{reddy15} and conflict with those of \citet{erb06}: \alephha~=
 \alephuvha$^{1.6}$.  They study
@@
 
+\bibitem[Reddy et al.(2015)]{reddy15} Reddy, N.~A., Kriek, M., 
+Shapley, A.~E., et al.\ 2015, arXiv:1504.02782
+
 \bibitem[Reddy et al.(2012)]{reddy12} Reddy, N., Dickinson, M.,

### 2015-05-13 response.txt
Final changes

@@
 
-The abstract has a small fraction of the content of the paper. Calzetti
-et al. 1994 has an extended discussion of the uniform screen model in
-sections 5.1 and 6.2.  We clarify our discussion of the uniform screen
-model in the Introduction.
+Calzetti et al. 1994 has an extended discussion of the uniform screen
+model in sections 5.1 and 6.2.  We clarify our discussion of the uniform
+screen model in the Introduction.
 
@@
 
+Fig. 2b of Madau & Dickinson 2014 shows negligible contamination to the
+UV luminosity from stars older than 10^8 Myr which were formed during a
+constant SFH.  L_UV/SFR reaches an asymptote, more or less.
+
+We do discuss the pitfalls of assuming that SFR(Halpha)=SFR(UV+IR).  Our
+method may not return relations with optimal dispersions.  We warn that
+this assumption will be unjustified for individual galaxies.  Thankfully
+we have large samples and are interested in average relations.
+
 An extended discussion on our part can be arbitrarily complex---for
@@
 
-We disagree.
+We believe that magnitudes are strange metrics.  A(Ha) = 2.5 is
+deceptive at a glance since we mean to write that we see only 10% of the
+intrinsic luminosity.  We have tried to write this paper for an audience
+comprising novices.
 
@@
 
-We hope our language clarifies this point.  We are only interested in
-the differential reddening if we believe the Calzetti formula applies to
-high-redshift dusty galaxies.  When we discuss whether high-redshift
-galaxies obey or disobey the Calzetti attenuation formula, we include Rv
-in our definition of the attenuation formula, k(lambda). (In short, we
+We hope our language clarifies this point.  When we discuss whether
+high-redshift galaxies obey or disobey the Calzetti attenuation formula,
+we include Rv in our definition of the attenuation formula, k(lambda).
+We are only interested in the E(B-V) relations if we believe the
+Calzetti formula applies to high-redshift dusty galaxies.  (In short, we
 do not aim to study the differential reddening.)
@@
 We say that morphology should be a wavelength-independent word.  We do
-not say that morphology itself is independent of wavelength.  In our
-view the community reserves the word morphology for "what we see at
-visible wavelengths."
+not say that morphology itself is independent of wavelength.
 
@@
 
-We clarify our summary of their conclusions.  The abstract has a small
-fraction of the content of the paper.  The clumpy distributions are
-discussed in detail in section 3.2.
+We clarify our summary of their conclusions.  The clumpy distributions
+are discussed in detail in section 3.2.
 
@@
 
-The referee has an incorrect link.  The paper we cite is: Calzetti, D.
-1997, AJ, 113, 162.
+The paper we cite is: Calzetti, D. 1997, AJ, 113, 162, not the paper at
+the provided link.
 
@@
 
-We don't know how else to cite the data.
+We don't know how else to cite the data.  We are publishing the data in
+the tables.
 
@@
 
-We are unsure what the referee means by "exactly."  Our subsequent
-sentences explain the IRX-beta relation.
+Our subsequent sentences explain the IRX-beta relation: the UV escape
+fraction is a function of IRX and an attenuation formula relates the
+escape fraction to beta.
 

### 2015-05-13 paper.tex
Final changes

@@
 high emergent UV luminosity and a low IR luminosity---a dust-poor
-galaxy---suffers a low amount of UV attenuation.  The \citet{calzetti00} formula
-predicts how much H$\alpha$ attenuation it should suffer; the prediction
-underestimates the measured H$\alpha$ attenuation.  The galaxy's regions with
+galaxy---has a high UV escape fraction.  The \citet{calzetti00} formula
+predicts its H$\alpha$ escape fraction; the prediction
+overestimates the measured H$\alpha$ escape fraction.  The galaxy's regions with
 $>10$ M$_{\odot}$ stars, which ionize gas, have more dust than its regions
@@
 point sources.  A number of studies find
-that H$\alpha$ and UV attenuation decrease with increasing radius
+that H$\alpha$ and UV escape fractions increase with increasing radius
 \citep{boissier04,prescott07,munoz09}.  Ionizing stars are surrounded by more
@@
 \citep{diaz10}.  Measuring a size is hard enough; imaging a distribution is
-even harder.  If a dusty galaxy's measured H$\alpha$ attenuation agreed with
+even harder.  If a dusty galaxy's measured H$\alpha$ escape fraction agreed with
 the prediction from the \citet{calzetti00} attenuation formula, we might
@@
 that the prediction is valid.  If a dusty galaxy's measured H$\alpha$
-attenuation disagreed with the prediction from the \citet{calzetti00}
+escape fraction disagreed with the prediction from the \citet{calzetti00}
 formula, the galaxy might have a nonuniform dust distribution, like that of a
@@
 In this paper, we ask the question, For dusty galaxies at $z \sim 0$ and
-$z \sim 1$, how does H$\alpha$ attenuation relate to the prediction made by
+$z \sim 1$, how do H$\alpha$ escape fractions relate to the predictions made by
 the \citet{calzetti00} attenuation formula?  We: (1) show that H$\alpha$
-attenuation differs from
+escape fractions differ from
 the prediction; (2) show that the relations between H$\alpha$ and UV
-attenuation differ from the relation for low-redshift dust-poor galaxies; and
+escape fractions differ from the relation for low-redshift dust-poor galaxies; and
 (3) argue that an interpretation in the context of dust distributions relies on
@@
 stars which ionize gas and a region with stars which emit in the UV and do not
-ionize gas; (2) a \emph{dust-poor} galaxy is selected from a UV image and
-generally has low values of UV and H$\alpha$ attenuation; and (3) a \emph{dusty}
-galaxy is selected from an IR image and generally has high values of UV and
-H$\alpha$ attenuation.  The samples of dust-poor and dusty galaxies are not
+ionize gas; (2) a \emph{dust-poor} galaxy generally has high values of UV and
+H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from an IR
+image and generally has low values of UV and H$\alpha$ escape fractions.  The
+samples of dust-poor and dusty galaxies are not
 dichotomous.  More details are in the following section.
@@
 
-We use IR, emergent UV, and H$\alpha$ luminosities to determine attenuation by
-dust.  In this section we detail our catalogs and samples.
+We use IR, emergent UV, and H$\alpha$ luminosities to determine escape
+fractions.  In this section we detail our catalogs and samples.
 
@@
 
-We use a nonstandard method to determine H$\alpha$ attenuation, so we test this
+We use a nonstandard method to determine H$\alpha$ escape fractions, so we test this
 method first for low-redshift dust-poor galaxies which have known dust
@@
 
-\bibitem[Calzetti(1997b)]{calzetti97b} Calzetti, D.\ 1997, American 
+\bibitem[Calzetti(1997b)]{calzetti97b} Calzetti, D.\ 1997b, American 
 Institute of Physics Conference Series, 408, 403
 
-\bibitem[Calzetti(1997a)]{calzetti97a} Calzetti, D.\ 1997, \aj, 113, 162
+\bibitem[Calzetti(1997a)]{calzetti97a} Calzetti, D.\ 1997a, \aj, 113, 162
 

### 2015-08-26 paper.tex
Started 2nd referee response

@@
 Susan Kassin\altaffilmark{6},
-Casey Papovich\altaffilmark{7},
+Casey Papovich\altaffilmark{7}, and
 Alexandra Pope\altaffilmark{8}
@@
 
+LBAs are a subset of galaxies from those in \citet{heckman05}.
+\citet{heckman05} match galaxies detected in the \emph{GALEX} All-Sky Imaging
+Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
+galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
+\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}
+\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
+and the radius is the half-light radius at 0.35$\,\micron$ ($u$-band);
+(3) $z < 0.3$; and (4) no evidence for emission from an AGN.
+
 We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
@@
 densities at
-0.15 and 0.23$\,\micron$ (NUV and FUV bands), from \emph{GALEX} observations.
+0.15 and 0.23$\,\micron$ (NUV and FUV bands).
 H$\alpha$ line
-fluxes, from SDSS observations, are from Overzier (private communication).  We
+fluxes are from Overzier (private communication).  We
 multiply the line fluxes by 1.67 as a fiber-aperture correction
@@
 \emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
+A low-redshift DOG has either: (1) a flux density at 9$\,\micron$ that is more
+than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
+12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
+A low-redshift control galaxy has a flux density at
+12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
+Among other criteria the sample of control galaxies is filled such that its
+distributions of IR luminosities and stellar masses match those of the sample
+of DOGs.
 The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
@@
 this \citet{kriek13} formula and our result implies that
-\alephha~= \alephuvha$^{2.2}$.  The \citep{reddy15} attenuation formula has
+\alephha~= \alephuvha$^{2.2}$.  The \citet{reddy15} attenuation formula has
 \alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
@@
 
+\bibitem[Heckman et al.(2005)]{heckman05} Heckman, T.~M., Hoopes, 
+C.~G., Seibert, M., et al.\ 2005, \apjl, 619, L35
+
 \bibitem[Kashino et al.(2013)]{kashino13} Kashino, D., Silverman, 
@@
 
-\bibitem[Price et al.(2013)]{price13} Price, S.~H., Kriek, M., 
+\bibitem[Price et al.(2014)]{price13} Price, S.~H., Kriek, M., 
 Brammer, G.~B., et al.\ 2014, \apj, 788, 86

### 2015-09-08 timeplot.py
Added code to generate timescale scatter plot

@@ -1,0 +1,131 @@
+#!/usr/bin/env python -tt
+
+import numpy
+import matplotlib.pyplot as plot
+from matplotlib.ticker import MultipleLocator
+
+table = numpy.genfromtxt('KFUV_KIR.dat')
+
+#sfrfinal = 30.
+
+uvfescs = 10.**(-.4*numpy.linspace(start = .55, stop = 5.5, num = 10))
+
+sfruv = uvfescs#*sfrfinal
+
+#sfrir = sfrfinal-sfruv
+
+sfrir = 1-sfruv
+
+kuvtime = 10.**(table[:,1])
+
+#kuvfinal = 1.4e-28*3.826e33/(3.e18/1600.)
+
+kuvfinal = kuvtime[-1]
+
+print kuvfinal
+
+uvcorrtime = kuvtime/kuvfinal
+
+newsfruv = numpy.dot(numpy.matrix(uvcorrtime).transpose(), numpy.matrix(sfruv))
+
+kirtime = 10.**table[:, 2:]
+
+#kirfinal = 4.5e-44*3.826e33
+
+kirfinal = kirtime[-1]
+
+print kirfinal
+
+ircorrtime = kirtime/kirfinal
+
+sfrirm = numpy.identity(sfrir.size)
+repind = numpy.diag_indices(sfrir.size)
+sfrirm[repind] = sfrir
+
+newsfrir = numpy.dot(numpy.matrix(ircorrtime), numpy.matrix(sfrirm))
+
+newsfrtot = newsfruv+newsfrir
+
+goodtimes = numpy.where(table[:,0] >= 7.3)[0]
+
+newsfrgood = newsfrtot[goodtimes, :]
+newsfruvgood = newsfruv[goodtimes, :]
+
+rangeuvfescs = (newsfruvgood/newsfrgood).transpose()
+
+hafescs = uvfescs**0.55
+
+sfrha = hafescs#*sfrfinal
+
+rangehafescs = (sfrha/newsfrgood).transpose()
+
+plot.rcParams['figure.figsize'] = [7.32, 7.32]
+color1 = '#d95f02'
+color2 = '#7570b3'
+fig, ax1 = plot.subplots()
+
+ax1.plot(uvfescs, rangehafescs, marker = 'o', color = 'k')
+
+ax1.plot(uvfescs, rangehafescs[:, -1], marker = 'o', color = color2)
+
[…]

### 2015-09-09 timeplot.py
timeplot makes a prettier plot

@@ -2,27 +2,25 @@
 
 import numpy
 import matplotlib.pyplot as plot
+import matplotlib.lines as mlines
+from matplotlib.legend_handler import HandlerLine2D
 from matplotlib.ticker import MultipleLocator
 
 table = numpy.genfromtxt('KFUV_KIR.dat')
 
-#sfrfinal = 30.
-
 uvfescs = 10.**(-.4*numpy.linspace(start = .55, stop = 5.5, num = 10))
 
-sfruv = uvfescs#*sfrfinal
-
-#sfrir = sfrfinal-sfruv
+sfruv = uvfescs
 
 sfrir = 1-sfruv
 
 kuvtime = 10.**(table[:,1])
 
-#kuvfinal = 1.4e-28*3.826e33/(3.e18/1600.)
+kuvfinal = 1.4e-28*3.826e33/(3.e18/1600.)
 
-kuvfinal = kuvtime[-1]
+#kuvfinal = kuvtime[-1]
 
-print kuvfinal
+#print kuvfinal
 
 uvcorrtime = kuvtime/kuvfinal
 
@@ -30,11 +28,11 @@ newsfruv = numpy.dot(numpy.matrix(uvcorrtime).transpose(), numpy.matrix(sfruv))
 
 kirtime = 10.**table[:, 2:]
 
-#kirfinal = 4.5e-44*3.826e33
+kirfinal = 4.5e-44*3.826e33
 
-kirfinal = kirtime[-1]
+#kirfinal = kirtime[-1]
 
-print kirfinal
+#print kirfinal
 
 ircorrtime = kirtime/kirfinal
 
@@ -55,22 +53,62 @@ rangeuvfescs = (newsfruvgood/newsfrgood).transpose()
 
 hafescs = uvfescs**0.55
 
-sfrha = hafescs#*sfrfinal
+sfrha = hafescs
 
 rangehafescs = (sfrha/newsfrgood).transpose()
 
 plot.rcParams['figure.figsize'] = [7.32, 7.32]
 color1 = '#d95f02'
-color2 = '#7570b3'
+color2 = '#1b9e77'
+
+#fig, ax1 = plot.subplots()
+
+#ax1.plot(uvfescs, rangehafescs, marker = 'o', color = 'k')
+
+#ax1.plot(uvfescs, rangehafescs[:, -1], marker = 'o', color = color2)
+
[…]

### 2015-09-14 paper.tex
Added code to generate timescale scatter plot
Added figure with duration spread and discussion

@@
 galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
-\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}
+\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}~
 \mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
@@
 because the true total SFR is higher, the true H$\alpha$ escape fraction is
-lower.  Another scenario is that massive stars stopped forming within the last
+lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
+could contribute to a given escape fraction.  The spread is imprecise for three
+reasons:
+\begin{enumerate}
+\item \citet{madau14} calculate conversion factors between luminosities and
+star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.  They
+assume a history of constant star formation rate to get factors as a function
+the duration of a star formation episode.
+\item \citet{madau14} use the models of \citet{conroy10} to calculate these
+conversion factors.  The conversion factor between $L_{\mathrm{IR}}$ and
+IR-derived SFR is a function of the UV escape fraction as well as the duration
+of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
+[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
+using the conversion factor for a fixed UV escape fraction.
+\item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
+$L_{\mathrm{IR}}$ are valid at different durations of the star formation
+episode.
+\end{enumerate}
+Another scenario is that massive stars stopped forming within the last
 15 Myr.  Perhaps some of the high-redshift dusty galaxies have
@@
 SFRs might lead to lower dispersion.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.5]{spread_hauv_age.eps}
+\caption{\label{spread}}
+\end{figure}
 
@@
 
+\bibitem[Conroy \& Gunn(2010)]{conroy10} Conroy, C., \& Gunn, J.~E.\ 2010, \apj,
+712, 833
+
 \bibitem[D{\'{\i}}az-Santos et al.(2010)]{diaz10} D{\'{\i}}az-Santos, T.,

### 2015-09-30 paper.tex
Final mods

@@
 The sample, from \citet{overzier11}, contains galaxies that lie roughly on
-the low-redshift IRX-$\beta$ relation.  This relation is a blunt instrument we
+the low-redshift IRX-$\beta$ relation (rederived in the same paper).  This
+relation is a blunt instrument we
 use to determine whether or not galaxies obey an attenuation formula at UV
@@
 is large, yet it is susceptible
-to our possibly invalid assumption that a galaxy's instantaneous SFR has,
-for at least $10^{8}$ yr, equaled its prolonged SFR.  For example, if most
+to our possibly invalid assumption that a galaxy's SFR has been
+constant for at least $10^{8}$ yr.  For example, if most
 massive stars formed over 15 Myr instead of 300 Myr, we should multiply
@@
 \item \citet{madau14} calculate conversion factors between luminosities and
-star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.  They
-assume a history of constant star formation rate to get factors as a function
-the duration of a star formation episode.
+star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.
 \item \citet{madau14} use the models of \citet{conroy10} to calculate these
@@
 [\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
-using the conversion factor for a fixed UV escape fraction.
+using the conversion factor for the given UV escape fraction.
 \item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
@@
 \includegraphics[scale=0.5]{spread_hauv_age.eps}
-\caption{\label{spread}}
+\caption{The spread of true escape fractions that could contribute to
+a given escape fraction if a galaxy's SFR has been constant for a
+duration different from $10^{8}$ yr.  We assign the input
+$f_{\mathrm{esc}}$ values to the conversion factors
+between luminosity and SFR in \citet{kennicutt98}.  The UV and IR conversion
+factors change as the duration of the star formation episode varies \citep{madau14}.
+The durations for the points shown here range from $2\times10^{7}$ to
+$1.5\times10^{10}$ yr.\label{spread}}
 \end{figure}

### 2015-09-30 timeplot.py

@@ -106,7 +106,7 @@ ax1.plot(rangeuvfescs, rangehafescs, marker = 'o', color = 'k', \
 linestyle = 'None')
 
 input = mlines.Line2D(uvfescs, hafescs, marker = 'o', color = color2, \
-linestyle = 'None', label = r'input f$_{esc}$', markeredgecolor = color2)
+linestyle = 'None', label = r'given f$_{esc}$', markeredgecolor = color2)
 
 ax1.add_line(input)
 
@@ -125,7 +125,7 @@ handles, labels = ax1.get_legend_handles_labels()
 extra = mlines.Line2D([], [], color = 'k', marker = 'o', linestyle = 'None')
 
 handles.append(extra)
-labels.append('output f$_{esc}$ for a different duration\nof a star formation history')
+labels.append('true f$_{esc}$ for a different duration\nof a star formation episode')
 
 handdict = {extra: HandlerLine2D(numpoints = 1), \
 input: HandlerLine2D(numpoints = 1)}

### 2015-10-29 paper.tex
Edits according to suggestions from Mark

@@
 interpretation of the overestimates for dusty galaxies at both redshifts is
-less clear.  If the attenuation formula is inapplicable to these galaxies,
+less clear.  If the Calzetti attenuation formula is inapplicable to these galaxies,
 perhaps the disagreements are unphysical; perhaps dust distributions in
@@
 We know little about dust distributions in low-redshift dusty galaxies, which
-have high IR luminosities and low-to-high emergent UV luminosities.  Their
+have high IR luminosities and wide-ranging emergent UV luminosities.  Their
 IR emitting regions span a range of sizes, from sub- to several kpc
@@
 stars which ionize gas and a region with stars which emit in the UV and do not
-ionize gas; (2) a \emph{dust-poor} galaxy generally has high values of UV and
-H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from an IR
+ionize gas; (2) a \emph{dust-poor} galaxy is selected from a UV image and
+generally has high values of UV and
+H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from a
+mid- or far-IR
 image and generally has low values of UV and H$\alpha$ escape fractions.  The
@@
 We replace $< 5\sigma$ H$\alpha$ line fluxes with limits.  We multiply the line
-fluxes and limits by 1.1 as an aperture correction.
+fluxes and limits by 1.1, the aperture correction.
 
@@
 100$\,\micron$ source to a source with a spectroscopic redshift in
-the catalogs of: \citet{lefevre04,szokoly04,mignoli05,yamada05,ravikumar07,
-vanzella08,lilly09,balestra10,fadda10,simpson12,kurk13,santini14}; Simpson et
-al. (in prep.); Almaini et al. (in prep.); and
-M. Dickinson (private communication).  Operationally both the
+the catalogs of:
+\citet{lefevre04,szokoly04,mignoli05,ravikumar07,vanzella08,
+balestra10,fadda10,kurk13,santini14}; and M. Dickinson (private communication)
+for GOODS-S;
+\citet{yamada05,simpson12}; Simpson et al. (in prep.); and
+Almaini et al. (in prep.) for UDS; and \citet{lilly09} for COSMOS.  Operationally both the
 100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
@@
 relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
-dust-obscured galaxies (DOGs) and a control sample: flux densities at
+dust-obscured galaxies (DOGs) and a control sample: flux densities ($S_{\nu}$
+units) at
 9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
@@
 each galaxy.  We redshift the \citet{chary01} template spectral energy
-distributions (SEDs) to the distance of each galaxy.  If the galaxy has one
-measured IR flux density, we find the SED that most closely matches that flux
+distributions (SEDs) to the distance of each galaxy.  Each template SED has
+an IR luminosity.  If the galaxy has one
+measured flux density at a rest-frame wavelength between 8 and 1000$\,\micron$,
+we find the redshifted SED that most closely matches that flux
 density and multiply the IR luminosity of the SED by the ratio between actual
@@
 the power-law fit to the rest-frame UV flux densities.  We refer to the
-luminosity as $0.16 \times L_{0.16}$.
+luminosity as $0.16 \times L_{0.16}$.  Fig. \ref{lir_luv} shows the IR and UV
+luminosities for all galaxies in our samples.  We emphasize that we use
+the adjective ``dusty'' because the average galaxy in the sample has a lower
+UV luminosity and a higher IR luminosity than does the average galaxy in the
+``dust-poor'' sample.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.44]{lir_luv_sample.eps}
+\caption{IR luminosity vs. emergent UV luminosity for the samples of dusty
+and dust-poor galaxies.\label{lir_luv}}
+\end{figure}
 
@@
 \begin{itemize}
-\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  In
+\item \alephuv~is the escape fraction of the continuum
+at rest-frame 0.16$\,\micron$.  In
 relation to A$_{\mathrm{UV}}$,
 f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
-\item \alephha~is the escape fraction of the H$\alpha$ line luminosity.
+\item \alephha~is the escape fraction of the H$\alpha$ emission line luminosity.
 \item \alephuvha~is the escape fraction extrapolated from \alephuv~to the
-wavelength of H$\alpha$---the attenuation formula prediction.  For the
+wavelength of H$\alpha$---the attenuation formula prediction for the escape
+fraction at rest-frame 0.66$\,\micron$.  For the
 attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
@@
 H$\alpha$ to H$\beta$
-line luminosities.  In the absence of dust the ratio is 2.86, so
-($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86~=~\alephha/\alephhb.  Since
-\alephhb~is a power-law function of \alephha, the ratio of line luminosities
-uniquely determines \alephha.
+line luminosities.  In the absence of dust and for Case B recombination
+the ratio is 2.86, so
+($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86 = \alephha/\alephhb.  Since
+they assume that \alephhb~is a power-law function of \alephha, the ratio of line
+luminosities uniquely determines \alephha.
 
@@
 fractions for low-redshift dust-poor galaxies; if we instead use the
-attenuation formula, we get \alephha~= \alephuvha$^{2.1}$.
+Calzetti attenuation formula, we get \alephha~= \alephuvha$^{2.1}$.
 
@@
 The sample, from \citet{overzier11}, contains galaxies that lie roughly on
-the low-redshift IRX-$\beta$ relation (rederived in the same paper).  This
+the low-redshift IRX-$\beta$ relation (rederived in the same paper).  IRX
+is IR luminosity divided by emergent UV luminosity.  This
 relation is a blunt instrument we
@@
 right panel of Fig. \ref{fha_fuv}).  This may reflect our constraint that
-\alephha~=1 when
-\alephuv~=1, but the lack of galaxies with H$\alpha$ escape fractions at or
-below the relation may be due to galaxies with H$\alpha$ SFRs below the limit
+\alephha~= 1 when
+\alephuv~= 1, but the lack of galaxies with H$\alpha$ escape fractions at or
+below the best-fit relation may be due to galaxies with H$\alpha$ SFRs below the limit
 of the sample.  We do not measure H$\alpha$ line flux limits for galaxies that
@@
 to a reasonable H$\alpha$ line flux limit for the grism observations
-($5 \times 10^{-17}$ erg s$^{-1}$ cm$^{-2}$), we fill in the space with low
+\citep[$5 \times 10^{-17}$ erg s$^{-1}$ cm$^{-2}$,][]{brammer12}, we fill in the space with low
 H$\alpha$ escape fractions at low UV escape fractions.  The decrease in
@@
 lower escape fractions than the extrapolation and higher escape fractions than
-they would have in low-redshift dust-poor galaxies.  A conclusion about the
-uniformity of dust distributions in high-redshift dusty galaxies is subject to
-an assumption about the attenuation formula.\label{fha_fuv}}}
+they would have in low-redshift dust-poor galaxies.\label{fha_fuv}}}
 \end{figure}
@@
 
-\bibitem[Santini et al.(2014)]{santini14} Santini, P., Ferguson, 
-H.~C., Fontana, A., et al.\ 2014, arXiv:1412.5180
+\bibitem[Santini et al.(2015)]{santini14} Santini, P., Ferguson, 
+H.~C., Fontana, A., et al.\ 2015, \apj, 801, 97
 

### 2015-10-29 paper.tex
Minor changes

@@
 relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
-dust-obscured galaxies (DOGs) and a control sample: flux densities ($S_{\nu}$
-units) at
+dust-obscured galaxies (DOGs) and a control sample: flux densities at
 9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
@@
 \emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
-A low-redshift DOG has either: (1) a flux density at 9$\,\micron$ that is more
+A low-redshift DOG has either: (1) a flux density, $S_{\nu}$, at 9$\,\micron$ that is more
 than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at

### 2016-03-08 paper_arxiv.tex
emulateapj version
Resize LIR vs LUV figure

--- 2015-05-13 paper.tex
@@
-\documentclass[preprint]{aastex}
-
-%\usepackage{phoenician}
-
-%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
-%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
-%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
-%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
-\usepackage{lscape}
+\documentclass[iop]{emulateapj}
+
 \usepackage{amsmath}
@@
 
-%This paper is organized as follows.  We present the data and derived quantities
-%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
-%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
 For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
@@
 all the low-redshift dust-poor galaxies have one measured IR flux density.
-%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
-%the signal-to-noise ratio of the flux density, in the single flux density
-%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
-%$\chi^{2}$-fitting case.
 
@@
 $\chi^{2}$.
-%The uncertainty on $\beta$ comes from the propagation of
-%flux density uncertainties, in the analytic case, or from the covariance
-%matrix times the reduced $\chi^{2}$, in the $\chi^{2}$-fitting case.
 
@@
 galaxies host an AGN \citep{overzier11}.
-
-\begin{landscape}
-\begin{deluxetable}{llllllllllllll}
-\tablecolumns{14}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the sample at $z > 0.7$
-\label{tbl:highz}}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA, IR} &
-\colhead{Dec, IR} &
-\colhead{RA, opt.} &
-\colhead{Dec, opt.} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{GOODS-S}
-53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
-53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
-53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
-53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
-53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09
-\enddata
-\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
-\tablecomments{Columns: RA and Dec, IR, are positions in the
-\emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
-priors.  RA and Dec, opt., are positions in the CANDELS catalogs.
-$L_{\mathrm{H}\alpha}$ lim. is a 5$\sigma$ upper limit to the H$\alpha$
-line luminosity.  The entire table is published in the electronic edition of
-\apj.  A portion is shown here for guidance regarding its form and content.}
-\end{deluxetable}
-\clearpage
-\end{landscape}
-
-\begin{landscape}
-\begin{deluxetable}{llllllllllllll}
-\tablecolumns{14}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the sample at $z > 0.7$}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA, IR} &
-\colhead{Dec, IR} &
-\colhead{RA, opt.} &
-\colhead{Dec, opt.} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{GOODS-S}
-53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
-53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
-53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
-53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
-53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09  \\
-53.177864 & -27.909479 & 53.177902 & -27.909540 & 1.104 & -2.24 & 0.07 & 5.7e+10 & 5.9e+08 & 4.5e+08 & 1.7e+07 & \ldots & 1.1e+11 & 4.7e+09  \\
-53.141853 & -27.901850 & 53.141862 & -27.901907 & 0.823 & -1.04 & 0.26 & 4.7e+09 & 3.3e+08 & 6.0e+07 & 6.7e+06 & \ldots & 9.4e+10 & 1.2e+09  \\
-53.086948 & -27.901337 & 53.086917 & -27.901404 & 0.967 & -1.69 & 0.18 & 1.3e+10 & 4.4e+08 & 2.5e+08 & 1.0e+07 & \ldots & 6.1e+10 & 1.1e+08  \\
-53.072140 & -27.898058 & 53.072299 & -27.898007 & 1.359 & -1.25 & 0.01 & 1.4e+10 & 1.2e+08 & 4.0e+08 & 2.0e+07 & \ldots & 2.2e+11 & 1.4e+10  \\
-53.169991 & -27.895391 & 53.170031 & -27.895423 & 0.977 & -2.06 & 0.17 & 1.3e+10 & 4.5e+08 & 4.0e+08 & 1.0e+07 & \ldots & 1.7e+11 & 1.4e+10  \\
-53.087067 & -27.895485 & 53.087099 & -27.895559 & 1.044 & 0.17 & 0.84 & 1.4e+09 & 1.9e+08 & \ldots & \ldots & 4.4e+07 & 1.3e+11 & 2.4e+10  \\
-53.232769 & -27.891096 & 53.232826 & -27.891097 & 0.983 & -1.67 & 0.20 & 1.6e+10 & 5.7e+08 & 4.0e+08 & 3.7e+07 & \ldots & 1.9e+11 & 6.1e+09  \\
-53.144283 & -27.890127 & 53.144189 & -27.890129 & 1.107 & -2.20 & 0.14 & 2.8e+10 & 5.0e+08 & 6.8e+08 & 2.9e+07 & \ldots & 4.6e+11 & 1.3e+10  \\
-53.197105 & -27.890034 & 53.197131 & -27.890055 & 1.296 & 0.00 & 0.15 & 1.8e+09 & 2.1e+08 & 2.1e+08 & 2.3e+07 & \ldots & 2.0e+11 & 4.0e+08  \\
-53.127056 & -27.886671 & 53.127085 & -27.886729 & 1.017 & -1.42 & 0.57 & 2.4e+09 & 2.7e+08 & 1.0e+08 & 1.3e+07 & \ldots & 8.4e+10 & 4.5e+09  \\
-53.213146 & -27.885704 & 53.213217 & -27.885701 & 0.979 & -1.51 & 0.22 & 1.3e+10 & 5.3e+08 & 3.2e+08 & 5.9e+07 & \ldots & 1.4e+11 & 8.0e+09  \\
-53.127460 & -27.881624 & 53.127474 & -27.881659 & 1.019 & -2.73 & 0.40 & 6.2e+09 & 4.2e+08 & 2.2e+08 & 3.1e+07 & \ldots & 1.2e+11 & 7.5e+09  \\
-53.198139 & -27.878679 & 53.198186 & -27.878674 & 1.249 & -1.82 & 0.08 & 6.9e+10 & 4.7e+08 & 8.4e+08 & 4.3e+07 & \ldots & 3.6e+11 & 5.1e+10  \\
-53.071480 & -27.880896 & 53.071486 & -27.880972 & 0.990 & -2.19 & 0.22 & 1.5e+10 & 5.9e+08 & \ldots & \ldots & 4.5e+08 & 1.3e+11 & 7.6e+09  \\
-53.076183 & -27.873486 & 53.076058 & -27.873614 & 0.740 & -0.40 & 0.25 & 3.2e+09 & 2.5e+08 & 2.1e+08 & 9.2e+06 & \ldots & 2.0e+11 & 1.1e+10  \\
-53.073376 & -27.874519 & 53.073386 & -27.874583 & 1.098 & -0.26 & 0.32 & 1.1e+10 & 4.3e+08 & 4.4e+08 & 4.6e+07 & \ldots & 3.7e+11 & 1.3e+10  \\
-53.071579 & -27.872364 & 53.071535 & -27.872459 & 1.097 & 0.28 & 0.57 & 3.9e+09 & 2.8e+08 & 3.1e+08 & 2.1e+07 & \ldots & 9.6e+11 & 9.4e+10  \\
-53.089268 & -27.864340 & 53.089349 & -27.864418 & 0.833 & -2.16 & 0.15 & 2.0e+10 & 7.6e+08 & 2.6e+08 & 1.1e+07 & \ldots & 6.5e+10 & 1.3e+07  \\
-53.178032 & -27.866461 & 53.178037 & -27.866461 & 1.123 & -1.53 & 0.47 & 5.2e+09 & 2.9e+08 & 2.4e+08 & 1.4e+07 & \ldots & 1.8e+11 & 9.6e+08  \\
-53.221905 & -27.859411 & 53.221923 & -27.859399 & 0.736 & -0.65 & 0.12 & 8.7e+09 & 3.5e+08 & \ldots & \ldots & 8.3e+07 & 8.3e+10 & 2.6e+09  \\
-53.135319 & -27.861332 & 53.135431 & -27.861352 & 0.997 & -1.67 & 0.41 & 4.9e+09 & 3.5e+08 & 1.5e+08 & 7.3e+06 & \ldots & 4.6e+10 & 1.9e+08  \\
-53.137783 & -27.856565 & 53.137827 & -27.856632 & 0.735 & 0.83 & 0.64 & 1.0e+09 & 2.0e+08 & \ldots & \ldots & 1.0e+08 & 5.6e+10 & 4.3e+09  \\
-53.130970 & -27.860342 & 53.130982 & -27.860409 & 1.382 & -1.25 & 0.01 & 1.9e+10 & 1.3e+08 & 3.4e+08 & 2.5e+07 & \ldots & 1.4e+11 & 5.5e+07  \\
-53.058479 & -27.856730 & 53.058534 & -27.856808 & 1.220 & -1.37 & 0.36 & 9.1e+09 & 2.7e+08 & \ldots & \ldots & 1.1e+08 & 1.7e+11 & 2.7e+08  \\
-53.056168 & -27.855335 & 53.056169 & -27.855367 & 1.226 & -1.75 & 0.20 & 1.8e+10 & 3.1e+08 & 4.8e+08 & 3.2e+07 & \ldots & 1.5e+11 & 7.3e+09  \\
-53.220245 & -27.854082 & 53.220274 & -27.854091 & 1.002 & -0.86 & 0.29 & 9.2e+09 & 4.4e+08 & 3.6e+08 & 3.7e+07 & \ldots & 4.3e+11 & 9.8e+09  \\
-53.220829 & -27.851294 & 53.220908 & -27.851331 & 0.734 & 4.05 & 1.17 & 8.7e+07 & 3.4e+07 & \ldots & \ldots & 7.0e+07 & 1.4e+11 & 1.3e+10  \\
-53.196545 & -27.851704 & 53.196571 & -27.851696 & 1.224 & 0.20 & 0.70 & 3.7e+09 & 2.0e+08 & 3.5e+08 & 2.3e+07 & \ldots & 6.3e+11 & 1.8e+10  \\
-53.122547 & -27.852680 & 53.122554 & -27.852730 & 0.735 & 1.74 & 1.32 & 2.2e+08 & 9.1e+07 & \ldots & \ldots & 4.9e+07 & 9.6e+10 & 3.2e+09  \\
-53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablenotemark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\
-53.070782 & -27.850611 & 53.070771 & -27.850671 & 0.991 & -3.56 & 0.72 & 2.8e+09 & 3.7e+08 & 1.8e+08 & 2.1e+07 & \ldots & 3.0e+11 & 8.7e+09  \\
-53.104969 & -27.849974 & 53.104994 & -27.850023 & 0.841 & -2.07 & 0.14 & 1.8e+10 & 6.4e+08 & 2.0e+08 & 1.4e+07 & \ldots & 4.8e+10 & 1.5e+09  \\
-53.115479 & -27.844624 & 53.115494 & -27.844666 & 1.097 & -0.94 & 0.30 & 1.1e+10 & 4.2e+08 & 6.5e+08 & 1.8e+07 & \ldots & 9.9e+11 & 8.1e+10  \\
-53.214821 & -27.845755 & 53.214866 & -27.845737 & 0.980 & -2.12 & 0.68 & 3.5e+09 & 4.1e+08 & 2.1e+08 & 1.7e+07 & \ldots & 1.1e+11 & 4.7e+09  \\
-53.186874 & -27.841162 & 53.186881 & -27.841169 & 0.783 & -1.43 & 0.14 & 1.2e+10 & 5.1e+08 & 1.0e+08 & 1.0e+07 & \ldots & 4.8e+10 & 2.1e+09  \\
-53.055374 & -27.843821 & 53.055380 & -27.843884 & 1.296 & -0.91 & 0.10 & 4.4e+09 & 2.8e+08 & \ldots & \ldots & 1.8e+08 & 2.1e+11 & 3.2e+09  \\
-53.107754 & -27.838791 & 53.107758 & -27.838812 & 1.095 & -1.93 & 0.11 & 2.7e+10 & 4.6e+08 & 1.1e+09 & 1.6e+08 & \ldots & 2.8e+11 & 6.6e+09  \\
-53.109276 & -27.835032 & 53.109331 & -27.834890 & 1.096 & -1.53 & 1.40 & 1.9e+09 & 3.3e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 1.3e+09  \\
-53.124714 & -27.842196 & 53.124767 & -27.842230 & 1.389 & -1.04 & 0.03 & 4.1e+09 & 8.6e+07 & 1.3e+08 & 1.3e+07 & \ldots & 1.4e+11 & 6.5e+09  \\
-53.214905 & -27.838238 & 53.214939 & -27.838237 & 0.853 & -1.59 & 0.09 & 3.1e+10 & 7.2e+08 & 5.1e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.8e+09  \\
-53.155365 & -27.835815 & 53.155401 & -27.835815 & 1.140 & -3.21 & 0.94 & 3.9e+09 & 3.7e+08 & \ldots & \ldots & 8.0e+07 & 1.1e+11 & 1.7e+09  \\
-53.215519 & -27.830894 & 53.215526 & -27.830835 & 0.736 & -0.17 & 0.15 & 7.1e+09 & 3.3e+08 & 4.6e+08 & 4.1e+07 & \ldots & 2.3e+11 & 3.3e+09  \\
-53.146038 & -27.833027 & 53.146185 & -27.832905 & 1.049 & -2.17 & 0.49 & 4.9e+09 & 3.7e+08 & 1.1e+08 & 1.0e+07 & \ldots & 6.8e+10 & 1.0e+09  \\
-53.218082 & -27.833673 & 53.218135 & -27.833687 & 0.853 & -1.05 & 0.21 & 8.2e+09 & 4.3e+08 & 2.6e+08 & 1.9e+07 & \ldots & 1.8e+11 & 6.5e+09  \\
-53.089886 & -27.828199 & 53.089889 & -27.828241 & 1.110 & -2.10 & 0.50 & 5.7e+09 & 3.3e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 1.4e+10  \\
-53.216496 & -27.821653 & 53.216570 & -27.821606 & 1.247 & -1.90 & 0.34 & 1.2e+10 & 2.5e+08 & \ldots & \ldots & 1.2e+08 & 1.5e+11 & 1.8e+09  \\
-53.051586 & -27.820166 & 53.051606 & -27.820193 & 1.048 & -2.14 & 0.09 & 4.2e+10 & 6.2e+08 & 1.9e+08 & 1.2e+07 & \ldots & 5.1e+10 & 4.2e+08  \\
-53.074184 & -27.821064 & 53.074268 & -27.821097 & 1.127 & -2.10 & 0.17 & 1.9e+10 & 4.0e+08 & 2.3e+08 & 2.4e+07 & \ldots & 6.9e+10 & 1.7e+09  \\
-53.066761 & -27.816540 & 53.066754 & -27.816593 & 1.413 & 11.31 & 11.23 & 9.3e+06 & 1.9e+09 & 3.5e+08 & 4.4e+07 & \ldots & 1.4e+12 & 6.6e+10  \\
-53.181011 & -27.817177 & 53.181037 & -27.817160 & 1.370 & -0.00 & 0.31 & 2.2e+09 & 6.3e+08 & \ldots & \ldots & 2.3e+08 & 9.8e+11 & 7.5e+10  \\
-53.149857 & -27.813999 & 53.149886 & -27.813998 & 1.307 & -1.44 & 0.06 & 7.6e+10 & 3.2e+09 & 8.8e+08 & 4.6e+07 & \ldots & 3.7e+11 & 3.8e+10  \\
-53.044754 & -27.816416 & 53.044892 & -27.816469 & 1.380 & -0.42 & 0.16 & 3.2e+09 & 3.8e+08 & \ldots & \ldots & 1.5e+08 & 3.4e+11 & 9.3e+10  \\
-53.145061 & -27.809834 & 53.145087 & -27.809851 & 1.245 & -1.87 & 0.14 & 9.4e+09 & 2.0e+08 & 2.5e+08 & 2.3e+07 & \ldots & 1.5e+11 & 2.0e+10  \\
-53.164284 & -27.810833 & 53.164307 & -27.810827 & 0.735 & 0.55 & 0.28 & 5.6e+08 & 6.5e+07 & 5.9e+07 & 1.1e+07 & \ldots & 3.6e+10 & 1.6e+08  \\
-53.073448 & -27.803240 & 53.073456 & -27.803292 & 0.735 & 2.17 & 1.10 & 2.3e+08 & 8.2e+07 & \ldots & \ldots & 6.6e+07 & 9.1e+10 & 1.3e+09  \\
-53.066555 & -27.797188 & 53.066761 & -27.797223 & 1.296 & 1.44 & 0.14 & 1.8e+09 & 3.2e+08 & \ldots & \ldots & 1.3e+08 & 3.1e+11 & 1.4e+10  \\
-53.076847 & -27.799187 & 53.076879 & -27.799206 & 1.079 & -2.19 & 0.24 & 1.3e+10 & 4.1e+08 & 1.7e+08 & 1.7e+07 & \ldots & 4.8e+10 & 7.1e+08  \\
-53.034164 & -27.797775 & 53.034171 & -27.797808 & 0.840 & 0.14 & 0.21 & 4.7e+09 & 2.6e+08 & 3.1e+08 & 2.3e+07 & \ldots & 3.2e+11 & 1.1e+10  \\
-53.156612 & -27.795471 & 53.156735 & -27.795577 & 1.097 & -1.51 & 0.10 & 1.5e+10 & 3.0e+08 & 2.7e+08 & 2.8e+07 & \ldots & 2.2e+11 & 2.2e+09  \\
-53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablenotemark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
-53.078960 & -27.799620 & 53.078906 & -27.799642 & 1.085 & -2.09 & 0.42 & 5.5e+09 & 3.1e+08 & 2.1e+08 & 1.1e+07 & \ldots & 6.7e+10 & 3.3e+07  \\
-53.026798 & -27.791296 & 53.026811 & -27.791322 & 1.022 & -1.04 & 0.22 & 1.0e+10 & 3.7e+08 & 5.7e+08 & 1.7e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
-53.184113 & -27.792627 & 53.184162 & -27.792636 & 0.737 & -0.82 & 0.06 & 9.3e+09 & 2.1e+08 & 2.1e+08 & 2.6e+07 & \ldots & 1.7e+11 & 1.5e+10  \\
-53.178066 & -27.792753 & 53.178077 & -27.792740 & 1.427 & -0.75 & 0.07 & 2.5e+09 & 1.1e+08 & \ldots & \ldots & 2.4e+08 & 2.8e+11 & 1.8e+08  \\
-53.086002 & -27.787987 & 53.086045 & -27.788089 & 0.734 & -0.29 & 0.11 & 7.2e+09 & 2.6e+08 & \ldots & \ldots & 1.1e+08 & 1.2e+11 & 5.3e+09  \\
-53.090660 & -27.790161 & 53.090665 & -27.790186 & 1.000 & -1.54 & 0.38 & 4.1e+09 & 3.0e+08 & 1.9e+08 & 1.1e+07 & \ldots & 1.1e+11 & 4.9e+09  \\
-53.166122 & -27.787506 & 53.166177 & -27.787515 & 1.112 & -2.06 & 0.07 & 3.3e+10 & 4.4e+08 & 7.3e+08 & 7.6e+07 & \ldots & 3.1e+11 & 1.8e+10  \\
-53.109558 & -27.788197 & 53.109568 & -27.788203 & 0.995 & -1.87 & 0.14 & 2.4e+10 & 5.8e+08 & 1.9e+08 & 1.4e+07 & \ldots & 6.0e+10 & 2.0e+08  \\
-53.176544 & -27.785450 & 53.176577 & -27.785446 & 1.314 & 2.94 & 0.31 & 5.3e+08 & 1.5e+08 & 9.9e+07 & 1.7e+07 & \ldots & 3.0e+11 & 2.7e+10  \\
-53.071011 & -27.785858 & 53.070981 & -27.785895 & 0.763 & -1.10 & 0.18 & 8.5e+09 & 4.5e+08 & 1.1e+08 & 1.2e+07 & \ldots & 1.2e+11 & 7.7e+08  \\
-53.197544 & -27.786417 & 53.197582 & -27.786395 & 1.098 & -2.98 & 0.77 & 1.3e+09 & 2.0e+08 & \ldots & \ldots & 1.3e+08 & 2.0e+11 & 5.9e+09  \\
-53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablenotemark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\
-53.104275 & -27.788363 & 53.104331 & -27.788388 & 1.357 & -0.62 & 0.20 & 4.7e+09 & 6.3e+08 & \ldots & \ldots & 8.8e+07 & 1.3e+11 & 4.9e+08  \\
-53.048252 & -27.783079 & 53.048272 & -27.783100 & 0.814 & -0.53 & 0.27 & 3.8e+09 & 2.8e+08 & 1.1e+08 & 6.4e+06 & \ldots & 8.5e+10 & 1.3e+10  \\
-53.135197 & -27.781746 & 53.135245 & -27.781672 & 1.437\tablenotemark{G} & -0.57 & 0.05 & 5.2e+09 & 1.9e+08 & 3.5e+08 & 1.7e+07 & \ldots & 2.5e+11 & 2.4e+10  \\
-53.044064 & -27.785015 & 53.044080 & -27.785048 & 1.045 & -1.39 & 0.19 & 1.4e+10 & 4.3e+08 & 1.8e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.5e+10  \\
-53.049721 & -27.779055 & 53.049747 & -27.779072 & 1.221 & -1.31 & 1.05 & 3.5e+09 & 2.5e+08 & 2.4e+08 & 2.2e+07 & \ldots & 3.1e+11 & 9.1e+09  \\
-53.128693 & -27.780367 & 53.128828 & -27.780418 & 1.173 & -1.03 & 0.43 & 3.5e+09 & 2.1e+08 & 2.0e+08 & 1.4e+07 & \ldots & 2.7e+11 & 9.2e+09  \\
-53.077465 & -27.780226 & 53.077453 & -27.780218 & 0.741 & 0.94 & 0.55 & 6.4e+08 & 1.1e+08 & 5.9e+07 & 7.7e+06 & \ldots & 6.2e+10 & 1.3e+09  \\
-53.064384 & -27.775332 & 53.064445 & -27.775372 & 0.735 & 3.60 & 0.86 & 1.9e+08 & 5.5e+07 & \ldots & \ldots & 1.0e+08 & 2.4e+11 & 1.9e+10  \\
-53.145199 & -27.777922 & 53.145238 & -27.777906 & 1.099 & -1.87 & 0.25 & 4.3e+09 & 2.0e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.0e+11 & 2.1e+10  \\
-53.058456 & -27.776129 & 53.058416 & -27.776186 & 0.837 & 1.28 & 0.73 & 6.5e+08 & 1.3e+08 & 7.0e+07 & 9.0e+06 & \ldots & 2.9e+11 & 2.8e+10  \\
-53.099220 & -27.777590 & 53.099269 & -27.777610 & 1.221 & -0.71 & 2.74 & 6.8e+08 & 1.4e+08 & \ldots & \ldots & 7.3e+07 & 9.6e+10 & 3.1e+08  \\
-53.050873 & -27.772442 & 53.050929 & -27.772409 & 1.033 & 0.48 & 0.55 & 3.6e+09 & 3.0e+08 & 2.1e+08 & 1.1e+07 & \ldots & 4.0e+11 & 2.4e+10  \\
-53.193066 & -27.775581 & 53.193097 & -27.775562 & 1.220 & 1.25 & 2.33 & 8.4e+08 & 1.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.2e+11 & 2.6e+07  \\
-53.036961 & -27.774698 & 53.037019 & -27.774734 & 1.032 & -3.31 & 0.86 & 3.2e+09 & 4.1e+08 & 1.8e+08 & 9.1e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
-53.105900 & -27.771418 & 53.105929 & -27.771412 & 0.896 & -1.20 & 0.30 & 6.4e+09 & 4.3e+08 & 4.3e+08 & 1.1e+07 & \ldots & 3.2e+11 & 2.2e+09  \\
-53.098351 & -27.766935 & 53.098373 & -27.766940 & 1.033 & 0.04 & 1.06 & 1.9e+09 & 3.2e+08 & \ldots & \ldots & 1.1e+08 & 2.6e+11 & 3.0e+10  \\
-53.162823 & -27.767178 & 53.162858 & -27.767160 & 1.216 & -1.65 & 0.02 & 1.7e+11 & 6.8e+08 & 3.0e+09 & 5.5e+07 & \ldots & 4.2e+11 & 1.2e+11  \\
-53.048225 & -27.773033 & 53.048221 & -27.773042 & 1.221 & -1.29 & 0.17 & 3.4e+10 & 4.2e+08 & 4.6e+08 & 3.9e+07 & \ldots & 2.3e+11 & 1.1e+10  \\
-53.149010 & -27.774282 & 53.149076 & -27.774305 & 1.094 & -1.03 & 0.43 & 2.7e+09 & 2.3e+08 & 1.0e+08 & 1.3e+07 & \ldots & 1.1e+11 & 1.2e+10  \\
-53.127968 & -27.771446 & 53.127979 & -27.771436 & 1.307 & -0.72 & 0.04 & 1.7e+10 & 4.7e+08 & 2.2e+08 & 3.8e+07 & \ldots & 2.1e+11 & 1.7e+10  \\
-53.102539 & -27.772264 & 53.102539 & -27.772288 & 1.221 & 0.97 & 1.49 & 1.5e+09 & 1.7e+08 & 1.3e+08 & 2.0e+07 & \ldots & 2.2e+11 & 2.4e+10  \\
-53.048153 & -27.770285 & 53.048020 & -27.770415 & 1.039 & -1.14 & 0.39 & 8.2e+09 & 4.7e+08 & \ldots & \ldots & 6.5e+07 & 1.6e+11 & 9.9e+09  \\
-53.181160 & -27.765703 & 53.181195 & -27.765678 & 1.220 & -1.57 & 0.23 & 2.0e+10 & 3.4e+08 & 7.7e+08 & 1.3e+08 & \ldots & 2.4e+11 & 1.2e+10  \\
-53.151356 & -27.766697 & 53.151369 & -27.766686 & 0.895 & -1.64 & 0.28 & 2.1e+09 & 1.7e+08 & 1.1e+08 & 5.2e+06 & \ldots & 9.8e+10 & 1.3e+10  \\
-53.026695 & -27.765194 & 53.026697 & -27.765210 & 1.329 & 3.30 & 0.76 & 2.7e+08 & 3.3e+08 & 3.2e+08 & 2.6e+07 & \ldots & 6.0e+11 & 1.4e+10  \\
-53.116947 & -27.768333 & 53.116997 & -27.768349 & 1.109 & -4.67 & 1.71 & 2.8e+09 & 5.1e+08 & 1.4e+08 & 1.1e+07 & \ldots & 2.7e+11 & 3.1e+10  \\
-53.096428 & -27.765188 & 53.096474 & -27.765180 & 1.223 & -0.98 & 0.44 & 8.4e+09 & 2.7e+08 & 4.1e+08 & 1.8e+07 & \ldots & 2.3e+11 & 1.6e+10  \\
-53.050854 & -27.765091 & 53.050873 & -27.765105 & 1.038 & -1.95 & 0.17 & 2.4e+10 & 6.1e+08 & 2.8e+08 & 1.9e+07 & \ldots & 1.4e+11 & 1.4e+09  \\
-53.094173 & -27.762905 & 53.094302 & -27.762978 & 0.840 & 0.26 & 3.08 & 2.0e+08 & 1.5e+08 & \ldots & \ldots & 2.9e+07 & 8.7e+10 & 9.6e+09  \\
-53.045513 & -27.762356 & 53.045611 & -27.762371 & 1.039 & -1.87 & 0.18 & 2.8e+10 & 7.2e+08 & 2.1e+08 & 1.5e+07 & \ldots & 5.7e+10 & 3.2e+07  \\
-53.163559 & -27.758949 & 53.163589 & -27.758952 & 1.095 & -0.30 & 0.22 & 4.9e+09 & 2.3e+08 & 1.8e+08 & 1.8e+07 & \ldots & 2.7e+11 & 2.3e+09  \\
-53.111877 & -27.757845 & 53.111931 & -27.757828 & 0.831 & -0.34 & 0.53 & 2.3e+09 & 3.1e+08 & 1.5e+08 & 1.4e+07 & \ldots & 2.0e+11 & 6.0e+09  \\
-53.195179 & -27.753788 & 53.195239 & -27.753782 & 0.840 & -0.74 & 0.26 & 5.2e+09 & 3.5e+08 & \ldots & \ldots & 6.6e+07 & 1.3e+11 & 6.3e+09  \\
-53.072784 & -27.757933 & 53.072914 & -27.757849 & 1.039 & -1.92 & 0.32 & 8.1e+09 & 4.0e+08 & 3.2e+08 & 9.0e+06 & \ldots & 2.7e+11 & 1.9e+10  \\
-53.022861 & -27.756960 & 53.022876 & -27.757005 & 1.189 & -1.94 & 1.47 & 2.1e+09 & 2.3e+08 & 3.5e+08 & 2.8e+07 & \ldots & 5.3e+11 & 2.1e+10  \\
-53.202320 & -27.751293 & 53.202349 & -27.751279 & 1.113 & -0.16 & 0.99 & 1.9e+09 & 2.2e+08 & \ldots & \ldots & 6.5e+07 & 2.6e+11 & 1.3e+10  \\
-53.024975 & -27.752018 & 53.024917 & -27.752059 & 1.068 & -1.89 & 0.30 & 7.9e+09 & 3.5e+08 & 3.8e+08 & 2.8e+07 & \ldots & 6.4e+11 & 1.2e+10  \\
-53.036190 & -27.752197 & 53.036203 & -27.752228 & 1.296 & 1.39 & 0.21 & 2.0e+09 & 5.6e+08 & 6.8e+08 & 2.8e+07 & \ldots & 8.4e+11 & 1.7e+10  \\
-53.096127 & -27.752499 & 53.096209 & -27.752536 & 0.995 & -1.44 & 0.85 & 2.3e+09 & 3.3e+08 & \ldots & \ldots & 4.8e+07 & 9.1e+10 & 5.1e+09  \\
-53.125889 & -27.751266 & 53.125899 & -27.751275 & 0.738 & -3.15 & 0.10 & 3.7e+10 & 1.1e+09 & 3.0e+08 & 8.7e+06 & \ldots & 1.2e+11 & 3.9e+10  \\
-53.063969 & -27.751907 & 53.063981 & -27.751923 & 0.861 & -1.44 & 0.18 & 1.0e+10 & 4.7e+08 & 1.6e+08 & 1.4e+07 & \ldots & 3.8e+10 & 1.9e+09  \\
-53.161648 & -27.746819 & 53.161600 & -27.746925 & 0.735 & 1.47 & 0.75 & 4.5e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 4.2e+11 & 8.9e+10  \\
-53.068554 & -27.746864 & 53.068721 & -27.746955 & 0.976 & -2.16 & 0.24 & 1.3e+10 & 5.7e+08 & 2.7e+08 & 2.2e+07 & \ldots & 3.0e+11 & 4.5e+09  \\
-53.110130 & -27.745434 & 53.110168 & -27.745444 & 1.014 & 11.47 & 7.24 & 1.0e+07 & 1.9e+07 & \ldots & \ldots & 5.8e+07 & 1.6e+11 & 6.6e+09  \\
-53.172813 & -27.744471 & 53.172863 & -27.744457 & 1.295 & -0.64 & 0.32 & 6.9e+09 & 1.5e+09 & \ldots & \ldots & 1.3e+08 & 3.0e+11 & 3.4e+10  \\
-53.107323 & -27.741886 & 53.107345 & -27.741911 & 0.891 & 2.54 & 2.80 & 1.6e+08 & 1.0e+08 & 1.4e+08 & 8.8e+06 & \ldots & 4.2e+11 & 5.3e+09  \\
-53.063469 & -27.743839 & 53.063481 & -27.743869 & 1.109 & -1.48 & 0.85 & 3.4e+09 & 3.4e+08 & 1.7e+08 & 1.7e+07 & \ldots & 2.2e+11 & 1.9e+10  \\
-53.068001 & -27.744961 & 53.067988 & -27.744958 & 1.111 & -2.23 & 0.24 & 1.4e+10 & 4.1e+08 & 2.7e+08 & 1.3e+07 & \ldots & 1.6e+11 & 7.2e+08  \\
-53.150074 & -27.739941 & 53.150126 & -27.739926 & 1.038 & -1.95 & 0.15 & 2.4e+10 & 5.6e+08 & 5.4e+08 & 4.0e+07 & \ldots & 2.0e+11 & 3.3e+09  \\
-53.083782 & -27.739586 & 53.083793 & -27.739570 & 1.217 & -0.44 & 0.44 & 7.4e+09 & 2.5e+08 & 4.2e+08 & 2.8e+07 & \ldots & 3.6e+11 & 1.8e+10  \\
-53.061565 & -27.742525 & 53.061590 & -27.742532 & 0.736 & 4.18 & 3.25 & 2.5e+07 & 2.5e+07 & 3.9e+07 & 4.0e+06 & \ldots & 1.5e+11 & 3.7e+09  \\
-53.204159 & -27.738546 & 53.204191 & -27.738536 & 0.984\tablenotemark{G} & -1.92 & 1.20 & 6.9e+09 & 1.3e+09 & 2.3e+08 & 1.5e+07 & \ldots & 1.4e+11 & 4.6e+09  \\
-53.144276 & -27.735434 & 53.144345 & -27.735558 & 1.224 & 0.90 & 1.11 & 2.2e+09 & 2.2e+08 & \ldots & \ldots & 9.1e+07 & 1.8e+11 & 1.0e+10  \\
-53.155808 & -27.735281 & 53.155851 & -27.735273 & 1.017 & -1.47 & 0.59 & 3.6e+09 & 3.5e+08 & 2.4e+08 & 1.5e+07 & \ldots & 1.7e+11 & 1.2e+10  \\
-53.175217 & -27.739241 & 53.175243 & -27.739235 & 1.152 & -2.55 & 0.42 & 8.3e+09 & 3.4e+08 & 2.1e+08 & 2.9e+07 & \ldots & 1.0e+11 & 5.6e+09  \\
-53.195465 & -27.735258 & 53.195491 & -27.735229 & 1.146 & -0.92 & 0.51 & 4.7e+09 & 2.7e+08 & 1.8e+08 & 1.2e+07 & \ldots & 2.2e+11 & 6.6e+08  \\
-53.099781 & -27.730268 & 53.099810 & -27.730302 & 1.311 & -1.63 & 0.02 & 3.5e+10 & 4.3e+08 & 5.6e+08 & 1.6e+07 & \ldots & 1.3e+11 & 4.2e+08  \\
-53.016594 & -27.727051 & 53.016606 & -27.727074 & 0.960 & -0.64 & 1.82 & 1.0e+09 & 3.3e+08 & 2.2e+08 & 1.4e+07 & \ldots & 4.1e+11 & 5.2e+09  \\
-53.061180 & -27.726936 & 53.061180 & -27.726970 & 0.981 & -2.02 & 0.37 & 3.8e+09 & 2.8e+08 & 1.0e+08 & 5.7e+06 & \ldots & 5.3e+10 & 9.6e+07  \\
-53.173592 & -27.724491 & 53.173807 & -27.724472 & 0.979 & -0.95 & 0.94 & 2.2e+09 & 3.5e+08 & 1.3e+08 & 9.9e+06 & \ldots & 2.9e+11 & 2.2e+10  \\
-53.039387 & -27.726641 & 53.039389 & -27.726633 & 1.023 & 2.94 & 1.30 & 6.3e+08 & 1.5e+08 & \ldots & \ldots & 4.8e+07 & 1.0e+11 & 2.4e+09  \\
-53.045628 & -27.724943 & 53.045637 & -27.724927 & 1.215 & -1.72 & 0.30 & 1.3e+10 & 3.1e+08 & 4.1e+08 & 2.1e+07 & \ldots & 2.3e+11 & 9.4e+09  \\
-53.125111 & -27.721893 & 53.125287 & -27.721940 & 1.098 & -0.23 & 0.25 & 9.2e+09 & 3.2e+08 & 5.0e+08 & 2.9e+07 & \ldots & 7.6e+11 & 2.1e+10  \\
-53.124729 & -27.716934 & 53.124780 & -27.717107 & 1.356 & -0.78 & 0.05 & 1.3e+10 & 4.8e+08 & 7.1e+08 & 4.2e+07 & \ldots & 1.2e+12 & 4.6e+10  \\
-53.094563 & -27.723654 & 53.094718 & -27.723585 & 0.738\tablenotemark{G} & -0.56 & 0.24 & 3.2e+09 & 2.4e+08 & 7.5e+07 & 6.7e+06 & \ldots & 3.1e+10 & 3.5e+07  \\
-53.173607 & -27.722679 & 53.173655 & -27.722641 & 0.978 & -2.56 & 17.70 & 1.2e+08 & 3.6e+08 & \ldots & \ldots & 4.3e+07 & 1.3e+11 & 3.8e+08  \\
-53.179310 & -27.722076 & 53.179350 & -27.722054 & 0.743 & -1.17 & 0.14 & 1.0e+10 & 4.4e+08 & 1.3e+08 & 1.3e+07 & \ldots & 5.8e+10 & 1.3e+09  \\
-53.171768 & -27.719393 & 53.171840 & -27.719363 & 1.222 & 4.77 & 9.38 & 9.0e+07 & 1.0e+08 & \ldots & \ldots & 6.5e+07 & 2.7e+11 & 6.3e+09  \\
-53.023632 & -27.714867 & 53.023645 & -27.714882 & 1.296 & -0.64 & 0.09 & 1.3e+10 & 1.2e+09 & 4.1e+08 & 2.1e+07 & \ldots & 2.5e+11 & 1.1e+10  \\
-53.150776 & -27.716162 & 53.150717 & -27.716194 & 0.967 & -1.22 & 0.09 & 3.9e+10 & 6.9e+08 & 8.7e+08 & 4.5e+07 & \ldots & 3.2e+11 & 1.3e+10  \\
-53.122067 & -27.712461 & 53.122076 & -27.712461 & 1.040 & -0.26 & 0.81 & 1.4e+09 & 1.9e+08 & 1.9e+08 & 1.0e+07 & \ldots & 1.6e+11 & 1.4e+10  \\
-53.142792 & -27.706961 & 53.142848 & -27.706937 & 1.088 & -0.40 & 0.29 & 1.2e+10 & 4.6e+08 & 3.3e+08 & 1.5e+07 & \ldots & 1.8e+11 & 3.2e+09  \\
-53.161484 & -27.705112 & 53.161488 & -27.705104 & 1.430 & -0.88 & 0.14 & 5.2e+09 & 4.8e+08 & 1.4e+08 & 1.6e+07 & \ldots & 2.9e+11 & 1.1e+09  \\
-53.166592 & -27.703928 & 53.166556 & -27.703810 & 0.815 & 3.03 & 0.09 & 7.6e+09 & 2.1e+08 & 1.1e+08 & 9.4e+06 & \ldots & 7.3e+10 & 1.1e+09  \\
-53.158775 & -27.705088 & 53.158811 & -27.705088 & 0.863 & -1.81 & 0.46 & 2.9e+09 & 3.3e+08 & 7.2e+07 & 8.6e+06 & \ldots & 5.8e+10 & 3.1e+10  \\
-53.139095 & -27.694304 & 53.139188 & -27.694145 & 1.045 & -1.01 & 0.54 & 5.2e+09 & 4.0e+08 & 1.9e+08 & 1.5e+07 & \ldots & 2.8e+11 & 9.0e+09  \\
-53.135094 & -27.697344 & 53.135083 & -27.697251 & 1.297 & -0.89 & 0.05 & 1.7e+10 & 5.0e+08 & 6.2e+08 & 4.2e+07 & \ldots & 4.3e+11 & 9.6e+09  \\
-53.111504 & -27.695997 & 53.111521 & -27.695987 & 0.734 & 0.40 & 0.48 & 1.4e+09 & 2.1e+08 & 1.0e+08 & 1.0e+07 & \ldots & 2.3e+11 & 5.7e+10  \\
-53.162651 & -27.692356 & 53.162680 & -27.692336 & 0.733\tablenotemark{G} & -1.34 & 0.15 & 8.7e+09 & 4.1e+08 & 9.0e+07 & 1.5e+07 & \ldots & 3.4e+10 & 9.1e+08  \\
-53.131149 & -27.688419 & 53.131169 & -27.688368 & 0.837 & -0.83 & 0.16 & 1.3e+10 & 5.4e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 4.2e+09  \\
-53.137051 & -27.689989 & 53.137075 & -27.689968 & 1.047 & -0.56 & 0.75 & 3.1e+09 & 3.4e+08 & 2.5e+08 & 4.2e+07 & \ldots & 3.3e+11 & 9.0e+09  \\
-53.088108 & -27.685200 & 53.088136 & -27.685181 & 1.110 & -1.41 & 0.43 & 1.0e+10 & 5.1e+08 & 2.9e+08 & 2.3e+07 & \ldots & 3.4e+11 & 1.4e+10  \\
-\cutinhead{COSMOS}
-150.137010 & 2.243688 & 150.137013 & 2.243673 & 0.752\tablenotemark{G} & 2.42 & 1.13 & 1.3e+08 & 6.4e+07 & \ldots & \ldots & 3.5e+07 & 6.9e+10 & 7.4e+09  \\
-150.117280 & 2.327124 & 150.117315 & 2.327120 & 0.903\tablenotemark{G} & -0.08 & 0.28 & 8.4e+09 & 1.1e+09 & 3.2e+08 & 2.0e+07 & \ldots & 2.7e+11 & 1.6e+10  \\
-150.130330 & 2.472160 & 150.130346 & 2.472122 & 0.924\tablenotemark{G} & 0.55 & 0.51 & 3.6e+09 & 8.6e+08 & 8.7e+07 & 1.2e+07 & \ldots & 1.1e+11 & 1.9e+08  \\
-150.155450 & 2.205458 & 150.155459 & 2.205452 & 0.783\tablenotemark{G} & 1.06 & 0.26 & 2.3e+09 & 2.5e+08 & 1.9e+08 & 1.3e+07 & \ldots & 2.9e+11 & 5.4e+09  \\
-150.067080 & 2.372434 & 150.067101 & 2.372425 & 1.257\tablenotemark{G} & 0.57 & 0.57 & 5.7e+09 & 3.1e+09 & 8.5e+08 & 5.5e+07 & \ldots & 6.9e+11 & 4.3e+10  \\
-150.105500 & 2.297602 & 150.105557 & 2.297617 & 0.951                  & 0.87 & 1.24 & 3.0e+09 & 1.7e+09 & 2.5e+08 & 1.5e+07 & \ldots & 6.7e+11 & 1.4e+10  \\
-150.064130 & 2.409601 & 150.064153 & 2.409603 & 0.895\tablenotemark{G} & 0.48 & 0.91 & 3.9e+09 & 1.7e+09 & 1.7e+08 & 1.3e+07 & \ldots & 1.6e+11 & 1.1e+10  \\
-150.112060 & 2.434008 & 150.112096 & 2.433991 & 1.120\tablenotemark{G} & 1.35 & 0.91 & 1.9e+09 & 1.6e+09 & \ldots & \ldots & 1.0e+08 & 2.3e+11 & 1.4e+10  \\
-150.096090 & 2.240252 & 150.096111 & 2.240252 & 0.802                  & 1.50 & 0.72 & 3.8e+08 & 1.1e+08 & 6.6e+07 & 1.3e+07 & \ldots & 2.5e+11 & 2.0e+10  \\
-150.095390 & 2.255131 & 150.095433 & 2.255139 & 0.727                  & 0.22 & 0.21 & 3.4e+09 & 3.2e+08 & \ldots & \ldots & 1.2e+08 & 2.3e+11 & 6.4e+09  \\
-150.164710 & 2.322803 & 150.164713 & 2.322820 & 0.791\tablenotemark{G} & -1.21 & 0.15 & 1.2e+10 & 7.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 1.2e+11 & 4.4e+09  \\
-150.103720 & 2.237653 & 150.103747 & 2.237663 & 0.799                  & -0.71 & 0.19 & 6.4e+09 & 4.9e+08 & 2.3e+08 & 3.2e+07 & \ldots & 8.1e+11 & 2.2e+11  \\
-150.078210 & 2.287351 & 150.078239 & 2.287367 & 0.931\tablenotemark{G} & 0.23 & 1.84 & 5.5e+08 & 4.9e+08 & \ldots & \ldots & 4.4e+07 & 8.9e+10 & 6.2e+07  \\
-150.071750 & 2.361027 & 150.071772 & 2.361027 & 0.908\tablenotemark{G} & 0.75 & 0.77 & 5.7e+09 & 2.2e+09 & 2.8e+08 & 3.4e+07 & \ldots & 3.3e+11 & 1.8e+10  \\
-150.134540 & 2.428741 & 150.134551 & 2.428717 & 0.932\tablenotemark{G} & 1.80 & 1.21 & 3.0e+08 & 2.2e+08 & 9.2e+07 & 1.4e+07 & \ldots & 1.5e+11 & 2.3e+09  \\
-150.068420 & 2.265476 & 150.068467 & 2.265490 & 0.981                  & 0.62 & 0.47 & 3.5e+09 & 7.6e+08 & 2.2e+08 & 2.7e+07 & \ldots & 1.9e+11 & 7.9e+09  \\
-150.179140 & 2.215912 & 150.179144 & 2.215902 & 0.806\tablenotemark{G} & -0.12 & 0.25 & 3.8e+09 & 3.9e+08 & 1.3e+08 & 2.6e+07 & \ldots & 1.5e+11 & 3.9e+07  \\
-150.177860 & 2.220603 & 150.177869 & 2.220627 & 1.148\tablenotemark{G} & -0.17 & 0.73 & 1.7e+09 & 6.4e+08 & \ldots & \ldots & 8.5e+07 & 2.1e+11 & 8.3e+09  \\
-150.115720 & 2.416342 & 150.115703 & 2.416347 & 1.119\tablenotemark{G} & -0.39 & 0.67 & 1.3e+10 & 4.1e+09 & 4.0e+08 & 3.6e+07 & \ldots & 4.6e+11 & 6.5e+09  \\
-150.089820 & 2.234895 & 150.089864 & 2.234888 & 0.838\tablenotemark{G} & 0.10 & 2.46 & 1.3e+09 & 1.4e+09 & \ldots & \ldots & 5.4e+07 & 1.7e+11 & 1.8e+10  \\
-150.075070 & 2.450793 & 150.075074 & 2.450787 & 0.942\tablenotemark{G} & 1.57 & 2.56 & 6.9e+08 & 1.0e+09 & \ldots & \ldots & 9.1e+07 & 2.3e+11 & 1.3e+09  \\
-150.188810 & 2.321018 & 150.188838 & 2.320997 & 1.000                  & 0.34 & 1.35 & 3.6e+09 & 2.0e+09 & 2.9e+08 & 2.6e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
-150.131530 & 2.294352 & 150.131561 & 2.294330 & 1.026\tablenotemark{G} & -1.08 & 0.23 & 1.4e+10 & 1.2e+09 & 3.1e+08 & 1.4e+07 & \ldots & 1.5e+11 & 4.4e+09  \\
-150.152270 & 2.219301 & 150.152287 & 2.219311 & 0.927                  & -0.01 & 0.32 & 5.6e+09 & 8.0e+08 & 4.8e+08 & 2.7e+07 & \ldots & 3.8e+11 & 8.2e+09  \\
-150.171950 & 2.278365 & 150.171969 & 2.278364 & 0.752\tablenotemark{G} & -0.13 & 0.35 & 1.7e+09 & 2.5e+08 & 7.6e+07 & 8.6e+06 & \ldots & 7.2e+10 & 2.6e+09  \\
-150.107370 & 2.329205 & 150.107409 & 2.329204 & 0.924                  & 0.65 & 1.38 & 5.2e+09 & 3.4e+09 & \ldots & \ldots & 1.3e+08 & 2.4e+11 & 6.1e+09  \\
-150.064780 & 2.336534 & 150.064830 & 2.336514 & 0.728\tablenotemark{G} & -0.22 & 0.27 & 2.5e+09 & 3.0e+08 & \ldots & \ldots & 6.9e+07 & 4.4e+10 & 1.5e+09  \\
-150.062250 & 2.366550 & 150.062272 & 2.366530 & 0.802\tablenotemark{G} & -0.39 & 0.25 & 3.7e+09 & 3.9e+08 & 2.1e+08 & 1.3e+07 & \ldots & 1.5e+11 & 3.7e+09  \\
-150.064500 & 2.264089 & 150.064595 & 2.264048 & 1.440\tablenotemark{G} & -0.39 & 0.34 & 9.5e+09 & 4.0e+09 & \ldots & \ldots & 3.0e+08 & 7.4e+11 & 5.5e+10  \\
-150.102160 & 2.438384 & 150.102177 & 2.438350 & 1.132\tablenotemark{G} & 1.27 & 0.87 & 2.8e+09 & 2.3e+09 & 7.2e+08 & 1.2e+08 & \ldots & 3.6e+11 & 1.9e+10  \\
-150.174710 & 2.360783 & 150.174714 & 2.360774 & 0.900                  & -0.34 & 0.86 & 1.1e+10 & 4.4e+09 & 2.5e+08 & 1.4e+07 & \ldots & 2.4e+11 & 5.8e+08  \\
-150.117960 & 2.374386 & 150.117998 & 2.374355 & 1.223\tablenotemark{G} & 0.41 & 0.69 & 3.8e+09 & 1.8e+09 & 4.1e+08 & 2.8e+07 & \ldots & 4.0e+11 & 2.9e+08  \\
-150.161460 & 2.320804 & 150.161505 & 2.320777 & 1.336\tablenotemark{G} & 1.32 & 0.63 & 6.9e+08 & 4.9e+08 & 1.8e+08 & 2.2e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
-150.099570 & 2.379767 & 150.099593 & 2.379752 & 0.902\tablenotemark{G} & 0.81 & 0.45 & 2.0e+09 & 4.6e+08 & 1.4e+08 & 1.3e+07 & \ldots & 1.2e+11 & 6.9e+09  \\
-150.142490 & 2.208299 & 150.142522 & 2.208290 & 0.847                  & -0.85 & 0.53 & 1.1e+10 & 2.4e+09 & 1.3e+08 & 1.6e+07 & \ldots & 8.6e+10 & 5.6e+09  \\
-150.070260 & 2.422965 & 150.070271 & 2.422970 & 0.754\tablenotemark{G} & -0.93 & 0.15 & 9.7e+09 & 6.4e+08 & 1.8e+08 & 1.1e+07 & \ldots & 1.1e+11 & 1.0e+10  \\
-150.123650 & 2.358258 & 150.123691 & 2.358244 & 0.728                  & -1.00 & 0.08 & 4.1e+10 & 1.5e+09 & 1.2e+09 & 7.0e+07 & \ldots & 3.7e+11 & 2.4e+10  \\
-150.152710 & 2.470547 & 150.152748 & 2.470508 & 0.843\tablenotemark{G} & -0.67 & 1.90 & 8.4e+09 & 6.7e+09 & \ldots & \ldots & 1.4e+08 & 1.9e+11 & 7.5e+09  \\
-150.152200 & 2.411514 & 150.152224 & 2.411407 & 0.897\tablenotemark{G} & 1.96 & 0.82 & 2.0e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 2.6e+11 & 1.9e+10  \\
-150.073580 & 2.346851 & 150.073650 & 2.346819 & 1.353                  & -0.34 & 0.32 & 3.2e+10 & 8.2e+09 & 9.0e+08 & 2.5e+07 & \ldots & 1.4e+12 & 1.4e+11  \\
-150.080390 & 2.238965 & 150.080432 & 2.238979 & 0.986\tablenotemark{G} & 1.35 & 1.40 & 2.8e+08 & 2.0e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 1.6e+07  \\
-150.081930 & 2.237998 & 150.081964 & 2.237983 & 0.984\tablenotemark{G} & -1.50 & 0.62 & 8.5e+09 & 2.0e+09 & 8.9e+07 & 1.3e+07 & \ldots & 1.3e+11 & 1.1e+10  \\
-150.148540 & 2.324634 & 150.148572 & 2.324626 & 0.837                  & 0.85 & 0.41 & 1.6e+09 & 2.9e+08 & 9.0e+07 & 1.2e+07 & \ldots & 1.6e+11 & 5.5e+08  \\
-150.167790 & 2.247098 & 150.167779 & 2.247093 & 0.870                  & 0.51 & 0.33 & 3.9e+09 & 6.2e+08 & 3.1e+08 & 1.9e+07 & \ldots & 2.5e+11 & 6.0e+09  \\
-150.149530 & 2.233487 & 150.149545 & 2.233485 & 0.731                  & -1.75 & 0.14 & 1.2e+10 & 7.5e+08 & \ldots & \ldots & 9.4e+07 & 1.5e+11 & 1.0e+10  \\
-150.154370 & 2.391244 & 150.154402 & 2.391255 & 0.902                  & -0.71 & 1.67 & 2.0e+10 & 1.5e+10 & 2.6e+08 & 2.7e+07 & \ldots & 2.1e+11 & 4.3e+08  \\
-150.116920 & 2.386939 & 150.116946 & 2.386924 & 0.940                  & -0.11 & 1.42 & 4.4e+09 & 2.7e+09 & 3.4e+08 & 1.6e+07 & \ldots & 2.6e+11 & 6.7e+09  \\
-150.071460 & 2.341721 & 150.071495 & 2.341707 & 0.941\tablenotemark{G} & 1.99 & 1.79 & 3.2e+08 & 3.3e+08 & 9.0e+07 & 1.5e+07 & \ldots & 2.6e+11 & 1.7e+10  \\
-150.087520 & 2.404057 & 150.087559 & 2.404051 & 0.748                  & 0.36 & 0.37 & 1.2e+09 & 2.0e+08 & 2.1e+08 & 1.5e+07 & \ldots & 1.6e+11 & 3.6e+09  \\
-150.102000 & 2.425978 & 150.102010 & 2.425966 & 0.727                  & 0.48 & 0.14 & 6.4e+09 & 4.1e+08 & 4.8e+08 & 4.3e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
-150.097510 & 2.401258 & 150.097538 & 2.401238 & 1.242\tablenotemark{G} & 0.92 & 1.23 & 6.2e+08 & 5.7e+08 & 2.1e+08 & 2.6e+07 & \ldots & 7.3e+11 & 3.2e+10  \\
-150.132210 & 2.437227 & 150.132215 & 2.437207 & 0.926\tablenotemark{G} & 0.86 & 1.70 & 2.2e+09 & 1.9e+09 & \ldots & \ldots & 1.4e+08 & 2.6e+11 & 1.3e+10  \\
-150.105220 & 2.435001 & 150.105247 & 2.434981 & 0.727                  & 2.22 & 0.30 & 1.0e+09 & 1.4e+08 & \ldots & \ldots & 6.0e+07 & 1.0e+11 & 1.9e+10  \\
-150.116700 & 2.265270 & 150.116728 & 2.265269 & 0.756\tablenotemark{G} & 1.00 & 0.40 & 9.7e+08 & 1.7e+08 & \ldots & \ldots & 7.7e+07 & 8.7e+10 & 2.8e+09  \\
-150.152130 & 2.444217 & 150.152159 & 2.444192 & 0.981\tablenotemark{G} & -0.63 & 1.05 & 1.3e+10 & 5.4e+09 & 2.6e+08 & 2.9e+07 & \ldots & 2.2e+11 & 1.5e+10  \\
-150.107380 & 2.206350 & 150.107397 & 2.206352 & 1.166\tablenotemark{G} & 3.24 & 1.39 & 2.9e+08 & 6.4e+08 & 2.8e+08 & 2.9e+07 & \ldots & 5.7e+11 & 3.4e+10  \\
-150.173220 & 2.363148 & 150.173229 & 2.363129 & 0.734\tablenotemark{G} & 1.28 & 0.55 & 5.3e+08 & 1.3e+08 & 7.2e+07 & 7.8e+06 & \ldots & 1.2e+11 & 3.3e+10  \\
-150.114380 & 2.221958 & 150.114410 & 2.221948 & 1.230\tablenotemark{G} & -0.35 & 0.74 & 3.2e+09 & 1.2e+09 & \ldots & \ldots & 1.2e+08 & 3.6e+11 & 2.8e+10  \\
-150.118560 & 2.223099 & 150.118579 & 2.223095 & 0.845\tablenotemark{G} & 1.33 & 1.79 & 6.4e+08 & 5.3e+08 & 1.1e+08 & 1.3e+07 & \ldots & 4.3e+11 & 5.8e+10  \\
-150.136430 & 2.320533 & 150.136464 & 2.320526 & 1.005\tablenotemark{G} & -1.01 & 1.33 & 2.3e+09 & 1.2e+09 & 1.6e+08 & 2.7e+07 & \ldots & 1.7e+11 & 3.7e+09  \\
-150.124970 & 2.310285 & 150.125006 & 2.310288 & 0.907\tablenotemark{G} & -0.95 & 0.67 & 1.2e+10 & 3.3e+09 & \ldots & \ldots & 4.9e+08 & 8.1e+10 & 6.1e+07  \\
-150.140310 & 2.365965 & 150.140338 & 2.365973 & 0.728                  & -0.32 & 0.22 & 3.8e+09 & 3.7e+08 & \ldots & \ldots & 1.2e+08 & 1.2e+11 & 1.1e+09  \\
-150.189650 & 2.316027 & 150.189674 & 2.316022 & 0.759\tablenotemark{G} & -0.22 & 0.31 & 2.2e+09 & 3.0e+08 & 9.6e+07 & 1.8e+07 & \ldots & 9.2e+10 & 5.1e+08  \\
-150.101190 & 2.460061 & 150.101191 & 2.460031 & 1.246\tablenotemark{G} & -0.03 & 0.86 & 2.2e+09 & 1.1e+09 & 2.4e+08 & 1.4e+07 & \ldots & 3.3e+11 & 1.5e+09  \\
-150.151420 & 2.294050 & 150.151440 & 2.294052 & 0.972\tablenotemark{G} & -0.27 & 0.83 & 3.8e+09 & 1.3e+09 & 1.6e+08 & 1.9e+07 & \ldots & 1.5e+11 & 7.0e+09  \\
-150.145470 & 2.293398 & 150.145507 & 2.293397 & 0.881                  & 0.36 & 1.09 & 2.6e+09 & 1.4e+09 & \ldots & \ldots & 6.6e+07 & 1.1e+11 & 4.9e+08  \\
-150.074170 & 2.384622 & 150.074210 & 2.384612 & 1.266\tablenotemark{G} & -1.53 & 4.14 & 4.0e+08 & 7.7e+08 & 1.6e+08 & 1.2e+07 & \ldots & 3.9e+11 & 1.6e+10  \\
-150.079370 & 2.408439 & 150.079421 & 2.408458 & 0.891                  & -1.25 & 0.30 & 1.0e+10 & 1.3e+09 & 9.9e+07 & 1.8e+07 & \ldots & 1.2e+11 & 6.3e+09  \\
-150.173920 & 2.317308 & 150.173946 & 2.317324 & 0.736                  & -0.47 & 0.19 & 5.2e+09 & 4.5e+08 & 1.4e+08 & 1.5e+07 & \ldots & 1.2e+11 & 1.2e+10  \\
-150.058980 & 2.301078 & 150.058982 & 2.301089 & 0.734\tablenotemark{G} & 0.59 & 0.40 & 1.1e+09 & 1.9e+08 & 9.4e+07 & 1.6e+07 & \ldots & 9.5e+10 & 1.9e+10  \\
-150.160250 & 2.300164 & 150.160269 & 2.300159 & 1.340\tablenotemark{G} & -0.54 & 0.45 & 2.8e+09 & 9.7e+08 & 1.2e+08 & 2.4e+07 & \ldots & 3.2e+11 & 1.0e+10  \\
-150.121460 & 2.267281 & 150.121483 & 2.267288 & 0.827                  & -1.50 & 0.58 & 2.8e+10 & 6.8e+09 & 3.5e+08 & 2.7e+07 & \ldots & 7.3e+10 & 3.0e+09  \\
-150.137630 & 2.340502 & 150.137613 & 2.340390 & 0.835\tablenotemark{G} & 2.69 & 2.03 & 3.5e+08 & 3.9e+08 & \ldots & \ldots & 4.9e+07 & 8.0e+10 & 3.1e+07  \\
-150.167260 & 2.355718 & 150.167275 & 2.355703 & 1.285\tablenotemark{G} & -0.72 & 0.66 & 4.0e+09 & 1.8e+09 & 2.3e+08 & 3.9e+07 & \ldots & 2.5e+11 & 1.6e+10  \\
-150.185690 & 2.222366 & 150.185690 & 2.222358 & 1.218\tablenotemark{G} & -0.12 & 0.37 & 8.4e+09 & 1.8e+09 & 4.7e+08 & 1.6e+07 & \ldots & 2.1e+11 & 5.7e+08  \\
-150.155170 & 2.405678 & 150.155234 & 2.405743 & 0.899\tablenotemark{G} & 2.31 & 2.33 & 1.0e+08 & 1.7e+08 & \ldots & \ldots & 5.8e+07 & 1.3e+11 & 3.9e+09  \\
-150.055920 & 2.233462 & 150.055985 & 2.233450 & 0.938                  & 0.14 & 0.28 & 1.2e+10 & 1.5e+09 & 3.8e+08 & 3.5e+07 & \ldots & 1.2e+12 & 9.1e+10  \\
-150.118520 & 2.415591 & 150.118543 & 2.415571 & 0.837                  & -1.77 & 0.18 & 6.5e+10 & 5.0e+09 & 5.6e+08 & 2.7e+07 & \ldots & 1.4e+11 & 2.8e+09  \\
-150.144420 & 2.415904 & 150.144400 & 2.415861 & 0.960\tablenotemark{G} & 0.01 & 1.05 & 3.3e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.9e+11 & 8.4e+09  \\
-150.126370 & 2.432899 & 150.126391 & 2.432867 & 1.277\tablenotemark{G} & 1.38 & 0.50 & 2.6e+09 & 1.6e+09 & 8.8e+08 & 3.9e+07 & \ldots & 1.0e+12 & 3.4e+10  \\
-150.081880 & 2.281767 & 150.081940 & 2.281754 & 0.736\tablenotemark{G} & -0.97 & 0.44 & 1.3e+09 & 2.5e+08 & 9.3e+07 & 1.7e+07 & \ldots & 9.8e+10 & 5.8e+07  \\
-150.100450 & 2.308010 & 150.100488 & 2.308021 & 0.950                  & -1.00 & 1.27 & 1.7e+10 & 8.5e+09 & 2.0e+08 & 3.5e+07 & \ldots & 1.6e+11 & 1.7e+09  \\
-150.136100 & 2.370533 & 150.136112 & 2.370532 & 0.927                  & 2.39 & 1.46 & 7.4e+08 & 6.9e+08 & 1.9e+08 & 2.0e+07 & \ldots & 7.4e+11 & 7.0e+10  \\
-150.169140 & 2.233916 & 150.169152 & 2.233893 & 1.233\tablenotemark{G} & -0.80 & 0.43 & 1.5e+10 & 3.1e+09 & 3.4e+08 & 3.2e+07 & \ldots & 2.3e+11 & 3.7e+08  \\
-150.108520 & 2.448166 & 150.108523 & 2.448100 & 1.413\tablenotemark{G} & 1.93 & 0.90 & 2.8e+08 & 7.7e+08 & 2.0e+08 & 3.1e+07 & \ldots & 4.6e+11 & 1.1e+10  \\
-150.112240 & 2.387377 & 150.112284 & 2.387391 & 0.757                  & 0.81 & 0.25 & 2.2e+09 & 2.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.3e+11 & 1.3e+10  \\
-150.103890 & 2.334655 & 150.103898 & 2.334752 & 0.940\tablenotemark{G} & -0.23 & 1.65 & 1.5e+09 & 1.1e+09 & 6.6e+07 & 8.3e+06 & \ldots & 1.8e+11 & 6.1e+09  \\
-150.190930 & 2.235499 & 150.190865 & 2.235393 & 0.864                  & -0.74 & 0.82 & 5.2e+09 & 1.9e+09 & 1.2e+08 & 1.3e+07 & \ldots & 9.5e+10 & 3.3e+08  \\
-150.128850 & 2.193221 & 150.128858 & 2.193227 & 0.878                  & 1.31 & 1.27 & 2.4e+09 & 1.6e+09 & \ldots & \ldots & 9.8e+07 & 1.5e+11 & 5.9e+09  \\
-150.128430 & 2.419489 & 150.128447 & 2.419440 & 0.741                  & -0.96 & 0.15 & 9.9e+09 & 6.8e+08 & 2.3e+08 & 2.0e+07 & \ldots & 9.8e+10 & 4.8e+08  \\
-150.170690 & 2.219165 & 150.170738 & 2.219240 & 0.958                  & 0.13 & 0.85 & 5.8e+09 & 2.1e+09 & \ldots & \ldots & 3.0e+08 & 2.0e+11 & 4.7e+09  \\
-150.192700 & 2.333416 & 150.192737 & 2.333482 & 1.081\tablenotemark{G} & 0.21 & 0.66 & 1.8e+09 & 7.8e+08 & \ldots & \ldots & 9.2e+07 & 1.3e+11 & 2.2e+08  \\
-150.159290 & 2.235417 & 150.159296 & 2.235413 & 0.932\tablenotemark{G} & -0.31 & 1.31 & 3.6e+09 & 2.0e+09 & \ldots & \ldots & 6.1e+07 & 1.4e+11 & 1.6e+10  \\
-150.130870 & 2.215121 & 150.130875 & 2.215134 & 0.859\tablenotemark{G} & 1.60 & 2.49 & 3.9e+08 & 5.8e+08 & \ldots & \ldots & 5.2e+07 & 2.1e+11 & 5.4e+09  \\
-150.110190 & 2.208473 & 150.110230 & 2.208474 & 1.249                  & -0.51 & 0.44 & 1.6e+10 & 3.6e+09 & 3.2e+08 & 4.1e+07 & \ldots & 2.5e+11 & 1.8e+08  \\
-150.109680 & 2.295734 & 150.109712 & 2.295693 & 1.325\tablenotemark{G} & -0.87 & 0.28 & 7.8e+09 & 1.7e+09 & 2.1e+08 & 3.0e+07 & \ldots & 3.7e+11 & 1.0e+10  \\
-150.172490 & 2.233643 & 150.172484 & 2.233629 & 0.925                  & -0.24 & 0.93 & 4.1e+09 & 1.7e+09 & 1.5e+08 & 1.7e+07 & \ldots & 1.5e+11 & 5.8e+09  \\
-150.094580 & 2.336367 & 150.094624 & 2.336350 & 0.910                  & 2.72 & 1.52 & 4.2e+08 & 4.3e+08 & 2.2e+08 & 1.5e+07 & \ldots & 5.4e+11 & 5.0e+10  \\
-150.083340 & 2.278458 & 150.083386 & 2.278446 & 0.837\tablenotemark{G} & 0.79 & 0.93 & 4.1e+08 & 1.7e+08 & 1.2e+08 & 1.0e+07 & \ldots & 2.6e+11 & 7.5e+09  \\
-150.114740 & 2.262723 & 150.114781 & 2.262725 & 0.750\tablenotemark{G} & -0.47 & 0.23 & 3.6e+09 & 3.7e+08 & 1.4e+08 & 1.4e+07 & \ldots & 7.8e+10 & 4.4e+09  \\
-150.172610 & 2.353894 & 150.172626 & 2.353883 & 0.757\tablenotemark{G} & 1.75 & 0.43 & 7.3e+08 & 1.4e+08 & 2.2e+08 & 3.4e+07 & \ldots & 4.6e+11 & 2.6e+10  \\
-150.067170 & 2.377246 & 150.067215 & 2.377236 & 0.804\tablenotemark{G} & -0.69 & 0.37 & 2.2e+09 & 3.4e+08 & 1.9e+08 & 9.6e+06 & \ldots & 1.6e+11 & 3.8e+09  \\
-150.118240 & 2.292143 & 150.118290 & 2.292122 & 1.103                  & 0.07 & 0.47 & 1.1e+10 & 3.0e+09 & 2.8e+08 & 2.6e+07 & \ldots & 3.5e+11 & 1.5e+10  \\
-150.103510 & 2.346108 & 150.103512 & 2.346125 & 1.031                  & -0.46 & 1.78 & 1.6e+10 & 1.1e+10 & 9.9e+08 & 8.5e+07 & \ldots & 6.8e+11 & 4.3e+09  \\
-150.117520 & 2.285153 & 150.117534 & 2.285159 & 0.921\tablenotemark{G} & -0.88 & 0.95 & 2.7e+09 & 1.1e+09 & 9.7e+07 & 1.5e+07 & \ldots & 9.7e+10 & 1.4e+10  \\
-150.165510 & 2.246267 & 150.165496 & 2.246271 & 0.870                  & -1.30 & 0.53 & 1.1e+10 & 2.4e+09 & 1.7e+08 & 2.4e+07 & \ldots & 1.0e+11 & 1.0e+10  \\
-150.164850 & 2.354424 & 150.164879 & 2.354407 & 1.263\tablenotemark{G} & -0.06 & 0.39 & 5.5e+09 & 1.8e+09 & 4.9e+08 & 2.6e+07 & \ldots & 3.9e+11 & 5.7e+10  \\
-150.082600 & 2.366448 & 150.082676 & 2.366546 & 1.208\tablenotemark{G} & -0.54 & 0.81 & 4.1e+09 & 1.7e+09 & \ldots & \ldots & 7.2e+07 & 1.6e+11 & 1.4e+08  \\
-150.085750 & 2.297658 & 150.085794 & 2.297659 & 1.254\tablenotemark{G} & 0.01 & 0.19 & 2.4e+10 & 3.9e+09 & 2.1e+09 & 8.3e+07 & \ldots & 2.0e+12 & 9.4e+10  \\
-150.114050 & 2.353890 & 150.114076 & 2.353853 & 1.100\tablenotemark{G} & 5.49 & 1.05 & 7.7e+08 & 2.7e+09 & 1.9e+08 & 1.6e+07 & \ldots & 3.3e+11 & 3.3e+09  \\
-150.063620 & 2.254643 & 150.063636 & 2.254647 & 1.087\tablenotemark{G} & -0.48 & 0.41 & 7.0e+09 & 1.6e+09 & 2.1e+08 & 1.3e+07 & \ldots & 1.0e+11 & 8.4e+07  \\
-150.135490 & 2.245705 & 150.135500 & 2.245705 & 0.907                  & 0.54 & 1.32 & 3.0e+09 & 1.9e+09 & 2.8e+08 & 4.4e+07 & \ldots & 3.2e+11 & 5.5e+09  \\
-150.097230 & 2.302491 & 150.097290 & 2.302497 & 1.462\tablenotemark{G} & -0.26 & 0.30 & 4.1e+09 & 2.0e+09 & 4.3e+08 & 4.0e+07 & \ldots & 5.6e+11 & 1.5e+08  \\
-150.144750 & 2.334391 & 150.144778 & 2.334385 & 0.861\tablenotemark{G} & 1.24 & 0.30 & 1.8e+09 & 2.9e+08 & 2.7e+08 & 2.3e+07 & \ldots & 2.1e+11 & 3.2e+10  \\
-150.073480 & 2.226387 & 150.073503 & 2.226385 & 1.040                  & -0.57 & 1.37 & 1.3e+10 & 6.6e+09 & \ldots & \ldots & 1.0e+09 & 3.8e+11 & 1.8e+10  \\
-150.187670 & 2.344660 & 150.187630 & 2.344672 & 1.302\tablenotemark{G} & -1.43 & 0.29 & 1.0e+10 & 1.5e+09 & 3.3e+08 & 1.8e+07 & \ldots & 3.5e+11 & 2.1e+08  \\
-150.101470 & 2.278431 & 150.101499 & 2.278435 & 0.755                  & -1.71 & 0.16 & 8.8e+09 & 6.2e+08 & \ldots & \ldots & 6.8e+07 & 1.0e+11 & 4.1e+09  \\
-150.148310 & 2.367414 & 150.148341 & 2.367409 & 1.429\tablenotemark{G} & -0.20 & 0.25 & 4.3e+09 & 1.3e+09 & 3.8e+08 & 4.1e+07 & \ldots & 4.5e+11 & 8.4e+10  \\
-150.143560 & 2.268420 & 150.143583 & 2.268431 & 0.886\tablenotemark{G} & 1.53 & 1.26 & 8.9e+08 & 6.2e+08 & 1.9e+08 & 1.7e+07 & \ldots & 2.4e+11 & 6.2e+09  \\
-150.141210 & 2.272969 & 150.141229 & 2.272974 & 0.942\tablenotemark{G} & -0.24 & 0.86 & 4.1e+09 & 1.5e+09 & 2.4e+08 & 8.3e+06 & \ldots & 1.4e+11 & 8.3e+08  \\
-150.077410 & 2.437059 & 150.077456 & 2.437006 & 0.897\tablenotemark{G} & 1.70 & 3.08 & 3.3e+08 & 5.9e+08 & 7.7e+07 & 1.3e+07 & \ldots & 8.9e+10 & 7.9e+07  \\
-150.148070 & 2.331341 & 150.148097 & 2.331332 & 0.856\tablenotemark{G} & 1.99 & 1.17 & 6.8e+08 & 4.9e+08 & 1.7e+08 & 1.8e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
-150.153930 & 2.276188 & 150.153960 & 2.276199 & 1.215\tablenotemark{G} & 0.45 & 0.63 & 6.7e+09 & 2.6e+09 & 4.7e+08 & 4.7e+07 & \ldots & 3.3e+11 & 1.1e+10  \\
-150.069910 & 2.295822 & 150.069951 & 2.295813 & 0.731                  & -0.57 & 0.41 & 1.5e+09 & 2.6e+08 & \ldots & \ldots & 7.3e+07 & 9.7e+10 & 1.9e+09  \\
-150.087940 & 2.326192 & 150.087979 & 2.326153 & 0.939\tablenotemark{G} & -0.12 & 0.62 & 7.9e+09 & 2.1e+09 & 2.7e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.2e+06  \\
-150.130570 & 2.361473 & 150.130581 & 2.361458 & 1.410\tablenotemark{G} & 0.19 & 0.10 & 9.4e+09 & 1.5e+09 & 3.2e+08 & 4.0e+07 & \ldots & 5.5e+11 & 4.2e+10  \\
-150.177530 & 2.261224 & 150.177536 & 2.261222 & 0.879                  & -1.50 & 0.39 & 1.8e+10 & 2.9e+09 & 1.5e+08 & 1.8e+07 & \ldots & 9.0e+10 & 1.0e+09  \\
-150.176210 & 2.264468 & 150.176229 & 2.264448 & 1.008\tablenotemark{G} & -0.78 & 0.59 & 6.7e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.8e+11 & 4.6e+07  \\
-150.145010 & 2.336923 & 150.145032 & 2.336921 & 0.937                  & 0.06 & 1.66 & 7.4e+09 & 5.4e+09 & 2.9e+08 & 5.7e+07 & \ldots & 2.9e+11 & 4.2e+07  \\
-150.088740 & 2.252818 & 150.088796 & 2.252822 & 0.728                  & 1.71 & 0.58 & 3.3e+08 & 8.7e+07 & \ldots & \ldots & 5.3e+07 & 1.3e+11 & 6.2e+09  \\
-150.139590 & 2.407071 & 150.139609 & 2.407059 & 0.901                  & 0.62 & 0.80 & 2.1e+09 & 8.2e+08 & 1.3e+08 & 2.1e+07 & \ldots & 1.2e+11 & 4.5e+09  \\
-150.143610 & 2.439931 & 150.143607 & 2.439900 & 1.150\tablenotemark{G} & 0.24 & 1.30 & 9.9e+08 & 9.7e+08 & \ldots & \ldots & 9.6e+07 & 3.0e+11 & 1.6e+10  \\
-150.169510 & 2.262296 & 150.169517 & 2.262296 & 1.106\tablenotemark{G} & 0.01 & 1.21 & 1.8e+09 & 1.3e+09 & 2.0e+08 & 1.6e+07 & \ldots & 2.1e+11 & 2.0e+08  \\
-150.079250 & 2.448390 & 150.079318 & 2.448336 & 1.401\tablenotemark{G} & -1.05 & 0.14 & 2.2e+10 & 3.2e+09 & 1.5e+08 & 2.7e+07 & \ldots & 2.9e+11 & 2.4e+08  \\
-150.108410 & 2.214345 & 150.108425 & 2.214340 & 0.986\tablenotemark{G} & -0.88 & 1.34 & 6.0e+09 & 3.2e+09 & 2.0e+08 & 1.9e+07 & \ldots & 2.0e+11 & 2.5e+08  \\
-150.157770 & 2.329275 & 150.157817 & 2.329266 & 0.905\tablenotemark{G} & 0.32 & 1.43 & 2.1e+09 & 1.4e+09 & \ldots & \ldots & 6.8e+07 & 3.6e+11 & 1.4e+10  \\
-150.153430 & 2.443099 & 150.153473 & 2.443077 & 0.901\tablenotemark{G} & -0.03 & 0.54 & 1.1e+10 & 2.7e+09 & 1.1e+08 & 1.8e+07 & \ldots & 4.6e+11 & 7.8e+10  \\
-150.075630 & 2.387739 & 150.075652 & 2.387737 & 1.264\tablenotemark{G} & -0.90 & 0.84 & 3.8e+09 & 2.0e+09 & 3.1e+08 & 2.5e+07 & \ldots & 3.9e+11 & 7.9e+07  \\
-150.090770 & 2.413311 & 150.090791 & 2.413293 & 0.732\tablenotemark{G} & 0.22 & 0.21 & 3.7e+09 & 3.5e+08 & 2.7e+08 & 2.8e+07 & \ldots & 1.3e+11 & 1.7e+10  \\
-150.147550 & 2.472620 & 150.147578 & 2.472604 & 0.900\tablenotemark{G} & 0.70 & 0.92 & 3.7e+09 & 1.7e+09 & 2.5e+08 & 2.3e+07 & \ldots & 3.0e+11 & 4.2e+10  \\
-150.105770 & 2.380248 & 150.105812 & 2.380245 & 0.916\tablenotemark{G} & -0.43 & 1.07 & 1.9e+10 & 8.9e+09 & 6.0e+08 & 3.8e+07 & \ldots & 5.0e+11 & 2.3e+10  \\
-150.115000 & 2.380963 & 150.115038 & 2.380956 & 1.137                  & 0.49 & 0.57 & 6.2e+09 & 2.4e+09 & 3.4e+08 & 4.1e+07 & \ldots & 2.7e+11 & 3.2e+09  \\
-150.133530 & 2.261941 & 150.133542 & 2.261944 & 0.751                  & -0.78 & 0.18 & 6.1e+09 & 4.8e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 2.1e+10  \\
-150.130290 & 2.259621 & 150.130309 & 2.259626 & 0.749                  & -1.00 & 0.30 & 2.3e+09 & 3.0e+08 & \ldots & \ldots & 5.9e+07 & 9.0e+10 & 5.4e+09  \\
-150.127840 & 2.277855 & 150.127861 & 2.277863 & 0.930\tablenotemark{G} & -0.51 & 0.38 & 4.1e+09 & 6.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 9.8e+10 & 9.8e+09  \\
-150.110260 & 2.193960 & 150.110268 & 2.193980 & 1.159                  & 1.18 & 0.97 & 2.4e+09 & 1.7e+09 & 2.3e+08 & 3.3e+07 & \ldots & 4.5e+11 & 7.0e+10  \\
-150.098190 & 2.414925 & 150.098213 & 2.414914 & 0.841\tablenotemark{G} & -0.19 & 1.87 & 2.5e+09 & 2.0e+09 & 1.0e+08 & 1.1e+07 & \ldots & 1.2e+11 & 1.7e+08  \\
-150.079710 & 2.295934 & 150.079746 & 2.295947 & 1.101\tablenotemark{G} & -0.18 & 0.44 & 1.0e+10 & 2.6e+09 & 3.7e+08 & 1.5e+07 & \ldots & 2.1e+11 & 3.5e+08  \\
-150.179060 & 2.364153 & 150.179074 & 2.364139 & 1.343                  & 0.31 & 0.18 & 1.4e+10 & 2.2e+09 & 8.6e+08 & 4.7e+07 & \ldots & 7.3e+11 & 2.6e+10  \\
-150.075420 & 2.336254 & 150.075468 & 2.336257 & 0.853                  & 1.97 & 1.29 & 4.9e+08 & 4.0e+08 & \ldots & \ldots & 6.6e+07 & 1.0e+11 & 4.3e+08  \\
-150.104260 & 2.440705 & 150.104283 & 2.440684 & 0.753\tablenotemark{G} & -0.56 & 0.80 & 5.7e+08 & 2.0e+08 & 7.6e+07 & 1.2e+07 & \ldots & 1.9e+11 & 1.7e+09  \\
-150.105960 & 2.213144 & 150.105985 & 2.213151 & 0.925                  & 0.31 & 1.19 & 3.7e+09 & 2.0e+09 & 2.7e+08 & 3.0e+07 & \ldots & 2.9e+11 & 1.5e+10  \\
-150.067460 & 2.223537 & 150.067493 & 2.223542 & 0.723                  & 0.47 & 0.17 & 5.7e+09 & 4.2e+08 & 3.8e+08 & 2.7e+07 & \ldots & 2.1e+11 & 1.1e+10  \\
-\cutinhead{UDS}
-34.289417 & -5.164467 & 34.289461 & -5.164426 & 0.904\tablenotemark{G} & 0.44 & 0.75 & 4.5e+08 & 1.3e+08 & 1.3e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
-34.483398 & -5.219781 & 34.483412 & -5.219763 & 0.740\tablenotemark{G} & 0.67 & 0.07 & 2.8e+09 & 9.3e+07 & 1.1e+08 & 2.0e+07 & \ldots & 9.6e+10 & 6.5e+09  \\
-34.463700 & -5.230395 & 34.463706 & -5.230378 & 1.279\tablenotemark{G} & -0.46 & 0.26 & 3.1e+09 & 5.7e+08 & 2.7e+08 & 2.0e+07 & \ldots & 4.9e+11 & 2.5e+10  \\
-34.241451 & -5.157997 & 34.241492 & -5.157975 & 0.855                  & 0.62 & 0.04 & 7.0e+09 & 1.2e+08 & 5.0e+08 & 2.5e+07 & \ldots & 2.8e+11 & 7.1e+09  \\
-34.370277 & -5.246929 & 34.370288 & -5.246901 & 0.922\tablenotemark{G} & 0.52 & 0.12 & 3.1e+09 & 1.4e+08 & 2.8e+08 & 1.4e+07 & \ldots & 4.7e+11 & 2.4e+09  \\
-34.286585 & -5.237958 & 34.286618 & -5.237961 & 1.277\tablenotemark{G} & 0.41 & 0.13 & 1.2e+09 & 1.3e+08 & 4.3e+08 & 1.6e+07 & \ldots & 1.1e+12 & 1.6e+10  \\
-34.315356 & -5.232962 & 34.315373 & -5.232970 & 1.415\tablenotemark{G} & 1.16 & 1.01 & 6.0e+08 & 5.8e+08 & 4.3e+08 & 3.4e+07 & \ldots & 1.0e+12 & 8.4e+10  \\
-34.480474 & -5.247719 & 34.480410 & -5.247806 & 1.469\tablenotemark{G} & 0.48 & 1.42 & 2.0e+09 & 1.9e+09 & 4.4e+08 & 6.6e+07 & \ldots & 7.8e+11 & 1.7e+10  \\
-34.325410 & -5.199980 & 34.325420 & -5.199968 & 1.095\tablenotemark{G} & 0.15 & 0.20 & 6.8e+09 & 7.1e+08 & 2.9e+08 & 2.9e+07 & \ldots & 2.9e+11 & 1.9e+10  \\
-34.334096 & -5.237701 & 34.334103 & -5.237683 & 0.920                  & 1.88 & 0.51 & 5.0e+08 & 9.5e+07 & 9.1e+07 & 9.4e+06 & \ldots & 1.5e+11 & 9.6e+09  \\
-34.435496 & -5.152846 & 34.435522 & -5.152819 & 0.801                  & 2.25 & 0.14 & 1.2e+09 & 7.4e+07 & \ldots & \ldots & 1.5e+08 & 3.5e+11 & 3.9e+10  \\
-34.332435 & -5.212034 & 34.332461 & -5.212009 & 1.378\tablenotemark{G} & 0.11 & 0.31 & 6.0e+09 & 1.4e+09 & 4.2e+08 & 2.5e+07 & \ldots & 4.7e+11 & 2.7e+09  \\
-34.325370 & -5.223768 & 34.325374 & -5.223737 & 1.415\tablenotemark{G} & 0.28 & 1.42 & 8.3e+08 & 8.0e+08 & 1.3e+08 & 2.1e+07 & \ldots & 8.3e+11 & 3.8e+10  \\
-34.368704 & -5.157358 & 34.368684 & -5.157395 & 0.835\tablenotemark{G} & 2.44 & 0.52 & 2.8e+08 & 5.9e+07 & 6.4e+07 & 1.0e+07 & \ldots & 1.4e+11 & 8.3e+09  \\
-34.574970 & -5.161715 & 34.574958 & -5.161686 & 1.195\tablenotemark{G} & -0.60 & 0.14 & 2.1e+10 & 1.3e+09 & 6.8e+08 & 2.9e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
-34.374753 & -5.227548 & 34.374772 & -5.227530 & 1.429\tablenotemark{G} & -0.15 & 0.32 & 1.1e+10 & 1.9e+09 & 5.8e+08 & 3.7e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
-34.435733 & -5.231665 & 34.435744 & -5.231653 & 0.914                  & -0.05 & 0.08 & 6.2e+09 & 1.8e+08 & \ldots & \ldots & 9.4e+07 & 2.3e+11 & 7.4e+09  \\
-34.231824 & -5.253116 & 34.231825 & -5.253016 & 0.823\tablenotemark{G} & 0.64 & 0.06 & 3.9e+09 & 9.1e+07 & 3.5e+08 & 1.4e+07 & \ldots & 3.4e+11 & 3.4e+09  \\
-34.457636 & -5.164808 & 34.457656 & -5.164792 & 0.916\tablenotemark{G} & -0.32 & 0.04 & 1.3e+10 & 2.1e+08 & \ldots & \ldots & 6.1e+08 & 3.6e+11 & 2.8e+09  \\
-34.375611 & -5.204026 & 34.375625 & -5.204000 & 0.915                  & -0.25 & 0.08 & 6.1e+09 & 1.8e+08 & \ldots & \ldots & 6.3e+07 & 1.8e+11 & 3.4e+09  \\
-34.359199 & -5.257633 & 34.359225 & -5.257605 & 0.803                  & 0.11 & 0.06 & 5.6e+09 & 1.3e+08 & \ldots & \ldots & 2.3e+08 & 8.9e+10 & 8.1e+09  \\
-34.250598 & -5.162615 & 34.250537 & -5.162659 & 0.829\tablenotemark{G} & -0.12 & 0.04 & 8.8e+09 & 1.4e+08 & 2.8e+08 & 2.8e+07 & \ldots & 1.4e+11 & 7.1e+08  \\
-34.457290 & -5.229210 & 34.457293 & -5.229258 & 0.929\tablenotemark{G} & -0.11 & 0.12 & 3.7e+09 & 1.6e+08 & 1.9e+08 & 1.3e+07 & \ldots & 1.9e+11 & 9.5e+09  \\
-34.268269 & -5.151559 & 34.268324 & -5.151551 & 1.012                  & -0.35 & 0.13 & 4.2e+09 & 1.7e+08 & 3.7e+08 & 1.8e+07 & \ldots & 3.8e+11 & 6.1e+09  \\
-34.369105 & -5.172428 & 34.369137 & -5.172404 & 0.825                  & 0.96 & 0.05 & 4.4e+09 & 9.9e+07 & 2.4e+08 & 1.7e+07 & \ldots & 1.6e+11 & 8.4e+09  \\
-34.481139 & -5.174353 & 34.481147 & -5.174333 & 1.275\tablenotemark{G} & 0.32 & 0.38 & 3.7e+09 & 1.0e+09 & 6.5e+08 & 1.7e+07 & \ldots & 1.2e+12 & 2.9e+10  \\
-34.444958 & -5.168239 & 34.444949 & -5.168229 & 1.417                  & -0.63 & 0.41 & 2.0e+10 & 4.4e+09 & 7.5e+08 & 5.5e+07 & \ldots & 8.3e+11 & 6.9e+10  \\
-34.377887 & -5.179532 & 34.377976 & -5.179501 & 1.270\tablenotemark{G} & 1.29 & 0.04 & 6.8e+08 & 1.6e+07 & 2.3e+08 & 1.7e+07 & \ldots & 6.3e+11 & 2.5e+10  \\
-34.246973 & -5.265455 & 34.246992 & -5.265421 & 1.420\tablenotemark{G} & 0.96 & 0.80 & 7.6e+08 & 4.4e+08 & 4.6e+08 & 3.9e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
-34.347189 & -5.175795 & 34.347225 & -5.175778 & 1.428\tablenotemark{G} & -0.58 & 0.47 & 1.0e+10 & 2.9e+09 & 4.7e+08 & 6.5e+07 & \ldots & 7.3e+11 & 3.6e+10  \\
-34.318401 & -5.229057 & 34.318417 & -5.229052 & 1.035\tablenotemark{G} & 0.49 & 0.42 & 1.3e+09 & 1.8e+08 & 1.6e+08 & 1.6e+07 & \ldots & 2.2e+11 & 1.3e+10  \\
-34.375082 & -5.164786 & 34.375134 & -5.164736 & 1.089\tablenotemark{G} & 0.93 & 0.52 & 2.3e+09 & 7.8e+08 & \ldots & \ldots & 7.2e+07 & 3.7e+11 & 1.9e+10  \\
-34.358432 & -5.175677 & 34.358447 & -5.175662 & 1.431\tablenotemark{G} & -0.98 & 0.35 & 1.5e+10 & 2.7e+09 & 8.2e+08 & 7.5e+07 & \ldots & 9.7e+11 & 7.8e+10  \\
-34.255834 & -5.167369 & 34.255891 & -5.167354 & 1.090\tablenotemark{G} & 0.01 & 0.43 & 4.5e+09 & 9.7e+08 & 2.1e+08 & 2.7e+07 & \ldots & 4.2e+11 & 4.5e+10  \\
-34.322860 & -5.167645 & 34.322906 & -5.167608 & 1.030                  & 1.30 & 0.11 & 5.0e+09 & 1.8e+08 & 6.5e+08 & 2.2e+07 & \ldots & 9.7e+11 & 1.5e+10  \\
-34.399563 & -5.224797 & 34.399633 & -5.224808 & 1.097\tablenotemark{G} & -0.73 & 0.04 & 1.8e+10 & 3.1e+08 & 3.2e+08 & 1.3e+07 & \ldots & 1.7e+11 & 1.9e+10  \\
-34.401748 & -5.153146 & 34.401803 & -5.153117 & 1.091\tablenotemark{G} & 1.55 & 0.47 & 6.4e+08 & 2.3e+08 & 1.6e+08 & 1.1e+07 & \ldots & 2.6e+11 & 9.8e+09  \\
-34.486134 & -5.254569 & 34.486173 & -5.254550 & 0.947\tablenotemark{G} & 0.53 & 0.22 & 2.2e+09 & 1.7e+08 & 1.4e+08 & 2.1e+07 & \ldots & 3.8e+11 & 1.7e+10  \\
-34.444281 & -5.248412 & 34.444279 & -5.248374 & 1.091\tablenotemark{G} & 1.39 & 0.14 & 8.3e+08 & 8.3e+07 & 1.0e+08 & 1.1e+07 & \ldots & 2.1e+11 & 1.5e+10  \\
-34.435300 & -5.158785 & 34.435317 & -5.158755 & 1.326\tablenotemark{G} & -0.95 & 0.34 & 1.0e+10 & 2.0e+09 & 4.1e+08 & 3.6e+07 & \ldots & 4.0e+11 & 3.0e+10  \\
-34.236833 & -5.197802 & 34.236869 & -5.197786 & 0.790\tablenotemark{G} & 5.96 & 2.43 & 1.3e+07 & 1.5e+07 & 5.0e+07 & 7.0e+06 & \ldots & 9.5e+10 & 5.4e+09  \\
-34.486535 & -5.240308 & 34.486568 & -5.240289 & 1.305\tablenotemark{G} & -0.64 & 0.24 & 3.2e+09 & 4.1e+08 & 2.2e+08 & 3.8e+07 & \ldots & 6.3e+11 & 6.5e+10  \\
-34.235814 & -5.168167 & 34.235951 & -5.168147 & 1.264\tablenotemark{G} & -1.14 & 0.06 & 1.9e+10 & 4.1e+08 & 5.7e+08 & 3.0e+07 & \ldots & 4.2e+12 & 6.2e+11  \\
-34.407596 & -5.239813 & 34.407597 & -5.239785 & 0.752                  & 2.04 & 0.14 & 8.6e+08 & 5.7e+07 & 8.3e+07 & 1.5e+07 & \ldots & 1.2e+11 & 4.8e+08  \\
-34.440375 & -5.240249 & 34.440380 & -5.240216 & 1.041\tablenotemark{G} & 1.16 & 0.71 & 6.2e+08 & 1.4e+08 & 9.9e+07 & 1.1e+07 & \ldots & 2.7e+11 & 1.2e+10  \\
-34.581318 & -5.178201 & 34.581313 & -5.178152 & 1.046\tablenotemark{G} & -0.65 & 0.07 & 1.0e+10 & 1.9e+08 & 2.9e+08 & 2.2e+07 & \ldots & 1.6e+11 & 1.4e+10  \\
-34.338810 & -5.191348 & 34.338853 & -5.191342 & 0.932\tablenotemark{G} & 1.82 & 0.48 & 6.5e+08 & 1.1e+08 & 1.2e+08 & 1.3e+07 & \ldots & 2.9e+11 & 4.1e+09  \\
-34.337205 & -5.214391 & 34.337215 & -5.214334 & 0.920\tablenotemark{G} & 1.06 & 0.50 & 5.7e+08 & 1.0e+08 & 7.6e+07 & 1.1e+07 & \ldots & 1.1e+11 & 1.6e+10  \\
-34.291195 & -5.191481 & 34.291192 & -5.191474 & 0.825\tablenotemark{G} & 6.82 & 3.02 & 1.3e+07 & 1.7e+07 & \ldots & \ldots & 3.5e+07 & 1.3e+11 & 1.2e+10  \\
-34.327458 & -5.197280 & 34.327395 & -5.197192 & 1.141\tablenotemark{G} & -0.63 & 0.10 & 1.2e+10 & 5.6e+08 & 1.8e+08 & 1.8e+07 & \ldots & 2.0e+11 & 2.5e+10  \\
-34.246650 & -5.238097 & 34.246662 & -5.238100 & 0.809                  & -0.97 & 0.04 & 8.9e+09 & 1.3e+08 & 1.9e+08 & 1.3e+07 & \ldots & 9.9e+10 & 8.4e+09  \\
-34.425930 & -5.174296 & 34.425949 & -5.174306 & 1.158\tablenotemark{G} & 0.38 & 0.34 & 2.0e+09 & 3.8e+08 & 6.3e+07 & 1.2e+07 & \ldots & 2.4e+11 & 2.1e+10  \\
-34.441478 & -5.203516 & 34.441496 & -5.203515 & 1.064\tablenotemark{G} & -0.86 & 0.94 & 7.9e+08 & 2.1e+08 & 9.9e+07 & 1.4e+07 & \ldots & 2.7e+11 & 8.5e+09  \\
-34.417250 & -5.220560 & 34.417268 & -5.220544 & 0.749\tablenotemark{G} & -0.08 & 0.04 & 5.2e+09 & 1.1e+08 & 1.1e+08 & 1.1e+07 & \ldots & 4.6e+10 & 1.0e+10  \\
-34.303624 & -5.187742 & 34.303640 & -5.187698 & 0.995\tablenotemark{G} & -1.24 & 0.13 & 4.8e+09 & 2.0e+08 & 1.5e+08 & 1.3e+07 & \ldots & 2.1e+11 & 3.0e+10  \\
-34.338168 & -5.206715 & 34.338190 & -5.206671 & 0.922                  & 2.68 & 0.20 & 1.4e+09 & 1.1e+08 & \ldots & \ldots & 8.2e+07 & 2.8e+11 & 7.2e+09  \\
-34.316711 & -5.166855 & 34.316746 & -5.166812 & 1.040\tablenotemark{G} & 2.41 & 2.45 & 1.5e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 2.0e+09  \\
-34.479187 & -5.233651 & 34.479221 & -5.233645 & 1.312\tablenotemark{G} & 0.77 & 0.31 & 1.7e+10 & 3.6e+09 & 1.3e+09 & 6.2e+07 & \ldots & 1.1e+12 & 1.0e+11  \\
-34.464574 & -5.205369 & 34.464597 & -5.205359 & 1.268\tablenotemark{G} & 0.20 & 0.38 & 2.3e+09 & 4.6e+08 & 5.2e+08 & 1.8e+07 & \ldots & 7.0e+11 & 2.0e+10  \\
-34.306728 & -5.161120 & 34.306745 & -5.161058 & 1.454                  & 0.26 & 0.43 & 9.5e+09 & 2.5e+09 & 1.5e+09 & 6.3e+07 & \ldots & 2.8e+12 & 1.6e+11  \\
-34.473469 & -5.202807 & 34.473484 & -5.202784 & 1.011\tablenotemark{G} & 0.84 & 0.23 & 1.9e+09 & 1.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.1e+11 & 7.0e+09  \\
-34.361009 & -5.189687 & 34.361031 & -5.189685 & 1.344\tablenotemark{G} & -1.00 & 0.37 & 8.1e+09 & 1.6e+09 & 2.2e+08 & 2.2e+07 & \ldots & 4.9e+11 & 5.5e+10  \\
-34.262690 & -5.198416 & 34.262708 & -5.198400 & 0.758\tablenotemark{G} & 4.66 & 0.80 & 6.3e+07 & 2.3e+07 & \ldots & \ldots & 5.6e+07 & 4.6e+11 & 6.0e+10  \\
-34.430803 & -5.206198 & 34.430856 & -5.206176 & 0.914\tablenotemark{G} & 0.64 & 0.13 & 2.5e+09 & 1.2e+08 & 1.2e+08 & 1.0e+07 & \ldots & 1.4e+11 & 9.8e+09  \\
-34.404478 & -5.239535 & 34.404464 & -5.239511 & 0.925\tablenotemark{G} & -1.25 & 0.03 & 1.7e+10 & 2.0e+08 & 1.8e+08 & 1.0e+07 & \ldots & 3.3e+10 & 8.5e+09  \\
-34.331573 & -5.180048 & 34.331575 & -5.180048 & 0.828                  & 2.80 & 0.21 & 7.2e+08 & 6.4e+07 & 2.2e+08 & 1.5e+07 & \ldots & 3.5e+11 & 6.3e+09  \\
-34.306272 & -5.150911 & 34.306301 & -5.150885 & 1.446\tablenotemark{G} & -0.07 & 0.38 & 4.0e+09 & 9.0e+08 & 5.2e+08 & 3.5e+07 & \ldots & 1.8e+12 & 1.4e+11  \\
-34.261751 & -5.204628 & 34.261780 & -5.204633 & 0.896                  & -0.48 & 0.04 & 1.2e+10 & 1.6e+08 & 2.6e+08 & 2.1e+07 & \ldots & 1.4e+11 & 1.6e+10  \\
-34.263048 & -5.136277 & 34.263053 & -5.136258 & 0.820\tablenotemark{G} & 2.84 & 0.38 & 2.7e+08 & 4.2e+07 & 1.3e+08 & 5.7e+06 & \ldots & 9.3e+10 & 7.3e+09  \\
-34.406678 & -5.198827 & 34.406674 & -5.198821 & 0.920                  & 1.91 & 0.14 & 1.8e+09 & 9.8e+07 & 2.3e+08 & 1.1e+07 & \ldots & 4.8e+11 & 1.2e+10  \\
-34.385521 & -5.205044 & 34.385550 & -5.205011 & 1.380\tablenotemark{G} & 2.02 & 0.57 & 1.1e+09 & 5.9e+08 & 5.7e+08 & 3.0e+07 & \ldots & 1.1e+12 & 9.2e+10  \\
-34.391148 & -5.240692 & 34.391130 & -5.240724 & 1.449\tablenotemark{G} & -0.82 & 0.54 & 8.7e+09 & 2.4e+09 & 2.4e+08 & 3.3e+07 & \ldots & 5.2e+11 & 3.3e+10  \\
-34.438796 & -5.165779 & 34.438816 & -5.165758 & 1.106\tablenotemark{G} & 1.36 & 0.10 & 2.7e+09 & 1.8e+08 & 3.0e+08 & 2.9e+07 & \ldots & 4.4e+11 & 1.7e+10  \\
-34.230979 & -5.176122 & 34.231025 & -5.176088 & 1.092                  & 0.34 & 0.37 & 1.2e+10 & 2.4e+09 & 1.0e+09 & 1.1e+08 & \ldots & 5.9e+11 & 3.0e+10  \\
-34.433604 & -5.153793 & 34.433623 & -5.153767 & 0.805                  & 0.74 & 0.08 & 3.0e+09 & 1.1e+08 & 1.3e+08 & 1.2e+07 & \ldots & 1.2e+11 & 8.8e+09  \\
-34.351795 & -5.210948 & 34.351808 & -5.210919 & 1.093\tablenotemark{G} & 0.92 & 0.00 & 2.1e+09 & 7.4e+06 & 2.5e+08 & 1.8e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
-34.367405 & -5.228523 & 34.367420 & -5.228497 & 1.189\tablenotemark{G} & 0.70 & 0.04 & 8.2e+09 & 1.8e+08 & 6.2e+08 & 2.7e+07 & \ldots & 6.7e+11 & 1.5e+10  \\
-34.583006 & -5.172723 & 34.582980 & -5.172715 & 1.280\tablenotemark{G} & -1.13 & 0.05 & 5.6e+09 & 1.0e+08 & 2.5e+08 & 1.6e+07 & \ldots & 3.0e+11 & 4.9e+10  \\
-34.338183 & -5.254102 & 34.338179 & -5.254077 & 1.039\tablenotemark{G} & 0.28 & 0.72 & 6.9e+08 & 1.5e+08 & 1.1e+08 & 1.3e+07 & \ldots & 3.0e+11 & 1.4e+10  \\
-34.335313 & -5.258985 & 34.335319 & -5.258979 & 0.879\tablenotemark{G} & -0.51 & 0.05 & 9.9e+09 & 1.9e+08 & \ldots & \ldots & 1.6e+08 & 1.2e+11 & 8.2e+09  \\
-34.265199 & -5.258207 & 34.265234 & -5.258198 & 0.807                  & 0.70 & 0.06 & 3.5e+09 & 9.4e+07 & 1.1e+08 & 1.6e+07 & \ldots & 3.6e+11 & 3.8e+10  \\
-34.266225 & -5.258304 & 34.266217 & -5.258304 & 0.806\tablenotemark{G} & 0.45 & 0.04 & 7.6e+09 & 1.3e+08 & 1.8e+08 & 2.2e+07 & \ldots & 2.6e+11 & 1.1e+10  \\
-34.282549 & -5.227706 & 34.282574 & -5.227709 & 1.047\tablenotemark{G} & 0.06 & 0.36 & 1.9e+09 & 2.1e+08 & 2.5e+08 & 3.6e+07 & \ldots & 4.1e+11 & 4.5e+10  \\
-34.417088 & -5.183261 & 34.417113 & -5.183254 & 0.920                  & 0.86 & 0.10 & 4.2e+09 & 1.5e+08 & 1.8e+08 & 1.8e+07 & \ldots & 1.8e+11 & 6.3e+09  \\
-34.287594 & -5.200242 & 34.287609 & -5.200223 & 0.787                  & 1.66 & 0.15 & 1.2e+09 & 7.8e+07 & 1.0e+08 & 1.6e+07 & \ldots & 1.9e+11 & 9.9e+09  \\
-34.438839 & -5.263612 & 34.438843 & -5.263605 & 0.784\tablenotemark{G} & 3.07 & 0.17 & 5.9e+08 & 4.5e+07 & 1.3e+08 & 8.7e+06 & \ldots & 2.5e+11 & 1.5e+10  \\
-34.412508 & -5.175668 & 34.412537 & -5.175642 & 1.291\tablenotemark{G} & 2.55 & 1.28 & 3.3e+08 & 4.5e+08 & 3.4e+08 & 2.4e+07 & \ldots & 5.9e+11 & 3.2e+10  \\
-34.341631 & -5.235338 & 34.341650 & -5.235318 & 1.100\tablenotemark{G} & 0.73 & 0.49 & 2.3e+09 & 6.9e+08 & 2.9e+08 & 1.0e+07 & \ldots & 2.8e+11 & 1.7e+10  \\
-34.288088 & -5.245493 & 34.288165 & -5.245476 & 1.474\tablenotemark{G} & -1.50 & 0.05 & 1.9e+10 & 1.1e+09 & 2.3e+08 & 3.2e+07 & \ldots & 4.9e+11 & 2.8e+10  \\
-34.315106 & -5.218825 & 34.315157 & -5.218789 & 1.030                  & 3.32 & 1.20 & 3.0e+08 & 1.1e+08 & 1.4e+08 & 1.2e+07 & \ldots & 2.3e+11 & 1.1e+10  \\
-34.334173 & -5.190787 & 34.334186 & -5.190781 & 0.916\tablenotemark{G} & 2.98 & 1.07 & 2.0e+08 & 7.9e+07 & 9.7e+07 & 1.5e+07 & \ldots & 4.9e+11 & 4.0e+09  \\
-34.258180 & -5.172100 & 34.258232 & -5.172124 & 1.094                  & -0.59 & 0.05 & 9.6e+09 & 2.0e+08 & 2.5e+08 & 1.4e+07 & \ldots & 1.2e+11 & 2.1e+10  \\
-34.259985 & -5.172752 & 34.260001 & -5.172724 & 1.410\tablenotemark{G} & 0.64 & 0.99 & 9.7e+08 & 7.4e+08 & \ldots & \ldots & 1.3e+08 & 4.7e+11 & 6.2e+10  \\
-34.405981 & -5.249941 & 34.405971 & -5.249905 & 1.067                  & -1.00 & 0.04 & 1.5e+10 & 1.9e+08 & 3.8e+08 & 1.7e+07 & \ldots & 1.8e+11 & 1.3e+10  \\
-34.317767 & -5.189676 & 34.317778 & -5.189662 & 0.915\tablenotemark{G} & 0.31 & 0.13 & 2.9e+09 & 1.3e+08 & 2.2e+08 & 1.2e+07 & \ldots & 2.4e+11 & 7.2e+09  \\
-34.238729 & -5.168098 & 34.238794 & -5.168072 & 0.821                  & 4.43 & 0.47 & 2.0e+08 & 4.0e+07 & \ldots & \ldots & 1.0e+08 & 1.9e+11 & 7.7e+09  \\
-34.370957 & -5.263670 & 34.370973 & -5.263634 & 0.910\tablenotemark{G} & 0.37 & 0.05 & 8.1e+09 & 1.6e+08 & 3.1e+08 & 4.5e+07 & \ldots & 2.2e+11 & 2.5e+09
-\enddata
-\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
-\tablecomments{Columns: RA and Dec, IR, are positions in the
-\emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
-priors.  RA and Dec, opt., are positions in the CANDELS catalogs.
-$L_{\mathrm{H}\alpha}$ lim. is a 5$\sigma$ upper limit to the H$\alpha$
-line luminosity.}
-\end{deluxetable}
-\clearpage
-\end{landscape}
-
-\begin{landscape}
-\begin{deluxetable}{lllllllllllll}
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the samples at $z < 0.2$
-\label{tbl:lowz}}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA} &
-\colhead{Dec} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\beta}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{Dust-poor galaxies}
-30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
-33.452250 & 12.997628 & 0.219 & -0.45 & 0.05 & 4.3e+10 & 4.3e+08 & 3.6e+07  & \ldots & 1.4e+08 & \ldots & 5.4e+11 & 3.0e+09 \\
-52.191625 & 1.197458 & 0.142 & -1.68 & 0.04 & 1.9e+10 & 1.7e+08 & 7.4e+07   & \ldots & 2.4e+08 & \ldots & 5.4e+10 & 1.0e+09 \\
-59.391667 & -5.622139 & 0.204 & -1.28 & 0.06 & 2.9e+10 & 3.5e+08 & 9.4e+07  & \ldots & 3.5e+08 & \ldots & 1.1e+11 & 1.9e+09 \\
-125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09
-\enddata
-\tablecomments{The entire table is published in the electronic edition of
-\apj.  A portion is shown here for guidance regarding its form and content.}
-\end{deluxetable}
-\clearpage
-\end{landscape}
-
-\begin{landscape}
-\begin{deluxetable}{lllllllllllll}
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the samples at $z < 0.2$}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA} &
-\colhead{Dec} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\beta}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{Dust-poor galaxies}
-30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
-33.452250 & 12.997628 & 0.219 & -0.45 & 0.05 & 4.3e+10 & 4.3e+08 & 3.6e+07  & \ldots & 1.4e+08 & \ldots & 5.4e+11 & 3.0e+09 \\
-52.191625 & 1.197458 & 0.142 & -1.68 & 0.04 & 1.9e+10 & 1.7e+08 & 7.4e+07   & \ldots & 2.4e+08 & \ldots & 5.4e+10 & 1.0e+09 \\
-59.391667 & -5.622139 & 0.204 & -1.28 & 0.06 & 2.9e+10 & 3.5e+08 & 9.4e+07  & \ldots & 3.5e+08 & \ldots & 1.1e+11 & 1.9e+09 \\
-125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09 \\
-129.515542 & 44.983411 & 0.143 & -1.93 & 0.03 & 2.3e+10 & 1.7e+08 & 8.5e+07 & \ldots & 2.5e+08 & \ldots & 3.2e+10 & 1.0e+09 \\
-140.901917 & 54.810903 & 0.222 & -1.75 & 0.07 & 2.9e+10 & 4.2e+08 & 9.4e+07 & \ldots & 3.4e+08 & \ldots & 7.6e+10 & 2.1e+09 \\
-141.501708 & 44.460036 & 0.181 & -2.32 & 0.03 & 4.3e+10 & 2.7e+08 & 2.3e+08 & \ldots & 6.9e+08 & \ldots & 8.8e+10 & 3.0e+09 \\
-144.556250 & 54.473636 & 0.102 & -1.75 & 0.01 & 3.3e+10 & 8.9e+07 & 1.7e+08 & \ldots & 5.5e+08 & \ldots & 1.2e+11 & 4.2e+08 \\
-156.558208 & 48.749706 & 0.160 & -1.44 & 0.04 & 2.5e+10 & 2.2e+08 & 8.9e+07 & \ldots & 2.8e+08 & \ldots & 9.1e+10 & 1.1e+09 \\
-208.482917 & 66.800164 & 0.198 & -0.99 & 0.03 & 5.3e+10 & 3.4e+08 & 1.5e+08 & \ldots & 5.4e+08 & \ldots & 1.3e+11 & 3.1e+09 \\
-218.571500 & 2.128494 & 0.180 & -1.03 & 0.05 & 2.7e+10 & 2.8e+08 & 8.3e+07  & \ldots & 3.4e+08 & \ldots & 1.2e+11 & 1.6e+09 \\
-326.251083 & 1.199328 & 0.204 & -0.65 & 0.08 & 2.4e+10 & 3.7e+08 & 1.3e+08  & \ldots & 4.8e+08 & \ldots & 1.3e+11 & 2.1e+09 \\
-358.448708 & 0.900578 & 0.223 & -1.66 & 0.10 & 2.2e+10 & 4.2e+08 & 1.0e+08  & \ldots & 3.2e+08 & \ldots & 8.5e+10 & 5.9e+09 \\
-\cutinhead{Dusty galaxies}
-154.474577 & 15.934370 & 0.079 & 0.28 & 0.72 & 1.3e+09 & 2.5e+08 & 4.9e+07 & 8.4e+05 & 3.9e+08 & 3.0e+06 & 3.4e+11 & 2.7e+09 \\
-158.388129 & 1.109763 & 0.066 & -1.10 & 0.56 & 9.4e+08 & 1.4e+08 & 1.7e+07 & 5.0e+05 & 1.3e+08 & 1.2e+06 & 2.2e+11 & 1.2e+10 \\
-237.971016 & 27.242680 & 0.059 & -1.14 & 0.76 & 1.0e+09 & 2.2e+08 & 1.2e+07 & 3.3e+05 & 9.7e+07 & 8.8e+05 & 2.0e+11 & 7.4e+09 \\
-7.449404 & -0.245792 & 0.061 & 0.18 & 0.24 & 4.4e+09 & 3.1e+08 & 5.4e+07 & 1.1e+06 & 2.8e+08 & 2.7e+06 & 1.2e+11 & 3.6e+09 \\
-10.901290 & -9.429965 & 0.050 & 0.70 & 0.20 & 8.5e+08 & 5.0e+07 & 2.5e+07 & 3.1e+05 & 1.3e+08 & 8.2e+05 & 8.8e+10 & 5.9e+08 \\
-27.858730 & -8.415234 & 0.051 & -0.76 & 0.05 & 1.3e+10 & 1.8e+08 & 4.0e+07 & 8.7e+05 & 1.9e+08 & 2.1e+06 & 1.1e+11 & 7.6e+09 \\
-120.588891 & 19.993689 & 0.068 & -0.54 & 0.62 & 1.9e+09 & 3.4e+08 & 5.1e+07 & 8.4e+05 & 3.5e+08 & 2.4e+06 & 3.4e+11 & 6.7e+09 \\
-126.945451 & 15.916297 & 0.055 & 0.05 & 0.40 & 3.1e+09 & 3.6e+08 & 4.2e+07 & 6.5e+05 & 2.0e+08 & 1.4e+06 & 8.8e+10 & 9.4e+08 \\
-131.509245 & 52.533070 & 0.053 & -0.94 & 0.03 & 1.9e+10 & 1.4e+08 & 3.6e+07 & 9.1e+05 & 1.7e+08 & 2.0e+06 & 8.6e+10 & 3.7e+09 \\
-135.288383 & 13.196000 & 0.052 & -0.13 & 0.32 & 1.7e+09 & 1.6e+08 & 1.8e+07 & 3.4e+05 & 1.1e+08 & 8.4e+05 & 7.8e+10 & 5.1e+08 \\
-144.201362 & 31.330777 & 0.076 & 0.39 & 0.24 & 6.1e+09 & 4.1e+08 & 7.4e+07 & 1.0e+06 & 4.0e+08 & 3.2e+06 & 3.1e+11 & 4.2e+09 \\
-156.207038 & 5.557543 & 0.067 & -0.76 & 0.05 & 5.9e+09 & 8.2e+07 & 3.6e+07 & 7.3e+05 & 1.7e+08 & 1.6e+06 & 1.3e+11 & 6.4e+09 \\
-157.561538 & 11.071065 & 0.065 & -0.92 & 0.19 & 1.4e+10 & 7.7e+08 & 6.7e+07 & 9.8e+05 & 2.9e+08 & 2.6e+06 & 2.2e+11 & 4.3e+09 \\
-161.115619 & 27.301748 & 0.076 & -1.28 & 0.17 & 2.8e+10 & 1.3e+09 & 1.2e+08 & 1.7e+06 & 4.3e+08 & 3.3e+06 & 1.4e+11 & 7.3e+07 \\
-163.210511 & 17.104119 & 0.055 & -0.60 & 0.05 & 3.2e+09 & 4.7e+07 & 2.9e+07 & 4.1e+05 & 1.5e+08 & 1.2e+06 & 1.2e+11 & 5.9e+09 \\
-165.068053 & 39.112798 & 0.073 & 0.25 & 0.47 & 3.2e+09 & 4.1e+08 & 5.1e+07 & 1.1e+06 & 3.2e+08 & 2.8e+06 & 2.1e+11 & 1.0e+10 \\
-167.405962 & 26.921014 & 0.070 & -0.42 & 0.34 & 5.5e+09 & 5.3e+08 & 6.5e+07 & 9.6e+05 & 3.2e+08 & 2.5e+06 & 3.3e+11 & 4.5e+10 \\
-168.081794 & 48.190468 & 0.058 & -0.56 & 0.25 & 6.4e+09 & 4.6e+08 & 5.3e+07 & 6.5e+05 & 2.2e+08 & 1.8e+06 & 1.0e+11 & 1.3e+09 \\
-168.202215 & 25.597371 & 0.051 & -0.09 & 0.48 & 1.5e+09 & 2.2e+08 & 3.2e+07 & 7.1e+05 & 1.8e+08 & 2.0e+06 & 8.6e+10 & 6.1e+08 \\
-174.714455 & 20.982557 & 0.065 & -0.17 & 0.20 & 1.1e+10 & 6.2e+08 & 1.2e+08 & 1.3e+06 & 7.3e+08 & 4.9e+06 & 4.6e+11 & 2.0e+10 \\
-175.317325 & 21.939374 & 0.063 & -1.91 & 0.08 & 8.7e+10 & 1.9e+09 & 2.4e+08 & 1.9e+06 & 9.0e+08 & 5.0e+06 & 2.7e+11 & 1.8e+10 \\
-176.292776 & 30.788122 & 0.059 & -1.50 & 0.11 & 2.9e+10 & 8.3e+08 & 9.3e+07 & 7.9e+05 & 2.5e+08 & 1.5e+06 & 1.6e+11 & 2.4e+08 \\
-177.740427 & 51.953195 & 0.053 & -0.33 & 0.21 & 5.9e+09 & 3.8e+08 & 2.0e+07 & 6.9e+05 & 9.7e+07 & 1.3e+06 & 8.0e+10 & 2.5e+09 \\
-181.448534 & 33.839435 & 0.054 & -1.50 & 0.20 & 3.9e+09 & 2.3e+08 & 1.9e+07 & 2.4e+05 & 1.1e+08 & 6.6e+05 & 1.2e+11 & 6.0e+09 \\
-182.654191 & -3.233095 & 0.058 & -0.65 & 0.58 & 1.9e+09 & 3.1e+08 & 2.2e+07 & 7.5e+05 & 1.5e+08 & 1.7e+06 & 1.1e+11 & 5.2e+09 \\
-184.248742 & 9.926954 & 0.057 & -0.24 & 0.36 & 3.8e+09 & 4.0e+08 & 2.5e+07 & 4.9e+05 & 1.3e+08 & 1.3e+06 & 8.8e+10 & 2.6e+09 \\
-186.816462 & 19.906459 & 0.051 & 0.75 & 0.84 & 8.5e+08 & 2.2e+08 & 1.5e+07 & 2.7e+05 & 8.6e+07 & 7.7e+05 & 7.1e+10 & 8.8e+08 \\
-188.015105 & 20.158206 & 0.064 & -1.86 & 0.03 & 8.8e+10 & 6.5e+08 & 1.7e+08 & 1.5e+06 & 6.4e+08 & 3.6e+06 & 3.5e+11 & 1.7e+08 \\
-189.883379 & 27.497340 & 0.057 & -0.27 & 0.25 & 3.0e+09 & 2.2e+08 & 3.1e+07 & 5.7e+05 & 1.9e+08 & 1.6e+06 & 1.3e+11 & 7.3e+09 \\
-191.550445 & 41.136642 & 0.067 & 0.10 & 0.51 & 2.0e+09 & 3.1e+08 & 1.0e+08 & 1.1e+06 & 4.8e+08 & 3.8e+06 & 3.3e+11 & 2.1e+10 \\
-192.017210 & 18.002434 & 0.075 & -0.74 & 0.55 & 2.9e+09 & 4.1e+08 & 6.0e+07 & 1.3e+06 & 4.2e+08 & 3.2e+06 & 2.0e+11 & 2.5e+08 \\
-196.262683 & 40.764720 & 0.057 & -0.72 & 0.15 & 6.3e+09 & 2.7e+08 & 5.9e+07 & 6.7e+05 & 2.7e+08 & 2.1e+06 & 1.6e+11 & 1.9e+09 \\
-196.443701 & 32.839531 & 0.052 & -0.29 & 0.15 & 5.5e+09 & 2.4e+08 & 9.6e+06 & 5.2e+05 & 4.5e+07 & 8.4e+05 & 6.2e+10 & 3.1e+09 \\
-197.424282 & 2.457934 & 0.057 & -1.12 & 0.16 & 1.6e+10 & 7.1e+08 & 4.1e+07 & 7.6e+05 & 1.8e+08 & 1.5e+06 & 1.2e+11 & 4.9e+09 \\
-198.249679 & 43.204312 & 0.062 & -0.92 & 0.10 & 2.0e+10 & 5.6e+08 & 7.6e+07 & 1.3e+06 & 4.4e+08 & 3.8e+06 & 2.0e+11 & 3.4e+09 \\
-198.576647 & 17.204395 & 0.073 & -0.09 & 0.47 & 3.0e+09 & 3.9e+08 & 3.3e+07 & 7.6e+05 & 2.2e+08 & 2.0e+06 & 2.2e+11 & 8.5e+09 \\
-200.864909 & 8.638164 & 0.073 & -1.05 & 0.23 & 5.3e+09 & 3.3e+08 & 6.6e+07 & 8.3e+05 & 3.2e+08 & 2.3e+06 & 1.8e+11 & 1.4e+09 \\
-201.432741 & 17.264658 & 0.079 & -0.63 & 0.20 & 2.3e+10 & 1.2e+09 & 1.1e+08 & 1.8e+06 & 5.3e+08 & 4.7e+06 & 2.7e+11 & 1.1e+10 \\
-203.549510 & 51.889024 & 0.063 & 0.10 & 0.36 & 6.2e+09 & 6.5e+08 & 7.2e+07 & 1.0e+06 & 3.5e+08 & 2.9e+06 & 1.7e+11 & 3.2e+09 \\
-208.483971 & -2.529896 & 0.051 & -1.12 & 0.40 & 3.9e+09 & 4.6e+08 & 5.3e+07 & 5.5e+05 & 2.5e+08 & 1.6e+06 & 1.6e+11 & 6.8e+09 \\
-214.777948 & 47.754134 & 0.072 & -0.81 & 0.23 & 1.4e+10 & 8.4e+08 & 5.4e+07 & 1.0e+06 & 2.8e+08 & 2.2e+06 & 2.1e+11 & 6.4e+09 \\
-215.283879 & 30.630220 & 0.051 & -1.03 & 0.15 & 1.1e+10 & 5.0e+08 & 2.5e+07 & 5.7e+05 & 1.1e+08 & 1.3e+06 & 1.1e+11 & 1.9e+09 \\
-217.679357 & 0.252884 & 0.055 & 0.75 & 0.57 & 1.6e+09 & 2.6e+08 & 1.4e+07 & 3.7e+05 & 1.1e+08 & 9.5e+05 & 8.9e+10 & 7.8e+08 \\
-220.337675 & -0.759540 & 0.080 & -0.58 & 0.10 & 6.3e+09 & 1.7e+08 & 5.5e+07 & 9.2e+05 & 3.0e+08 & 2.3e+06 & 2.6e+11 & 8.5e+09 \\
-220.968122 & 16.474242 & 0.054 & -0.54 & 0.23 & 8.2e+09 & 5.3e+08 & 7.9e+07 & 9.9e+05 & 3.9e+08 & 3.0e+06 & 1.6e+11 & 1.2e+10 \\
-222.786507 & 27.157482 & 0.065 & -0.20 & 0.12 & 3.1e+10 & 1.1e+09 & 2.7e+08 & 2.1e+06 & 8.5e+08 & 4.7e+06 & 3.2e+11 & 1.2e+09 \\
-222.976115 & 16.222138 & 0.056 & 2.35 & 0.91 & 1.1e+09 & 2.9e+08 & 2.0e+07 & 5.4e+05 & 1.4e+08 & 1.3e+06 & 1.0e+11 & 6.8e+09 \\
-234.661258 & 15.958267 & 0.052 & -0.56 & 0.49 & 2.0e+09 & 3.0e+08 & 2.5e+07 & 3.8e+05 & 1.4e+08 & 1.1e+06 & 7.8e+10 & 4.6e+09 \\
-235.272762 & 32.080750 & 0.053 & 0.41 & 0.49 & 1.5e+09 & 2.3e+08 & 1.4e+07 & 1.9e+05 & 8.0e+07 & 6.1e+05 & 1.5e+11 & 8.5e+09 \\
-235.907040 & 39.491740 & 0.064 & 0.59 & 0.56 & 1.1e+09 & 1.8e+08 & 1.8e+07 & 5.1e+05 & 1.3e+08 & 1.3e+06 & 1.1e+11 & 3.9e+09 \\
-246.251584 & 24.405032 & 0.057 & -1.64 & 0.31 & 4.2e+09 & 3.9e+08 & 3.9e+07 & 5.6e+05 & 2.2e+08 & 1.7e+06 & 1.2e+11 & 3.0e+08 \\
-254.332592 & 25.570317 & 0.053 & 1.11 & 0.94 & 3.5e+08 & 9.7e+07 & 8.9e+06 & 2.8e+05 & 5.5e+07 & 5.6e+05 & 7.2e+10 & 6.5e+09 \\
-256.212271 & 34.817332 & 0.056 & 0.34 & 0.27 & 3.3e+09 & 2.6e+08 & 6.7e+07 & 7.1e+05 & 3.7e+08 & 2.4e+06 & 2.7e+11 & 6.0e+09 \\
-339.895154 & -9.516226 & 0.074 & -0.54 & 0.30 & 4.3e+09 & 3.5e+08 & 4.7e+07 & 8.7e+05 & 2.7e+08 & 2.2e+06 & 2.3e+11 & 4.2e+09 \\
-359.226274 & -10.268143 & 0.074 & -0.58 & 0.03 & 1.5e+10 & 1.1e+08 & 1.6e+08 & 1.2e+06 & 6.4e+08 & 3.0e+06 & 4.2e+11 & 7.2e+10
-\enddata
-\end{deluxetable}
-\clearpage
-\end{landscape}
 
@@
 SFR)/(IR SFR + emergent UV SFR).
-%\item \alephuvha~= \alephuv$^{0.33}$.
 \item Following the assumptions in \ref{sfrs}: \alephha~=
@@
 preface `inapplicable' with `seemingly.'
-
-%\begin{figure}[!ht]
-%\centering
-%\includegraphics[scale=0.5]{aha_auv_lowzdog.eps}
-%\caption{The H$\alpha$ escape fraction, \alephha, as a function of the UV
-%escape fraction, \alephuv, for the low-redshift dusty galaxies.  The dashed
-%purple line shows \alephuvha, the extrapolation of \alephuv~to the wavelength
-%of H$\alpha$ using the \citet{calzetti00} attenuation formula, as a function of
-%\alephuv.  This is the uniform dust distribution hypothesis for the attenuation
-%formula.  If low-redshift dust-poor galaxies were to have this range of UV
-%escape fractions, their H$\alpha$ escape fractions would be lower than this
-%extrapolation (dotted black line).  Our fit is the solid orange line.  We find
-%that, in low-redshift dusty galaxies, regions with ionizing stars have lower
-%escape fractions than the extrapolation and higher escape fractions than they
-%would in low-redshift dust-poor galaxies.\label{lowzdog}}
-%\end{figure}
 
@@
 
-\begin{deluxetable}{lllll}
+\begin{deluxetable*}{lllll}
 \tablecolumns{5}
-\tablewidth{0pc}
+\tablewidth{272.42545pt}
 \tablecaption{Summary of regressions\label{regress}}
@@
 \enddata
-\end{deluxetable}
-
-%\begin{figure}[!ht]
-%\centering
-%\includegraphics[scale=0.5]{aha_auv_highz_py.eps}
-%\caption{The H$\alpha$ escape fraction, \alephha, as a function of the UV
-%escape fraction, \alephuv, for the high-redshift dusty galaxies.  The
-%dashed purple line shows \alephuvha, the extrapolation of \alephuv~to the
-%wavelength of H$\alpha$ using the \citet{calzetti00} attenuation formula, as a
-%function of \alephuv.  This is the uniform dust distribution hypothesis for the
-%attenuation formula.  If low-redshift dust-poor galaxies were to have this
-%range of UV escape fractions, their H$\alpha$ escape fractions would be lower
-%than this extrapolation (dotted black line).  Our fit is the solid orange line.
-%We find that, in high-redshift dusty galaxies, regions with ionizing stars have
-%lower escape fractions than the extrapolation and higher escape fractions than
-%they would in low-redshift dust-poor galaxies.\label{highz}}
-%\end{figure}
+\end{deluxetable*}
 
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
 \centering
-\includegraphics[scale=0.365]{fha_fuv.eps}
+\includegraphics[scale=0.4]{fha_fuv.eps}
 \caption{{\small \emph{Top left}: The H$\alpha$ escape fraction, \alephha, as a
@@
 an assumption about the attenuation formula.\label{fha_fuv}}}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\includegraphics[scale=0.5]{ahb_aha_lowzdog.eps}
+\includegraphics[scale=0.45]{ahb_aha_lowzdog.eps}
 \caption{H$\beta$ escape fraction, \alephhb, as a function of H$\alpha$ escape
@@
 
+\clearpage
+
+\begin{turnpage}
+\begin{deluxetable}{llllllllllllll}
+\tablecolumns{14}
+\tablewidth{576.97723pt}
+\tablecaption{Measured and derived quantities for the sample at $z > 0.7$
+\label{tbl:highz}}
+\tabletypesize{\tiny}
+\tablehead{
+\colhead{RA, IR} &
+\colhead{Dec, IR} &
+\colhead{RA, opt.} &
+\colhead{Dec, opt.} &
+\colhead{$z$} &
+\colhead{$\beta$} &
+\colhead{$\sigma_{\beta}$} &
+\colhead{$0.16 \times L_{0.16}$} &
+\colhead{$\sigma_{L_{0.16}}$} &
+\colhead{$L_{\mathrm{H}\alpha}$} &
+\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
+\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
+\colhead{$L_{\mathrm{IR}}$} &
+\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
+\colhead{deg} &
+\colhead{deg} &
+\colhead{deg} &
+\colhead{deg} &
+\colhead{} &
+\colhead{} &
+\colhead{} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$}
+}
+\startdata
+\cutinhead{GOODS-S}
+53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
+53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
+53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
+53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
+53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09
+\enddata
+\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
+\tablecomments{Columns: RA and Dec, IR, are positions in the
+\emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
+priors.  RA and Dec, opt., are positions in the CANDELS catalogs.
+$L_{\mathrm{H}\alpha}$ lim. is a 5$\sigma$ upper limit to the H$\alpha$
+line luminosity.  The entire table is published in the electronic edition of
+\apj.  A portion is shown here for guidance regarding its form and content.}
+\end{deluxetable}
+
+\clearpage
+
+\begin{deluxetable}{lllllllllllll}
+\tablecolumns{13}
+\tablewidth{493.65451pt}
+\tablecaption{Measured and derived quantities for the samples at $z < 0.2$
+\label{tbl:lowz}}
+\tabletypesize{\tiny}
+\tablehead{
+\colhead{RA} &
+\colhead{Dec} &
+\colhead{$z$} &
+\colhead{$\beta$} &
+\colhead{$\sigma_{\beta}$} &
+\colhead{$0.16 \times L_{0.16}$} &
+\colhead{$\sigma_{L_{0.16}}$} &
+\colhead{$L_{\mathrm{H}\beta}$} &
+\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
+\colhead{$L_{\mathrm{H}\alpha}$} &
+\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
+\colhead{$L_{\mathrm{IR}}$} &
+\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
+\colhead{deg} &
+\colhead{deg} &
+\colhead{} &
+\colhead{} &
+\colhead{} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$} &
+\colhead{$L_{\odot}$}
+}
+\startdata
+\cutinhead{Dust-poor galaxies}
+30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
+33.452250 & 12.997628 & 0.219 & -0.45 & 0.05 & 4.3e+10 & 4.3e+08 & 3.6e+07  & \ldots & 1.4e+08 & \ldots & 5.4e+11 & 3.0e+09 \\
+52.191625 & 1.197458 & 0.142 & -1.68 & 0.04 & 1.9e+10 & 1.7e+08 & 7.4e+07   & \ldots & 2.4e+08 & \ldots & 5.4e+10 & 1.0e+09 \\
+59.391667 & -5.622139 & 0.204 & -1.28 & 0.06 & 2.9e+10 & 3.5e+08 & 9.4e+07  & \ldots & 3.5e+08 & \ldots & 1.1e+11 & 1.9e+09 \\
+125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09
+\enddata
+\tablecomments{The entire table is published in the electronic edition of
+\apj.  A portion is shown here for guidance regarding its form and content.}
+\end{deluxetable}
+\end{turnpage}
+\clearpage
+
 \end{document}

### 2016-03-08 sfhist_regress.py
Initial version of regression test

@@ -1,0 +1,83 @@
+#!/usr/bin/env python -tt
+
+import numpy as np
+from scipy.optimize import curve_fit
+from scipy.optimize import brentq
+from scipy.interpolate import interp1d
+from scipy.interpolate import interp2d
+from scipy.optimize import root
+
+highztable = np.genfromtxt('error_fit_highz')
+
+sfruv = highztable[:,2]
+sfrir = highztable[:,3]
+sfrha = highztable[:,0]
+sfrhaerr = highztable[:,1]
+
+uvesc = highztable[:,2]/(highztable[:,2]+highztable[:,3])
+haesc = highztable[:,0]/(highztable[:,2]+highztable[:,3])
+haescerr = highztable[:,1]/(highztable[:,2]+highztable[:,3])
+
+def escregress(x, q):
+  return np.power(x, q)
+
+param0 = .76
+
+param, paramcov = curve_fit(escregress, uvesc, haesc, sigma = haescerr, \
+absolute_sigma = True, p0 = param0)
+
+converttable = np.genfromtxt('KFUV_KIR.dat')
+
+time = 10.**(converttable[:,0])
+
+kuvtime = 10.**(converttable[:,1])
+
+kuvfinal = 1.4e-28*3.826e33/(3.e18/1600.)
+
+uvcorrtime = kuvtime/kuvfinal
+
+kirtime = 10.**converttable[:, 2:]
+
+kirfinal = 4.5e-44*3.826e33
+
+ircorrtime = kirtime/kirfinal
+
+uvzerofind = interp1d(time, uvcorrtime-1.)
+
+uvduration = brentq(uvzerofind, time[0], time[-1])
+
+uvnewdurations = np.random.uniform(low = uvduration - 7.e7, \
+high = uvduration + 7.e7, size = len(uvesc))
+
+uvcorr_newdurations = uvzerofind(uvnewdurations)+1.
+
+newsfruv = sfruv*uvcorr_newdurations
+
+mark_uvesc = 10.**(-.4*np.linspace(start = .55, stop = 5.5, num = 10))
+
+closest_uvesc = np.abs(np.subtract.outer(mark_uvesc, uvesc)).argmin(0)
+
+newsfrir = np.zeros(sfrir.shape)
+
+for i in xrange(len(mark_uvesc)):
+  irzerofind = interp1d(time, ircorrtime[:, i]-1.)
+  irduration = brentq(irzerofind, time[0], time[-1])
[…]

### 2016-03-15 sfhist_regress.py
Changed all SFR conversion factors to Marks values

@@ -25,11 +25,12 @@ time = 10.**(converttable[:,0])
 
 kuvtime = 10.**(converttable[:,1])
 
-kuvfinal = 1.4e-28*3.826e33/(3.e18/1600.)
+kuvfinal = 1.313e-28*3.826e33/(3.e18/1500.)
 
 uvcorrtime = kuvtime/kuvfinal
 
 uvzerofind = interp1d(time, uvcorrtime-1.)
+uvtimeinterp = interp1d(time, kuvtime)
 
 uvduration = brentq(uvzerofind, time[0], time[-1])
 
@@ -43,16 +44,20 @@ param0 = .55
 #param, paramcov = curve_fit(escregress, uvesc, haesc, sigma = haescerr, \
 #absolute_sigma = True, p0 = param0)
 
+#print param
+
 mark_uvesc = 10.**(-.4*np.linspace(start = .55, stop = 5.5, num = 10))
 
 closest_uvesc = np.abs(np.subtract.outer(mark_uvesc, uvesc)).argmin(0)
 
 for j in xrange(10000):
 
-  uvnewdurations = np.random.uniform(low = uvduration, \
-  high = uvduration + 9.e7, size = len(uvesc))
+  uvnewdurations = np.random.uniform(low = 10.**7.3, \
+  high = 10.**10.175, size = len(uvesc))
   
-  uvcorr_newdurations = uvzerofind(uvnewdurations)+1.
+  #uvnewdurations = np.zeros(len(uvesc))+uvduration
+  
+  uvcorr_newdurations = uvtimeinterp(uvnewdurations)/kuvfinal
   
   newsfruv = sfruv*uvcorr_newdurations
 
@@ -67,8 +72,8 @@ for j in xrange(10000):
     ind_gals = (closest_uvesc == i)
     irnewdurations = uvnewdurations[ind_gals]
     kirtime_gals = irinterp(irnewdurations)
-    kirfinal_gals = irinterp(uvduration)
-  #  kirfinal_gals = 4.5e-44*3.826e33
+  #  kirfinal_gals = irinterp(uvduration)
+    kirfinal_gals = 4.5e-44*3.826e33
     newsfrir[ind_gals] = sfrir[ind_gals]*kirtime_gals/kirfinal_gals
   
   newuvesc = newsfruv/(newsfruv+newsfrir)

### 2016-03-15 timeplot.py

@@ -23,7 +23,7 @@ sfrir = 1-sfruv
 
 kuvtime = 10.**(table[:,1])
 
-kuvfinal = 1.4e-28*3.826e33/(3.e18/1600.)
+kuvfinal = 1.313e-28*3.826e33/(3.e18/1500.)
 
 #kuvfinal = kuvtime[-1]
 
@@ -51,8 +51,8 @@ kirfinal = numpy.zeros(uvfescs.shape)
 
 for i in xrange(len(uvfescs)):
   irinterp = interp1d(time, kirtime[:, i])
-  kirfinal[i] = irinterp(uvduration)
-#  kirfinal[i] = 4.5e-44*3.826e33
+#  kirfinal[i] = irinterp(uvduration)
+  kirfinal[i] = 4.5e-44*3.826e33
 
 ircorrtime = kirtime/kirfinal
 
@@ -64,14 +64,14 @@ newsfrir = numpy.dot(numpy.matrix(ircorrtime), numpy.matrix(sfrirm))
 
 newsfrtot = newsfruv+newsfrir
 
-goodtimes = numpy.where(time >= uvduration)[0]
+goodtimes = numpy.where(time > 10.**7.3)[0]
 
 newsfrgood = newsfrtot[goodtimes, :]
 newsfruvgood = newsfruv[goodtimes, :]
 
 rangeuvfescs = (newsfruvgood/newsfrgood).transpose()
 
-hafescs = uvfescs**0.55
+hafescs = uvfescs**0.537
 
 sfrha = (sfruv+sfrir)*hafescs
 
@@ -118,9 +118,9 @@ color2 = '#1b9e77'
 
 fig, ax1 = plot.subplots()
 
-ax1.plot([.001, 1], numpy.power([.001, 1], 0.55), linestyle = '-', \
+ax1.plot([.001, 1], numpy.power([.001, 1], 0.537), linestyle = '-', \
 color = color1, linewidth = 4, marker = None, \
-label = r'f$_{esc}$(H$\alpha$) = f$_{esc}$(0.16$\mu$m)$^{0.55}$')
+label = r'f$_{esc}$(H$\alpha$) = f$_{esc}$(0.16$\mu$m)$^{0.537}$')
 
 ax1.plot(rangeuvfescs, rangehafescs, marker = 'o', color = 'k', \
 linestyle = 'None')

### 2016-03-16 paper.tex
Resize LIR vs LUV figure
Paragraph on MC for varying durations

@@
 \centering
-\includegraphics[scale=0.44]{lir_luv_sample.eps}
+\includegraphics[scale=0.32]{lir_luv_sample.eps}
 \caption{IR luminosity vs. emergent UV luminosity for the samples of dusty
@@
 
-The equations in \citet{kennicutt98} relate IR, emergent UV, and emergent
-H$\alpha$ luminosities to star formation rates (SFRs).  We assume
-that a galaxy's total SFR: (1) is the sum of its IR- and emergent UV-derived
-SFR; and (2) equals the intrinsic (not emergent)
+Equations in \citet{kennicutt98} and \citet{madau14} relate IR, emergent UV,
+and emergent H$\alpha$ luminosities to star formation rates (SFRs).  We multiply
+UV luminosities by $2.68\times10^{-10}$ M$_{\odot}$ yr$^{-1}$ $L_{\odot}^{-1}$;
+IR luminosities by $1.72\times10^{-10}$ M$_{\odot}$ yr$^{-1}$ $L_{\odot}^{-1}$;
+and H$\alpha$ luminosities by
+$3.02\times10^{-8}$ M$_{\odot}$ yr$^{-1}$ $L_{\odot}^{-1}$.
+We assume that a galaxy's total SFR: (1) is the sum of its IR- and emergent
+UV-derived SFR; and (2) equals the intrinsic (not emergent)
 H$\alpha$-derived SFR.  The SFR equations are valid under different assumptions
 for the duration of a galaxy's star formation episode.  Our assumptions will not
-conflict with those of \citet{kennicutt98} if: (1) the SFR has been
-constant for $\sim 10^{8}$ yr, so that the instantaneous H$\alpha$-derived SFR
-equals the prolonged UV- and IR-derived SFRs; and (2) the dominant
-source for the IR luminosity is not old stars or an active nucleus.
+conflict with those of \citet{kennicutt98} and \citet{madau14} if: (1) the SFR
+has been constant for 415 Myr, so that the instantaneous
+H$\alpha$-derived SFR equals the prolonged UV- and IR-derived SFRs; and (2)
+the dominant source for the IR luminosity is not old stars or an active nucleus.
+We explore the uncertainty in our results due to variable durations of star
+formation episodes in \S\ref{sec:discuss}.
 
@@
 \begin{itemize}
-\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
+\item \alephuv~= ($L_{\mathrm{IR}}$/($1.56\times0.16\times
 L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
@@
 
-The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.80}$
+The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.77}$
 for the low-redshift
 dust-poor galaxies.  If we use the IR and UV luminosities from
-\citealt{overzier11}, \alephha~= \alephuv$^{0.84}$.  We lack
+\citealt{overzier11}, \alephha~= \alephuv$^{XXXX}$.  We lack
 uncertainties on any SFRs so we also perform a robust linear regression,
@@
 The top right panel of Fig. \ref{fha_fuv} shows that \alephha~=
-\alephuv$^{0.55}$ for the low-redshift
+\alephuv$^{0.53}$ for the low-redshift
 dusty galaxies.  We use uncertainties only on the emergent H$\alpha$-derived
@@
 The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
-\alephuv$^{0.55}$ for high-redshift
+\alephuv$^{0.54}$ for high-redshift
 dusty galaxies.  We leave limits out of this fit.  The uncertainty in
@@
 The dispersion about the best-fit relation is large; the central 50\% of
-galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.45}$
-and \alephha~= \alephuv$^{0.66}$.  A survival regression, which incorporates
+galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{XXXX}$
+and \alephha~= \alephuv$^{XXXX}$.  A survival regression, which incorporates
 H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
-$q\,\log\,$\alephuv, finds $q = 0.47$, as does a simple linear regression using
+$q\,\log\,$\alephuv, finds $q = XXXX$, as does a simple linear regression using
 only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
@@
 \startdata
-Low-z dust-poor & 0.799 & 0.094 & 6.0  & 13 \\
-Low-z dusty     & 0.548 & 0.029 & 67.0 & 54 \\
-High-z dusty    & 0.549 & 0.008 & 6.6  & 320
+Low-z dust-poor & 0.766 & XXXX & XXXX & XXXX \\
+Low-z dusty     & 0.532 & XXXX & XXXX & XXXX \\
+High-z dusty    & 0.537 & XXXX & XXXX  & XXXX
 \enddata
@@
 this \citet{kriek13} formula and our result implies that
-\alephha~= \alephuvha$^{2.2}$.  The \citet{reddy15} attenuation formula has
-\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
+\alephha~= \alephuvha$^{2.1}$.  The \citet{reddy15} attenuation formula has
+\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.3}$.
 If the true formula instead has a
@@
 fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
-\alephuv$^{0.55}$---we conclude that for dusty
+\alephuv$^{0.54}$---we conclude that for dusty
 galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
@@
 to our possibly invalid assumption that a galaxy's SFR has been
-constant for at least $10^{8}$ yr.  For example, if most
-massive stars formed over 15 Myr instead of 300 Myr, we should multiply
-$L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
-UV and IR SFRs.  The true UV SFR is 57\% higher and the true IR SFR is 63\%
+constant for at least 415 Myr.  For example, if most
+massive stars formed over 15 Myr instead of 415 Myr, we should multiply
+$0.16 \times L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
+UV and IR SFRs.  The true UV SFR is 56\% higher and the true IR SFR is 60\%
 higher \citep{madau14}.  The true UV escape fraction is little different;
@@
 lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
-could contribute to a given escape fraction.  The spread is imprecise for three
+could contribute to a given escape fraction.  The spread is imprecise for two
 reasons:
 \begin{enumerate}
-\item \citet{madau14} calculate conversion factors between luminosities and
-star formation rates at 0.15$\,\micron$ rather than 0.16$\,\micron$.
-\item \citet{madau14} use the models of \citet{conroy10} to calculate these
-conversion factors.  The conversion factor between $L_{\mathrm{IR}}$ and
+\item We define the UV escape fraction as a function of UV- and IR-derived SFRs.
+\citet{madau14} use the models of \citet{conroy10} to calculate
+conversion factors between luminosities and SFRs.  The
+conversion factor between $L_{\mathrm{IR}}$ and
 IR-derived SFR is a function of the UV escape fraction as well as the duration
 of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
-[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We calculate the spread
-using the conversion factor for the given UV escape fraction.
-\item The \citet{kennicutt98} conversion factors for $L_{0.16}$ and
-$L_{\mathrm{IR}}$ are valid at different durations of the star formation
-episode.
+[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We set aside the
+circularity that results from using both these functions by fixing the UV
+escape fraction in the SFR(IR)/$L_{\mathrm{IR}}$ function to the
+given UV escape fraction.
+\item Since SFR(IR)/$L_{\mathrm{IR}}$ is a function of more than duration of the
+star formation episode, at a duration of 415 Myr most of the IR
+conversion factors differ from our adopted value in \S\ref{sfrs}.
 \end{enumerate}
@@
 
+We perform a second experiment to investigate the effect of episodes of constant
+star formation rate with variable duration on the dispersion about the best-fit
+relation.  For each high-redshift dusty galaxy we draw a random duration from a
+uniform distribution with limits at 20 Myr and 15 Gyr.  We calculate the
+galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
+The IR conversion factor requires a UV escape fraction from one of the given
+UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
+fraction which is closest to the galaxy's UV escape fraction for a duration
+of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
+escape fractions for the random duration.  We perform a regression for the
+sample of galaxies, record $q$, and repeat the process 10,000 times.  Fig.
+\ref{} shows the distribution of $q$ values from this process.  While the
+$q$ values bounding the central 50\% of the sample encompass the range of $q$
+values in Fig. \ref{}, we caution that this simulation involves many
+assumptions.
+
 \begin{figure}[!ht]
@@
 a given escape fraction if a galaxy's SFR has been constant for a
-duration different from $10^{8}$ yr.  We assign the input
+duration different from 415 Myr.  We assign the input
 $f_{\mathrm{esc}}$ values to the conversion factors
-between luminosity and SFR in \citet{kennicutt98}.  The UV and IR conversion
+between luminosities and SFRs in \S\ref{sfrs}.  The UV and IR conversion
 factors change as the duration of the star formation episode varies \citep{madau14}.
@@
 recover the \citet{calzetti97b} relation between H$\alpha$ and UV escape
-fractions: \alephha~= \alephuv$^{0.80}$.  Our nonstandard method for determining
+fractions: \alephha~= \alephuv$^{0.77}$.  Our nonstandard method for determining
 H$\alpha$ escape fractions should be grossly correct.
 \item For the \citet{hwang13} sample of low-redshift dusty galaxies, we find
-that \alephha~= \alephuv$^{0.55}$.
+that \alephha~= \alephuv$^{0.53}$.
 \item For our sample of dusty galaxies at $0.7 < z < 1.5$, we find that
-\alephha~= \alephuv$^{0.55}$.  The dispersion about the best-fit relation is
+\alephha~= \alephuv$^{0.54}$.  The dispersion about the best-fit relation is
 large.

### 2016-03-17 paper.tex
Standardized year
Filled in numbers

@@
 dust-poor galaxies.  If we use the IR and UV luminosities from
-\citealt{overzier11}, \alephha~= \alephuv$^{XXXX}$.  We lack
+\citealt{overzier11}, \alephha~= \alephuv$^{0.80}$.  We lack
 uncertainties on any SFRs so we also perform a robust linear regression,
@@
 The dispersion about the best-fit relation is large; the central 50\% of
-galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{XXXX}$
-and \alephha~= \alephuv$^{XXXX}$.  A survival regression, which incorporates
+galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.44}$
+and \alephha~= \alephuv$^{0.63}$.  A survival regression, which incorporates
 H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
-$q\,\log\,$\alephuv, finds $q = XXXX$, as does a simple linear regression using
+$q\,\log\,$\alephuv, finds $q = 0.46$, as does a simple linear regression using
 only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
@@
 \startdata
-Low-z dust-poor & 0.766 & XXXX & XXXX & XXXX \\
-Low-z dusty     & 0.532 & XXXX & XXXX & XXXX \\
-High-z dusty    & 0.537 & XXXX & XXXX  & XXXX
+Low-z dust-poor & 0.766 & 0.091 & 6.1 & 13 \\
+Low-z dusty     & 0.532 & 0.027 & 65.0 & 54 \\
+High-z dusty    & 0.537 & 0.008 & 6.5 & 320
 \enddata
@@
 star formation episode, at a duration of 415 Myr most of the IR
-conversion factors differ from our adopted value in \S\ref{sfrs}.
+conversion factors differ from the value we adopt in \S\ref{sfrs}.
 \end{enumerate}
@@
 
-We perform a second experiment to investigate the effect of episodes of constant
+We perform a second test to investigate the effect of episodes of constant
 star formation rate with variable duration on the dispersion about the best-fit
 relation.  For each high-redshift dusty galaxy we draw a random duration from a
-uniform distribution with limits at 20 Myr and 15 Gyr.  We calculate the
+uniform distribution with limits at 20 Myr and 2 Gyr.  We calculate the
 galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
@@
 $q$ values bounding the central 50\% of the sample encompass the range of $q$
-values in Fig. \ref{}, we caution that this simulation involves many
-assumptions.
+values in Fig. \ref{}, we caution that our assumption of a uniform distribution
+of durations is likely incorrect.
 
@@
 factors change as the duration of the star formation episode varies \citep{madau14}.
-The durations for the points shown here range from $2\times10^{7}$ to
-$1.5\times10^{10}$ yr.\label{spread}}
+The durations for the points shown here range from 20 Myr to
+2 Gyr.\label{spread}}
 \end{figure}

### 2016-03-17 sfhist_regress.py

@@ -5,6 +5,7 @@ from scipy.optimize import curve_fit
 from scipy.optimize import brentq
 from scipy.interpolate import interp1d
 import matplotlib.pyplot as plot
+from matplotlib.ticker import FormatStrFormatter
 
 newparams = np.zeros(10000)
 
@@ -53,7 +54,7 @@ closest_uvesc = np.abs(np.subtract.outer(mark_uvesc, uvesc)).argmin(0)
 for j in xrange(10000):
 
   uvnewdurations = np.random.uniform(low = 10.**7.3, \
-  high = 10.**10.175, size = len(uvesc))
+  high = 10.**9.3, size = len(uvesc))
   
   #uvnewdurations = np.zeros(len(uvesc))+uvduration
   
@@ -84,6 +85,17 @@ for j in xrange(10000):
   sigma = newhaescerr, absolute_sigma = True, p0 = param0)
   
   newparams[j] = newparam
-  
-plot.hist(newparams, bins = 20)
-plot.show()
+
+plot.rcParams['figure.figsize'] = [7.32, 7.32]
+majorFormatter = FormatStrFormatter('%0.3f')
+
+fig, ax = plot.subplots()
+plot.hist(newparams, bins = 16, histtype = 'step', color = 'black', \
+range = (0.52, 0.56))
+ax.set_xlabel(r'best-fit q for f$_{esc}$(H$\alpha$) = f$_{esc}$(0.16$\mu$m)$^{q}$')
+ax.set_ylabel(r'Number')
+ax.xaxis.set_major_formatter(majorFormatter)
+ax.set_xticks(np.arange(.52, .56, .01))
+ax.set_xticks(np.arange(.52, .56, .0025), minor = True)
+
+plot.savefig('dist_hauv_age.eps')

### 2016-03-17 timeplot.py

@@ -64,7 +64,7 @@ newsfrir = numpy.dot(numpy.matrix(ircorrtime), numpy.matrix(sfrirm))
 
 newsfrtot = newsfruv+newsfrir
 
-goodtimes = numpy.where(time > 10.**7.3)[0]
+goodtimes = numpy.where((time > 10.**7.3) & (time < 10.**9.3))[0]
 
 newsfrgood = newsfrtot[goodtimes, :]
 newsfruvgood = newsfruv[goodtimes, :]

### 2016-03-18 paper.tex
Incoporated figure into paper

@@
 
-We perform a second test to investigate the effect of episodes of constant
-star formation rate with variable duration on the dispersion about the best-fit
-relation.  For each high-redshift dusty galaxy we draw a random duration from a
-uniform distribution with limits at 20 Myr and 2 Gyr.  We calculate the
-galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
-The IR conversion factor requires a UV escape fraction from one of the given
-UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
-fraction which is closest to the galaxy's UV escape fraction for a duration
-of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
-escape fractions for the random duration.  We perform a regression for the
-sample of galaxies, record $q$, and repeat the process 10,000 times.  Fig.
-\ref{} shows the distribution of $q$ values from this process.  While the
-$q$ values bounding the central 50\% of the sample encompass the range of $q$
-values in Fig. \ref{}, we caution that our assumption of a uniform distribution
-of durations is likely incorrect.
-
 \begin{figure}[!ht]
@@
 2 Gyr.\label{spread}}
+\end{figure}
+
+We perform a second test to investigate the effect of episodes of constant
+star formation rate with variable duration on the dispersion about the best-fit
+relation.  For each high-redshift dusty galaxy we draw a random duration from a
+uniform distribution with limits at 20 Myr and 2 Gyr.  We calculate the
+galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
+The IR conversion factor requires a UV escape fraction from one of the given
+UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
+fraction which is closest to the galaxy's UV escape fraction for a duration
+of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
+escape fractions for the random duration.  We perform a regression for the
+sample of galaxies, record the $q$ value, and repeat the process 10,000 times.  Fig.
+\ref{distq} shows the distribution of $q$ values.  While the
+$q$ values bounding the central 50\% of the sample encompass the range of $q$
+values in Fig. \ref{distq}, we caution that our assumption of a uniform
+distribution of durations is likely incorrect.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.5]{dist_hauv_age.eps}
+\caption{A distribution of best-fit power-law indices, $q$ values, for the
+relation between H$\alpha$ and UV escape fractions for the dusty galaxies at
+high redshift.  This distribution comes from drawing for each galaxy in the
+sample a random duration between 20 Myr and 2 Gyr for an episode of constant
+star formation rate.\label{distq}}
 \end{figure}

### 2016-10-05 paper_aa.tex
AA format

--- 2016-03-18 paper.tex
@@
-\documentclass[preprint]{aastex}
+\documentclass[referee]{aa}
 
@@
 \usepackage{amsmath}
-\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
+\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\mu$m)}
 \newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
-\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
+\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\mu$m)}
 \newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}
@@
 
-\author{Kyle Penner\altaffilmark{1}, Mark Dickinson\altaffilmark{2},
-Benjamin Weiner\altaffilmark{3}, Hanae Inami\altaffilmark{2},
-Jeyhan Kartaltepe\altaffilmark{2}, Janine Pforr\altaffilmark{4},
-Hooshang Nayyeri\altaffilmark{5},
-Susan Kassin\altaffilmark{6},
-Casey Papovich\altaffilmark{7}, and
-Alexandra Pope\altaffilmark{8}
+\author{K. Penner\inst{\ref{inst1}}
+\and M. Dickinson\inst{\ref{inst2}}
+\and B. Weiner\inst{\ref{inst3}}
+\and H. Inami\inst{\ref{inst2}}
+\and J. Kartaltepe\inst{\ref{inst2}}
+\and J. Pforr\inst{\ref{inst4}}
+\and H. Nayyeri\inst{\ref{inst5}}
+\and S. Kassin\inst{\ref{inst6}}
+\and C. Papovich\inst{\ref{inst7}}
+\and A. Pope\inst{\ref{inst8}}
 }
 
-\email{kdpenner@gmail.com}
-
-\altaffiltext{1}{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
-91191 Gif-sur-Yvette, France}
-\altaffiltext{2}{National Optical Astronomy Observatory,
-Tucson, AZ 85719, USA}
-\altaffiltext{3}{Department of Astronomy, University of Arizona,
-Tucson, AZ 85721, USA}
-\altaffiltext{4}{Laboratoire d'Astrophysique de Marseille, Aix
-Marseille Universit\'e, 13388 Marseille cedex 13, France}
-\altaffiltext{5}{Department of Physics \& Astronomy, University of California
-Irvine, Irvine, CA 92697, USA}
-\altaffiltext{6}{Space Telescope Science Institute, Baltimore, MD 21218, USA}
-\altaffiltext{7}{Department of Physics \& Astronomy, Texas A\&M University,
-College Station, TX 77843, USA}
-\altaffiltext{8}{Department of Astronomy, University of Massachusetts Amherst,
-Amherst, MA 01003, USA}
-
-\begin{abstract}
+\institute{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
+91191 Gif-sur-Yvette, France\email{kdpenner@gmail.com}\label{inst1}
+\and National Optical Astronomy Observatory, Tucson, AZ 85719, USA\label{inst2}
+\and Department of Astronomy, University of Arizona, Tucson, AZ 85721, USA\label{inst3}
+\and Laboratoire d'Astrophysique de Marseille, Aix Marseille Universit\'e,
+13388 Marseille cedex 13, France\label{inst4}
+\and Department of Physics \& Astronomy, University of California
+Irvine, Irvine, CA 92697, USA\label{inst5}
+\and Space Telescope Science Institute, Baltimore, MD 21218, USA\label{inst6}
+\and Department of Physics \& Astronomy, Texas A\&M University,
+College Station, TX 77843, USA\label{inst7}
+\and Department of Astronomy, University of Massachusetts Amherst,
+Amherst, MA 01003, USA\label{inst8}}
+
+\date{Received date / Accepted date}
+
+\abstract{
 Do spatial distributions of dust grains in galaxies have typical forms, as do
@@
 indicates diverse dust morphologies and the implausibility of the screen
-assumption.
-\end{abstract}
+assumption.}
+
+\keywords{ISM: dust, extinction -- galaxies: ISM -- galaxies: high-redshift}
+
+\titlerunning{The degeneracy between dust distributions and the attenuation formula}
+\authorrunning{K. Penner et al.}
+
+\maketitle
 
@@
 Our study uses observations of the GOODS-S, COSMOS, and UDS regions.  A
-catalog of \emph{Herschel}/PACS 100$\,\micron$ sources for GOODS-S comes from
+catalog of \emph{Herschel}/PACS 100$\,\mu$m sources for GOODS-S comes from
 \citet{magnelli13}; for COSMOS and UDS, we use catalogs produced for the
 \emph{Herschel} survey of CANDELS regions (Inami et al., in prep).  A
-100$\,\micron$ source is defined as a $\ge 3\sigma$ flux density measurement
-from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\micron$ source, which is based
-on an IRAC 3.6$\,\micron$ source prior.  In GOODS-S, the catalog has
-flux densities at 24, 70, 100, and 160$\,\micron$; in COSMOS and
+100$\,\mu$m source is defined as a $\ge 3\sigma$ flux density measurement
+from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\mu$m source, which is based
+on an IRAC 3.6$\,\mu$m source prior.  In GOODS-S, the catalog has
+flux densities at 24, 70, 100, and 160$\,\mu$m; in COSMOS and
 UDS, the catalogs have flux densities at 24, 100, 160, 250, 350,
-and 500$\,\micron$.  All flux densities are $\ge 3\sigma$.  We do not use the
-250, 350, and 500$\,\micron$ flux
+and 500$\,\mu$m.  All flux densities are $\ge 3\sigma$.  We do not use the
+250, 350, and 500$\,\mu$m flux
 densities in the COSMOS and UDS catalogs, to avoid the effects of source
@@
 
-We associate each 100$\,\micron$ source with a 1.6$\,\micron$ ($H$-band) source
+We associate each 100$\,\mu$m source with a 1.6$\,\mu$m ($H$-band) source
 in the
@@
 broadband flux densities at many wavelengths, not all of which are common to the
-other two.  We require the 1.6$\,\micron$ source to be a unique match
-within 0.7$\arcsec$ of the position of the 100$\,\micron$ source's
-3.6$\,\micron$ prior.  The match radius is an estimate for maximizing the
+other two.  We require the 1.6$\,\mu$m source to be a unique match
+within 0.7$\arcsec$ of the position of the 100$\,\mu$m source's
+3.6$\,\mu$m prior.  The match radius is an estimate for maximizing the
 number of unique matches while minimizing the number of multiple matches.
@@
 \emph{HST}/WFC3-IR grism survey 3D-\emph{HST} \citep{brammer12}.
-We match each 100$\,\micron$ source to a counterpart in the direct image
+We match each 100$\,\mu$m source to a counterpart in the direct image
 accompanying the grism observations.  Two people in our group visually inspect
@@
 H$\alpha$ and [N II] lines are blended; we assume that the line flux of [NII]
-at $\lambda = 0.6583\,\micron$ is 0.3 times the H$\alpha$ line flux and that
-the line flux of [N II] at $\lambda = 0.6548\,\micron$ is 0.1 times the
+at $\lambda = 0.6583\,\mu$m is 0.3 times the H$\alpha$ line flux and that
+the line flux of [N II] at $\lambda = 0.6548\,\mu$m is 0.1 times the
 H$\alpha$ line flux.  The ratio of [N II] to H$\alpha$ line fluxes depends on
@@
 line flux.  To determine line flux upper limits for these sources, we match each
-100$\,\micron$ source to a source with a spectroscopic redshift in
+100$\,\mu$m source to a source with a spectroscopic redshift in
 the catalogs of:
@@
 Almaini et al. (in prep.) for UDS; and \citet{lilly09} for COSMOS.  Operationally both the
-100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
-If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
+100$\,\mu$m and spectroscopic catalogs are matched to the CANDELS catalogs.
+If the 100$\,\mu$m source has a spectroscopic redshift that is unconfirmed
 by an uncontaminated grism spectrum, we estimate the widths of the invisible
@@
 To summarize, our high-redshift sample contains galaxies with: (1) detected
-emission at 100$\,\micron$; (2) detected emission at 1.6$\,\micron$; and (3)
+emission at 100$\,\mu$m; (2) detected emission at 1.6$\,\mu$m; and (3)
 spectroscopically-determined redshifts at $0.7 < z < 1.5$.
@@
 Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
-galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
+galaxies with: (1) luminosity at 0.153$\,\mu$m$, 0.153 \times L_{0.153},
 \ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}~
-\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
-and the radius is the half-light radius at 0.35$\,\micron$ ($u$-band);
+\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\mu$m
+and the radius is the half-light radius at 0.35$\,\mu$m ($u$-band);
 (3) $z < 0.3$; and (4) no evidence for emission from an AGN.
 
-We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
-the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
+We use 24$\,\mu$m flux densities in the \emph{Spitzer} Heritage Archive.  Of
+the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\mu$m flux
 densities per the recommendations in the enhanced imaging products quick start
@@
 densities at
-0.15 and 0.23$\,\micron$ (NUV and FUV bands).
+0.15 and 0.23$\,\mu$m (NUV and FUV bands).
 H$\alpha$ line
@@
 dust-obscured galaxies (DOGs) and a control sample: flux densities at
-9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
-\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
+9, 12, 22, 25, 60, 100, and 140$\,\mu$m, from \emph{IRAS}, \emph{AKARI}, and
+\emph{WISE} observations; 0.15 and 0.23$\,\mu$m flux densities, from
 \emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
-A low-redshift DOG has either: (1) a flux density, $S_{\nu}$, at 9$\,\micron$ that is more
-than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
-12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
+A low-redshift DOG has either: (1) a flux density, $S_{\nu}$, at 9$\,\mu$m that is more
+than 982 times its flux density at 0.22$\,\mu$m; or (2) a flux density at
+12$\,\mu$m that is more than 892 times its flux density at 0.22$\,\mu$m.
 A low-redshift control galaxy has a flux density at
-12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
+12$\,\mu$m that is less than 892 times its flux density at 0.22$\,\mu$m.
 Among other criteria the sample of control galaxies is filled such that its
@@
 The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
-differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
+differences, in the accompanying 0.62$\,\mu$m ($r$-band) images, between
 Petrosian flux
@@
 
-We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
+We estimate a total IR luminosity (8--1000$\,\mu$m; $L_{\mathrm{IR}}$) for
 each galaxy.  We redshift the \citet{chary01} template spectral energy
@@
 an IR luminosity.  If the galaxy has one
-measured flux density at a rest-frame wavelength between 8 and 1000$\,\micron$,
+measured flux density at a rest-frame wavelength between 8 and 1000$\,\mu$m,
 we find the redshifted SED that most closely matches that flux
@@
 not fit low-redshift dust-poor galaxies as well as other SEDs.  They measured
-IR flux density limits at 70 and 160$\,\micron$ as well as flux densities at
-24$\,\micron$.  The footnote explains that the \citet{chary01} SEDs, when
-fit to 24$\,\micron$ flux densities, predict flux densities at 70 and
-160$\,\micron$ that fall above their upper limits.  Our IR luminosities are
+IR flux density limits at 70 and 160$\,\mu$m as well as flux densities at
+24$\,\mu$m.  The footnote explains that the \citet{chary01} SEDs, when
+fit to 24$\,\mu$m flux densities, predict flux densities at 70 and
+160$\,\mu$m that fall above their upper limits.  Our IR luminosities are
 high compared to theirs---on average, a factor of 1.4 times higher; at most, a
@@
 For galaxies with UV emission from newly formed massive stars the continuum
-between 0.125 and 0.263$\,\micron$ is approximately a power law with index
+between 0.125 and 0.263$\,\mu$m is approximately a power law with index
 $\beta$:
@@
 We estimate an emergent UV luminosity or a
-limit at rest-frame 0.16$\,\micron$ for each galaxy using its redshift and
+limit at rest-frame 0.16$\,\mu$m for each galaxy using its redshift and
 the power-law fit to the rest-frame UV flux densities.  We refer to the
@@
 
-\begin{landscape}
-\begin{deluxetable}{llllllllllllll}
-\tablecolumns{14}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the sample at $z > 0.7$
+\begin{sidewaystable*}
+%\tablecolumns{14}
+%\tablewidth{0pc}
+\caption{Measured and derived quantities for the sample at $z > 0.7$
 \label{tbl:highz}}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA, IR} &
-\colhead{Dec, IR} &
-\colhead{RA, opt.} &
-\colhead{Dec, opt.} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{GOODS-S}
-53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
+\tiny
+\begin{tabular}{llllllllllllll}
+\hline \hline
+RA, IR &
+Dec, IR &
+RA, opt. &
+Dec, opt. &
+$z$ &
+$\beta$ &
+$\sigma_{\beta}$ &
+$0.16 \times L_{0.16}$ &
+$\sigma_{L_{0.16}}$ &
+$L_{\mathrm{H}\alpha}$ &
+$\sigma_{L_{\mathrm{H}\alpha}}$ &
+$L_{\mathrm{H}\alpha}$ lim. &
+$L_{\mathrm{IR}}$ &
+$\sigma_{L_{\mathrm{IR}}}$ \\
+%{UV SFR} &
+%{H$\alpha$ SFR} &
+%{H$\alpha$ SFR lim.} &
+%{IR SFR} \\
+deg &
+deg &
+deg &
+deg &
+ &
+ &
+ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ \\
+%{M$_{\odot}$ yr$^{-1}$} &
+%{M$_{\odot}$ yr$^{-1}$} &
+%{M$_{\odot}$ yr$^{-1}$} &
+%{M$_{\odot}$ yr$^{-1}$}
+\hline
+\multicolumn{14}{c}{GOODS-S} \\
+\hline
+53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablefootmark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
 53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
@@
 53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
-53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09
-\enddata
-\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
-\tablecomments{Columns: RA and Dec, IR, are positions in the
+53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09 \\
+\hline
+\end{tabular}
+\tablefoot{Columns: RA and Dec, IR, are positions in the
 \emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
@@
 line luminosity.  The entire table is published in the electronic edition of
-\apj.  A portion is shown here for guidance regarding its form and content.}
-\end{deluxetable}
-\clearpage
-\end{landscape}
-
+\aap.  A portion is shown here for guidance regarding its form and content.}
+\tablefoottext{G}{Spectroscopic redshift solely from grism observations.}
+\end{sidewaystable*}
+
+\longtab{
 \begin{landscape}
-\begin{deluxetable}{llllllllllllll}
-\tablecolumns{14}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the sample at $z > 0.7$}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA, IR} &
-\colhead{Dec, IR} &
-\colhead{RA, opt.} &
-\colhead{Dec, opt.} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{GOODS-S}
-53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
+%\tablecolumns{14}
+%\tablewidth{0pc}
+\tiny
+\begin{longtable}{llllllllllllll}
+\caption{Measured and derived quantities for the sample at $z > 0.7$} \\
+\hline \hline
+RA, IR &
+Dec, IR &
+RA, opt. &
+Dec, opt. &
+$z$ &
+$\beta$ &
+$\sigma_{\beta}$ &
+$0.16 \times L_{0.16}$ &
+$\sigma_{L_{0.16}}$ &
+$L_{\mathrm{H}\alpha}$ &
+$\sigma_{L_{\mathrm{H}\alpha}}$ &
+$L_{\mathrm{H}\alpha}$ lim. &
+$L_{\mathrm{IR}}$ &
+$\sigma_{L_{\mathrm{IR}}}$ \\
+%{UV SFR} &
+%{H$\alpha$ SFR} &
+%{H$\alpha$ SFR lim.} &
+%{IR SFR} \\
+deg &
+deg &
+deg &
+deg &
+ &
+ &
+ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ \\
+%{M$_{\odot}$ yr$^{-1}$} &
+%{M$_{\odot}$ yr$^{-1}$} &
+%{M$_{\odot}$ yr$^{-1}$} &
+%{M$_{\odot}$ yr$^{-1}$}
+\hline
+\multicolumn{14}{c}{GOODS-S} \\
+\hline
+53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablefootmark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
 53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
@@
 53.122547 & -27.852680 & 53.122554 & -27.852730 & 0.735 & 1.74 & 1.32 & 2.2e+08 & 9.1e+07 & \ldots & \ldots & 4.9e+07 & 9.6e+10 & 3.2e+09  \\
-53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablenotemark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\
+53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablefootmark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\
 53.070782 & -27.850611 & 53.070771 & -27.850671 & 0.991 & -3.56 & 0.72 & 2.8e+09 & 3.7e+08 & 1.8e+08 & 2.1e+07 & \ldots & 3.0e+11 & 8.7e+09  \\
@@
 53.156612 & -27.795471 & 53.156735 & -27.795577 & 1.097 & -1.51 & 0.10 & 1.5e+10 & 3.0e+08 & 2.7e+08 & 2.8e+07 & \ldots & 2.2e+11 & 2.2e+09  \\
-53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablenotemark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
+53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablefootmark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
 53.078960 & -27.799620 & 53.078906 & -27.799642 & 1.085 & -2.09 & 0.42 & 5.5e+09 & 3.1e+08 & 2.1e+08 & 1.1e+07 & \ldots & 6.7e+10 & 3.3e+07  \\
@@
 53.197544 & -27.786417 & 53.197582 & -27.786395 & 1.098 & -2.98 & 0.77 & 1.3e+09 & 2.0e+08 & \ldots & \ldots & 1.3e+08 & 2.0e+11 & 5.9e+09  \\
-53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablenotemark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\
+53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablefootmark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\
 53.104275 & -27.788363 & 53.104331 & -27.788388 & 1.357 & -0.62 & 0.20 & 4.7e+09 & 6.3e+08 & \ldots & \ldots & 8.8e+07 & 1.3e+11 & 4.9e+08  \\
 53.048252 & -27.783079 & 53.048272 & -27.783100 & 0.814 & -0.53 & 0.27 & 3.8e+09 & 2.8e+08 & 1.1e+08 & 6.4e+06 & \ldots & 8.5e+10 & 1.3e+10  \\
-53.135197 & -27.781746 & 53.135245 & -27.781672 & 1.437\tablenotemark{G} & -0.57 & 0.05 & 5.2e+09 & 1.9e+08 & 3.5e+08 & 1.7e+07 & \ldots & 2.5e+11 & 2.4e+10  \\
+53.135197 & -27.781746 & 53.135245 & -27.781672 & 1.437\tablefootmark{G} & -0.57 & 0.05 & 5.2e+09 & 1.9e+08 & 3.5e+08 & 1.7e+07 & \ldots & 2.5e+11 & 2.4e+10  \\
 53.044064 & -27.785015 & 53.044080 & -27.785048 & 1.045 & -1.39 & 0.19 & 1.4e+10 & 4.3e+08 & 1.8e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.5e+10  \\
@@
 53.061565 & -27.742525 & 53.061590 & -27.742532 & 0.736 & 4.18 & 3.25 & 2.5e+07 & 2.5e+07 & 3.9e+07 & 4.0e+06 & \ldots & 1.5e+11 & 3.7e+09  \\
-53.204159 & -27.738546 & 53.204191 & -27.738536 & 0.984\tablenotemark{G} & -1.92 & 1.20 & 6.9e+09 & 1.3e+09 & 2.3e+08 & 1.5e+07 & \ldots & 1.4e+11 & 4.6e+09  \\
+53.204159 & -27.738546 & 53.204191 & -27.738536 & 0.984\tablefootmark{G} & -1.92 & 1.20 & 6.9e+09 & 1.3e+09 & 2.3e+08 & 1.5e+07 & \ldots & 1.4e+11 & 4.6e+09  \\
 53.144276 & -27.735434 & 53.144345 & -27.735558 & 1.224 & 0.90 & 1.11 & 2.2e+09 & 2.2e+08 & \ldots & \ldots & 9.1e+07 & 1.8e+11 & 1.0e+10  \\
@@
 53.124729 & -27.716934 & 53.124780 & -27.717107 & 1.356 & -0.78 & 0.05 & 1.3e+10 & 4.8e+08 & 7.1e+08 & 4.2e+07 & \ldots & 1.2e+12 & 4.6e+10  \\
-53.094563 & -27.723654 & 53.094718 & -27.723585 & 0.738\tablenotemark{G} & -0.56 & 0.24 & 3.2e+09 & 2.4e+08 & 7.5e+07 & 6.7e+06 & \ldots & 3.1e+10 & 3.5e+07  \\
+53.094563 & -27.723654 & 53.094718 & -27.723585 & 0.738\tablefootmark{G} & -0.56 & 0.24 & 3.2e+09 & 2.4e+08 & 7.5e+07 & 6.7e+06 & \ldots & 3.1e+10 & 3.5e+07  \\
 53.173607 & -27.722679 & 53.173655 & -27.722641 & 0.978 & -2.56 & 17.70 & 1.2e+08 & 3.6e+08 & \ldots & \ldots & 4.3e+07 & 1.3e+11 & 3.8e+08  \\
@@
 53.111504 & -27.695997 & 53.111521 & -27.695987 & 0.734 & 0.40 & 0.48 & 1.4e+09 & 2.1e+08 & 1.0e+08 & 1.0e+07 & \ldots & 2.3e+11 & 5.7e+10  \\
-53.162651 & -27.692356 & 53.162680 & -27.692336 & 0.733\tablenotemark{G} & -1.34 & 0.15 & 8.7e+09 & 4.1e+08 & 9.0e+07 & 1.5e+07 & \ldots & 3.4e+10 & 9.1e+08  \\
+53.162651 & -27.692356 & 53.162680 & -27.692336 & 0.733\tablefootmark{G} & -1.34 & 0.15 & 8.7e+09 & 4.1e+08 & 9.0e+07 & 1.5e+07 & \ldots & 3.4e+10 & 9.1e+08  \\
 53.131149 & -27.688419 & 53.131169 & -27.688368 & 0.837 & -0.83 & 0.16 & 1.3e+10 & 5.4e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 4.2e+09  \\
@@
 53.088108 & -27.685200 & 53.088136 & -27.685181 & 1.110 & -1.41 & 0.43 & 1.0e+10 & 5.1e+08 & 2.9e+08 & 2.3e+07 & \ldots & 3.4e+11 & 1.4e+10  \\
-\cutinhead{COSMOS}
-150.137010 & 2.243688 & 150.137013 & 2.243673 & 0.752\tablenotemark{G} & 2.42 & 1.13 & 1.3e+08 & 6.4e+07 & \ldots & \ldots & 3.5e+07 & 6.9e+10 & 7.4e+09  \\
-150.117280 & 2.327124 & 150.117315 & 2.327120 & 0.903\tablenotemark{G} & -0.08 & 0.28 & 8.4e+09 & 1.1e+09 & 3.2e+08 & 2.0e+07 & \ldots & 2.7e+11 & 1.6e+10  \\
-150.130330 & 2.472160 & 150.130346 & 2.472122 & 0.924\tablenotemark{G} & 0.55 & 0.51 & 3.6e+09 & 8.6e+08 & 8.7e+07 & 1.2e+07 & \ldots & 1.1e+11 & 1.9e+08  \\
-150.155450 & 2.205458 & 150.155459 & 2.205452 & 0.783\tablenotemark{G} & 1.06 & 0.26 & 2.3e+09 & 2.5e+08 & 1.9e+08 & 1.3e+07 & \ldots & 2.9e+11 & 5.4e+09  \\
-150.067080 & 2.372434 & 150.067101 & 2.372425 & 1.257\tablenotemark{G} & 0.57 & 0.57 & 5.7e+09 & 3.1e+09 & 8.5e+08 & 5.5e+07 & \ldots & 6.9e+11 & 4.3e+10  \\
+\hline
+\multicolumn{14}{c}{COSMOS} \\
+\hline
+150.137010 & 2.243688 & 150.137013 & 2.243673 & 0.752\tablefootmark{G} & 2.42 & 1.13 & 1.3e+08 & 6.4e+07 & \ldots & \ldots & 3.5e+07 & 6.9e+10 & 7.4e+09  \\
+150.117280 & 2.327124 & 150.117315 & 2.327120 & 0.903\tablefootmark{G} & -0.08 & 0.28 & 8.4e+09 & 1.1e+09 & 3.2e+08 & 2.0e+07 & \ldots & 2.7e+11 & 1.6e+10  \\
+150.130330 & 2.472160 & 150.130346 & 2.472122 & 0.924\tablefootmark{G} & 0.55 & 0.51 & 3.6e+09 & 8.6e+08 & 8.7e+07 & 1.2e+07 & \ldots & 1.1e+11 & 1.9e+08  \\
+150.155450 & 2.205458 & 150.155459 & 2.205452 & 0.783\tablefootmark{G} & 1.06 & 0.26 & 2.3e+09 & 2.5e+08 & 1.9e+08 & 1.3e+07 & \ldots & 2.9e+11 & 5.4e+09  \\
+150.067080 & 2.372434 & 150.067101 & 2.372425 & 1.257\tablefootmark{G} & 0.57 & 0.57 & 5.7e+09 & 3.1e+09 & 8.5e+08 & 5.5e+07 & \ldots & 6.9e+11 & 4.3e+10  \\
 150.105500 & 2.297602 & 150.105557 & 2.297617 & 0.951                  & 0.87 & 1.24 & 3.0e+09 & 1.7e+09 & 2.5e+08 & 1.5e+07 & \ldots & 6.7e+11 & 1.4e+10  \\
-150.064130 & 2.409601 & 150.064153 & 2.409603 & 0.895\tablenotemark{G} & 0.48 & 0.91 & 3.9e+09 & 1.7e+09 & 1.7e+08 & 1.3e+07 & \ldots & 1.6e+11 & 1.1e+10  \\
-150.112060 & 2.434008 & 150.112096 & 2.433991 & 1.120\tablenotemark{G} & 1.35 & 0.91 & 1.9e+09 & 1.6e+09 & \ldots & \ldots & 1.0e+08 & 2.3e+11 & 1.4e+10  \\
+150.064130 & 2.409601 & 150.064153 & 2.409603 & 0.895\tablefootmark{G} & 0.48 & 0.91 & 3.9e+09 & 1.7e+09 & 1.7e+08 & 1.3e+07 & \ldots & 1.6e+11 & 1.1e+10  \\
+150.112060 & 2.434008 & 150.112096 & 2.433991 & 1.120\tablefootmark{G} & 1.35 & 0.91 & 1.9e+09 & 1.6e+09 & \ldots & \ldots & 1.0e+08 & 2.3e+11 & 1.4e+10  \\
 150.096090 & 2.240252 & 150.096111 & 2.240252 & 0.802                  & 1.50 & 0.72 & 3.8e+08 & 1.1e+08 & 6.6e+07 & 1.3e+07 & \ldots & 2.5e+11 & 2.0e+10  \\
 150.095390 & 2.255131 & 150.095433 & 2.255139 & 0.727                  & 0.22 & 0.21 & 3.4e+09 & 3.2e+08 & \ldots & \ldots & 1.2e+08 & 2.3e+11 & 6.4e+09  \\
-150.164710 & 2.322803 & 150.164713 & 2.322820 & 0.791\tablenotemark{G} & -1.21 & 0.15 & 1.2e+10 & 7.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 1.2e+11 & 4.4e+09  \\
+150.164710 & 2.322803 & 150.164713 & 2.322820 & 0.791\tablefootmark{G} & -1.21 & 0.15 & 1.2e+10 & 7.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 1.2e+11 & 4.4e+09  \\
 150.103720 & 2.237653 & 150.103747 & 2.237663 & 0.799                  & -0.71 & 0.19 & 6.4e+09 & 4.9e+08 & 2.3e+08 & 3.2e+07 & \ldots & 8.1e+11 & 2.2e+11  \\
-150.078210 & 2.287351 & 150.078239 & 2.287367 & 0.931\tablenotemark{G} & 0.23 & 1.84 & 5.5e+08 & 4.9e+08 & \ldots & \ldots & 4.4e+07 & 8.9e+10 & 6.2e+07  \\
-150.071750 & 2.361027 & 150.071772 & 2.361027 & 0.908\tablenotemark{G} & 0.75 & 0.77 & 5.7e+09 & 2.2e+09 & 2.8e+08 & 3.4e+07 & \ldots & 3.3e+11 & 1.8e+10  \\
-150.134540 & 2.428741 & 150.134551 & 2.428717 & 0.932\tablenotemark{G} & 1.80 & 1.21 & 3.0e+08 & 2.2e+08 & 9.2e+07 & 1.4e+07 & \ldots & 1.5e+11 & 2.3e+09  \\
+150.078210 & 2.287351 & 150.078239 & 2.287367 & 0.931\tablefootmark{G} & 0.23 & 1.84 & 5.5e+08 & 4.9e+08 & \ldots & \ldots & 4.4e+07 & 8.9e+10 & 6.2e+07  \\
+150.071750 & 2.361027 & 150.071772 & 2.361027 & 0.908\tablefootmark{G} & 0.75 & 0.77 & 5.7e+09 & 2.2e+09 & 2.8e+08 & 3.4e+07 & \ldots & 3.3e+11 & 1.8e+10  \\
+150.134540 & 2.428741 & 150.134551 & 2.428717 & 0.932\tablefootmark{G} & 1.80 & 1.21 & 3.0e+08 & 2.2e+08 & 9.2e+07 & 1.4e+07 & \ldots & 1.5e+11 & 2.3e+09  \\
 150.068420 & 2.265476 & 150.068467 & 2.265490 & 0.981                  & 0.62 & 0.47 & 3.5e+09 & 7.6e+08 & 2.2e+08 & 2.7e+07 & \ldots & 1.9e+11 & 7.9e+09  \\
-150.179140 & 2.215912 & 150.179144 & 2.215902 & 0.806\tablenotemark{G} & -0.12 & 0.25 & 3.8e+09 & 3.9e+08 & 1.3e+08 & 2.6e+07 & \ldots & 1.5e+11 & 3.9e+07  \\
-150.177860 & 2.220603 & 150.177869 & 2.220627 & 1.148\tablenotemark{G} & -0.17 & 0.73 & 1.7e+09 & 6.4e+08 & \ldots & \ldots & 8.5e+07 & 2.1e+11 & 8.3e+09  \\
-150.115720 & 2.416342 & 150.115703 & 2.416347 & 1.119\tablenotemark{G} & -0.39 & 0.67 & 1.3e+10 & 4.1e+09 & 4.0e+08 & 3.6e+07 & \ldots & 4.6e+11 & 6.5e+09  \\
-150.089820 & 2.234895 & 150.089864 & 2.234888 & 0.838\tablenotemark{G} & 0.10 & 2.46 & 1.3e+09 & 1.4e+09 & \ldots & \ldots & 5.4e+07 & 1.7e+11 & 1.8e+10  \\
-150.075070 & 2.450793 & 150.075074 & 2.450787 & 0.942\tablenotemark{G} & 1.57 & 2.56 & 6.9e+08 & 1.0e+09 & \ldots & \ldots & 9.1e+07 & 2.3e+11 & 1.3e+09  \\
+150.179140 & 2.215912 & 150.179144 & 2.215902 & 0.806\tablefootmark{G} & -0.12 & 0.25 & 3.8e+09 & 3.9e+08 & 1.3e+08 & 2.6e+07 & \ldots & 1.5e+11 & 3.9e+07  \\
+150.177860 & 2.220603 & 150.177869 & 2.220627 & 1.148\tablefootmark{G} & -0.17 & 0.73 & 1.7e+09 & 6.4e+08 & \ldots & \ldots & 8.5e+07 & 2.1e+11 & 8.3e+09  \\
+150.115720 & 2.416342 & 150.115703 & 2.416347 & 1.119\tablefootmark{G} & -0.39 & 0.67 & 1.3e+10 & 4.1e+09 & 4.0e+08 & 3.6e+07 & \ldots & 4.6e+11 & 6.5e+09  \\
+150.089820 & 2.234895 & 150.089864 & 2.234888 & 0.838\tablefootmark{G} & 0.10 & 2.46 & 1.3e+09 & 1.4e+09 & \ldots & \ldots & 5.4e+07 & 1.7e+11 & 1.8e+10  \\
+150.075070 & 2.450793 & 150.075074 & 2.450787 & 0.942\tablefootmark{G} & 1.57 & 2.56 & 6.9e+08 & 1.0e+09 & \ldots & \ldots & 9.1e+07 & 2.3e+11 & 1.3e+09  \\
 150.188810 & 2.321018 & 150.188838 & 2.320997 & 1.000                  & 0.34 & 1.35 & 3.6e+09 & 2.0e+09 & 2.9e+08 & 2.6e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
-150.131530 & 2.294352 & 150.131561 & 2.294330 & 1.026\tablenotemark{G} & -1.08 & 0.23 & 1.4e+10 & 1.2e+09 & 3.1e+08 & 1.4e+07 & \ldots & 1.5e+11 & 4.4e+09  \\
+150.131530 & 2.294352 & 150.131561 & 2.294330 & 1.026\tablefootmark{G} & -1.08 & 0.23 & 1.4e+10 & 1.2e+09 & 3.1e+08 & 1.4e+07 & \ldots & 1.5e+11 & 4.4e+09  \\
 150.152270 & 2.219301 & 150.152287 & 2.219311 & 0.927                  & -0.01 & 0.32 & 5.6e+09 & 8.0e+08 & 4.8e+08 & 2.7e+07 & \ldots & 3.8e+11 & 8.2e+09  \\
-150.171950 & 2.278365 & 150.171969 & 2.278364 & 0.752\tablenotemark{G} & -0.13 & 0.35 & 1.7e+09 & 2.5e+08 & 7.6e+07 & 8.6e+06 & \ldots & 7.2e+10 & 2.6e+09  \\
+150.171950 & 2.278365 & 150.171969 & 2.278364 & 0.752\tablefootmark{G} & -0.13 & 0.35 & 1.7e+09 & 2.5e+08 & 7.6e+07 & 8.6e+06 & \ldots & 7.2e+10 & 2.6e+09  \\
 150.107370 & 2.329205 & 150.107409 & 2.329204 & 0.924                  & 0.65 & 1.38 & 5.2e+09 & 3.4e+09 & \ldots & \ldots & 1.3e+08 & 2.4e+11 & 6.1e+09  \\
-150.064780 & 2.336534 & 150.064830 & 2.336514 & 0.728\tablenotemark{G} & -0.22 & 0.27 & 2.5e+09 & 3.0e+08 & \ldots & \ldots & 6.9e+07 & 4.4e+10 & 1.5e+09  \\
-150.062250 & 2.366550 & 150.062272 & 2.366530 & 0.802\tablenotemark{G} & -0.39 & 0.25 & 3.7e+09 & 3.9e+08 & 2.1e+08 & 1.3e+07 & \ldots & 1.5e+11 & 3.7e+09  \\
-150.064500 & 2.264089 & 150.064595 & 2.264048 & 1.440\tablenotemark{G} & -0.39 & 0.34 & 9.5e+09 & 4.0e+09 & \ldots & \ldots & 3.0e+08 & 7.4e+11 & 5.5e+10  \\
-150.102160 & 2.438384 & 150.102177 & 2.438350 & 1.132\tablenotemark{G} & 1.27 & 0.87 & 2.8e+09 & 2.3e+09 & 7.2e+08 & 1.2e+08 & \ldots & 3.6e+11 & 1.9e+10  \\
+150.064780 & 2.336534 & 150.064830 & 2.336514 & 0.728\tablefootmark{G} & -0.22 & 0.27 & 2.5e+09 & 3.0e+08 & \ldots & \ldots & 6.9e+07 & 4.4e+10 & 1.5e+09  \\
+150.062250 & 2.366550 & 150.062272 & 2.366530 & 0.802\tablefootmark{G} & -0.39 & 0.25 & 3.7e+09 & 3.9e+08 & 2.1e+08 & 1.3e+07 & \ldots & 1.5e+11 & 3.7e+09  \\
+150.064500 & 2.264089 & 150.064595 & 2.264048 & 1.440\tablefootmark{G} & -0.39 & 0.34 & 9.5e+09 & 4.0e+09 & \ldots & \ldots & 3.0e+08 & 7.4e+11 & 5.5e+10  \\
+150.102160 & 2.438384 & 150.102177 & 2.438350 & 1.132\tablefootmark{G} & 1.27 & 0.87 & 2.8e+09 & 2.3e+09 & 7.2e+08 & 1.2e+08 & \ldots & 3.6e+11 & 1.9e+10  \\
 150.174710 & 2.360783 & 150.174714 & 2.360774 & 0.900                  & -0.34 & 0.86 & 1.1e+10 & 4.4e+09 & 2.5e+08 & 1.4e+07 & \ldots & 2.4e+11 & 5.8e+08  \\
-150.117960 & 2.374386 & 150.117998 & 2.374355 & 1.223\tablenotemark{G} & 0.41 & 0.69 & 3.8e+09 & 1.8e+09 & 4.1e+08 & 2.8e+07 & \ldots & 4.0e+11 & 2.9e+08  \\
-150.161460 & 2.320804 & 150.161505 & 2.320777 & 1.336\tablenotemark{G} & 1.32 & 0.63 & 6.9e+08 & 4.9e+08 & 1.8e+08 & 2.2e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
-150.099570 & 2.379767 & 150.099593 & 2.379752 & 0.902\tablenotemark{G} & 0.81 & 0.45 & 2.0e+09 & 4.6e+08 & 1.4e+08 & 1.3e+07 & \ldots & 1.2e+11 & 6.9e+09  \\
+150.117960 & 2.374386 & 150.117998 & 2.374355 & 1.223\tablefootmark{G} & 0.41 & 0.69 & 3.8e+09 & 1.8e+09 & 4.1e+08 & 2.8e+07 & \ldots & 4.0e+11 & 2.9e+08  \\
+150.161460 & 2.320804 & 150.161505 & 2.320777 & 1.336\tablefootmark{G} & 1.32 & 0.63 & 6.9e+08 & 4.9e+08 & 1.8e+08 & 2.2e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
+150.099570 & 2.379767 & 150.099593 & 2.379752 & 0.902\tablefootmark{G} & 0.81 & 0.45 & 2.0e+09 & 4.6e+08 & 1.4e+08 & 1.3e+07 & \ldots & 1.2e+11 & 6.9e+09  \\
 150.142490 & 2.208299 & 150.142522 & 2.208290 & 0.847                  & -0.85 & 0.53 & 1.1e+10 & 2.4e+09 & 1.3e+08 & 1.6e+07 & \ldots & 8.6e+10 & 5.6e+09  \\
-150.070260 & 2.422965 & 150.070271 & 2.422970 & 0.754\tablenotemark{G} & -0.93 & 0.15 & 9.7e+09 & 6.4e+08 & 1.8e+08 & 1.1e+07 & \ldots & 1.1e+11 & 1.0e+10  \\
+150.070260 & 2.422965 & 150.070271 & 2.422970 & 0.754\tablefootmark{G} & -0.93 & 0.15 & 9.7e+09 & 6.4e+08 & 1.8e+08 & 1.1e+07 & \ldots & 1.1e+11 & 1.0e+10  \\
 150.123650 & 2.358258 & 150.123691 & 2.358244 & 0.728                  & -1.00 & 0.08 & 4.1e+10 & 1.5e+09 & 1.2e+09 & 7.0e+07 & \ldots & 3.7e+11 & 2.4e+10  \\
-150.152710 & 2.470547 & 150.152748 & 2.470508 & 0.843\tablenotemark{G} & -0.67 & 1.90 & 8.4e+09 & 6.7e+09 & \ldots & \ldots & 1.4e+08 & 1.9e+11 & 7.5e+09  \\
-150.152200 & 2.411514 & 150.152224 & 2.411407 & 0.897\tablenotemark{G} & 1.96 & 0.82 & 2.0e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 2.6e+11 & 1.9e+10  \\
+150.152710 & 2.470547 & 150.152748 & 2.470508 & 0.843\tablefootmark{G} & -0.67 & 1.90 & 8.4e+09 & 6.7e+09 & \ldots & \ldots & 1.4e+08 & 1.9e+11 & 7.5e+09  \\
+150.152200 & 2.411514 & 150.152224 & 2.411407 & 0.897\tablefootmark{G} & 1.96 & 0.82 & 2.0e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 2.6e+11 & 1.9e+10  \\
 150.073580 & 2.346851 & 150.073650 & 2.346819 & 1.353                  & -0.34 & 0.32 & 3.2e+10 & 8.2e+09 & 9.0e+08 & 2.5e+07 & \ldots & 1.4e+12 & 1.4e+11  \\
-150.080390 & 2.238965 & 150.080432 & 2.238979 & 0.986\tablenotemark{G} & 1.35 & 1.40 & 2.8e+08 & 2.0e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 1.6e+07  \\
-150.081930 & 2.237998 & 150.081964 & 2.237983 & 0.984\tablenotemark{G} & -1.50 & 0.62 & 8.5e+09 & 2.0e+09 & 8.9e+07 & 1.3e+07 & \ldots & 1.3e+11 & 1.1e+10  \\
+150.080390 & 2.238965 & 150.080432 & 2.238979 & 0.986\tablefootmark{G} & 1.35 & 1.40 & 2.8e+08 & 2.0e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 1.6e+07  \\
+150.081930 & 2.237998 & 150.081964 & 2.237983 & 0.984\tablefootmark{G} & -1.50 & 0.62 & 8.5e+09 & 2.0e+09 & 8.9e+07 & 1.3e+07 & \ldots & 1.3e+11 & 1.1e+10  \\
 150.148540 & 2.324634 & 150.148572 & 2.324626 & 0.837                  & 0.85 & 0.41 & 1.6e+09 & 2.9e+08 & 9.0e+07 & 1.2e+07 & \ldots & 1.6e+11 & 5.5e+08  \\
@@
 150.116920 & 2.386939 & 150.116946 & 2.386924 & 0.940                  & -0.11 & 1.42 & 4.4e+09 & 2.7e+09 & 3.4e+08 & 1.6e+07 & \ldots & 2.6e+11 & 6.7e+09  \\
-150.071460 & 2.341721 & 150.071495 & 2.341707 & 0.941\tablenotemark{G} & 1.99 & 1.79 & 3.2e+08 & 3.3e+08 & 9.0e+07 & 1.5e+07 & \ldots & 2.6e+11 & 1.7e+10  \\
+150.071460 & 2.341721 & 150.071495 & 2.341707 & 0.941\tablefootmark{G} & 1.99 & 1.79 & 3.2e+08 & 3.3e+08 & 9.0e+07 & 1.5e+07 & \ldots & 2.6e+11 & 1.7e+10  \\
 150.087520 & 2.404057 & 150.087559 & 2.404051 & 0.748                  & 0.36 & 0.37 & 1.2e+09 & 2.0e+08 & 2.1e+08 & 1.5e+07 & \ldots & 1.6e+11 & 3.6e+09  \\
 150.102000 & 2.425978 & 150.102010 & 2.425966 & 0.727                  & 0.48 & 0.14 & 6.4e+09 & 4.1e+08 & 4.8e+08 & 4.3e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
-150.097510 & 2.401258 & 150.097538 & 2.401238 & 1.242\tablenotemark{G} & 0.92 & 1.23 & 6.2e+08 & 5.7e+08 & 2.1e+08 & 2.6e+07 & \ldots & 7.3e+11 & 3.2e+10  \\
-150.132210 & 2.437227 & 150.132215 & 2.437207 & 0.926\tablenotemark{G} & 0.86 & 1.70 & 2.2e+09 & 1.9e+09 & \ldots & \ldots & 1.4e+08 & 2.6e+11 & 1.3e+10  \\
+150.097510 & 2.401258 & 150.097538 & 2.401238 & 1.242\tablefootmark{G} & 0.92 & 1.23 & 6.2e+08 & 5.7e+08 & 2.1e+08 & 2.6e+07 & \ldots & 7.3e+11 & 3.2e+10  \\
+150.132210 & 2.437227 & 150.132215 & 2.437207 & 0.926\tablefootmark{G} & 0.86 & 1.70 & 2.2e+09 & 1.9e+09 & \ldots & \ldots & 1.4e+08 & 2.6e+11 & 1.3e+10  \\
 150.105220 & 2.435001 & 150.105247 & 2.434981 & 0.727                  & 2.22 & 0.30 & 1.0e+09 & 1.4e+08 & \ldots & \ldots & 6.0e+07 & 1.0e+11 & 1.9e+10  \\
-150.116700 & 2.265270 & 150.116728 & 2.265269 & 0.756\tablenotemark{G} & 1.00 & 0.40 & 9.7e+08 & 1.7e+08 & \ldots & \ldots & 7.7e+07 & 8.7e+10 & 2.8e+09  \\
-150.152130 & 2.444217 & 150.152159 & 2.444192 & 0.981\tablenotemark{G} & -0.63 & 1.05 & 1.3e+10 & 5.4e+09 & 2.6e+08 & 2.9e+07 & \ldots & 2.2e+11 & 1.5e+10  \\
-150.107380 & 2.206350 & 150.107397 & 2.206352 & 1.166\tablenotemark{G} & 3.24 & 1.39 & 2.9e+08 & 6.4e+08 & 2.8e+08 & 2.9e+07 & \ldots & 5.7e+11 & 3.4e+10  \\
-150.173220 & 2.363148 & 150.173229 & 2.363129 & 0.734\tablenotemark{G} & 1.28 & 0.55 & 5.3e+08 & 1.3e+08 & 7.2e+07 & 7.8e+06 & \ldots & 1.2e+11 & 3.3e+10  \\
-150.114380 & 2.221958 & 150.114410 & 2.221948 & 1.230\tablenotemark{G} & -0.35 & 0.74 & 3.2e+09 & 1.2e+09 & \ldots & \ldots & 1.2e+08 & 3.6e+11 & 2.8e+10  \\
-150.118560 & 2.223099 & 150.118579 & 2.223095 & 0.845\tablenotemark{G} & 1.33 & 1.79 & 6.4e+08 & 5.3e+08 & 1.1e+08 & 1.3e+07 & \ldots & 4.3e+11 & 5.8e+10  \\
-150.136430 & 2.320533 & 150.136464 & 2.320526 & 1.005\tablenotemark{G} & -1.01 & 1.33 & 2.3e+09 & 1.2e+09 & 1.6e+08 & 2.7e+07 & \ldots & 1.7e+11 & 3.7e+09  \\
-150.124970 & 2.310285 & 150.125006 & 2.310288 & 0.907\tablenotemark{G} & -0.95 & 0.67 & 1.2e+10 & 3.3e+09 & \ldots & \ldots & 4.9e+08 & 8.1e+10 & 6.1e+07  \\
+150.116700 & 2.265270 & 150.116728 & 2.265269 & 0.756\tablefootmark{G} & 1.00 & 0.40 & 9.7e+08 & 1.7e+08 & \ldots & \ldots & 7.7e+07 & 8.7e+10 & 2.8e+09  \\
+150.152130 & 2.444217 & 150.152159 & 2.444192 & 0.981\tablefootmark{G} & -0.63 & 1.05 & 1.3e+10 & 5.4e+09 & 2.6e+08 & 2.9e+07 & \ldots & 2.2e+11 & 1.5e+10  \\
+150.107380 & 2.206350 & 150.107397 & 2.206352 & 1.166\tablefootmark{G} & 3.24 & 1.39 & 2.9e+08 & 6.4e+08 & 2.8e+08 & 2.9e+07 & \ldots & 5.7e+11 & 3.4e+10  \\
+150.173220 & 2.363148 & 150.173229 & 2.363129 & 0.734\tablefootmark{G} & 1.28 & 0.55 & 5.3e+08 & 1.3e+08 & 7.2e+07 & 7.8e+06 & \ldots & 1.2e+11 & 3.3e+10  \\
+150.114380 & 2.221958 & 150.114410 & 2.221948 & 1.230\tablefootmark{G} & -0.35 & 0.74 & 3.2e+09 & 1.2e+09 & \ldots & \ldots & 1.2e+08 & 3.6e+11 & 2.8e+10  \\
+150.118560 & 2.223099 & 150.118579 & 2.223095 & 0.845\tablefootmark{G} & 1.33 & 1.79 & 6.4e+08 & 5.3e+08 & 1.1e+08 & 1.3e+07 & \ldots & 4.3e+11 & 5.8e+10  \\
+150.136430 & 2.320533 & 150.136464 & 2.320526 & 1.005\tablefootmark{G} & -1.01 & 1.33 & 2.3e+09 & 1.2e+09 & 1.6e+08 & 2.7e+07 & \ldots & 1.7e+11 & 3.7e+09  \\
+150.124970 & 2.310285 & 150.125006 & 2.310288 & 0.907\tablefootmark{G} & -0.95 & 0.67 & 1.2e+10 & 3.3e+09 & \ldots & \ldots & 4.9e+08 & 8.1e+10 & 6.1e+07  \\
 150.140310 & 2.365965 & 150.140338 & 2.365973 & 0.728                  & -0.32 & 0.22 & 3.8e+09 & 3.7e+08 & \ldots & \ldots & 1.2e+08 & 1.2e+11 & 1.1e+09  \\
-150.189650 & 2.316027 & 150.189674 & 2.316022 & 0.759\tablenotemark{G} & -0.22 & 0.31 & 2.2e+09 & 3.0e+08 & 9.6e+07 & 1.8e+07 & \ldots & 9.2e+10 & 5.1e+08  \\
-150.101190 & 2.460061 & 150.101191 & 2.460031 & 1.246\tablenotemark{G} & -0.03 & 0.86 & 2.2e+09 & 1.1e+09 & 2.4e+08 & 1.4e+07 & \ldots & 3.3e+11 & 1.5e+09  \\
-150.151420 & 2.294050 & 150.151440 & 2.294052 & 0.972\tablenotemark{G} & -0.27 & 0.83 & 3.8e+09 & 1.3e+09 & 1.6e+08 & 1.9e+07 & \ldots & 1.5e+11 & 7.0e+09  \\
+150.189650 & 2.316027 & 150.189674 & 2.316022 & 0.759\tablefootmark{G} & -0.22 & 0.31 & 2.2e+09 & 3.0e+08 & 9.6e+07 & 1.8e+07 & \ldots & 9.2e+10 & 5.1e+08  \\
+150.101190 & 2.460061 & 150.101191 & 2.460031 & 1.246\tablefootmark{G} & -0.03 & 0.86 & 2.2e+09 & 1.1e+09 & 2.4e+08 & 1.4e+07 & \ldots & 3.3e+11 & 1.5e+09  \\
+150.151420 & 2.294050 & 150.151440 & 2.294052 & 0.972\tablefootmark{G} & -0.27 & 0.83 & 3.8e+09 & 1.3e+09 & 1.6e+08 & 1.9e+07 & \ldots & 1.5e+11 & 7.0e+09  \\
 150.145470 & 2.293398 & 150.145507 & 2.293397 & 0.881                  & 0.36 & 1.09 & 2.6e+09 & 1.4e+09 & \ldots & \ldots & 6.6e+07 & 1.1e+11 & 4.9e+08  \\
-150.074170 & 2.384622 & 150.074210 & 2.384612 & 1.266\tablenotemark{G} & -1.53 & 4.14 & 4.0e+08 & 7.7e+08 & 1.6e+08 & 1.2e+07 & \ldots & 3.9e+11 & 1.6e+10  \\
+150.074170 & 2.384622 & 150.074210 & 2.384612 & 1.266\tablefootmark{G} & -1.53 & 4.14 & 4.0e+08 & 7.7e+08 & 1.6e+08 & 1.2e+07 & \ldots & 3.9e+11 & 1.6e+10  \\
 150.079370 & 2.408439 & 150.079421 & 2.408458 & 0.891                  & -1.25 & 0.30 & 1.0e+10 & 1.3e+09 & 9.9e+07 & 1.8e+07 & \ldots & 1.2e+11 & 6.3e+09  \\
 150.173920 & 2.317308 & 150.173946 & 2.317324 & 0.736                  & -0.47 & 0.19 & 5.2e+09 & 4.5e+08 & 1.4e+08 & 1.5e+07 & \ldots & 1.2e+11 & 1.2e+10  \\
-150.058980 & 2.301078 & 150.058982 & 2.301089 & 0.734\tablenotemark{G} & 0.59 & 0.40 & 1.1e+09 & 1.9e+08 & 9.4e+07 & 1.6e+07 & \ldots & 9.5e+10 & 1.9e+10  \\
-150.160250 & 2.300164 & 150.160269 & 2.300159 & 1.340\tablenotemark{G} & -0.54 & 0.45 & 2.8e+09 & 9.7e+08 & 1.2e+08 & 2.4e+07 & \ldots & 3.2e+11 & 1.0e+10  \\
+150.058980 & 2.301078 & 150.058982 & 2.301089 & 0.734\tablefootmark{G} & 0.59 & 0.40 & 1.1e+09 & 1.9e+08 & 9.4e+07 & 1.6e+07 & \ldots & 9.5e+10 & 1.9e+10  \\
+150.160250 & 2.300164 & 150.160269 & 2.300159 & 1.340\tablefootmark{G} & -0.54 & 0.45 & 2.8e+09 & 9.7e+08 & 1.2e+08 & 2.4e+07 & \ldots & 3.2e+11 & 1.0e+10  \\
 150.121460 & 2.267281 & 150.121483 & 2.267288 & 0.827                  & -1.50 & 0.58 & 2.8e+10 & 6.8e+09 & 3.5e+08 & 2.7e+07 & \ldots & 7.3e+10 & 3.0e+09  \\
-150.137630 & 2.340502 & 150.137613 & 2.340390 & 0.835\tablenotemark{G} & 2.69 & 2.03 & 3.5e+08 & 3.9e+08 & \ldots & \ldots & 4.9e+07 & 8.0e+10 & 3.1e+07  \\
-150.167260 & 2.355718 & 150.167275 & 2.355703 & 1.285\tablenotemark{G} & -0.72 & 0.66 & 4.0e+09 & 1.8e+09 & 2.3e+08 & 3.9e+07 & \ldots & 2.5e+11 & 1.6e+10  \\
-150.185690 & 2.222366 & 150.185690 & 2.222358 & 1.218\tablenotemark{G} & -0.12 & 0.37 & 8.4e+09 & 1.8e+09 & 4.7e+08 & 1.6e+07 & \ldots & 2.1e+11 & 5.7e+08  \\
-150.155170 & 2.405678 & 150.155234 & 2.405743 & 0.899\tablenotemark{G} & 2.31 & 2.33 & 1.0e+08 & 1.7e+08 & \ldots & \ldots & 5.8e+07 & 1.3e+11 & 3.9e+09  \\
+150.137630 & 2.340502 & 150.137613 & 2.340390 & 0.835\tablefootmark{G} & 2.69 & 2.03 & 3.5e+08 & 3.9e+08 & \ldots & \ldots & 4.9e+07 & 8.0e+10 & 3.1e+07  \\
+150.167260 & 2.355718 & 150.167275 & 2.355703 & 1.285\tablefootmark{G} & -0.72 & 0.66 & 4.0e+09 & 1.8e+09 & 2.3e+08 & 3.9e+07 & \ldots & 2.5e+11 & 1.6e+10  \\
+150.185690 & 2.222366 & 150.185690 & 2.222358 & 1.218\tablefootmark{G} & -0.12 & 0.37 & 8.4e+09 & 1.8e+09 & 4.7e+08 & 1.6e+07 & \ldots & 2.1e+11 & 5.7e+08  \\
+150.155170 & 2.405678 & 150.155234 & 2.405743 & 0.899\tablefootmark{G} & 2.31 & 2.33 & 1.0e+08 & 1.7e+08 & \ldots & \ldots & 5.8e+07 & 1.3e+11 & 3.9e+09  \\
 150.055920 & 2.233462 & 150.055985 & 2.233450 & 0.938                  & 0.14 & 0.28 & 1.2e+10 & 1.5e+09 & 3.8e+08 & 3.5e+07 & \ldots & 1.2e+12 & 9.1e+10  \\
 150.118520 & 2.415591 & 150.118543 & 2.415571 & 0.837                  & -1.77 & 0.18 & 6.5e+10 & 5.0e+09 & 5.6e+08 & 2.7e+07 & \ldots & 1.4e+11 & 2.8e+09  \\
-150.144420 & 2.415904 & 150.144400 & 2.415861 & 0.960\tablenotemark{G} & 0.01 & 1.05 & 3.3e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.9e+11 & 8.4e+09  \\
-150.126370 & 2.432899 & 150.126391 & 2.432867 & 1.277\tablenotemark{G} & 1.38 & 0.50 & 2.6e+09 & 1.6e+09 & 8.8e+08 & 3.9e+07 & \ldots & 1.0e+12 & 3.4e+10  \\
-150.081880 & 2.281767 & 150.081940 & 2.281754 & 0.736\tablenotemark{G} & -0.97 & 0.44 & 1.3e+09 & 2.5e+08 & 9.3e+07 & 1.7e+07 & \ldots & 9.8e+10 & 5.8e+07  \\
+150.144420 & 2.415904 & 150.144400 & 2.415861 & 0.960\tablefootmark{G} & 0.01 & 1.05 & 3.3e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.9e+11 & 8.4e+09  \\
+150.126370 & 2.432899 & 150.126391 & 2.432867 & 1.277\tablefootmark{G} & 1.38 & 0.50 & 2.6e+09 & 1.6e+09 & 8.8e+08 & 3.9e+07 & \ldots & 1.0e+12 & 3.4e+10  \\
+150.081880 & 2.281767 & 150.081940 & 2.281754 & 0.736\tablefootmark{G} & -0.97 & 0.44 & 1.3e+09 & 2.5e+08 & 9.3e+07 & 1.7e+07 & \ldots & 9.8e+10 & 5.8e+07  \\
 150.100450 & 2.308010 & 150.100488 & 2.308021 & 0.950                  & -1.00 & 1.27 & 1.7e+10 & 8.5e+09 & 2.0e+08 & 3.5e+07 & \ldots & 1.6e+11 & 1.7e+09  \\
 150.136100 & 2.370533 & 150.136112 & 2.370532 & 0.927                  & 2.39 & 1.46 & 7.4e+08 & 6.9e+08 & 1.9e+08 & 2.0e+07 & \ldots & 7.4e+11 & 7.0e+10  \\
-150.169140 & 2.233916 & 150.169152 & 2.233893 & 1.233\tablenotemark{G} & -0.80 & 0.43 & 1.5e+10 & 3.1e+09 & 3.4e+08 & 3.2e+07 & \ldots & 2.3e+11 & 3.7e+08  \\
-150.108520 & 2.448166 & 150.108523 & 2.448100 & 1.413\tablenotemark{G} & 1.93 & 0.90 & 2.8e+08 & 7.7e+08 & 2.0e+08 & 3.1e+07 & \ldots & 4.6e+11 & 1.1e+10  \\
+150.169140 & 2.233916 & 150.169152 & 2.233893 & 1.233\tablefootmark{G} & -0.80 & 0.43 & 1.5e+10 & 3.1e+09 & 3.4e+08 & 3.2e+07 & \ldots & 2.3e+11 & 3.7e+08  \\
+150.108520 & 2.448166 & 150.108523 & 2.448100 & 1.413\tablefootmark{G} & 1.93 & 0.90 & 2.8e+08 & 7.7e+08 & 2.0e+08 & 3.1e+07 & \ldots & 4.6e+11 & 1.1e+10  \\
 150.112240 & 2.387377 & 150.112284 & 2.387391 & 0.757                  & 0.81 & 0.25 & 2.2e+09 & 2.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.3e+11 & 1.3e+10  \\
-150.103890 & 2.334655 & 150.103898 & 2.334752 & 0.940\tablenotemark{G} & -0.23 & 1.65 & 1.5e+09 & 1.1e+09 & 6.6e+07 & 8.3e+06 & \ldots & 1.8e+11 & 6.1e+09  \\
+150.103890 & 2.334655 & 150.103898 & 2.334752 & 0.940\tablefootmark{G} & -0.23 & 1.65 & 1.5e+09 & 1.1e+09 & 6.6e+07 & 8.3e+06 & \ldots & 1.8e+11 & 6.1e+09  \\
 150.190930 & 2.235499 & 150.190865 & 2.235393 & 0.864                  & -0.74 & 0.82 & 5.2e+09 & 1.9e+09 & 1.2e+08 & 1.3e+07 & \ldots & 9.5e+10 & 3.3e+08  \\
@@
 150.170690 & 2.219165 & 150.170738 & 2.219240 & 0.958                  & 0.13 & 0.85 & 5.8e+09 & 2.1e+09 & \ldots & \ldots & 3.0e+08 & 2.0e+11 & 4.7e+09  \\
-150.192700 & 2.333416 & 150.192737 & 2.333482 & 1.081\tablenotemark{G} & 0.21 & 0.66 & 1.8e+09 & 7.8e+08 & \ldots & \ldots & 9.2e+07 & 1.3e+11 & 2.2e+08  \\
-150.159290 & 2.235417 & 150.159296 & 2.235413 & 0.932\tablenotemark{G} & -0.31 & 1.31 & 3.6e+09 & 2.0e+09 & \ldots & \ldots & 6.1e+07 & 1.4e+11 & 1.6e+10  \\
-150.130870 & 2.215121 & 150.130875 & 2.215134 & 0.859\tablenotemark{G} & 1.60 & 2.49 & 3.9e+08 & 5.8e+08 & \ldots & \ldots & 5.2e+07 & 2.1e+11 & 5.4e+09  \\
+150.192700 & 2.333416 & 150.192737 & 2.333482 & 1.081\tablefootmark{G} & 0.21 & 0.66 & 1.8e+09 & 7.8e+08 & \ldots & \ldots & 9.2e+07 & 1.3e+11 & 2.2e+08  \\
+150.159290 & 2.235417 & 150.159296 & 2.235413 & 0.932\tablefootmark{G} & -0.31 & 1.31 & 3.6e+09 & 2.0e+09 & \ldots & \ldots & 6.1e+07 & 1.4e+11 & 1.6e+10  \\
+150.130870 & 2.215121 & 150.130875 & 2.215134 & 0.859\tablefootmark{G} & 1.60 & 2.49 & 3.9e+08 & 5.8e+08 & \ldots & \ldots & 5.2e+07 & 2.1e+11 & 5.4e+09  \\
 150.110190 & 2.208473 & 150.110230 & 2.208474 & 1.249                  & -0.51 & 0.44 & 1.6e+10 & 3.6e+09 & 3.2e+08 & 4.1e+07 & \ldots & 2.5e+11 & 1.8e+08  \\
-150.109680 & 2.295734 & 150.109712 & 2.295693 & 1.325\tablenotemark{G} & -0.87 & 0.28 & 7.8e+09 & 1.7e+09 & 2.1e+08 & 3.0e+07 & \ldots & 3.7e+11 & 1.0e+10  \\
+150.109680 & 2.295734 & 150.109712 & 2.295693 & 1.325\tablefootmark{G} & -0.87 & 0.28 & 7.8e+09 & 1.7e+09 & 2.1e+08 & 3.0e+07 & \ldots & 3.7e+11 & 1.0e+10  \\
 150.172490 & 2.233643 & 150.172484 & 2.233629 & 0.925                  & -0.24 & 0.93 & 4.1e+09 & 1.7e+09 & 1.5e+08 & 1.7e+07 & \ldots & 1.5e+11 & 5.8e+09  \\
 150.094580 & 2.336367 & 150.094624 & 2.336350 & 0.910                  & 2.72 & 1.52 & 4.2e+08 & 4.3e+08 & 2.2e+08 & 1.5e+07 & \ldots & 5.4e+11 & 5.0e+10  \\
-150.083340 & 2.278458 & 150.083386 & 2.278446 & 0.837\tablenotemark{G} & 0.79 & 0.93 & 4.1e+08 & 1.7e+08 & 1.2e+08 & 1.0e+07 & \ldots & 2.6e+11 & 7.5e+09  \\
-150.114740 & 2.262723 & 150.114781 & 2.262725 & 0.750\tablenotemark{G} & -0.47 & 0.23 & 3.6e+09 & 3.7e+08 & 1.4e+08 & 1.4e+07 & \ldots & 7.8e+10 & 4.4e+09  \\
-150.172610 & 2.353894 & 150.172626 & 2.353883 & 0.757\tablenotemark{G} & 1.75 & 0.43 & 7.3e+08 & 1.4e+08 & 2.2e+08 & 3.4e+07 & \ldots & 4.6e+11 & 2.6e+10  \\
-150.067170 & 2.377246 & 150.067215 & 2.377236 & 0.804\tablenotemark{G} & -0.69 & 0.37 & 2.2e+09 & 3.4e+08 & 1.9e+08 & 9.6e+06 & \ldots & 1.6e+11 & 3.8e+09  \\
+150.083340 & 2.278458 & 150.083386 & 2.278446 & 0.837\tablefootmark{G} & 0.79 & 0.93 & 4.1e+08 & 1.7e+08 & 1.2e+08 & 1.0e+07 & \ldots & 2.6e+11 & 7.5e+09  \\
+150.114740 & 2.262723 & 150.114781 & 2.262725 & 0.750\tablefootmark{G} & -0.47 & 0.23 & 3.6e+09 & 3.7e+08 & 1.4e+08 & 1.4e+07 & \ldots & 7.8e+10 & 4.4e+09  \\
+150.172610 & 2.353894 & 150.172626 & 2.353883 & 0.757\tablefootmark{G} & 1.75 & 0.43 & 7.3e+08 & 1.4e+08 & 2.2e+08 & 3.4e+07 & \ldots & 4.6e+11 & 2.6e+10  \\
+150.067170 & 2.377246 & 150.067215 & 2.377236 & 0.804\tablefootmark{G} & -0.69 & 0.37 & 2.2e+09 & 3.4e+08 & 1.9e+08 & 9.6e+06 & \ldots & 1.6e+11 & 3.8e+09  \\
 150.118240 & 2.292143 & 150.118290 & 2.292122 & 1.103                  & 0.07 & 0.47 & 1.1e+10 & 3.0e+09 & 2.8e+08 & 2.6e+07 & \ldots & 3.5e+11 & 1.5e+10  \\
 150.103510 & 2.346108 & 150.103512 & 2.346125 & 1.031                  & -0.46 & 1.78 & 1.6e+10 & 1.1e+10 & 9.9e+08 & 8.5e+07 & \ldots & 6.8e+11 & 4.3e+09  \\
-150.117520 & 2.285153 & 150.117534 & 2.285159 & 0.921\tablenotemark{G} & -0.88 & 0.95 & 2.7e+09 & 1.1e+09 & 9.7e+07 & 1.5e+07 & \ldots & 9.7e+10 & 1.4e+10  \\
+150.117520 & 2.285153 & 150.117534 & 2.285159 & 0.921\tablefootmark{G} & -0.88 & 0.95 & 2.7e+09 & 1.1e+09 & 9.7e+07 & 1.5e+07 & \ldots & 9.7e+10 & 1.4e+10  \\
 150.165510 & 2.246267 & 150.165496 & 2.246271 & 0.870                  & -1.30 & 0.53 & 1.1e+10 & 2.4e+09 & 1.7e+08 & 2.4e+07 & \ldots & 1.0e+11 & 1.0e+10  \\
-150.164850 & 2.354424 & 150.164879 & 2.354407 & 1.263\tablenotemark{G} & -0.06 & 0.39 & 5.5e+09 & 1.8e+09 & 4.9e+08 & 2.6e+07 & \ldots & 3.9e+11 & 5.7e+10  \\
-150.082600 & 2.366448 & 150.082676 & 2.366546 & 1.208\tablenotemark{G} & -0.54 & 0.81 & 4.1e+09 & 1.7e+09 & \ldots & \ldots & 7.2e+07 & 1.6e+11 & 1.4e+08  \\
-150.085750 & 2.297658 & 150.085794 & 2.297659 & 1.254\tablenotemark{G} & 0.01 & 0.19 & 2.4e+10 & 3.9e+09 & 2.1e+09 & 8.3e+07 & \ldots & 2.0e+12 & 9.4e+10  \\
-150.114050 & 2.353890 & 150.114076 & 2.353853 & 1.100\tablenotemark{G} & 5.49 & 1.05 & 7.7e+08 & 2.7e+09 & 1.9e+08 & 1.6e+07 & \ldots & 3.3e+11 & 3.3e+09  \\
-150.063620 & 2.254643 & 150.063636 & 2.254647 & 1.087\tablenotemark{G} & -0.48 & 0.41 & 7.0e+09 & 1.6e+09 & 2.1e+08 & 1.3e+07 & \ldots & 1.0e+11 & 8.4e+07  \\
+150.164850 & 2.354424 & 150.164879 & 2.354407 & 1.263\tablefootmark{G} & -0.06 & 0.39 & 5.5e+09 & 1.8e+09 & 4.9e+08 & 2.6e+07 & \ldots & 3.9e+11 & 5.7e+10  \\
+150.082600 & 2.366448 & 150.082676 & 2.366546 & 1.208\tablefootmark{G} & -0.54 & 0.81 & 4.1e+09 & 1.7e+09 & \ldots & \ldots & 7.2e+07 & 1.6e+11 & 1.4e+08  \\
+150.085750 & 2.297658 & 150.085794 & 2.297659 & 1.254\tablefootmark{G} & 0.01 & 0.19 & 2.4e+10 & 3.9e+09 & 2.1e+09 & 8.3e+07 & \ldots & 2.0e+12 & 9.4e+10  \\
+150.114050 & 2.353890 & 150.114076 & 2.353853 & 1.100\tablefootmark{G} & 5.49 & 1.05 & 7.7e+08 & 2.7e+09 & 1.9e+08 & 1.6e+07 & \ldots & 3.3e+11 & 3.3e+09  \\
+150.063620 & 2.254643 & 150.063636 & 2.254647 & 1.087\tablefootmark{G} & -0.48 & 0.41 & 7.0e+09 & 1.6e+09 & 2.1e+08 & 1.3e+07 & \ldots & 1.0e+11 & 8.4e+07  \\
 150.135490 & 2.245705 & 150.135500 & 2.245705 & 0.907                  & 0.54 & 1.32 & 3.0e+09 & 1.9e+09 & 2.8e+08 & 4.4e+07 & \ldots & 3.2e+11 & 5.5e+09  \\
-150.097230 & 2.302491 & 150.097290 & 2.302497 & 1.462\tablenotemark{G} & -0.26 & 0.30 & 4.1e+09 & 2.0e+09 & 4.3e+08 & 4.0e+07 & \ldots & 5.6e+11 & 1.5e+08  \\
-150.144750 & 2.334391 & 150.144778 & 2.334385 & 0.861\tablenotemark{G} & 1.24 & 0.30 & 1.8e+09 & 2.9e+08 & 2.7e+08 & 2.3e+07 & \ldots & 2.1e+11 & 3.2e+10  \\
+150.097230 & 2.302491 & 150.097290 & 2.302497 & 1.462\tablefootmark{G} & -0.26 & 0.30 & 4.1e+09 & 2.0e+09 & 4.3e+08 & 4.0e+07 & \ldots & 5.6e+11 & 1.5e+08  \\
+150.144750 & 2.334391 & 150.144778 & 2.334385 & 0.861\tablefootmark{G} & 1.24 & 0.30 & 1.8e+09 & 2.9e+08 & 2.7e+08 & 2.3e+07 & \ldots & 2.1e+11 & 3.2e+10  \\
 150.073480 & 2.226387 & 150.073503 & 2.226385 & 1.040                  & -0.57 & 1.37 & 1.3e+10 & 6.6e+09 & \ldots & \ldots & 1.0e+09 & 3.8e+11 & 1.8e+10  \\
-150.187670 & 2.344660 & 150.187630 & 2.344672 & 1.302\tablenotemark{G} & -1.43 & 0.29 & 1.0e+10 & 1.5e+09 & 3.3e+08 & 1.8e+07 & \ldots & 3.5e+11 & 2.1e+08  \\
+150.187670 & 2.344660 & 150.187630 & 2.344672 & 1.302\tablefootmark{G} & -1.43 & 0.29 & 1.0e+10 & 1.5e+09 & 3.3e+08 & 1.8e+07 & \ldots & 3.5e+11 & 2.1e+08  \\
 150.101470 & 2.278431 & 150.101499 & 2.278435 & 0.755                  & -1.71 & 0.16 & 8.8e+09 & 6.2e+08 & \ldots & \ldots & 6.8e+07 & 1.0e+11 & 4.1e+09  \\
-150.148310 & 2.367414 & 150.148341 & 2.367409 & 1.429\tablenotemark{G} & -0.20 & 0.25 & 4.3e+09 & 1.3e+09 & 3.8e+08 & 4.1e+07 & \ldots & 4.5e+11 & 8.4e+10  \\
-150.143560 & 2.268420 & 150.143583 & 2.268431 & 0.886\tablenotemark{G} & 1.53 & 1.26 & 8.9e+08 & 6.2e+08 & 1.9e+08 & 1.7e+07 & \ldots & 2.4e+11 & 6.2e+09  \\
-150.141210 & 2.272969 & 150.141229 & 2.272974 & 0.942\tablenotemark{G} & -0.24 & 0.86 & 4.1e+09 & 1.5e+09 & 2.4e+08 & 8.3e+06 & \ldots & 1.4e+11 & 8.3e+08  \\
-150.077410 & 2.437059 & 150.077456 & 2.437006 & 0.897\tablenotemark{G} & 1.70 & 3.08 & 3.3e+08 & 5.9e+08 & 7.7e+07 & 1.3e+07 & \ldots & 8.9e+10 & 7.9e+07  \\
-150.148070 & 2.331341 & 150.148097 & 2.331332 & 0.856\tablenotemark{G} & 1.99 & 1.17 & 6.8e+08 & 4.9e+08 & 1.7e+08 & 1.8e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
-150.153930 & 2.276188 & 150.153960 & 2.276199 & 1.215\tablenotemark{G} & 0.45 & 0.63 & 6.7e+09 & 2.6e+09 & 4.7e+08 & 4.7e+07 & \ldots & 3.3e+11 & 1.1e+10  \\
+150.148310 & 2.367414 & 150.148341 & 2.367409 & 1.429\tablefootmark{G} & -0.20 & 0.25 & 4.3e+09 & 1.3e+09 & 3.8e+08 & 4.1e+07 & \ldots & 4.5e+11 & 8.4e+10  \\
+150.143560 & 2.268420 & 150.143583 & 2.268431 & 0.886\tablefootmark{G} & 1.53 & 1.26 & 8.9e+08 & 6.2e+08 & 1.9e+08 & 1.7e+07 & \ldots & 2.4e+11 & 6.2e+09  \\
+150.141210 & 2.272969 & 150.141229 & 2.272974 & 0.942\tablefootmark{G} & -0.24 & 0.86 & 4.1e+09 & 1.5e+09 & 2.4e+08 & 8.3e+06 & \ldots & 1.4e+11 & 8.3e+08  \\
+150.077410 & 2.437059 & 150.077456 & 2.437006 & 0.897\tablefootmark{G} & 1.70 & 3.08 & 3.3e+08 & 5.9e+08 & 7.7e+07 & 1.3e+07 & \ldots & 8.9e+10 & 7.9e+07  \\
+150.148070 & 2.331341 & 150.148097 & 2.331332 & 0.856\tablefootmark{G} & 1.99 & 1.17 & 6.8e+08 & 4.9e+08 & 1.7e+08 & 1.8e+07 & \ldots & 2.8e+11 & 1.8e+10  \\
+150.153930 & 2.276188 & 150.153960 & 2.276199 & 1.215\tablefootmark{G} & 0.45 & 0.63 & 6.7e+09 & 2.6e+09 & 4.7e+08 & 4.7e+07 & \ldots & 3.3e+11 & 1.1e+10  \\
 150.069910 & 2.295822 & 150.069951 & 2.295813 & 0.731                  & -0.57 & 0.41 & 1.5e+09 & 2.6e+08 & \ldots & \ldots & 7.3e+07 & 9.7e+10 & 1.9e+09  \\
-150.087940 & 2.326192 & 150.087979 & 2.326153 & 0.939\tablenotemark{G} & -0.12 & 0.62 & 7.9e+09 & 2.1e+09 & 2.7e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.2e+06  \\
-150.130570 & 2.361473 & 150.130581 & 2.361458 & 1.410\tablenotemark{G} & 0.19 & 0.10 & 9.4e+09 & 1.5e+09 & 3.2e+08 & 4.0e+07 & \ldots & 5.5e+11 & 4.2e+10  \\
+150.087940 & 2.326192 & 150.087979 & 2.326153 & 0.939\tablefootmark{G} & -0.12 & 0.62 & 7.9e+09 & 2.1e+09 & 2.7e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.2e+06  \\
+150.130570 & 2.361473 & 150.130581 & 2.361458 & 1.410\tablefootmark{G} & 0.19 & 0.10 & 9.4e+09 & 1.5e+09 & 3.2e+08 & 4.0e+07 & \ldots & 5.5e+11 & 4.2e+10  \\
 150.177530 & 2.261224 & 150.177536 & 2.261222 & 0.879                  & -1.50 & 0.39 & 1.8e+10 & 2.9e+09 & 1.5e+08 & 1.8e+07 & \ldots & 9.0e+10 & 1.0e+09  \\
-150.176210 & 2.264468 & 150.176229 & 2.264448 & 1.008\tablenotemark{G} & -0.78 & 0.59 & 6.7e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.8e+11 & 4.6e+07  \\
+150.176210 & 2.264468 & 150.176229 & 2.264448 & 1.008\tablefootmark{G} & -0.78 & 0.59 & 6.7e+09 & 1.5e+09 & 1.6e+08 & 1.7e+07 & \ldots & 1.8e+11 & 4.6e+07  \\
 150.145010 & 2.336923 & 150.145032 & 2.336921 & 0.937                  & 0.06 & 1.66 & 7.4e+09 & 5.4e+09 & 2.9e+08 & 5.7e+07 & \ldots & 2.9e+11 & 4.2e+07  \\
@@
 150.139590 & 2.407071 & 150.139609 & 2.407059 & 0.901                  & 0.62 & 0.80 & 2.1e+09 & 8.2e+08 & 1.3e+08 & 2.1e+07 & \ldots & 1.2e+11 & 4.5e+09  \\
-150.143610 & 2.439931 & 150.143607 & 2.439900 & 1.150\tablenotemark{G} & 0.24 & 1.30 & 9.9e+08 & 9.7e+08 & \ldots & \ldots & 9.6e+07 & 3.0e+11 & 1.6e+10  \\
-150.169510 & 2.262296 & 150.169517 & 2.262296 & 1.106\tablenotemark{G} & 0.01 & 1.21 & 1.8e+09 & 1.3e+09 & 2.0e+08 & 1.6e+07 & \ldots & 2.1e+11 & 2.0e+08  \\
-150.079250 & 2.448390 & 150.079318 & 2.448336 & 1.401\tablenotemark{G} & -1.05 & 0.14 & 2.2e+10 & 3.2e+09 & 1.5e+08 & 2.7e+07 & \ldots & 2.9e+11 & 2.4e+08  \\
-150.108410 & 2.214345 & 150.108425 & 2.214340 & 0.986\tablenotemark{G} & -0.88 & 1.34 & 6.0e+09 & 3.2e+09 & 2.0e+08 & 1.9e+07 & \ldots & 2.0e+11 & 2.5e+08  \\
-150.157770 & 2.329275 & 150.157817 & 2.329266 & 0.905\tablenotemark{G} & 0.32 & 1.43 & 2.1e+09 & 1.4e+09 & \ldots & \ldots & 6.8e+07 & 3.6e+11 & 1.4e+10  \\
-150.153430 & 2.443099 & 150.153473 & 2.443077 & 0.901\tablenotemark{G} & -0.03 & 0.54 & 1.1e+10 & 2.7e+09 & 1.1e+08 & 1.8e+07 & \ldots & 4.6e+11 & 7.8e+10  \\
-150.075630 & 2.387739 & 150.075652 & 2.387737 & 1.264\tablenotemark{G} & -0.90 & 0.84 & 3.8e+09 & 2.0e+09 & 3.1e+08 & 2.5e+07 & \ldots & 3.9e+11 & 7.9e+07  \\
-150.090770 & 2.413311 & 150.090791 & 2.413293 & 0.732\tablenotemark{G} & 0.22 & 0.21 & 3.7e+09 & 3.5e+08 & 2.7e+08 & 2.8e+07 & \ldots & 1.3e+11 & 1.7e+10  \\
-150.147550 & 2.472620 & 150.147578 & 2.472604 & 0.900\tablenotemark{G} & 0.70 & 0.92 & 3.7e+09 & 1.7e+09 & 2.5e+08 & 2.3e+07 & \ldots & 3.0e+11 & 4.2e+10  \\
-150.105770 & 2.380248 & 150.105812 & 2.380245 & 0.916\tablenotemark{G} & -0.43 & 1.07 & 1.9e+10 & 8.9e+09 & 6.0e+08 & 3.8e+07 & \ldots & 5.0e+11 & 2.3e+10  \\
+150.143610 & 2.439931 & 150.143607 & 2.439900 & 1.150\tablefootmark{G} & 0.24 & 1.30 & 9.9e+08 & 9.7e+08 & \ldots & \ldots & 9.6e+07 & 3.0e+11 & 1.6e+10  \\
+150.169510 & 2.262296 & 150.169517 & 2.262296 & 1.106\tablefootmark{G} & 0.01 & 1.21 & 1.8e+09 & 1.3e+09 & 2.0e+08 & 1.6e+07 & \ldots & 2.1e+11 & 2.0e+08  \\
+150.079250 & 2.448390 & 150.079318 & 2.448336 & 1.401\tablefootmark{G} & -1.05 & 0.14 & 2.2e+10 & 3.2e+09 & 1.5e+08 & 2.7e+07 & \ldots & 2.9e+11 & 2.4e+08  \\
+150.108410 & 2.214345 & 150.108425 & 2.214340 & 0.986\tablefootmark{G} & -0.88 & 1.34 & 6.0e+09 & 3.2e+09 & 2.0e+08 & 1.9e+07 & \ldots & 2.0e+11 & 2.5e+08  \\
+150.157770 & 2.329275 & 150.157817 & 2.329266 & 0.905\tablefootmark{G} & 0.32 & 1.43 & 2.1e+09 & 1.4e+09 & \ldots & \ldots & 6.8e+07 & 3.6e+11 & 1.4e+10  \\
+150.153430 & 2.443099 & 150.153473 & 2.443077 & 0.901\tablefootmark{G} & -0.03 & 0.54 & 1.1e+10 & 2.7e+09 & 1.1e+08 & 1.8e+07 & \ldots & 4.6e+11 & 7.8e+10  \\
+150.075630 & 2.387739 & 150.075652 & 2.387737 & 1.264\tablefootmark{G} & -0.90 & 0.84 & 3.8e+09 & 2.0e+09 & 3.1e+08 & 2.5e+07 & \ldots & 3.9e+11 & 7.9e+07  \\
+150.090770 & 2.413311 & 150.090791 & 2.413293 & 0.732\tablefootmark{G} & 0.22 & 0.21 & 3.7e+09 & 3.5e+08 & 2.7e+08 & 2.8e+07 & \ldots & 1.3e+11 & 1.7e+10  \\
+150.147550 & 2.472620 & 150.147578 & 2.472604 & 0.900\tablefootmark{G} & 0.70 & 0.92 & 3.7e+09 & 1.7e+09 & 2.5e+08 & 2.3e+07 & \ldots & 3.0e+11 & 4.2e+10  \\
+150.105770 & 2.380248 & 150.105812 & 2.380245 & 0.916\tablefootmark{G} & -0.43 & 1.07 & 1.9e+10 & 8.9e+09 & 6.0e+08 & 3.8e+07 & \ldots & 5.0e+11 & 2.3e+10  \\
 150.115000 & 2.380963 & 150.115038 & 2.380956 & 1.137                  & 0.49 & 0.57 & 6.2e+09 & 2.4e+09 & 3.4e+08 & 4.1e+07 & \ldots & 2.7e+11 & 3.2e+09  \\
@@
 150.130290 & 2.259621 & 150.130309 & 2.259626 & 0.749                  & -1.00 & 0.30 & 2.3e+09 & 3.0e+08 & \ldots & \ldots & 5.9e+07 & 9.0e+10 & 5.4e+09  \\
-150.127840 & 2.277855 & 150.127861 & 2.277863 & 0.930\tablenotemark{G} & -0.51 & 0.38 & 4.1e+09 & 6.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 9.8e+10 & 9.8e+09  \\
+150.127840 & 2.277855 & 150.127861 & 2.277863 & 0.930\tablefootmark{G} & -0.51 & 0.38 & 4.1e+09 & 6.6e+08 & 1.1e+08 & 1.5e+07 & \ldots & 9.8e+10 & 9.8e+09  \\
 150.110260 & 2.193960 & 150.110268 & 2.193980 & 1.159                  & 1.18 & 0.97 & 2.4e+09 & 1.7e+09 & 2.3e+08 & 3.3e+07 & \ldots & 4.5e+11 & 7.0e+10  \\
-150.098190 & 2.414925 & 150.098213 & 2.414914 & 0.841\tablenotemark{G} & -0.19 & 1.87 & 2.5e+09 & 2.0e+09 & 1.0e+08 & 1.1e+07 & \ldots & 1.2e+11 & 1.7e+08  \\
-150.079710 & 2.295934 & 150.079746 & 2.295947 & 1.101\tablenotemark{G} & -0.18 & 0.44 & 1.0e+10 & 2.6e+09 & 3.7e+08 & 1.5e+07 & \ldots & 2.1e+11 & 3.5e+08  \\
+150.098190 & 2.414925 & 150.098213 & 2.414914 & 0.841\tablefootmark{G} & -0.19 & 1.87 & 2.5e+09 & 2.0e+09 & 1.0e+08 & 1.1e+07 & \ldots & 1.2e+11 & 1.7e+08  \\
+150.079710 & 2.295934 & 150.079746 & 2.295947 & 1.101\tablefootmark{G} & -0.18 & 0.44 & 1.0e+10 & 2.6e+09 & 3.7e+08 & 1.5e+07 & \ldots & 2.1e+11 & 3.5e+08  \\
 150.179060 & 2.364153 & 150.179074 & 2.364139 & 1.343                  & 0.31 & 0.18 & 1.4e+10 & 2.2e+09 & 8.6e+08 & 4.7e+07 & \ldots & 7.3e+11 & 2.6e+10  \\
 150.075420 & 2.336254 & 150.075468 & 2.336257 & 0.853                  & 1.97 & 1.29 & 4.9e+08 & 4.0e+08 & \ldots & \ldots & 6.6e+07 & 1.0e+11 & 4.3e+08  \\
-150.104260 & 2.440705 & 150.104283 & 2.440684 & 0.753\tablenotemark{G} & -0.56 & 0.80 & 5.7e+08 & 2.0e+08 & 7.6e+07 & 1.2e+07 & \ldots & 1.9e+11 & 1.7e+09  \\
+150.104260 & 2.440705 & 150.104283 & 2.440684 & 0.753\tablefootmark{G} & -0.56 & 0.80 & 5.7e+08 & 2.0e+08 & 7.6e+07 & 1.2e+07 & \ldots & 1.9e+11 & 1.7e+09  \\
 150.105960 & 2.213144 & 150.105985 & 2.213151 & 0.925                  & 0.31 & 1.19 & 3.7e+09 & 2.0e+09 & 2.7e+08 & 3.0e+07 & \ldots & 2.9e+11 & 1.5e+10  \\
 150.067460 & 2.223537 & 150.067493 & 2.223542 & 0.723                  & 0.47 & 0.17 & 5.7e+09 & 4.2e+08 & 3.8e+08 & 2.7e+07 & \ldots & 2.1e+11 & 1.1e+10  \\
-\cutinhead{UDS}
-34.289417 & -5.164467 & 34.289461 & -5.164426 & 0.904\tablenotemark{G} & 0.44 & 0.75 & 4.5e+08 & 1.3e+08 & 1.3e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
-34.483398 & -5.219781 & 34.483412 & -5.219763 & 0.740\tablenotemark{G} & 0.67 & 0.07 & 2.8e+09 & 9.3e+07 & 1.1e+08 & 2.0e+07 & \ldots & 9.6e+10 & 6.5e+09  \\
-34.463700 & -5.230395 & 34.463706 & -5.230378 & 1.279\tablenotemark{G} & -0.46 & 0.26 & 3.1e+09 & 5.7e+08 & 2.7e+08 & 2.0e+07 & \ldots & 4.9e+11 & 2.5e+10  \\
+\hline
+\multicolumn{14}{c}{UDS} \\
+\hline
+34.289417 & -5.164467 & 34.289461 & -5.164426 & 0.904\tablefootmark{G} & 0.44 & 0.75 & 4.5e+08 & 1.3e+08 & 1.3e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
+34.483398 & -5.219781 & 34.483412 & -5.219763 & 0.740\tablefootmark{G} & 0.67 & 0.07 & 2.8e+09 & 9.3e+07 & 1.1e+08 & 2.0e+07 & \ldots & 9.6e+10 & 6.5e+09  \\
+34.463700 & -5.230395 & 34.463706 & -5.230378 & 1.279\tablefootmark{G} & -0.46 & 0.26 & 3.1e+09 & 5.7e+08 & 2.7e+08 & 2.0e+07 & \ldots & 4.9e+11 & 2.5e+10  \\
 34.241451 & -5.157997 & 34.241492 & -5.157975 & 0.855                  & 0.62 & 0.04 & 7.0e+09 & 1.2e+08 & 5.0e+08 & 2.5e+07 & \ldots & 2.8e+11 & 7.1e+09  \\
-34.370277 & -5.246929 & 34.370288 & -5.246901 & 0.922\tablenotemark{G} & 0.52 & 0.12 & 3.1e+09 & 1.4e+08 & 2.8e+08 & 1.4e+07 & \ldots & 4.7e+11 & 2.4e+09  \\
-34.286585 & -5.237958 & 34.286618 & -5.237961 & 1.277\tablenotemark{G} & 0.41 & 0.13 & 1.2e+09 & 1.3e+08 & 4.3e+08 & 1.6e+07 & \ldots & 1.1e+12 & 1.6e+10  \\
-34.315356 & -5.232962 & 34.315373 & -5.232970 & 1.415\tablenotemark{G} & 1.16 & 1.01 & 6.0e+08 & 5.8e+08 & 4.3e+08 & 3.4e+07 & \ldots & 1.0e+12 & 8.4e+10  \\
-34.480474 & -5.247719 & 34.480410 & -5.247806 & 1.469\tablenotemark{G} & 0.48 & 1.42 & 2.0e+09 & 1.9e+09 & 4.4e+08 & 6.6e+07 & \ldots & 7.8e+11 & 1.7e+10  \\
-34.325410 & -5.199980 & 34.325420 & -5.199968 & 1.095\tablenotemark{G} & 0.15 & 0.20 & 6.8e+09 & 7.1e+08 & 2.9e+08 & 2.9e+07 & \ldots & 2.9e+11 & 1.9e+10  \\
+34.370277 & -5.246929 & 34.370288 & -5.246901 & 0.922\tablefootmark{G} & 0.52 & 0.12 & 3.1e+09 & 1.4e+08 & 2.8e+08 & 1.4e+07 & \ldots & 4.7e+11 & 2.4e+09  \\
+34.286585 & -5.237958 & 34.286618 & -5.237961 & 1.277\tablefootmark{G} & 0.41 & 0.13 & 1.2e+09 & 1.3e+08 & 4.3e+08 & 1.6e+07 & \ldots & 1.1e+12 & 1.6e+10  \\
+34.315356 & -5.232962 & 34.315373 & -5.232970 & 1.415\tablefootmark{G} & 1.16 & 1.01 & 6.0e+08 & 5.8e+08 & 4.3e+08 & 3.4e+07 & \ldots & 1.0e+12 & 8.4e+10  \\
+34.480474 & -5.247719 & 34.480410 & -5.247806 & 1.469\tablefootmark{G} & 0.48 & 1.42 & 2.0e+09 & 1.9e+09 & 4.4e+08 & 6.6e+07 & \ldots & 7.8e+11 & 1.7e+10  \\
+34.325410 & -5.199980 & 34.325420 & -5.199968 & 1.095\tablefootmark{G} & 0.15 & 0.20 & 6.8e+09 & 7.1e+08 & 2.9e+08 & 2.9e+07 & \ldots & 2.9e+11 & 1.9e+10  \\
 34.334096 & -5.237701 & 34.334103 & -5.237683 & 0.920                  & 1.88 & 0.51 & 5.0e+08 & 9.5e+07 & 9.1e+07 & 9.4e+06 & \ldots & 1.5e+11 & 9.6e+09  \\
 34.435496 & -5.152846 & 34.435522 & -5.152819 & 0.801                  & 2.25 & 0.14 & 1.2e+09 & 7.4e+07 & \ldots & \ldots & 1.5e+08 & 3.5e+11 & 3.9e+10  \\
-34.332435 & -5.212034 & 34.332461 & -5.212009 & 1.378\tablenotemark{G} & 0.11 & 0.31 & 6.0e+09 & 1.4e+09 & 4.2e+08 & 2.5e+07 & \ldots & 4.7e+11 & 2.7e+09  \\
-34.325370 & -5.223768 & 34.325374 & -5.223737 & 1.415\tablenotemark{G} & 0.28 & 1.42 & 8.3e+08 & 8.0e+08 & 1.3e+08 & 2.1e+07 & \ldots & 8.3e+11 & 3.8e+10  \\
-34.368704 & -5.157358 & 34.368684 & -5.157395 & 0.835\tablenotemark{G} & 2.44 & 0.52 & 2.8e+08 & 5.9e+07 & 6.4e+07 & 1.0e+07 & \ldots & 1.4e+11 & 8.3e+09  \\
-34.574970 & -5.161715 & 34.574958 & -5.161686 & 1.195\tablenotemark{G} & -0.60 & 0.14 & 2.1e+10 & 1.3e+09 & 6.8e+08 & 2.9e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
-34.374753 & -5.227548 & 34.374772 & -5.227530 & 1.429\tablenotemark{G} & -0.15 & 0.32 & 1.1e+10 & 1.9e+09 & 5.8e+08 & 3.7e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
+34.332435 & -5.212034 & 34.332461 & -5.212009 & 1.378\tablefootmark{G} & 0.11 & 0.31 & 6.0e+09 & 1.4e+09 & 4.2e+08 & 2.5e+07 & \ldots & 4.7e+11 & 2.7e+09  \\
+34.325370 & -5.223768 & 34.325374 & -5.223737 & 1.415\tablefootmark{G} & 0.28 & 1.42 & 8.3e+08 & 8.0e+08 & 1.3e+08 & 2.1e+07 & \ldots & 8.3e+11 & 3.8e+10  \\
+34.368704 & -5.157358 & 34.368684 & -5.157395 & 0.835\tablefootmark{G} & 2.44 & 0.52 & 2.8e+08 & 5.9e+07 & 6.4e+07 & 1.0e+07 & \ldots & 1.4e+11 & 8.3e+09  \\
+34.574970 & -5.161715 & 34.574958 & -5.161686 & 1.195\tablefootmark{G} & -0.60 & 0.14 & 2.1e+10 & 1.3e+09 & 6.8e+08 & 2.9e+07 & \ldots & 3.4e+11 & 1.3e+10  \\
+34.374753 & -5.227548 & 34.374772 & -5.227530 & 1.429\tablefootmark{G} & -0.15 & 0.32 & 1.1e+10 & 1.9e+09 & 5.8e+08 & 3.7e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
 34.435733 & -5.231665 & 34.435744 & -5.231653 & 0.914                  & -0.05 & 0.08 & 6.2e+09 & 1.8e+08 & \ldots & \ldots & 9.4e+07 & 2.3e+11 & 7.4e+09  \\
-34.231824 & -5.253116 & 34.231825 & -5.253016 & 0.823\tablenotemark{G} & 0.64 & 0.06 & 3.9e+09 & 9.1e+07 & 3.5e+08 & 1.4e+07 & \ldots & 3.4e+11 & 3.4e+09  \\
-34.457636 & -5.164808 & 34.457656 & -5.164792 & 0.916\tablenotemark{G} & -0.32 & 0.04 & 1.3e+10 & 2.1e+08 & \ldots & \ldots & 6.1e+08 & 3.6e+11 & 2.8e+09  \\
+34.231824 & -5.253116 & 34.231825 & -5.253016 & 0.823\tablefootmark{G} & 0.64 & 0.06 & 3.9e+09 & 9.1e+07 & 3.5e+08 & 1.4e+07 & \ldots & 3.4e+11 & 3.4e+09  \\
+34.457636 & -5.164808 & 34.457656 & -5.164792 & 0.916\tablefootmark{G} & -0.32 & 0.04 & 1.3e+10 & 2.1e+08 & \ldots & \ldots & 6.1e+08 & 3.6e+11 & 2.8e+09  \\
 34.375611 & -5.204026 & 34.375625 & -5.204000 & 0.915                  & -0.25 & 0.08 & 6.1e+09 & 1.8e+08 & \ldots & \ldots & 6.3e+07 & 1.8e+11 & 3.4e+09  \\
 34.359199 & -5.257633 & 34.359225 & -5.257605 & 0.803                  & 0.11 & 0.06 & 5.6e+09 & 1.3e+08 & \ldots & \ldots & 2.3e+08 & 8.9e+10 & 8.1e+09  \\
-34.250598 & -5.162615 & 34.250537 & -5.162659 & 0.829\tablenotemark{G} & -0.12 & 0.04 & 8.8e+09 & 1.4e+08 & 2.8e+08 & 2.8e+07 & \ldots & 1.4e+11 & 7.1e+08  \\
-34.457290 & -5.229210 & 34.457293 & -5.229258 & 0.929\tablenotemark{G} & -0.11 & 0.12 & 3.7e+09 & 1.6e+08 & 1.9e+08 & 1.3e+07 & \ldots & 1.9e+11 & 9.5e+09  \\
+34.250598 & -5.162615 & 34.250537 & -5.162659 & 0.829\tablefootmark{G} & -0.12 & 0.04 & 8.8e+09 & 1.4e+08 & 2.8e+08 & 2.8e+07 & \ldots & 1.4e+11 & 7.1e+08  \\
+34.457290 & -5.229210 & 34.457293 & -5.229258 & 0.929\tablefootmark{G} & -0.11 & 0.12 & 3.7e+09 & 1.6e+08 & 1.9e+08 & 1.3e+07 & \ldots & 1.9e+11 & 9.5e+09  \\
 34.268269 & -5.151559 & 34.268324 & -5.151551 & 1.012                  & -0.35 & 0.13 & 4.2e+09 & 1.7e+08 & 3.7e+08 & 1.8e+07 & \ldots & 3.8e+11 & 6.1e+09  \\
 34.369105 & -5.172428 & 34.369137 & -5.172404 & 0.825                  & 0.96 & 0.05 & 4.4e+09 & 9.9e+07 & 2.4e+08 & 1.7e+07 & \ldots & 1.6e+11 & 8.4e+09  \\
-34.481139 & -5.174353 & 34.481147 & -5.174333 & 1.275\tablenotemark{G} & 0.32 & 0.38 & 3.7e+09 & 1.0e+09 & 6.5e+08 & 1.7e+07 & \ldots & 1.2e+12 & 2.9e+10  \\
+34.481139 & -5.174353 & 34.481147 & -5.174333 & 1.275\tablefootmark{G} & 0.32 & 0.38 & 3.7e+09 & 1.0e+09 & 6.5e+08 & 1.7e+07 & \ldots & 1.2e+12 & 2.9e+10  \\
 34.444958 & -5.168239 & 34.444949 & -5.168229 & 1.417                  & -0.63 & 0.41 & 2.0e+10 & 4.4e+09 & 7.5e+08 & 5.5e+07 & \ldots & 8.3e+11 & 6.9e+10  \\
-34.377887 & -5.179532 & 34.377976 & -5.179501 & 1.270\tablenotemark{G} & 1.29 & 0.04 & 6.8e+08 & 1.6e+07 & 2.3e+08 & 1.7e+07 & \ldots & 6.3e+11 & 2.5e+10  \\
-34.246973 & -5.265455 & 34.246992 & -5.265421 & 1.420\tablenotemark{G} & 0.96 & 0.80 & 7.6e+08 & 4.4e+08 & 4.6e+08 & 3.9e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
-34.347189 & -5.175795 & 34.347225 & -5.175778 & 1.428\tablenotemark{G} & -0.58 & 0.47 & 1.0e+10 & 2.9e+09 & 4.7e+08 & 6.5e+07 & \ldots & 7.3e+11 & 3.6e+10  \\
-34.318401 & -5.229057 & 34.318417 & -5.229052 & 1.035\tablenotemark{G} & 0.49 & 0.42 & 1.3e+09 & 1.8e+08 & 1.6e+08 & 1.6e+07 & \ldots & 2.2e+11 & 1.3e+10  \\
-34.375082 & -5.164786 & 34.375134 & -5.164736 & 1.089\tablenotemark{G} & 0.93 & 0.52 & 2.3e+09 & 7.8e+08 & \ldots & \ldots & 7.2e+07 & 3.7e+11 & 1.9e+10  \\
-34.358432 & -5.175677 & 34.358447 & -5.175662 & 1.431\tablenotemark{G} & -0.98 & 0.35 & 1.5e+10 & 2.7e+09 & 8.2e+08 & 7.5e+07 & \ldots & 9.7e+11 & 7.8e+10  \\
-34.255834 & -5.167369 & 34.255891 & -5.167354 & 1.090\tablenotemark{G} & 0.01 & 0.43 & 4.5e+09 & 9.7e+08 & 2.1e+08 & 2.7e+07 & \ldots & 4.2e+11 & 4.5e+10  \\
+34.377887 & -5.179532 & 34.377976 & -5.179501 & 1.270\tablefootmark{G} & 1.29 & 0.04 & 6.8e+08 & 1.6e+07 & 2.3e+08 & 1.7e+07 & \ldots & 6.3e+11 & 2.5e+10  \\
+34.246973 & -5.265455 & 34.246992 & -5.265421 & 1.420\tablefootmark{G} & 0.96 & 0.80 & 7.6e+08 & 4.4e+08 & 4.6e+08 & 3.9e+07 & \ldots & 6.3e+11 & 5.0e+10  \\
+34.347189 & -5.175795 & 34.347225 & -5.175778 & 1.428\tablefootmark{G} & -0.58 & 0.47 & 1.0e+10 & 2.9e+09 & 4.7e+08 & 6.5e+07 & \ldots & 7.3e+11 & 3.6e+10  \\
+34.318401 & -5.229057 & 34.318417 & -5.229052 & 1.035\tablefootmark{G} & 0.49 & 0.42 & 1.3e+09 & 1.8e+08 & 1.6e+08 & 1.6e+07 & \ldots & 2.2e+11 & 1.3e+10  \\
+34.375082 & -5.164786 & 34.375134 & -5.164736 & 1.089\tablefootmark{G} & 0.93 & 0.52 & 2.3e+09 & 7.8e+08 & \ldots & \ldots & 7.2e+07 & 3.7e+11 & 1.9e+10  \\
+34.358432 & -5.175677 & 34.358447 & -5.175662 & 1.431\tablefootmark{G} & -0.98 & 0.35 & 1.5e+10 & 2.7e+09 & 8.2e+08 & 7.5e+07 & \ldots & 9.7e+11 & 7.8e+10  \\
+34.255834 & -5.167369 & 34.255891 & -5.167354 & 1.090\tablefootmark{G} & 0.01 & 0.43 & 4.5e+09 & 9.7e+08 & 2.1e+08 & 2.7e+07 & \ldots & 4.2e+11 & 4.5e+10  \\
 34.322860 & -5.167645 & 34.322906 & -5.167608 & 1.030                  & 1.30 & 0.11 & 5.0e+09 & 1.8e+08 & 6.5e+08 & 2.2e+07 & \ldots & 9.7e+11 & 1.5e+10  \\
-34.399563 & -5.224797 & 34.399633 & -5.224808 & 1.097\tablenotemark{G} & -0.73 & 0.04 & 1.8e+10 & 3.1e+08 & 3.2e+08 & 1.3e+07 & \ldots & 1.7e+11 & 1.9e+10  \\
-34.401748 & -5.153146 & 34.401803 & -5.153117 & 1.091\tablenotemark{G} & 1.55 & 0.47 & 6.4e+08 & 2.3e+08 & 1.6e+08 & 1.1e+07 & \ldots & 2.6e+11 & 9.8e+09  \\
-34.486134 & -5.254569 & 34.486173 & -5.254550 & 0.947\tablenotemark{G} & 0.53 & 0.22 & 2.2e+09 & 1.7e+08 & 1.4e+08 & 2.1e+07 & \ldots & 3.8e+11 & 1.7e+10  \\
-34.444281 & -5.248412 & 34.444279 & -5.248374 & 1.091\tablenotemark{G} & 1.39 & 0.14 & 8.3e+08 & 8.3e+07 & 1.0e+08 & 1.1e+07 & \ldots & 2.1e+11 & 1.5e+10  \\
-34.435300 & -5.158785 & 34.435317 & -5.158755 & 1.326\tablenotemark{G} & -0.95 & 0.34 & 1.0e+10 & 2.0e+09 & 4.1e+08 & 3.6e+07 & \ldots & 4.0e+11 & 3.0e+10  \\
-34.236833 & -5.197802 & 34.236869 & -5.197786 & 0.790\tablenotemark{G} & 5.96 & 2.43 & 1.3e+07 & 1.5e+07 & 5.0e+07 & 7.0e+06 & \ldots & 9.5e+10 & 5.4e+09  \\
-34.486535 & -5.240308 & 34.486568 & -5.240289 & 1.305\tablenotemark{G} & -0.64 & 0.24 & 3.2e+09 & 4.1e+08 & 2.2e+08 & 3.8e+07 & \ldots & 6.3e+11 & 6.5e+10  \\
-34.235814 & -5.168167 & 34.235951 & -5.168147 & 1.264\tablenotemark{G} & -1.14 & 0.06 & 1.9e+10 & 4.1e+08 & 5.7e+08 & 3.0e+07 & \ldots & 4.2e+12 & 6.2e+11  \\
+34.399563 & -5.224797 & 34.399633 & -5.224808 & 1.097\tablefootmark{G} & -0.73 & 0.04 & 1.8e+10 & 3.1e+08 & 3.2e+08 & 1.3e+07 & \ldots & 1.7e+11 & 1.9e+10  \\
+34.401748 & -5.153146 & 34.401803 & -5.153117 & 1.091\tablefootmark{G} & 1.55 & 0.47 & 6.4e+08 & 2.3e+08 & 1.6e+08 & 1.1e+07 & \ldots & 2.6e+11 & 9.8e+09  \\
+34.486134 & -5.254569 & 34.486173 & -5.254550 & 0.947\tablefootmark{G} & 0.53 & 0.22 & 2.2e+09 & 1.7e+08 & 1.4e+08 & 2.1e+07 & \ldots & 3.8e+11 & 1.7e+10  \\
+34.444281 & -5.248412 & 34.444279 & -5.248374 & 1.091\tablefootmark{G} & 1.39 & 0.14 & 8.3e+08 & 8.3e+07 & 1.0e+08 & 1.1e+07 & \ldots & 2.1e+11 & 1.5e+10  \\
+34.435300 & -5.158785 & 34.435317 & -5.158755 & 1.326\tablefootmark{G} & -0.95 & 0.34 & 1.0e+10 & 2.0e+09 & 4.1e+08 & 3.6e+07 & \ldots & 4.0e+11 & 3.0e+10  \\
+34.236833 & -5.197802 & 34.236869 & -5.197786 & 0.790\tablefootmark{G} & 5.96 & 2.43 & 1.3e+07 & 1.5e+07 & 5.0e+07 & 7.0e+06 & \ldots & 9.5e+10 & 5.4e+09  \\
+34.486535 & -5.240308 & 34.486568 & -5.240289 & 1.305\tablefootmark{G} & -0.64 & 0.24 & 3.2e+09 & 4.1e+08 & 2.2e+08 & 3.8e+07 & \ldots & 6.3e+11 & 6.5e+10  \\
+34.235814 & -5.168167 & 34.235951 & -5.168147 & 1.264\tablefootmark{G} & -1.14 & 0.06 & 1.9e+10 & 4.1e+08 & 5.7e+08 & 3.0e+07 & \ldots & 4.2e+12 & 6.2e+11  \\
 34.407596 & -5.239813 & 34.407597 & -5.239785 & 0.752                  & 2.04 & 0.14 & 8.6e+08 & 5.7e+07 & 8.3e+07 & 1.5e+07 & \ldots & 1.2e+11 & 4.8e+08  \\
-34.440375 & -5.240249 & 34.440380 & -5.240216 & 1.041\tablenotemark{G} & 1.16 & 0.71 & 6.2e+08 & 1.4e+08 & 9.9e+07 & 1.1e+07 & \ldots & 2.7e+11 & 1.2e+10  \\
-34.581318 & -5.178201 & 34.581313 & -5.178152 & 1.046\tablenotemark{G} & -0.65 & 0.07 & 1.0e+10 & 1.9e+08 & 2.9e+08 & 2.2e+07 & \ldots & 1.6e+11 & 1.4e+10  \\
-34.338810 & -5.191348 & 34.338853 & -5.191342 & 0.932\tablenotemark{G} & 1.82 & 0.48 & 6.5e+08 & 1.1e+08 & 1.2e+08 & 1.3e+07 & \ldots & 2.9e+11 & 4.1e+09  \\
-34.337205 & -5.214391 & 34.337215 & -5.214334 & 0.920\tablenotemark{G} & 1.06 & 0.50 & 5.7e+08 & 1.0e+08 & 7.6e+07 & 1.1e+07 & \ldots & 1.1e+11 & 1.6e+10  \\
-34.291195 & -5.191481 & 34.291192 & -5.191474 & 0.825\tablenotemark{G} & 6.82 & 3.02 & 1.3e+07 & 1.7e+07 & \ldots & \ldots & 3.5e+07 & 1.3e+11 & 1.2e+10  \\
-34.327458 & -5.197280 & 34.327395 & -5.197192 & 1.141\tablenotemark{G} & -0.63 & 0.10 & 1.2e+10 & 5.6e+08 & 1.8e+08 & 1.8e+07 & \ldots & 2.0e+11 & 2.5e+10  \\
+34.440375 & -5.240249 & 34.440380 & -5.240216 & 1.041\tablefootmark{G} & 1.16 & 0.71 & 6.2e+08 & 1.4e+08 & 9.9e+07 & 1.1e+07 & \ldots & 2.7e+11 & 1.2e+10  \\
+34.581318 & -5.178201 & 34.581313 & -5.178152 & 1.046\tablefootmark{G} & -0.65 & 0.07 & 1.0e+10 & 1.9e+08 & 2.9e+08 & 2.2e+07 & \ldots & 1.6e+11 & 1.4e+10  \\
+34.338810 & -5.191348 & 34.338853 & -5.191342 & 0.932\tablefootmark{G} & 1.82 & 0.48 & 6.5e+08 & 1.1e+08 & 1.2e+08 & 1.3e+07 & \ldots & 2.9e+11 & 4.1e+09  \\
+34.337205 & -5.214391 & 34.337215 & -5.214334 & 0.920\tablefootmark{G} & 1.06 & 0.50 & 5.7e+08 & 1.0e+08 & 7.6e+07 & 1.1e+07 & \ldots & 1.1e+11 & 1.6e+10  \\
+34.291195 & -5.191481 & 34.291192 & -5.191474 & 0.825\tablefootmark{G} & 6.82 & 3.02 & 1.3e+07 & 1.7e+07 & \ldots & \ldots & 3.5e+07 & 1.3e+11 & 1.2e+10  \\
+34.327458 & -5.197280 & 34.327395 & -5.197192 & 1.141\tablefootmark{G} & -0.63 & 0.10 & 1.2e+10 & 5.6e+08 & 1.8e+08 & 1.8e+07 & \ldots & 2.0e+11 & 2.5e+10  \\
 34.246650 & -5.238097 & 34.246662 & -5.238100 & 0.809                  & -0.97 & 0.04 & 8.9e+09 & 1.3e+08 & 1.9e+08 & 1.3e+07 & \ldots & 9.9e+10 & 8.4e+09  \\
-34.425930 & -5.174296 & 34.425949 & -5.174306 & 1.158\tablenotemark{G} & 0.38 & 0.34 & 2.0e+09 & 3.8e+08 & 6.3e+07 & 1.2e+07 & \ldots & 2.4e+11 & 2.1e+10  \\
-34.441478 & -5.203516 & 34.441496 & -5.203515 & 1.064\tablenotemark{G} & -0.86 & 0.94 & 7.9e+08 & 2.1e+08 & 9.9e+07 & 1.4e+07 & \ldots & 2.7e+11 & 8.5e+09  \\
-34.417250 & -5.220560 & 34.417268 & -5.220544 & 0.749\tablenotemark{G} & -0.08 & 0.04 & 5.2e+09 & 1.1e+08 & 1.1e+08 & 1.1e+07 & \ldots & 4.6e+10 & 1.0e+10  \\
-34.303624 & -5.187742 & 34.303640 & -5.187698 & 0.995\tablenotemark{G} & -1.24 & 0.13 & 4.8e+09 & 2.0e+08 & 1.5e+08 & 1.3e+07 & \ldots & 2.1e+11 & 3.0e+10  \\
+34.425930 & -5.174296 & 34.425949 & -5.174306 & 1.158\tablefootmark{G} & 0.38 & 0.34 & 2.0e+09 & 3.8e+08 & 6.3e+07 & 1.2e+07 & \ldots & 2.4e+11 & 2.1e+10  \\
+34.441478 & -5.203516 & 34.441496 & -5.203515 & 1.064\tablefootmark{G} & -0.86 & 0.94 & 7.9e+08 & 2.1e+08 & 9.9e+07 & 1.4e+07 & \ldots & 2.7e+11 & 8.5e+09  \\
+34.417250 & -5.220560 & 34.417268 & -5.220544 & 0.749\tablefootmark{G} & -0.08 & 0.04 & 5.2e+09 & 1.1e+08 & 1.1e+08 & 1.1e+07 & \ldots & 4.6e+10 & 1.0e+10  \\
+34.303624 & -5.187742 & 34.303640 & -5.187698 & 0.995\tablefootmark{G} & -1.24 & 0.13 & 4.8e+09 & 2.0e+08 & 1.5e+08 & 1.3e+07 & \ldots & 2.1e+11 & 3.0e+10  \\
 34.338168 & -5.206715 & 34.338190 & -5.206671 & 0.922                  & 2.68 & 0.20 & 1.4e+09 & 1.1e+08 & \ldots & \ldots & 8.2e+07 & 2.8e+11 & 7.2e+09  \\
-34.316711 & -5.166855 & 34.316746 & -5.166812 & 1.040\tablenotemark{G} & 2.41 & 2.45 & 1.5e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 2.0e+09  \\
-34.479187 & -5.233651 & 34.479221 & -5.233645 & 1.312\tablenotemark{G} & 0.77 & 0.31 & 1.7e+10 & 3.6e+09 & 1.3e+09 & 6.2e+07 & \ldots & 1.1e+12 & 1.0e+11  \\
-34.464574 & -5.205369 & 34.464597 & -5.205359 & 1.268\tablenotemark{G} & 0.20 & 0.38 & 2.3e+09 & 4.6e+08 & 5.2e+08 & 1.8e+07 & \ldots & 7.0e+11 & 2.0e+10  \\
+34.316711 & -5.166855 & 34.316746 & -5.166812 & 1.040\tablefootmark{G} & 2.41 & 2.45 & 1.5e+08 & 1.1e+08 & \ldots & \ldots & 4.7e+07 & 1.8e+11 & 2.0e+09  \\
+34.479187 & -5.233651 & 34.479221 & -5.233645 & 1.312\tablefootmark{G} & 0.77 & 0.31 & 1.7e+10 & 3.6e+09 & 1.3e+09 & 6.2e+07 & \ldots & 1.1e+12 & 1.0e+11  \\
+34.464574 & -5.205369 & 34.464597 & -5.205359 & 1.268\tablefootmark{G} & 0.20 & 0.38 & 2.3e+09 & 4.6e+08 & 5.2e+08 & 1.8e+07 & \ldots & 7.0e+11 & 2.0e+10  \\
 34.306728 & -5.161120 & 34.306745 & -5.161058 & 1.454                  & 0.26 & 0.43 & 9.5e+09 & 2.5e+09 & 1.5e+09 & 6.3e+07 & \ldots & 2.8e+12 & 1.6e+11  \\
-34.473469 & -5.202807 & 34.473484 & -5.202784 & 1.011\tablenotemark{G} & 0.84 & 0.23 & 1.9e+09 & 1.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.1e+11 & 7.0e+09  \\
-34.361009 & -5.189687 & 34.361031 & -5.189685 & 1.344\tablenotemark{G} & -1.00 & 0.37 & 8.1e+09 & 1.6e+09 & 2.2e+08 & 2.2e+07 & \ldots & 4.9e+11 & 5.5e+10  \\
-34.262690 & -5.198416 & 34.262708 & -5.198400 & 0.758\tablenotemark{G} & 4.66 & 0.80 & 6.3e+07 & 2.3e+07 & \ldots & \ldots & 5.6e+07 & 4.6e+11 & 6.0e+10  \\
-34.430803 & -5.206198 & 34.430856 & -5.206176 & 0.914\tablenotemark{G} & 0.64 & 0.13 & 2.5e+09 & 1.2e+08 & 1.2e+08 & 1.0e+07 & \ldots & 1.4e+11 & 9.8e+09  \\
-34.404478 & -5.239535 & 34.404464 & -5.239511 & 0.925\tablenotemark{G} & -1.25 & 0.03 & 1.7e+10 & 2.0e+08 & 1.8e+08 & 1.0e+07 & \ldots & 3.3e+10 & 8.5e+09  \\
+34.473469 & -5.202807 & 34.473484 & -5.202784 & 1.011\tablefootmark{G} & 0.84 & 0.23 & 1.9e+09 & 1.4e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.1e+11 & 7.0e+09  \\
+34.361009 & -5.189687 & 34.361031 & -5.189685 & 1.344\tablefootmark{G} & -1.00 & 0.37 & 8.1e+09 & 1.6e+09 & 2.2e+08 & 2.2e+07 & \ldots & 4.9e+11 & 5.5e+10  \\
+34.262690 & -5.198416 & 34.262708 & -5.198400 & 0.758\tablefootmark{G} & 4.66 & 0.80 & 6.3e+07 & 2.3e+07 & \ldots & \ldots & 5.6e+07 & 4.6e+11 & 6.0e+10  \\
+34.430803 & -5.206198 & 34.430856 & -5.206176 & 0.914\tablefootmark{G} & 0.64 & 0.13 & 2.5e+09 & 1.2e+08 & 1.2e+08 & 1.0e+07 & \ldots & 1.4e+11 & 9.8e+09  \\
+34.404478 & -5.239535 & 34.404464 & -5.239511 & 0.925\tablefootmark{G} & -1.25 & 0.03 & 1.7e+10 & 2.0e+08 & 1.8e+08 & 1.0e+07 & \ldots & 3.3e+10 & 8.5e+09  \\
 34.331573 & -5.180048 & 34.331575 & -5.180048 & 0.828                  & 2.80 & 0.21 & 7.2e+08 & 6.4e+07 & 2.2e+08 & 1.5e+07 & \ldots & 3.5e+11 & 6.3e+09  \\
-34.306272 & -5.150911 & 34.306301 & -5.150885 & 1.446\tablenotemark{G} & -0.07 & 0.38 & 4.0e+09 & 9.0e+08 & 5.2e+08 & 3.5e+07 & \ldots & 1.8e+12 & 1.4e+11  \\
+34.306272 & -5.150911 & 34.306301 & -5.150885 & 1.446\tablefootmark{G} & -0.07 & 0.38 & 4.0e+09 & 9.0e+08 & 5.2e+08 & 3.5e+07 & \ldots & 1.8e+12 & 1.4e+11  \\
 34.261751 & -5.204628 & 34.261780 & -5.204633 & 0.896                  & -0.48 & 0.04 & 1.2e+10 & 1.6e+08 & 2.6e+08 & 2.1e+07 & \ldots & 1.4e+11 & 1.6e+10  \\
-34.263048 & -5.136277 & 34.263053 & -5.136258 & 0.820\tablenotemark{G} & 2.84 & 0.38 & 2.7e+08 & 4.2e+07 & 1.3e+08 & 5.7e+06 & \ldots & 9.3e+10 & 7.3e+09  \\
+34.263048 & -5.136277 & 34.263053 & -5.136258 & 0.820\tablefootmark{G} & 2.84 & 0.38 & 2.7e+08 & 4.2e+07 & 1.3e+08 & 5.7e+06 & \ldots & 9.3e+10 & 7.3e+09  \\
 34.406678 & -5.198827 & 34.406674 & -5.198821 & 0.920                  & 1.91 & 0.14 & 1.8e+09 & 9.8e+07 & 2.3e+08 & 1.1e+07 & \ldots & 4.8e+11 & 1.2e+10  \\
-34.385521 & -5.205044 & 34.385550 & -5.205011 & 1.380\tablenotemark{G} & 2.02 & 0.57 & 1.1e+09 & 5.9e+08 & 5.7e+08 & 3.0e+07 & \ldots & 1.1e+12 & 9.2e+10  \\
-34.391148 & -5.240692 & 34.391130 & -5.240724 & 1.449\tablenotemark{G} & -0.82 & 0.54 & 8.7e+09 & 2.4e+09 & 2.4e+08 & 3.3e+07 & \ldots & 5.2e+11 & 3.3e+10  \\
-34.438796 & -5.165779 & 34.438816 & -5.165758 & 1.106\tablenotemark{G} & 1.36 & 0.10 & 2.7e+09 & 1.8e+08 & 3.0e+08 & 2.9e+07 & \ldots & 4.4e+11 & 1.7e+10  \\
+34.385521 & -5.205044 & 34.385550 & -5.205011 & 1.380\tablefootmark{G} & 2.02 & 0.57 & 1.1e+09 & 5.9e+08 & 5.7e+08 & 3.0e+07 & \ldots & 1.1e+12 & 9.2e+10  \\
+34.391148 & -5.240692 & 34.391130 & -5.240724 & 1.449\tablefootmark{G} & -0.82 & 0.54 & 8.7e+09 & 2.4e+09 & 2.4e+08 & 3.3e+07 & \ldots & 5.2e+11 & 3.3e+10  \\
+34.438796 & -5.165779 & 34.438816 & -5.165758 & 1.106\tablefootmark{G} & 1.36 & 0.10 & 2.7e+09 & 1.8e+08 & 3.0e+08 & 2.9e+07 & \ldots & 4.4e+11 & 1.7e+10  \\
 34.230979 & -5.176122 & 34.231025 & -5.176088 & 1.092                  & 0.34 & 0.37 & 1.2e+10 & 2.4e+09 & 1.0e+09 & 1.1e+08 & \ldots & 5.9e+11 & 3.0e+10  \\
 34.433604 & -5.153793 & 34.433623 & -5.153767 & 0.805                  & 0.74 & 0.08 & 3.0e+09 & 1.1e+08 & 1.3e+08 & 1.2e+07 & \ldots & 1.2e+11 & 8.8e+09  \\
-34.351795 & -5.210948 & 34.351808 & -5.210919 & 1.093\tablenotemark{G} & 0.92 & 0.00 & 2.1e+09 & 7.4e+06 & 2.5e+08 & 1.8e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
-34.367405 & -5.228523 & 34.367420 & -5.228497 & 1.189\tablenotemark{G} & 0.70 & 0.04 & 8.2e+09 & 1.8e+08 & 6.2e+08 & 2.7e+07 & \ldots & 6.7e+11 & 1.5e+10  \\
-34.583006 & -5.172723 & 34.582980 & -5.172715 & 1.280\tablenotemark{G} & -1.13 & 0.05 & 5.6e+09 & 1.0e+08 & 2.5e+08 & 1.6e+07 & \ldots & 3.0e+11 & 4.9e+10  \\
-34.338183 & -5.254102 & 34.338179 & -5.254077 & 1.039\tablenotemark{G} & 0.28 & 0.72 & 6.9e+08 & 1.5e+08 & 1.1e+08 & 1.3e+07 & \ldots & 3.0e+11 & 1.4e+10  \\
-34.335313 & -5.258985 & 34.335319 & -5.258979 & 0.879\tablenotemark{G} & -0.51 & 0.05 & 9.9e+09 & 1.9e+08 & \ldots & \ldots & 1.6e+08 & 1.2e+11 & 8.2e+09  \\
+34.351795 & -5.210948 & 34.351808 & -5.210919 & 1.093\tablefootmark{G} & 0.92 & 0.00 & 2.1e+09 & 7.4e+06 & 2.5e+08 & 1.8e+07 & \ldots & 2.4e+11 & 1.3e+10  \\
+34.367405 & -5.228523 & 34.367420 & -5.228497 & 1.189\tablefootmark{G} & 0.70 & 0.04 & 8.2e+09 & 1.8e+08 & 6.2e+08 & 2.7e+07 & \ldots & 6.7e+11 & 1.5e+10  \\
+34.583006 & -5.172723 & 34.582980 & -5.172715 & 1.280\tablefootmark{G} & -1.13 & 0.05 & 5.6e+09 & 1.0e+08 & 2.5e+08 & 1.6e+07 & \ldots & 3.0e+11 & 4.9e+10  \\
+34.338183 & -5.254102 & 34.338179 & -5.254077 & 1.039\tablefootmark{G} & 0.28 & 0.72 & 6.9e+08 & 1.5e+08 & 1.1e+08 & 1.3e+07 & \ldots & 3.0e+11 & 1.4e+10  \\
+34.335313 & -5.258985 & 34.335319 & -5.258979 & 0.879\tablefootmark{G} & -0.51 & 0.05 & 9.9e+09 & 1.9e+08 & \ldots & \ldots & 1.6e+08 & 1.2e+11 & 8.2e+09  \\
 34.265199 & -5.258207 & 34.265234 & -5.258198 & 0.807                  & 0.70 & 0.06 & 3.5e+09 & 9.4e+07 & 1.1e+08 & 1.6e+07 & \ldots & 3.6e+11 & 3.8e+10  \\
-34.266225 & -5.258304 & 34.266217 & -5.258304 & 0.806\tablenotemark{G} & 0.45 & 0.04 & 7.6e+09 & 1.3e+08 & 1.8e+08 & 2.2e+07 & \ldots & 2.6e+11 & 1.1e+10  \\
-34.282549 & -5.227706 & 34.282574 & -5.227709 & 1.047\tablenotemark{G} & 0.06 & 0.36 & 1.9e+09 & 2.1e+08 & 2.5e+08 & 3.6e+07 & \ldots & 4.1e+11 & 4.5e+10  \\
+34.266225 & -5.258304 & 34.266217 & -5.258304 & 0.806\tablefootmark{G} & 0.45 & 0.04 & 7.6e+09 & 1.3e+08 & 1.8e+08 & 2.2e+07 & \ldots & 2.6e+11 & 1.1e+10  \\
+34.282549 & -5.227706 & 34.282574 & -5.227709 & 1.047\tablefootmark{G} & 0.06 & 0.36 & 1.9e+09 & 2.1e+08 & 2.5e+08 & 3.6e+07 & \ldots & 4.1e+11 & 4.5e+10  \\
 34.417088 & -5.183261 & 34.417113 & -5.183254 & 0.920                  & 0.86 & 0.10 & 4.2e+09 & 1.5e+08 & 1.8e+08 & 1.8e+07 & \ldots & 1.8e+11 & 6.3e+09  \\
 34.287594 & -5.200242 & 34.287609 & -5.200223 & 0.787                  & 1.66 & 0.15 & 1.2e+09 & 7.8e+07 & 1.0e+08 & 1.6e+07 & \ldots & 1.9e+11 & 9.9e+09  \\
-34.438839 & -5.263612 & 34.438843 & -5.263605 & 0.784\tablenotemark{G} & 3.07 & 0.17 & 5.9e+08 & 4.5e+07 & 1.3e+08 & 8.7e+06 & \ldots & 2.5e+11 & 1.5e+10  \\
-34.412508 & -5.175668 & 34.412537 & -5.175642 & 1.291\tablenotemark{G} & 2.55 & 1.28 & 3.3e+08 & 4.5e+08 & 3.4e+08 & 2.4e+07 & \ldots & 5.9e+11 & 3.2e+10  \\
-34.341631 & -5.235338 & 34.341650 & -5.235318 & 1.100\tablenotemark{G} & 0.73 & 0.49 & 2.3e+09 & 6.9e+08 & 2.9e+08 & 1.0e+07 & \ldots & 2.8e+11 & 1.7e+10  \\
-34.288088 & -5.245493 & 34.288165 & -5.245476 & 1.474\tablenotemark{G} & -1.50 & 0.05 & 1.9e+10 & 1.1e+09 & 2.3e+08 & 3.2e+07 & \ldots & 4.9e+11 & 2.8e+10  \\
+34.438839 & -5.263612 & 34.438843 & -5.263605 & 0.784\tablefootmark{G} & 3.07 & 0.17 & 5.9e+08 & 4.5e+07 & 1.3e+08 & 8.7e+06 & \ldots & 2.5e+11 & 1.5e+10  \\
+34.412508 & -5.175668 & 34.412537 & -5.175642 & 1.291\tablefootmark{G} & 2.55 & 1.28 & 3.3e+08 & 4.5e+08 & 3.4e+08 & 2.4e+07 & \ldots & 5.9e+11 & 3.2e+10  \\
+34.341631 & -5.235338 & 34.341650 & -5.235318 & 1.100\tablefootmark{G} & 0.73 & 0.49 & 2.3e+09 & 6.9e+08 & 2.9e+08 & 1.0e+07 & \ldots & 2.8e+11 & 1.7e+10  \\
+34.288088 & -5.245493 & 34.288165 & -5.245476 & 1.474\tablefootmark{G} & -1.50 & 0.05 & 1.9e+10 & 1.1e+09 & 2.3e+08 & 3.2e+07 & \ldots & 4.9e+11 & 2.8e+10  \\
 34.315106 & -5.218825 & 34.315157 & -5.218789 & 1.030                  & 3.32 & 1.20 & 3.0e+08 & 1.1e+08 & 1.4e+08 & 1.2e+07 & \ldots & 2.3e+11 & 1.1e+10  \\
-34.334173 & -5.190787 & 34.334186 & -5.190781 & 0.916\tablenotemark{G} & 2.98 & 1.07 & 2.0e+08 & 7.9e+07 & 9.7e+07 & 1.5e+07 & \ldots & 4.9e+11 & 4.0e+09  \\
+34.334173 & -5.190787 & 34.334186 & -5.190781 & 0.916\tablefootmark{G} & 2.98 & 1.07 & 2.0e+08 & 7.9e+07 & 9.7e+07 & 1.5e+07 & \ldots & 4.9e+11 & 4.0e+09  \\
 34.258180 & -5.172100 & 34.258232 & -5.172124 & 1.094                  & -0.59 & 0.05 & 9.6e+09 & 2.0e+08 & 2.5e+08 & 1.4e+07 & \ldots & 1.2e+11 & 2.1e+10  \\
-34.259985 & -5.172752 & 34.260001 & -5.172724 & 1.410\tablenotemark{G} & 0.64 & 0.99 & 9.7e+08 & 7.4e+08 & \ldots & \ldots & 1.3e+08 & 4.7e+11 & 6.2e+10  \\
+34.259985 & -5.172752 & 34.260001 & -5.172724 & 1.410\tablefootmark{G} & 0.64 & 0.99 & 9.7e+08 & 7.4e+08 & \ldots & \ldots & 1.3e+08 & 4.7e+11 & 6.2e+10  \\
 34.405981 & -5.249941 & 34.405971 & -5.249905 & 1.067                  & -1.00 & 0.04 & 1.5e+10 & 1.9e+08 & 3.8e+08 & 1.7e+07 & \ldots & 1.8e+11 & 1.3e+10  \\
-34.317767 & -5.189676 & 34.317778 & -5.189662 & 0.915\tablenotemark{G} & 0.31 & 0.13 & 2.9e+09 & 1.3e+08 & 2.2e+08 & 1.2e+07 & \ldots & 2.4e+11 & 7.2e+09  \\
+34.317767 & -5.189676 & 34.317778 & -5.189662 & 0.915\tablefootmark{G} & 0.31 & 0.13 & 2.9e+09 & 1.3e+08 & 2.2e+08 & 1.2e+07 & \ldots & 2.4e+11 & 7.2e+09  \\
 34.238729 & -5.168098 & 34.238794 & -5.168072 & 0.821                  & 4.43 & 0.47 & 2.0e+08 & 4.0e+07 & \ldots & \ldots & 1.0e+08 & 1.9e+11 & 7.7e+09  \\
-34.370957 & -5.263670 & 34.370973 & -5.263634 & 0.910\tablenotemark{G} & 0.37 & 0.05 & 8.1e+09 & 1.6e+08 & 3.1e+08 & 4.5e+07 & \ldots & 2.2e+11 & 2.5e+09
-\enddata
-\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
-\tablecomments{Columns: RA and Dec, IR, are positions in the
+34.370957 & -5.263670 & 34.370973 & -5.263634 & 0.910\tablefootmark{G} & 0.37 & 0.05 & 8.1e+09 & 1.6e+08 & 3.1e+08 & 4.5e+07 & \ldots & 2.2e+11 & 2.5e+09 \\
+\hline
+\end{longtable}
+\tablefoot{Columns: RA and Dec, IR, are positions in the
 \emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
@@
 line luminosity.}
-\end{deluxetable}
-\clearpage
+\tablefoottext{G}{Spectroscopic redshift solely from grism observations.}
 \end{landscape}
-
-\begin{landscape}
-\begin{deluxetable}{lllllllllllll}
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the samples at $z < 0.2$
+}
+
+\begin{sidewaystable*}
+%\tablecolumns{13}
+%\tablewidth{0pc}
+\caption{Measured and derived quantities for the samples at $z < 0.2$
 \label{tbl:lowz}}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA} &
-\colhead{Dec} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\beta}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{Dust-poor galaxies}
+\tiny
+\begin{tabular}{lllllllllllll}
+\hline \hline
+RA &
+Dec &
+$z$ &
+$\beta$ &
+$\sigma_{\beta}$ &
+$0.16 \times L_{0.16}$ &
+$\sigma_{L_{0.16}}$ &
+$L_{\mathrm{H}\beta}$ &
+$\sigma_{L_{\mathrm{H}\beta}}$ &
+$L_{\mathrm{H}\alpha}$ &
+$\sigma_{L_{\mathrm{H}\alpha}}$ &
+$L_{\mathrm{IR}}$ &
+$\sigma_{L_{\mathrm{IR}}}$ \\
+%UV SFR} &
+%H$\alpha$ SFR} &
+%H$\alpha$ SFR lim.} &
+%IR SFR} \\
+deg &
+deg &
+ &
+ &
+ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ \\
+%M$_{\odot}$ yr$^{-1}$} &
+%M$_{\odot}$ yr$^{-1}$} &
+%M$_{\odot}$ yr$^{-1}$} &
+%M$_{\odot}$ yr$^{-1}$}
+\hline
+\multicolumn{13}{c}{Dust-poor galaxies} \\
+\hline
 30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
@@
 59.391667 & -5.622139 & 0.204 & -1.28 & 0.06 & 2.9e+10 & 3.5e+08 & 9.4e+07  & \ldots & 3.5e+08 & \ldots & 1.1e+11 & 1.9e+09 \\
-125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09
-\enddata
-\tablecomments{The entire table is published in the electronic edition of
-\apj.  A portion is shown here for guidance regarding its form and content.}
-\end{deluxetable}
-\clearpage
-\end{landscape}
-
+125.007167 & 50.844211 & 0.217 & -1.55 & 0.08 & 2.6e+10 & 4.0e+08 & 2.4e+08 & \ldots & 8.1e+08 & \ldots & 4.8e+11 & 4.9e+09 \\
+\hline
+\end{tabular}
+\tablefoot{The entire table is published in the electronic edition of
+\aap.  A portion is shown here for guidance regarding its form and content.}
+\end{sidewaystable*}
+
+\longtab{
 \begin{landscape}
-\begin{deluxetable}{lllllllllllll}
-\tablecolumns{13}
-\tablewidth{0pc}
-\tablecaption{Measured and derived quantities for the samples at $z < 0.2$}
-\tabletypesize{\tiny}
-\tablehead{
-\colhead{RA} &
-\colhead{Dec} &
-\colhead{$z$} &
-\colhead{$\beta$} &
-\colhead{$\sigma_{\beta}$} &
-\colhead{$0.16 \times L_{0.16}$} &
-\colhead{$\sigma_{L_{0.16}}$} &
-\colhead{$L_{\mathrm{H}\beta}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\beta}}$} &
-\colhead{$L_{\mathrm{H}\alpha}$} &
-\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
-\colhead{$L_{\mathrm{IR}}$} &
-\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
-%\colhead{UV SFR} &
-%\colhead{H$\alpha$ SFR} &
-%\colhead{H$\alpha$ SFR lim.} &
-%\colhead{IR SFR} \\
-\colhead{deg} &
-\colhead{deg} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$} &
-\colhead{$L_{\odot}$}
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$} &
-%\colhead{M$_{\odot}$ yr$^{-1}$}
-}
-\startdata
-\cutinhead{Dust-poor galaxies}
+%\tablecolumns{13}
+%\tablewidth{0pc}
+\tiny
+\begin{longtable}{lllllllllllll}
+\caption{Measured and derived quantities for the samples at $z < 0.2$} \\
+\hline \hline
+RA &
+Dec &
+$z$ &
+$\beta$ &
+$\sigma_{\beta}$ &
+$0.16 \times L_{0.16}$ &
+$\sigma_{L_{0.16}}$ &
+$L_{\mathrm{H}\beta}$ &
+$\sigma_{L_{\mathrm{H}\beta}}$ &
+$L_{\mathrm{H}\alpha}$ &
+$\sigma_{L_{\mathrm{H}\alpha}}$ &
+$L_{\mathrm{IR}}$ &
+$\sigma_{L_{\mathrm{IR}}}$ \\
+%UV SFR} &
+%H$\alpha$ SFR} &
+%H$\alpha$ SFR lim.} &
+%IR SFR} \\
+deg &
+deg &
+ &
+ &
+ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ &
+$L_{\odot}$ \\
+%M$_{\odot}$ yr$^{-1}$} &
+%M$_{\odot}$ yr$^{-1}$} &
+%M$_{\odot}$ yr$^{-1}$} &
+%M$_{\odot}$ yr$^{-1}$}
+\hline
+\multicolumn{13}{c}{Dust-poor galaxies} \\
+\hline
 30.987125 & -8.132919 & 0.189 & -1.66 & 0.04 & 3.5e+10 & 2.9e+08 & 1.4e+08  & \ldots & 4.6e+08 & \ldots & 8.5e+10 & 1.8e+09 \\
@@
 358.448708 & 0.900578 & 0.223 & -1.66 & 0.10 & 2.2e+10 & 4.2e+08 & 1.0e+08  & \ldots & 3.2e+08 & \ldots & 8.5e+10 & 5.9e+09 \\
-\cutinhead{Dusty galaxies}
+\hline
+\multicolumn{13}{c}{Dusty galaxies} \\
+\hline
 154.474577 & 15.934370 & 0.079 & 0.28 & 0.72 & 1.3e+09 & 2.5e+08 & 4.9e+07 & 8.4e+05 & 3.9e+08 & 3.0e+06 & 3.4e+11 & 2.7e+09 \\
@@
 339.895154 & -9.516226 & 0.074 & -0.54 & 0.30 & 4.3e+09 & 3.5e+08 & 4.7e+07 & 8.7e+05 & 2.7e+08 & 2.2e+06 & 2.3e+11 & 4.2e+09 \\
-359.226274 & -10.268143 & 0.074 & -0.58 & 0.03 & 1.5e+10 & 1.1e+08 & 1.6e+08 & 1.2e+06 & 6.4e+08 & 3.0e+06 & 4.2e+11 & 7.2e+10
-\enddata
-\end{deluxetable}
-\clearpage
+359.226274 & -10.268143 & 0.074 & -0.58 & 0.03 & 1.5e+10 & 1.1e+08 & 1.6e+08 & 1.2e+06 & 6.4e+08 & 3.0e+06 & 4.2e+11 & 7.2e+10 \\
+\hline
+\end{longtable}
 \end{landscape}
+}
 
@@
 \item \alephuv~is the escape fraction of the continuum
-at rest-frame 0.16$\,\micron$.  In
+at rest-frame 0.16$\,\mu$m.  In
 relation to A$_{\mathrm{UV}}$,
-f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
+f$_{\mathrm{esc}}$(0.16$\,\mu$m) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
 \item \alephha~is the escape fraction of the H$\alpha$ emission line luminosity.
@@
 wavelength of H$\alpha$---the attenuation formula prediction for the escape
-fraction at rest-frame 0.66$\,\micron$.  For the
+fraction at rest-frame 0.66$\,\mu$m.  For the
 attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
@@
 UV-emitting stars.  In this framework \alephuvha~is the escape fraction
-of the 0.66$\,\micron$ continuum emission from low-to-high mass stars and
-\alephha~is the escape fraction of the 0.66$\,\micron$ line emission from gas
+of the 0.66$\,\mu$m continuum emission from low-to-high mass stars and
+\alephha~is the escape fraction of the 0.66$\,\mu$m line emission from gas
 ionized by high mass stars.  These galaxies have \alephha~= \alephuv$^{0.69}$,
@@
 
-The UV and 0.66$\,\micron$ escape fractions in \citet{calzetti94} come from
+The UV and 0.66$\,\mu$m escape fractions in \citet{calzetti94} come from
 comparing spectra of
@@
 
-Our hypothesis is that the H$\alpha$ and 0.66$\,\micron$ escape fractions
+Our hypothesis is that the H$\alpha$ and 0.66$\,\mu$m escape fractions
 agree---that dusty galaxies have uniform dust distributions.
@@
 
-\begin{deluxetable}{lllll}
-\tablecolumns{5}
-\tablewidth{0pc}
-\tablecaption{Summary of regressions\label{regress}}
-\tablehead{
-\colhead{Sample} &
-\colhead{$q$} &
-\colhead{Std. error of $q$} &
-\colhead{Residual std. error} &
-\colhead{DOF}
-}
-\startdata
+\begin{table*}
+\caption{Summary of regressions\label{regress}}
+\begin{tabular}{lllll}
+\hline \hline
+Sample &
+$q$ &
+Std. error of $q$ &
+Residual std. error &
+DOF \\
+\hline
 Low-z dust-poor & 0.766 & 0.091 & 6.1 & 13 \\
 Low-z dusty     & 0.532 & 0.027 & 65.0 & 54 \\
-High-z dusty    & 0.537 & 0.008 & 6.5 & 320
-\enddata
-\end{deluxetable}
+High-z dusty    & 0.537 & 0.008 & 6.5 & 320 \\
+\hline
+\end{tabular}
+\end{table*}
 
@@
 formula; and (2) were to all have the same UV spectrum in the absence of dust;
-our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
+our results indicate that their H$\alpha$ and 0.66$\,\mu$m escape
 fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
@@
 formula, which complicates our interpretation of the more basic relation
-between UV and 0.66$\,\micron$ escape fractions---the relation between
+between UV and 0.66$\,\mu$m escape fractions---the relation between
 escape fractions for just the regions with nonionizing UV-emitting stars
 \citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
-formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
+formula for dusty galaxies may have a higher 0.66$\,\mu$m escape fraction
 for a given UV escape fraction than does the \citet{calzetti00} formula.  A
 formula modified according to
-\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
+\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\mu$m has
 \alephuvha~=
@@
 If the true formula instead has a
-much lower 0.66$\,\micron$ escape fraction for a given UV escape
+much lower 0.66$\,\mu$m escape fraction for a given UV escape
 fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
 \alephuv$^{0.54}$---we conclude that for dusty
-galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
+galaxies the H$\alpha$ and 0.66$\,\mu$m escape fractions agree.  Our
 conclusion regarding the uniformity of dust distributions depends on the
@@
 \item We define the UV escape fraction as a function of UV- and IR-derived SFRs.
-\citet{madau14} use the models of \citet{conroy10} to calculate
+\citet{madau14} use the models of \citet{conroy10} and a uniform foreground
+screen of dust to calculate
 conversion factors between luminosities and SFRs.  The
@@
 of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
-[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We set aside the
+[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\mu$m$)]$.  We set aside the
 circularity that results from using both these functions by fixing the UV
@@
 distributions.  Either way, this test provides no information on the relation
-between UV and 0.66$\,\micron$ escape fractions; more extrapolations are
+between UV and 0.66$\,\mu$m escape fractions; more extrapolations are
 necessary to definitively interpret Fig. \ref{fha_fuv}.
@@
 \emph{HST}/WFC3-IR grism spectra, for $z \sim 1$ galaxies with detected
-100$\,\micron$ emission.  We determine rest-frame UV continuum power-law
+100$\,\mu$m emission.  We determine rest-frame UV continuum power-law
 indices ($\beta$ values) and ratios of IR to UV luminosities (IRX values).
 \item For each galaxy we determine \alephuv, the escape fraction at
-0.16$\,\micron$, from IRX.  We determine \alephha, the H$\alpha$ escape
+0.16$\,\mu$m, from IRX.  We determine \alephha, the H$\alpha$ escape
 fraction, from the H$\alpha$ luminosity and the total star formation rate.
@@
 
-\begin{thebibliography}
+\begin{thebibliography}{}
 
